### 2017-01-19 magret_draft_6.0/draft.tex
initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jpccck,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\author{Niket Thakkar}
\affiliation[Department of Applied Mathematics, University of Washington]
{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
\author{David J. Masiello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\alsoaffiliation[Department of Applied Mathematics, University of Washington]
{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Understanding Retardation Effects on the Energy Ordering of Magnetic Plasmons}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{plasmon, hybridization, magnetic, retardation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Magnetic plasmons, the collective response of cyclic arrangements of electric plasmon-supporting metal nanoparticles, have been of recent theoretical and experimental interest. As magnetic-plasmon-supporting aggregates are often large (hundreds of nanometers to microns in size), information takes time to propagate across such nanostructures. As a result, they are not well-described in the quasistatic limit with plasmon hybridization theory. In this Letter it is shown that for small magnetic oligomers the quasistatic approximation is sufficient, but, as the systems grow in size, retardation effects must be considered. The quasistatic tight-binding model can be manipulated to include retardation effects by utilizing the full electric field of a dipole. This fully retarded tight-binding model accurately predicts the energy-ordering of magnetic plasmon modes in agreement with full-wave simulations.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
When an electric field is incident upon a metal surface, the metal imperfectly screens the electric field, allowing penetration up to a distance known as the skin depth. When the spatial extent of a metal nanoparticle (MNP) is on the order of the skin depth, the external electric field penetrates the entire particle and forces the conduction electrons to collect at the surface.\cite{KREIBIG1985}. Releasing the force causes the electrons to oscillate collectively and coherently about their equilibrium configuration until the energy dissipates. The conduction electrons oscillate at a characteristic frequency that depends on the material and morphology of the MNP. When resonantly driven by an oscillating electric field, a localized surface plasmon resonance (LSPR), or simply a plasmon, is excited, with the lowest energy excitation being dipolar in character.

Bringing two MNPs together causes their individual plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Plasmon hybridization theory is applied to aggregates of MNPs and explains their collective behavior within the quasistatic limit in which the speed of light is taken to be infinite\cite{NordHal2003,NordProdan2004,Oubre2004,Gomez2009}. Recently, retardation effects on plasmon hybridization have been the focus of study for large particles\cite{Abajo2008,Gu2010} as well as dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and 2-D arrays\cite{Schatz2003,Royer2005,Chumanov2010} of nanoparticles. Specific arrangements of nanoparticles in 2-D arrays, such as three or more nanoparticles arranged on the vertices of a regular polygon, support a collective mode in which all of the dipole plasmons are oriented head-to-tail, as demonstrated in Figure~\ref{fig1}. This generates a fictitious, oscillating current loop resulting in an oscillating magnetic dipole moment in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. These so-called magnetic plasmons are the lowest-energy collective modes of the oligomers and couple to and enhance the magnetic field of incident light\cite{Shalaev2007,Qian2015,Nord2007}, offering a route to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}. The rich plasmonic modes of magnetic-plasmon-supporting systems are well-described using plasmon hybridization theory, but when in the quasistatic limit, the energy-ordering of the modes is not.

Plasmon hybridization theory treats LSPRs as point dipoles centered on their associated nanoparticles that interact through dipole-dipole coupling. In the quasistatic limit, these dipoles couple only through time-independent, electric near-field interactions\cite{jackson_classical_1999}:

\begin{equation}
  U_{\textrm{qs}} = -\textbf{p}_2 \cdot \textbf{E}_{\textrm{qs},1} = -\left[\frac{3(\textbf{p}_2 \cdot \hat{\textbf{r}}) (\hat{\textbf{r}} \cdot \textbf{p}_1) - \textbf{p}_2 \cdot \textbf{p}_1}{r^3}\right] = -\textbf{p}_2 \cdot \boldsymbol{\Lambda}_{\textrm{qs}} \cdot \textbf{p}_1, \label{eqn1}
  \end{equation}

where, $\textbf{p}_i$ is the dipole moment of each plasmon, $\textbf{E}_{\textrm{qs}}$ is the near-electric field in the quasistatic limit, and $r$ is the distance between dipoles with associated unit vector $\hat{\textbf{r}}$.

When the distance between nanoparticles becomes large, this approximation breaks down and intermediate- and far-field effects must be considered, as well as the time-delay effects in the near-field\cite{jackson_classical_1999}:

\begin{equation}
  U_{\textrm{NF}} = U_{\textrm{qs}}\, \cos\left(\frac{\omega r}{c}\right)=-\textbf{p}_2 \cdot \boldsymbol{\Lambda}_{\textrm{NF}} \cdot \textbf{p}_1 ;\label{near}
  \end{equation}

\begin{equation}
  U_{\textrm{IF}} = -\textbf{p}_2 \cdot \textbf{E}_{\textrm{IF},1} = \frac{\omega}{c}\left[\frac{3(\textbf{p}_2 \cdot \hat{\textbf{r}})( \hat{\textbf{r}} \cdot \textbf{p}_1) - \textbf{p}_2 \cdot \textbf{p}_1}{r^2}\right]\,\sin\left(\frac{\omega r}{c}\right)=-\textbf{p}_2 \cdot \boldsymbol{\Lambda}_{\textrm{IF}} \cdot \textbf{p}_1 ; \label{eqn2}
\end{equation}

\begin{equation}
  U_{\textrm{FF}} = -\textbf{p}_2 \cdot \textbf{E}_{\textrm{FF},1} = \frac{\omega^2}{c^2}\left[\frac{\textbf{p}_2 \cdot \textbf{p}_1 -(\textbf{p}_2 \cdot \hat{\textbf{r}}) (\hat{\textbf{r}} \cdot \textbf{p}_1)}{r}\right]\,\cos\left(\frac{\omega r}{c}\right)=-\textbf{p}_2 \cdot \boldsymbol{\Lambda}_{\textrm{FF}} \cdot \textbf{p}_1; \label{eqn3}
\end{equation}

where $\omega$ refers to the resonance frequency of a particular plasmonic mode. The aim of this Letter is to incorporate the fully retarded electric field into plasmon hybridization theory and extend studies of retardation effects to magnetic plasmon oligomers. Specifically, systems of metal nanoparticles arranged in shapes analogous to benzene and naphthalene are explored\cite{Cherqui2014}. The benzene-like ring, comprising six nanoparticles as diagrammed in Figure~\ref{fig1}D, is denoted the magnetic monomer and forms the basic magnetic unit cell. The naphthalene-like ring comprises ten nanoparticles and is constructed with two monomers sharing two central nanoparticles; consequently, it is denoted the magnetic dimer and it is diagrammed in Figure~\ref{fig1}. Through theory and simulation, it will be shown that the magnetic eigenmodes of large dimer systems can be obtained through quasistatic plasmon hybridization theory, but that their energy-ordering requires consideration of retardation effects.

%\begin{wrapfigure}
\begin{figure}
  \begin{center}
  \includegraphics[trim = 0.5in 0 0.3in 0,clip=true,scale=0.4]{all_the_diagrams.png}
  \caption{Four examples of magnetic oligomer rings and their lowest-energy collective mode exhibiting a magnetic dipole moment. Note that each dipole is oriented ``tip-to-tail.'' This is similar to the lowest-energy mode of aromatic rings as diagrammed in various Frost diagrams in which the carbon ring has no nodes in its electron density. Panel E diagrams the magnetic oligomer dimer system, constructed from two of the magnetic oligomers in panel D. $r_0$ is the radius of each sphere and $r=2.2r_0$ is the center-to-center separation distance between spheres. To study this system with EELS, placing the electron beam at the purple dot (A) selectively excites the north-south mode and placing the beam at the blue dot (B) selectively excites the north-north mode.}
  \label{fig1}
  \end{center}
\end{figure}
%\end{wrapfigure}

For the magnetic dimer, only the two planar dipoles per particle are considered in the tight binding model, yielding a total of twenty. The dipoles are mapped onto a set of harmonic oscillators and are described by the following Hamiltonian:

\begin{equation}
  H = \sum_{i=1}^{n}\left[\frac{1}{2m_{sp,i}}\textbf{P}_{i}^{2}+\frac{1}{2}m_{sp,i}\omega_{sp,i}^{2}\textbf{Q}_{i}^{2}\right]-e^2\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{\textrm{full},ij}\cdot\textbf{Q}_{j} \label{eqn4}
\end{equation}

where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{Q}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{\textrm{full},ij}=\boldsymbol{\Lambda}_{\textrm{NF},ij}+\boldsymbol{\Lambda}_{\textrm{IF},ij}+\boldsymbol{\Lambda}_{\textrm{FF},ij}$. In order to reduce this to the quasistatic limit, $\boldsymbol{\Lambda}_{\textrm{full},ij}$ is replaced with $\boldsymbol{\Lambda}_{\textrm{qs},ij}$ as in Equation~\ref{eqn1}. Diagonalizing this Hamiltonian yields a set of eigenvalues and eigenmodes which correspond to the plasmonic modes of the system.

In the theoretical studies of Cherqui \textit{et al.}\cite{Cherqui2014}, it was found using the quasistatic tight-binding model described above that the magnetic dimer system supports twenty planar modes, with the two lowest-energy modes, denoted north-south (NS) and north-north (NN), exhibiting magnetic character. The NS mode supports two out-of-phase effective current loops (Figure~\ref{fig3}A) and, consequently, out-of-phase magnetic moments in each ring. The NN mode supports a single, in-phase, effective current loop about the entire system (Figure~\ref{fig3}B), generating two in-phase magnetic dipole moments within the rings.

However, at odds with the tight-binding model results, previous full-wave electrodynamics simulations conclude the opposite: the NN mode lies at lower energy than the NS mode. This discrepancy is the result of retardation effects, as the original tight-binding model uses the quasistatic approximation, while the simulations use the fully retarded electric field. Because retardation effects contribute more with growing size, small systems behave predictably within the quasistatic approximation and the NS mode is the lowest in energy. At larger sizes, when retardation effects contribute, the NN mode is the lowest in energy. In the quasistatic limit, the tight-binding model accurately predicts the eigenmodes of the dimer, but is unable to account for the variation in each mode's eigenvalue as a function of size.

The electric field in the quasistatic approximation is proportional to $\frac{1}{r^3}$, dictating that nearest-neighbor interactions dominate the dipole-dipole coupling. In both the NN and NS mode, all of the nearest-neighbor interactions are ``bonding,'' or energetically preferred. These two modes differ at the central two particles where the NS mode exhibits head-to-tail, collinear dipoles (Figure~\ref{fig3}A, green box), while in the NN mode supports anti-parallel dipoles (Figure~\ref{fig3}B, red box). The $3(\textbf{p}_2 \cdot \hat{\textbf{r}}) (\hat{\textbf{r}} \cdot \textbf{p}_1)$ term in the coupling dictates that collinear dipoles are more energetically preferable than anti-parallel dipoles. As a result, the NS mode is energetically preferred, followed by the NN mode. When the fully retarded field is taken into account, all inter-particle interactions contribute to the energy-ordering.

\begin{figure}
  \begin{center}
  \includegraphics[trim = 0.5in 0.5in 0.5in 0.5in,clip=true,scale=0.4]{nn-ns-boxes_3.png}
  \caption{The NS (A) and NN (B) modes of the magnetic dimer system, including dipole arrangements in each mode. The green (NS) and red (NN) boxes highlight the interactions between the center two nanoparticles. In the NS mode, the dipoles are in a collinear arrangement, which is energetically favorable over the anti-parallel arrangement of the NN mode. The purple (NS) and blue (NN) boxes show some of the long-distance interactions. The purple box contains an anti-collinear arrangement of dipoles, which is more energetically unfavorable than the collinear arrangement contained within the blue box. Overall the long-distance interactions in the NN mode appear to be more favorable than the long-distance interactions in the NS mode. The red glow indicates a ``north'' magnetic moment, and the blue glow indicates a ``south'' magnetic moment.}
  \label{fig3}
  \end{center}
\end{figure}

The fully retarded electric field is composed of three parts: the near-field term (Equation 2), the intermediate-field term (Equation 3), and the far-field term (Equation 4). The intermediate-field term contributes the same energy ordering as the near-field term: collinear dipoles are favored more than anti-parallel dipoles. The far-field term, however, is energetically unfavorable for anti-parallel interactions and energetically preferable for parallel interactions. These three terms account for all of the retardation effects\cite{Purcell1973}.

\begin{figure}
  \includegraphics[scale=0.5]{dimer_interaction_3.png}
  \caption{Breakdown of the distance dependence of the fully retarded electric field for various dipole arrangements. A) At short range, collinear dipoles are energetically favorable in the near- and intermediate-field terms. There is long-distance regime in which collinear dipoles are unfavorable at around 150 nm. The far-field does not contribute. B) Anti-parallel dipoles are preferred in the near- and intermediate-field but are not in the far-field at short ditances. At longer distances (80-120 nm), the far-field term causes anti-parallel dipoles to become energetically favorable. C) The anti-collinear dipoles exhibit the opposite behavior of the collinear dipoles, becoming enegetically favorable at longer distances. D) The parallel dipoles exhibit the opposite behavior of the unfavorable at long distances. For large systems, the expected energy-ordering of ``bonding'' and ``anti-bonding'' hybridized modes in the quasistatic limit is not replicated by the fully retarded interaction. }
  \label{fig4}
\end{figure}

To understand the contributions to dipole-dipole coupling of each part of the fully retarded electric field, the interaction strengths for each term were computed for four planar hybridized modes of a silver nanosphere dimer. The results of these computations are displayed in Figure~\ref{fig4} and show how the interaction terms behave in various size regimes. The most obvious trait to note is that the far-field term is zero for both collinear and anti-collinear arrangements of dipoles. Second, the collinear and anti-collinear interactions are exact opposites of each other, with the same being true for the parallel and anti-parallel arrangements, as these represent equal and opposite interactions. Third the interaction strengths have slow oscillatory behavior over long length scales. Fourth, and perhaps most importantly, there are distinct distance regimes in which each term is more energetically favorable than the others. This final observation lends credence to the idea that the long-distance interactions in the NN mode are more favorable than those in the NS mode.

Incorporating the fully retarded electric field, the inter-particle coupling is no longer approximately a nearest-neighbor interaction, but rather a short- and long-distance coupling that accounts for the interactions among all particles. As the system grows larger, intermediate- and far-field interactions become stronger in proportion to the dominant near-field interactions. In the purple box of Figure~\ref{fig3}A, the dipoles are in an anti-collinear, anti-bonding arrangement: an energetically unfavorable interaction in both the near- and intermediate-field terms. Conversely, the dipole arrangement in the blue box of Figure~\ref{fig3}B is a collinear, bonding interaction, which is energetically preferred. Additionally, observing all of the complementary dipoles around the two ring system for both modes, it can be seen that the long-distance interactions in the NN mode are energetically favorable, and the long-distance interactions in the NS mode are energetically unfavorable. In the quasistatic limit, these interactions are weak, but when the intermediate- and far-field contributions are included, these interactions contribute to the total energy of each mode and the NN mode becomes energetically preferred over the NS mode at large enough sizes.

Returning to the tight-binding model, retardation effects are included by using the full interaction term in the Hamiltonian. The interaction terms depend on $\omega$, the frequency at which the collective mode resonates. This means that the Hamiltonian must now be diagonalized iteratively, beginning by using the LSPR frequency $\omega_{sp}$ of a sphere and resubstituting the resonant frequency of the mode of interest until the value converges. Additionally, the contribution of radiation damping\cite{vonPlessen2007} is introduced by adding a term to the bulk damping coefficient proportional to $\tau=\frac{2e^2}{3m_{sp}c^3}$ which causes a slight redshift in the LSPR frequency. Figure~\ref{fig5} tracks the eigenvalues of the NN and NS mode as a function of radius using the full Hamiltonian. The nanoparticle radius ranges from 1 nm to 20 nm, and the center-to-center distance between nanoparticles is always $2.2 \, r_0$, as in the diagram in Figure~\ref{fig1}. Below 10 nm, NS is the lowest-energy mode. Between 10 and 11 nm, the eigenvalues cross, and from 11 nm onward NN is the lowest-energy mode.

\begin{figure}
  \begin{center}
  \includegraphics[trim= 0 0 0 0,clip=true,scale=0.3]{nn-ns-eigen_3.png}
  \caption{The eigenenergies of the NS and NN modes are tracked as a function of increasing radius. The critical radius is between 10 and 11 nm, where the NN mode becomes energetically preferential to the NS mode.}
  \label{fig5}
  \end{center}
\end{figure}

This is further verified by full-wave electrodynamics simulations\cite{Hohenester2012}. EELS simulations on magnetic dimer systems of different sizes show that in the quasistatic limit the NN mode is always higher in energy than the NS mode. Conversely, fully retarded simulations show that the NN mode eventually redshifts past the NS mode with increasing dimer size. Because the NS and NN modes are energetically nearly degenerate and their linewidths are broad, a Drude model for silver with a reduced damping coefficient was used as the dielectric function for the spheres. Running simulations for sphere radii between 1 nm and 10 nm and separation distances of $2.2 \, r_0$, it is found that the NN mode redshifts past the NS mode between 5 and 10 nm. The simulated EEL spectra are presented in Figure~\ref{fig6}. In the quasistatic limit, just as predicted, the modes did not change in energy with increasing particle size, due to the fact that the separation distances are parameterized by the radius. The interaction energy scales as $\frac{1}{r_{0}^{3}}$ and the polarizability scales as $r_{0}^{3}$, so these effects directly cancel and the modes do not change with increasing particle size in the quasistatic limit.

\begin{figure}
  \begin{center}
  \includegraphics[trim = 0.8in 0 1.2in 0,clip=true,scale=0.5]{bem_spectra_3.png}
  \caption{Simulated quasistatic and fully retarded EEL spectra for the magnetic dimer with $r_0$ = 1 nm, 2.5 nm, 5 nm, and 10 nm. When the particles are very small, the quasistatic NS (green) and NN (red) modes are nearly energetically degenerate with the fully retarded NS (purple) and NN (blue) modes. As the size increases, the red and green traces do not move, but the purple and blue traces begin to redshift. Between 5 and 10 nm, the blue trace redshifts past the purple trace, indicating that in this size regime the NN mode is energetically favorable.}
  \label{fig6}
  \end{center}
\end{figure}

It has been shown that for small magnetic oligomer systems, specifically naphthalene-like decamers of silver nanospheres, quasistatic plasmon hybridization theory and fully retarded, full-wave numerical simulations agree on the energy-ordering of the magnetic modes. However, as the individual nanoparticles become larger and proportionally farther apart, the quasistatic limit breaks down and the simulations predict a different energy-ordering than the tight-binding model. Introducing retardation effects into the tight-binding model requires including the time-dependence of the near-field as well as the entire intermediate- and far-field terms. Consideration of these retardation effects also introduces radiation damping, which further impacts the resonant frequencies and broadening of the collective modes. Implementing this and iteratively solving for the eigenvalues of the collective magnetic modes, it is shown that including the fully retarded electric field properly predicts the energy-ordering in agreement with simulation. This gives a new route to the qualitative characterization of large, multi-constituent nanoparticle aggregates and accurately predicting the energy-ordering of the collective modes in various size regimes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The ``Acknowledgement'' section can be given in all manuscript
%% classes.  This should be given within the ``acknowledgement''
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
Thanks mom and dad, also whoever paid us. Thanks Masiello group for being cool. Thanks for not barfing after you read this. And thanks Hillary Clinton for being my idol.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

### 2017-01-19 chains/chains.py

@@ -1,0 +1,153 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 18; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NNNN = []
+	NSSN = []
+	NNSS = []
+	NSNS = []
+	for r in range (10,301):
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		rij = 2.2*a0
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([-3*e2,2*e1]),np.array([-4*e2,e1]),np.array([-4*e2,-e1]),np.array([-3*e2,-2*e1]),
+			   np.array([0, e1]),np.array([-e2, 2*e1]),np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
+		       np.array([-e2, -2*e1]),np.array([0, -e1]),np.array([e2, -2*e1]),np.array([2*e2, -e1]),
+		       np.array([2*e2 , e1]),np.array([e2 , 2*e1]),np.array([3*e2,-2*e1]),np.array([4*e2,-e1]),
[…]

### 2017-01-19 chains/three/three_plotter.py

@@ -1,0 +1,62 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.interpolate as scint
+
+'''A = np.loadtxt('nm1_three_chain')
+B = np.loadtxt('nm4_chain_three')
+C = np.loadtxt('nm8_chain_three')
+D = np.loadtxt('nm10_chain_three')'''
+
+A = np.loadtxt('three_chain_eigen',skiprows=1)
+NNN = np.loadtxt('../NNN.txt')
+N_S = np.loadtxt('../N_S.txt')
+NSN = np.loadtxt('../NSN.txt')
+
+rad = A[:,0]
+NSN_BEM = A[:,1]
+N_S_BEM = A[:,2]
+NNN_BEM = A[:,3]
+radnew = np.linspace(1,10,291)
+
+NNN_smooth = scint.interp1d(rad,NNN_BEM,'quadratic')
+N_S_smooth = scint.interp1d(rad,N_S_BEM,'quadratic')
+NSN_smooth = scint.interp1d(rad,NSN_BEM,'quadratic')
+
+r = np.linspace(1,30,291)
+plt.figure(1)
+plt.plot(r,NNN,lw=3,label='NNN theory')
+plt.plot(r,N_S,lw=3,label='N_S theory')
+plt.plot(r,NSN,lw=3,label='NSN theory')
+plt.xlim(1,30)
+plt.xlabel('Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.legend()
+plt.savefig('three_chain_theory.pdf')
+plt.figure(2)
+plt.plot(radnew,NNN_smooth(radnew),lw=3,label='NNN bem')
+plt.plot(radnew,N_S_smooth(radnew),lw=3,label='N_S bem')
+plt.plot(radnew,NSN_smooth(radnew),lw=3,label='NSN bem')
+plt.ylim([3.02,3.10])
+plt.xlabel('Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.legend()
+plt.savefig('three_chain_mnpbem.pdf')
+plt.show()
+
+'''plt.figure(1)
+plt.plot(A[:,0],A[:,1],label = 'left')
+plt.plot(A[:,0],A[:,2],label = 'top')
+plt.legend()
+plt.figure(2)
+plt.plot(B[:,0],B[:,1],label = 'left')
+plt.plot(B[:,0],B[:,2],label = 'top')
[…]

### 2017-01-19 coronine_ret/6mer.py

@@ -1,0 +1,220 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+dipole = [] # doubly degenerate
+no_dipole = [] # doubly degenerate
+all_N = [] #all north
+out_N_in_S = [] # that weird "excited state"
+alt_NS = [] # maximally out of phase magnets
+center = np.zeros(7,dtype=object)
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 24; #number of particles
+	a0 = 0.1*r*10**-7; #sphere radius in cm
+	index = r - 10
+	''' now determine geometry.'''
+
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),np.array([0,-2*e1]),
+		   np.array([e2,-e1]),np.array([e2,e1]),np.array([2*e2,2*e1]),np.array([3*e2,e1]),
+		   np.array([3*e2,-e1]),np.array([2*e2,-2*e1]),np.array([2*e2,-4*e1]),np.array([e2,-5*e1]),
+		   np.array([0,-4*e1]),np.array([-e2,-5*e1]),np.array([-2*e2,-4*e1]),np.array([-2*e2,-2*e1]),
+		   np.array([-3*e2,-e1]),np.array([-3*e2,e1]),np.array([-2*e2,2*e1]),np.array([-2*e2,4*e1]),
+		   np.array([-e2,5*e1]),np.array([0, 4*e1]),np.array([e2,5*e1]),np.array([2*e2,4*e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
+	center[0] = (Loc[0]+Loc[3])*0.5
+	center[1] = (Loc[6]+Loc[9])*0.5
[…]

### 2017-01-19 coronine_ret/bem_spectra/plotting.py

@@ -1,0 +1,13 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+for num in range(0,40):
+	spec = np.loadtxt('_'.join(['Spectrum_nm',str(num+1)]))
+	eV = 1.24/spec[:,1]
+	abs = spec[:,3]
+
+	plt.plot(eV,abs,linewidth=3)
+	plt.legend(['absorption'])
+	plt.title(str(num))
+	plt.show()
+	raw_input('press enter')

### 2017-01-19 coronine_ret/eigenvec_plotter.py

@@ -1,0 +1,31 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+numPart = 24; #number of particles
+
+for r in range(18,41):
+	for num in range(1,8):
+		a0 = 0.5*r*10**-7; #sphere radius in cm
+
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),np.array([0,-2*e1]),
+			   np.array([e2,-e1]),np.array([e2,e1]),np.array([2*e2,2*e1]),np.array([3*e2,e1]),
+			   np.array([3*e2,-e1]),np.array([2*e2,-2*e1]),np.array([2*e2,-4*e1]),np.array([e2,-5*e1]),
+			   np.array([0,-4*e1]),np.array([-e2,-5*e1]),np.array([-2*e2,-4*e1]),np.array([-2*e2,-2*e1]),
+			   np.array([-3*e2,-e1]),np.array([-3*e2,e1]),np.array([-2*e2,2*e1]),np.array([-2*e2,4*e1]),
+			   np.array([-e2,5*e1]),np.array([0, 4*e1]),np.array([e2,5*e1]),np.array([2*e2,4*e1])]
+
+		x,y = zip(*Loc)
+		eigenvec = np.loadtxt('_'.join([str(r),'nm','.'.join([str(num),'txt'])]))
+		vec = np.reshape(eigenvec, (24,2))
+		#print Loc[:]
+		
+		#y = Loc[:,1]
+		u,v = zip(*vec)
+		#v = vec[:,1]
+		plt.title(''.join(['radius =',str(r*0.5)]))
+		plt.quiver(x,y,u,v)
+		plt.show()

### 2017-01-19 coronine_ret/plotter.py

@@ -1,0 +1,20 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+cross = np.loadtxt('crossing')
+eps = np.arange(1,16)
+plt.plot(np.sqrt(eps),cross,linewidth=3)
+plt.show()
+
+
+'''all_N = np.loadtxt('epsilon_1/altl_N_eigen')
+alt_NS = np.loadtxt('epsilon_1/alt_NS_eigen')
+out_N_in_S = np.loadtxt('epsilon_1/out_N_in_S_eigen')
+dipole = np.loadtxt('epsilon_1/dipole_eigen')
+nodipole = np.loadtxt('epsilon_1/nodipole_eigen')
+
+r = np.linspace(1,30,291)
+dipole = np.reshape(dipole,[291,2])
+nodipole = np.reshape(nodipole,[291,2])
+plt.plot(r,all_N,r,alt_NS,r,out_N_in_S,r,dipole[:,1],r,nodipole[:,1],linewidth=3)
+plt.show()'''

### 2017-01-19 dielectric_study/data_plotter.py

@@ -1,0 +1,39 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+NN_nearest = np.loadtxt('NN_eps_1.txt')
+NS_nearest = np.loadtxt('NS_eps_1.txt')
+NN_next = np.loadtxt('../unfused_twomer/NN_corners')
+NS_next = np.loadtxt('../unfused_twomer/NS_corners')
+NN_next_next = np.loadtxt('../unfused_twomer/NN_onespace')
+NS_next_next = np.loadtxt('../unfused_twomer/NS_onespace')
+
+r = np.linspace(1,30,len(NN_nearest))
+plt.figure(1)
+plt.plot(r,NN_nearest,lw=3,label='North-North Theory')
+plt.plot(r,NS_nearest,lw=3,label='North-South Theory')
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.xlim([1,30])
+plt.legend()
+plt.savefig('NN_NS_theory.pdf')
+
+plt.figure(2)
+plt.plot(r,NN_next,lw=3,label='North-North Corner')
+plt.plot(r,NS_next,lw=3,label='North-South Corner')
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.xlim([1,30])
+plt.legend()
+plt.savefig('NN_NS_corners.pdf')
+
+plt.figure(3)
+plt.plot(r,NN_next_next,lw=3,label='North-North One Space')
+plt.plot(r,NS_next_next,lw=3,label='North-South One Space')
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.xlim([1,30])
+plt.legend()
+plt.savefig('NN_NS_spaced.pdf')
+plt.show()

### 2017-01-19 dielectric_study/diel_plotter.py

@@ -1,0 +1,58 @@
+#from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.interpolate import spline
+
+fig = plt.figure()
+#ax = fig.add_subplot(111, projection='3d')
+'''NN_eig = np.loadtxt('NN_eig')
+NS_eig = np.loadtxt('NS_eig')
+r = [1,2.5,5,6,7,8,9,10]
+plt.plot(r,NN_eig,r,NS_eig,linewidth=3)
+plt.show()'''
+
+
+'''cross = np.loadtxt('crossing')
+eps = np.arange(1,16)
+plt.plot(eps,np.square(cross),linewidth=3)
+plt.show()'''
+NN_surface = np.zeros([10,291])
+NS_surface = np.zeros([10,291])
+X = []
+Y = []
+for epsb in range (1,11):
+	A = np.loadtxt('.'.join(['_'.join(['NN_eps',str(epsb)]),'txt']))
+	B = np.loadtxt('.'.join(['_'.join(['NS_eps',str(epsb)]),'txt']))
+	NN_surface[epsb-1] = A
+	NS_surface[epsb-1] = B
+
+x = np.linspace(1,30,291)
+epsb = np.linspace(1,10,10)
+limit = np.linspace(1,10,10)
+
+diff_5 = (NN_surface[:,51]-NS_surface[:,51])
+diff_10 = (NN_surface[:,101]-NS_surface[:,101])
+diff_15 = (NN_surface[:,151]-NS_surface[:,151])
+diff_20 = (NN_surface[:,201]-NS_surface[:,201])
+
+qnew = np.linspace(epsb.min(),epsb.max(),300)
+
+q_smooth = spline(epsb,diff_5,qnew)
+r_smooth = spline(epsb,diff_10,qnew)
+s_smooth = spline(epsb,diff_15,qnew)
+t_smooth = spline(epsb,diff_20,qnew)
+
+'''X,Y = np.meshgrid(x,epsb)
+ax.plot_wireframe(X,Y,NN_surface)
+ax.plot_wireframe(X,Y,NS_surface)
+ax.legend(['NN','NS'])'''
+plt.plot(qnew,q_smooth,qnew,r_smooth,qnew,s_smooth,qnew,t_smooth,linewidth=3)
+plt.plot(limit,np.zeros(10),'k--',linewidth=3)
[…]

### 2017-01-19 dielectric_study/naph_diel.py

@@ -1,0 +1,125 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+static_NN = []
+static_NS = []
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 10; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NN = []
+	NS = []
+	for r in range (10,301):
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		rij = 2.2*a0
+		e1 = float(1)/float(2) * (2.5*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.5*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),np.array([-2*e2, e1]),np.array([-2*e2, -e1]),np.array([-e2, -2*e1]),np.array([0, -e1]),np.array([e2, -2*e1]),np.array([2*e2, -e1]),np.array([2*e2 , e1]),np.array([e2 , 2*e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
+
[…]

### 2017-01-19 dielectric_study/plotter.py

@@ -1,0 +1,26 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+one = np.zeros(40)
+two = np.zeros(40)
+for epsb in range (1,17):
+	for x in range(0,40):
+		A = np.loadtxt('/'.join(['_'.join(['diel',str(epsb)]),'_'.join(['epsb',str(epsb),str(x+1),'nm_eigen.txt'])]))
+		if x == 0:
+			one[x] = A[19]
+			two[x] = A[18]
+		elif x == 1:
+			one[x] = A[19]
+			two[x] = A[18]
+		else:
+			if two[x-1]-A[18] < two[x-2]-two[x-1]:
+				one[x] = A[18]
+				two[x] = A[19]
+			else: 
+				one[x] = A[19]
+				two[x] = A[18]
+
+		
+	r = np.arange(1,41)
+	plt.plot(r,one,r,two,linewidth=3)
+	plt.show()

### 2017-01-19 dimer/dimer.py

@@ -1,0 +1,130 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+coll_near=[]
+coll_int=[]
+coll_far =[]
+coll_tot = []
+
+anpa_near = []
+anpa_int = []
+anpa_far = []
+anpa_tot = []
+
+para_near = []
+para_int = []
+para_far = []
+para_tot = []
+
+anco_near = []
+anco_int =[]
+anco_far = []
+anco_tot = []
+collinear = [np.array([1,0]),np.array([1,0])]
+antiparallel = [np.array([0,1]),np.array([0,-1])]
+parallel = [np.array([0,1]),np.array([0,1])]
+anticollinear = [np.array([1,0]),np.array([-1,0])]
+r = 10
+elec = 1.60217662e-19 # regular coulombs
+numPart = 2; #number of particles
+a0 = 10e-7; #sphere radius in cm
+
+''' now determine geometry.'''
+
+# make unit vectors in centimeters.
+for number in range(0,100):
+	dist = float(number+1)/4
+	sep = (2+dist*.25)*a0
+	Loc = [np.array([sep/2, 0]),np.array([-sep/2, 0])]
+
+	#Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	#H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
+	c = 2.99e10; # speed of light in cm/s
+	eps0 = 8.85418782e-12; # permittivity of free space
[…]

### 2017-01-19 dimer/dimer_stat.py

@@ -1,0 +1,95 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+
+r = 15
+elec = 1.60217662e-19 # regular coulombs
+numPart = 2; #number of particles
+a0 = 15e-7; #sphere radius in cm
+
+''' now determine geometry.'''
+
+# make unit vectors in centimeters.
+for number in range(0,41):
+	dist = float(number+1)/4
+	sep = (2+dist)*a0
+	Loc = [np.array([sep/2, 0]),np.array([-sep/2, 0])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
+	c = 2.99e10; # speed of light in cm/s
+	eps0 = 8.85418782e-12; # permittivity of free space
+	epsb = 1; # background dielectric - right now we're in vacuum
+	epsinf = 3.77; # does this have units?
+	'''Properties for silver.'''
+	Eplasma = 1.46599161e-18; # J
+	gamma = 0.05*elec/(hbar*16)
+	wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+	wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
+	'''initialize w_0 and eigen'''
+	eigen = np.ones(2*numPart)
+
+
+	alphasp = (a0**3)*(3/(epsinf+2)); # polarizability (cm^3)
+	msp = (ch**2)/(alphasp*((wsp_0)**2)); # sp mass (grams)
+	tau = (2*ch**2)/(3*msp*c**3) # radiation damping time
+	gamma_eV = gamma*hbar/elec
+	for n in range (0,2*numPart):
+		for m in range (n,2*numPart):
[…]

### 2017-01-19 dimer/stat/eigenplot.py

@@ -1,0 +1,9 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+A = np.loadtxt('lowest.txt')
+B = np.loadtxt('second.txt')
+x = np.arange(1,42)
+plt.plot(x,A,'b',x,B,'purple',linewidth=3,)
+plt.xlim([0.0,42])
+plt.show()

### 2017-01-19 dimer/stat/plotter.py

@@ -1,0 +1,12 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+lowest = np.zeros(41)
+second = np.zeros(41)
+for x in range(0,41):
+	A = np.loadtxt('_'.join([str(float(x+1)/4),'nm_eigen.txt']))
+	lowest[x] = A[3]
+	second[x] = A[2]
+
+np.savetxt('lowest.txt',lowest)
+np.savetxt('second.txt',second)

### 2017-01-19 magnetic_dipole_basis/graphene/graphene.py

@@ -1,0 +1,150 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../../mie_omegas_eV.txt')
+nn_near = np.loadtxt('../../dielectric_study/NN_eps_1.txt')
+ns_near = np.loadtxt('../../dielectric_study/NS_eps_1.txt')
+nn_sec = np.loadtxt('../../unfused_twomer/NN_corners')
+ns_sec = np.loadtxt('../../unfused_twomer/NS_corners')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+NN = []
+NS = []
+omegas = []
+for r in range(1,31):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = r*10**-7 #sphere radius in cm
+	mie_index = (r-1)*10
+	index = r-1
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
[…]

### 2017-01-19 magnetic_dipole_basis/graphene/surface_plotter.py

@@ -1,0 +1,14 @@
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+import numpy as np
+
+x = np.linspace(-1,1,80)
+[X,Y] = np.meshgrid(x,x)
+Z_plus = np.loadtxt('20_nm_E_plus.txt')
+Z_minus= np.loadtxt('20_nm_E_minus.txt')
+
+ax.plot_surface(X,Y,Z_plus,color='red')
+ax.plot_surface(X,Y,Z_minus,color='blue')
+plt.show()

### 2017-01-19 magnetic_dipole_basis/ising.py

@@ -1,0 +1,10 @@
+import numpy as np
+import matplotlib.plot as plt
+import scipy.linalg as sp
+import math
+
+'''Start with spins, basis vectors, etc.'''
+
+M = [0, 0, 1]
+bas1 = [1, 0, 0]
+bas2 = [-0.5*math.sqrt(3), 0.5, 0]

### 2017-01-19 magnetic_dipole_basis/magnetization_plotter.py

@@ -1,0 +1,26 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+A = np.loadtxt('chain_magnetization_eps1')
+B = np.loadtxt('chain_magnetization_eps2')
+C = np.loadtxt('chain_magnetization_eps3')
+D = np.loadtxt('chain_magnetization_eps4')
+E = np.loadtxt('chain_magnetization_eps5')
+F = np.loadtxt('chain_magnetization_eps9')
+
+r = np.linspace(1,30,291)
+plt.figure(1)
+plt.plot(r,A,linewidth=3,label='Epsb=1')
+plt.plot(r,B,linewidth=3,label='Epsb=2')
+plt.plot(r,C,linewidth=3,label='Epsb=3')
+plt.plot(r,D,linewidth=3,label='Epsb=4')
+plt.plot(r,E,linewidth=3,label='Epsb=5')
+plt.plot(r,F,linewidth=3,label='Epsb=9')
+plt.ylim([-0.1,1.1])
+plt.xlim([1,30])
+plt.legend(loc=2)
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Normalized Net Magnetization (unitless)')
+plt.show()

### 2017-01-19 magnetic_dipole_basis/periodic_array.py

@@ -1,0 +1,233 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+nn_near = np.loadtxt('../dielectric_study/NN_right.txt')
+ns_near = np.loadtxt('../dielectric_study/NS_right.txt')
+#nn_sec = np.loadtxt('../unfused_twomer/NN_sec_near')
+#ns_sec = np.loadtxt('../unfused_twomer/NS_sec_near')
+#nn_third = np.loadtxt('../unfused_twomer/NN_third_near')
+#ns_third = np.loadtxt('../unfused_twomer/NS_third_near')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+all_N = []
+alt_NS = []
+dipole =[]
+nodipole =[]
+excited = []
+
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = .1*r*10**-7 #sphere radius in cm
+	mie_index = r-10
+	index = r-10
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
[…]

### 2017-01-19 magnetic_dipole_basis/periodic_chain.py

@@ -1,0 +1,229 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+net_magnetization = []
+mie_omegas = np.loadtxt('../eps_10_mie_omegas.txt')
+nn_near = np.loadtxt('../dielectric_study/NN_eps_10.txt')
+ns_near = np.loadtxt('../dielectric_study/NS_eps_10.txt')
+#nn_sec = np.loadtxt('../unfused_twomer/NN_sec_near')
+#ns_sec = np.loadtxt('../unfused_twomer/NS_sec_near')
+#nn_third = np.loadtxt('../unfused_twomer/NN_third_near')
+#ns_third = np.loadtxt('../unfused_twomer/NS_third_near')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = .1*r*10**-7 #sphere radius in cm
+	mie_index = r-10
+	index = r-10
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
[…]

### 2017-01-19 magnetic_dipole_basis/sixmer.py

@@ -1,0 +1,231 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+nn_near = np.loadtxt('../dielectric_study/NN_right.txt')
+ns_near = np.loadtxt('../dielectric_study/NS_right.txt')
+nn_sec = np.loadtxt('../unfused_twomer/NN_sec_near')
+ns_sec = np.loadtxt('../unfused_twomer/NS_sec_near')
+nn_third = np.loadtxt('../unfused_twomer/NN_corners')
+ns_third = np.loadtxt('../unfused_twomer/NS_corners')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+all_N = []
+alt_NS = []
+dipole =[]
+nodipole =[]
+excited = []
+
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = .1*r*10**-7 #sphere radius in cm
+	mie_index = r-10
+	index = r-10
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
[…]

### 2017-01-19 magnetic_dipole_basis/three_chain.py

@@ -1,0 +1,188 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+nn_near = np.loadtxt('../dielectric_study/NN_right.txt')
+ns_near = np.loadtxt('../dielectric_study/NS_right.txt')
+nn_sec = np.loadtxt('../unfused_twomer/NN_sec_near')
+ns_sec = np.loadtxt('../unfused_twomer/NS_sec_near')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+NNN = []
+NSN = []
+N_S = []
+
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = .1*r*10**-7 #sphere radius in cm
+	mie_index = r-10
+	index = r-10
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
+	c = 2.99e10; # speed of light in cm/s
[…]

### 2017-01-19 magnetic_dipole_basis/twomer.py

@@ -1,0 +1,186 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+north_north = np.loadtxt('../dielectric_study/NN_right.txt')
+north_south = np.loadtxt('../dielectric_study/NS_right.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+NN = []
+NS = []
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = .1*r*10**-7 #sphere radius in cm
+	mie_index = r-10
+	index = r-10
+
+	''' now determine geometry.'''
+	''' begin with electric dipole on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	Q_mag_2 = [0,0,-1]
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
+	c = 2.99e10; # speed of light in cm/s
+	eps0 = 8.85418782e-12; # permittivity of free space
+	epsb = 1; # background dielectric - right now we're in vacuum
+	epsinf = 3.77; # does this have units?
[…]

### 2017-01-19 newdata/eigenplot.py

@@ -1,0 +1,9 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+A = np.loadtxt('NN.txt')
+B = np.loadtxt('NS.txt')
+x = np.arange(1,20)
+plt.plot(x,A,'b',x,B,'purple',linewidth=3,)
+#plt.axis([0.6,2.4,0,1.1])
+plt.show()

### 2017-01-19 newdata/plotter.py

@@ -1,0 +1,17 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+
+lowest = np.zeros(12)
+second = np.zeros(12)
+for x in range(0,12):
+	A = np.loadtxt('_'.join([str(x+1),'nm_eigen.txt']))
+	lowest[x] = A[3]
+	second[x] = A[2]
+
+'''for x in range(10,19):
+	A = np.loadtxt('_'.join([str(x+1),'nm_eigen.txt']))
+	NN[x] = A[19]
+	NS[x] = A[18]'''
+
+np.savetxt('lowest.txt',lowest)
+np.savetxt('second.txt',second)

### 2017-01-19 no_middle_twomer/no_middle.py

@@ -1,0 +1,121 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 8; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NN = []
+	NS = []
+	for r in range (10,301):
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([-e2, 2*e1]),
+			   np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
+			   np.array([-e2, -2*e1]),
+			   np.array([e2,-2*e1]),np.array([2*e2,-e1]),
+			   np.array([2*e2, e1]),np.array([e2, e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
+
+		'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
[…]

### 2017-01-19 polarizability_nonsense/polarizability.py

@@ -1,0 +1,82 @@
+import numpy as np
+import scipy as sp
+import math
+import matplotlib.pyplot as plt
+
+# make six particles
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+frequency = np.linspace(1,6,1001) # we will need this later
+
+'''nn_near = np.loadtxt('../../dielectric_study/NN_eps_1.txt')
+ns_near = np.loadtxt('../../dielectric_study/NS_eps_1.txt')
+nn_sec = np.loadtxt('../../unfused_twomer/NN_corners')
+ns_sec = np.loadtxt('../../unfused_twomer/NS_corners')'''
+
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+for r in range(10,11):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 6 #number of particles
+	a0 = r*10**-7 #sphere radius in cm
+	mie_index = (r-1)*10
+	index = r-1
+	ll = 1
+	''' now determine geometry.'''
+	''' begin with electric dipoles on the six-member ring '''
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	m_sep = 2*e2
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+	pol_vectors = [np.array([-1,0]),np.array([-0.5,-math.sqrt(3)/2]),np.array([0.5,-math.sqrt(3)/2]),
+		   		   np.array([1,0]),np.array([0.5,math.sqrt(3)/2]),np.array([-0.5,math.sqrt(3)/2])]
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	'''More constants'''
+	
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
[…]

### 2017-01-19 rhombus/rhombus.py

@@ -1,0 +1,154 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 16; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NNNN = []
+	NSNS = []
+	NNSS = []
+	NSSN = []
+	for r in range (10,301):
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		rij = 2.2*a0
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([-e2,4*e1]),np.array([0,5*e1]),np.array([e2,4*e1]),
+			   np.array([0, e1]),np.array([-e2, 2*e1]),np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
+		       np.array([-e2, -2*e1]),np.array([0, -e1]),np.array([e2, -2*e1]),np.array([2*e2, -e1]),
+		       np.array([2*e2 , e1]),np.array([e2 , 2*e1]),
[…]

### 2017-01-19 spacing_coro/6mer_spacing.py

@@ -1,0 +1,206 @@
+import numpy as np
+import math
+import scipy.linalg
+import scipy.sparse.linalg
+import matplotlib.pyplot as plt
+
+all_NS_vec = np.loadtxt('all_NS.txt')
+out_N_in_S_vec = np.loadtxt('out_N_in_S.txt')
+dipole_1_vec = np.loadtxt('dipole_1.txt')
+dipole_2_vec = np.loadtxt('dipole_2.txt')
+no_dipole_1_vec = np.loadtxt('no_dipole_1.txt')
+no_dipole_2_vec = np.loadtxt('no_dipole_2.txt')
+all_N_vec = np.loadtxt('all_N.txt')
+dipole = []
+all_N = []
+alt_NS = []
+out_N_in_S = []
+no_dipole = []
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+modes = np.zeros(7,dtype=object)
+eigen_unsort = np.zeros(7,dtype=object)
+epsb = 1
+for dist in range (90,131): # separation distance
+	index = dist - 90 
+	all_mag_dipole = np.zeros(7,dtype=object)
+	
+	center = np.zeros(7,dtype=object)
+	for r in range(20,21):
+		elec = 1.60217662e-19 # regular coulombs
+		numPart = 24; #number of particles
+		a0 = r*10**-7; #sphere radius in cm
+
+		''' now determine geometry.'''
+
+		# make unit vectors in centimeters.
+		e1 = float(1)/float(2) * 2*(a0+(dist*.1)*10**-7) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * 2*(a0+(dist*.1)*10**-7); #long side of 30-60-90 triangle
+		Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),np.array([0,-2*e1]),
+			   np.array([e2,-e1]),np.array([e2,e1]),np.array([2*e2,2*e1]),np.array([3*e2,e1]),
+			   np.array([3*e2,-e1]),np.array([2*e2,-2*e1]),np.array([2*e2,-4*e1]),np.array([e2,-5*e1]),
+			   np.array([0,-4*e1]),np.array([-e2,-5*e1]),np.array([-2*e2,-4*e1]),np.array([-2*e2,-2*e1]),
[…]

### 2017-01-19 spacing_study/naph_spacing.py

@@ -1,0 +1,105 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+elec = 1.60217662e-19 # regular coulombs
+numPart = 10; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+NN = []
+NS = []
+for dist in range(10,51):
+	print dist
+	r = 30
+	a0 = r*10**-7; #sphere radius in cm
+
+	''' now determine geometry.'''
+
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * 2*(a0+(dist*10**-7)) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * 2*(a0+(dist*10**-7)); #long side of 30-60-90 triangle
+	Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),np.array([-2*e2, e1]),np.array([-2*e2, -e1]),np.array([-e2, -2*e1]),np.array([0, -e1]),np.array([e2, -2*e1]),np.array([2*e2, -e1]),np.array([2*e2 , e1]),np.array([e2 , 2*e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
[…]

### 2017-01-19 sphere_dimer/dimer_plotter.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.signal import argrelextrema
+
+#index = []
+collinear = []
+anticollinear = []
+parallel = []
+antiparallel = []
+count = 0
+for r in range(1,41):
+	bound = 0
+	spectrum = np.loadtxt(''.join(['radius_',''.join([str(r),'nm'])]),skiprows=1)
+	eV = spectrum[:,0]
+	#print spectrum[0,1]
+	#print eV
+	'''plt.figure
+	plt.plot(eV,spectrum[:,2],linewidth=3)
+	plt.show()'''
+	for i in enumerate(spectrum[:,2]):
+		if i[0] < len(spectrum[:,2]):
+			if spectrum[i[0],2] > bound:
+				bound = spectrum[i[0],2]
+				if spectrum[i[0]+1,2] < spectrum[i[0],2]:
+					count = count+1
+					bound = spectrum[i[0]+1,2]
+		if count == 2:
+			index = i[0]
+			break	
+	antiparallel.append(eV[index])
+#,'top','middle'
+r = np.arange(1,41)
+plt.figure
+plt.plot(r,antiparallel,linewidth=3)
+plt.show()
+np.savetxt('anti_para_eig',antiparallel)

### 2017-01-19 sphere_dimer/dimer_ret.py

@@ -1,0 +1,139 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+coll = []
+para = []
+anti_coll = []
+anti_para = []
+
+for r in range(10,301):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 2; #number of particles
+	a0 = 0.1*r*10**-7; #sphere radius in cm
+	index = r-10
+	''' now determine geometry.'''
+
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([e1, 0]),np.array([-e1, 0])]
+	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+
+	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
+	H = np.zeros((2*numPart,2*numPart)) #initialize Hammy with zeros, twenty by twenty in this case.
+
+	'''More constants'''
+
+	me = 9.10938291e-28; # electron mass in g
+	ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+	hbar = 1.054571726e-34; # modified Planck in J*s
+	c = 2.99e10; # speed of light in cm/s
+	eps0 = 8.85418782e-12; # permittivity of free space
+	epsb = 1; # background dielectric - right now we're in vacuum
+	epsinf = 3.77; # does this have units?
+	'''Properties for silver.'''
+	Eplasma = 1.46599161e-18; # J
+	gamma = 0.05*elec/(hbar*16)
+	wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
+	wsp_0 = mie_omegas[index]*elec/hbar
+	'''initialize w_0 and eigen'''
[…]

### 2017-01-19 trimer_ring/ring_trimer.py

@@ -1,0 +1,128 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+static_NN = []
+static_NS = []
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 13; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NN = []
+	NS = []
+	for r in range (10,301):
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		rij = 2.2*a0
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),
+			   np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
+			   np.array([-e2, -2*e1]),np.array([0, -e1]),
+			   np.array([e2, -2*e1]),np.array([2*e2, -e1]),
+			   np.array([2*e2 , e1]),np.array([e2 , 2*e1]),
[…]

### 2017-01-19 trimer_ring/trimer_plotter.py

@@ -1,0 +1,40 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.interpolate as scint
+
+NN_theory = np.loadtxt('NN_eps_1.txt')
+NS_theory = np.loadtxt('NS_eps_1.txt')
+A = np.loadtxt('eigenTrimer',skiprows=1)
+rad = A[:,0]
+NN_BEM = A[:,1]
+NS_BEM = A[:,2]
+
+r = np.linspace(1,30,len(NN_theory))
+plt.figure(1)
+plt.plot(r,NN_theory,lw=3,label='All North Theory')
+plt.plot(r,NS_theory[:,0],lw=3,label='North-South Theory')
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.xlim([1, 30])
+plt.legend()
+plt.savefig('ring_trimer_theory.pdf')
+
+#rad = [1,2.5,5,6,7,8,9,10]
+
+radnew = np.linspace(1,10,291)
+
+#NN_smooth = spline(rad,NN_BEM,radnew)
+#NS_smooth = spline(rad,NS_BEM,radnew)
+
+NN_smooth = scint.interp1d(rad,NN_BEM,'quadratic')
+NS_smooth = scint.interp1d(rad,NS_BEM,'quadratic')
+
+plt.figure(2)
+plt.plot(radnew,NN_smooth(radnew),lw=3,label='All North MNPBEM')
+plt.plot(radnew,NS_smooth(radnew),lw=3,label='North-South MNPBEM')
+plt.xlabel('Particle Radius (nm)')
+plt.ylabel('Energy (eV)')
+plt.ylim([3.02, 3.1])
+plt.legend()
+plt.savefig('ring_trimer_MNPBEM.pdf')
+plt.show()

### 2017-01-19 unfused_twomer/naph_diel.py

@@ -1,0 +1,142 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 12; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NN = []
+	NS = []
+	for r in range (10,301):
+		
+		a0 = .1*r*10**-7; #sphere radius in cm
+		index = r-10
+		''' now determine geometry.'''
+		print index
+		# make unit vectors in centimeters.
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		Loc = [np.array([-e2, 2*e1]),np.array([-e2, 4*e1]),
+			   np.array([0, 5*e1]),np.array([e2, 4*e1]),
+			   np.array([e2, 2*e1]),np.array([0, e1]),
+			   np.array([-e2, -2*e1]),np.array([-e2, -4*e1]),
+			   np.array([0, -5*e1]),np.array([e2, -4*e1]),
+			   np.array([e2 , -2*e1]),np.array([0 , -e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
[…]

### 2017-02-13 paper/draft.tex
edited the paper. editec the onemer calculations. Produced data files.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\author{David J. Masiello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\alsoaffiliation[Department of Applied Mathematics, University of Washington]
{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Towards Tunable Negative-Index Metamaterials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{plasmon, hybridization, magnetic, retardation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials. Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing. For these reasons, it is imperative to understand the properties of such systems on both small and large scales. We show through theory and simulation that the energy ordering of the magnetic resonances of small oligomers depends greatly on the size and scale of the nanoparticle assembly in ways that purely electric plasmons do not. Following this, we determine the effective pemeability and permittivity of periodic arrays of nanoparticles and show that in certain size regimes they exhibit a negative index of refraction at optical frequencies. As a final exercise, we propose a negative-index material composed of charge tunable semiconductor quantum dots to emphasize the direct control of the optical properties of 2-D magnetic materials.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Bringing two or more metal nanoparticles (MNPs) together allows their individual electric plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Plasmon hybridization theory is applied to aggregates of MNPs and explains their collective behavior within the quasistatic limit in which the speed of light is taken to be infinite\cite{NordHal2003,NordProdan2004,Oubre2004,Gomez2009}. Recently, retardation effects on plasmon hybridization have been the focus of study for large particles\cite{Abajo2008,Gu2010} as well as dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and 2-D arrays\cite{Schatz2003,Royer2005,Chumanov2010} of nanoparticles. Specific arrangements of nanoparticles in 2-D arrays, such as three or more nanoparticles arranged on the vertices of a regular polygon, support a collective mode in which all of the dipole plasmons are oriented head-to-tail. This generates a fictitious, oscillating current loop resulting in an oscillating magnetic dipole moment in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}. These so-called magnetic plasmons are the lowest-energy collective modes of the oligomers and couple to and enhance the magnetic field of incident light\cite{Shalaev2007,Qian2015,Nord2007}, offering a route to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}. The rich plasmonic modes of magnetic-plasmon-supporting systems are well-described using plasmon hybridization theory, but when in the quasistatic limit, the energy-order of the modes is not.

Plasmon hybridization theory treats plasmons as point dipoles centered on their associated nanoparticles that interact through dipole-dipole coupling. In the quasistatic limit, these dipoles couple only through time-independent, electric near-field interactions\cite{jackson_classical_1999}, but when the size of and distance between nanoparticles becomes large, this approximation breaks down and intermediate- and far-field effects must be considered, as well as time-delay effects in the near-field\cite{jackson_classical_1999}. The aim of this paper is to incorporate the fully retarded electric field into plasmon hybridization theory and extend studies of retardation effects to magnetic plasmon oligomers. Specifically, we begin by exploring oligomers comprising two and three rings of nanoparticles and compare to full-wave simulation \cite{Hohenester2012} to verify that our approach qualitatively predicts the energy-ordering of the magnetic modes.\cite{Cherqui2014,Cherqui2016}. Following this, we calaculate the coupling betwen individual rings in various oligomers in order to parametrize an effective magnetic-magnetic coupling between magnetic dipoles. Using this new basis, we describe periodic chains and arrays of oligomers.

The calculations presented here are performed using an electric tight-binding model, parametrizing the magnetic couplings, and then introducing these coupling constants into a magnetic tight-binding model. For all following magnetic oligomers, only the two planar dipoles per particle are considered in the electric tight binding model. The dipoles are mapped onto a set of harmonic oscillators and are described by the following Hamiltonian:

\begin{equation}
H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{\textrm{full},ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
\end{equation}

where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{\textrm{full},ij}$ is the fully retarded dipole-dipole relay tensor (expanded below). To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$. Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{\textrm{full},ij}$, we get:

\begin{equation}
\begin{aligned}
H = 
\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
\end{aligned}
\end{equation}

In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}}{r_{ij}^3}\cos\left(\frac{\omega r_{ij}}{c}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}\omega}{r_{ij}^2 c}\sin\left(\frac{\omega r_{ij}}{c}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}\omega^2}{r_{ij} c^2}\cos\left(\frac{\omega r_{ij}}{c}\right)$, respectively. Additionally, the polarizability $\alpha_{sp} = \frac{e^2}{m_{sp}\omega_{sp}^2}$, $r_{ij}$ is the distance between the ith and jth LSPs, and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPs. Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973}.

It should be noted that this Hamiltonian, when diagonilzed, results in a transcendental equation. The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues of the eigenvectors. In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues. Using the eigenvalue associated with the mode of interest, the Hamiltonian is diagonalized to convergence. The process is repeated for each mode of interest.

\section{results and discussion}
The first systems we examine are a magnetic dimer\cite{Cherqui2014}, a three-ring chain, and three rings arranged in a triangle. Because we are interested in the effects of scale, we must define a scaling parameter for the system. Each of our systems begins from a unit cell: six silver, spherical MNPs placed at the corners of a regular hexagon. To create the dimer, two unit cells are tiled so that they share an edge, and thus two particles. In general, if any two unit cells share an edge, they also share two nanoparticles, as in the diagrams in Figure~\ref{theory_simul} Each particle has radius $a_0$ and particles are separated by lattice spacing $r=2.2\times a_0$. With the radius of the particles defining the scale of the system, there now exists a way to probe the energy ordering of the modes as a function of size.

\begin{figure}
\begin{center}
\includegraphics{theory_bem_comparison_fig1.pdf}
\caption{Pending.}
\label{theory_simul}
\end{center}
\end{figure}

The results of our theoretical calculations and full-wave simulations for the aforementioned oligomers are dispayed in Figure~\ref{theory_simul}. Both theory and simulation predict that as a function of size, the energy ordering of the magnetic plasmon modes should change. In the dimer system, there are two magnetic modes. When the system is small, the lowest energy mode is the alternating north-south (NS) mode and the in-phase north-north mode is highest. When we add a ring to the system, we see a trend emerge. The alternating (NSN) mode is lower than the N-S mode, which is in turn lower than the NNN mode. As a function of size, the modes change order. The triangle system, as a result of its threefold symmetry (as opposed to twofold for the chains) has slightly different properties. At small size, its lowest energy mode is a pair of degenerate NS modes, while its higher energy mode is an all-north mode. These again switch order as a function of size. In chains with more than three rings, the pattern continues - the magnetic resonances with the most nodes between rings are the lowest energy when small, but the highest when large.

\begin{figure}
\begin{center}
\includegraphics{twomer_dimer.pdf}
\caption{Pending.}
\label{twomer_dimer}
\end{center}
\end{figure}

This is an unexpected phenomenon. When one considers the energy-order of the four (six) hybridized modes of the nanosphere dimer, it becomes clear that they do not exhibit this effect (Figure~\ref{twomer_dimer}). Notably, the sphere dimer shows no crossings while the oligomer dimer does. The reason for this outcome is the oligomer dimer's complex structure\cite{Cherqui2016}. The sphere dimer has only one length scale and consitutes only one pairwise interaction. However, the oligomer dimer contains many pairs of nanoparticles over multiple length scales. As a result, different configurations of electric dipoles will be favored at different oligomer sizes, hence the flip of the magnetic modes.

\begin{figure}
\begin{center}
\includegraphics{interactions.pdf}
\caption{Pending.}
\label{int_strength}
\end{center}
\end{figure}

To gain a more visual and intuitive sense of the length scales of each of the terms (near, intermediate, and far) in the fully retarded electric field of a dipole (found in the coupling terms of Equation~\ref{elec_hammy_2}), we calculated the relative interaction strength between pairs of dipoles (the collective modes of the sphere dimer) as a function of dipole separation distance. The results of these calculations are displayed in Figure~\ref{int_strength}, showing that at different length scales, different terms in the field contribute more to the energy of the system. Significantly, the interaction strengths display oscillatory motion, which confirms and reinforces past studies on the oscillatory nature of radiation damping.\cite{vonPlessen2007}

\begin{figure}
\begin{center}
\includegraphics{coupling_comparison.pdf}
\caption{Pending.}
\label{ring_spacing}
\end{center}
\end{figure}

With a functional and accurate electric dipole tight binding model, we seek a way to simplify our model. Figure~\ref{ring_spacing} displays the eigenvalue curves for three arrangements of two-ring systems, with the rings as (A) nearest neighbors (B) next-nearest neighbors and (C) next-next-nearest neighbors. It is clear that again, at different length scales and relative orientations, the eigenvalue curves behave differently, having different crossing points and energy ordering. Using these eigenvalue curves, the electric dipole model is transformed into a magnetic dipole model. A magnetic dipole is placed at the center of each ring with orientation perpendicular to the plane of the ring. Each dipole has natural frequency $\omega_{\textrm{M}}$, which we determine using the electric tight-binding model for a single ring. The coupling between each magnetic dipole is pulled from the plots in figure (w/e) - depending on the spacing between the rings, the dipoles couple through nearest, next-nearest, or next-next-nearest neighbor coupling. The Hamiltonian

\begin{equation}
H = \frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i}^{n}[\pi_{i}^{2}+q_{i}^{2}]+\frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i\neq j}g_{ij}^{\textrm{M}}q_{i}q_{j}
\label{mag_hammy}
\end{equation}

is used in the same way as Equation~\ref{elec_hammy_2} - diagonalizing it for a set of $n$ magnetic dipoles produces $n$ collective magnetic modes. The benefit of this model is shown by example. For the oligomer dimer, there are ten MNPs, each with two electric dipoles, resulting in twenty collectivel electric modes, two of which were magnetic in character. In the magnetic dipole basis, because there are two rings, there are only two modes - the magnetic modes. This simplifies the data analysis procedures greatly. We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in figure (whatever), the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly. We find, furthermore, that truncating to nearest or next-nearest neighbors in the magnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models. It is this finding that will allow us the extension of the model to larger systems considering only nearest or next-nearest neigbor coupling.

The significant challenge here is to find a colloquial, qualitative, and accurate way to describe extended systems. By considering the magnetic dimer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model. Here, however, the atoms are the rings of the dimer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above. More on this model will be presented later.

\section{Dielectric Background and a Measure of Quasistaticity}

As an additional exercise, and to emphasize the tunability and versatility of magnetic plasmon oligomers, the effect of the dielectric constant of the background ($\varepsilon_{b}$) is also taken into account. The dielectric constant screens the electric dipoles from each other by effectively weakening their induced electric fields. This means that as $\varepsilon_{b}$ gets large, intermediate and far field effects will weaken in comparison to near field contributions to the electric field. Thus, magnetic plasmon oligomers will be more likely to behave quasistatically when large. In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic dimers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes. The results show that when highly screened, even large magnetic plasmon oligomers behave quasistatically.

\begin{figure}
\begin{center}
\includegraphics{diel_magnetization.pdf}
\caption{Pending.}
\label{diel_eff}
\end{center}
\end{figure}

To extend this to a potential application, we consider now a periodic chain of magnetic monomers - essentially a 1-D system - with only nearest neighbor coupling. When the radii of the particles in the chain are small, the lowest energy collective mode of the chain will be an all-alternating magnetic mode, and when the radii are large it will be an all in-phase magnetic mode. A way to quantify this is through a measure of net magnetization. Diagonalizing the magnetic Hamiltonian [reference the equation], summing the eigenvectors, and dividing by n (the number of rings) gives a measure of whether the system is magnetized, and this is plotted as a function of particle radius in Figure~\ref{diel_eff}B. More importantly, the point at which the magnetization ``switches on'' can be controlled through the dielectric background. This gives rise to the ability of the experimentalist to directly introduce a phase-lag in an extended chain of magnetic oligomers by embedding certain segments of the chain in different materials. This is not so different from certain techniques that are being studied presently in the field\cite{odom_lasing}

\section{Periodic Arrays of Rings - Permeability, Permittivity, and Index of Refraction}
To determine the permeability, permittivity, and index of refraction of the six-member ring that is the unit cell, we follow Alu and Engheta\cite{Alu2006}. Preparing the magnetic mode of the six-member ring induces a dipole moment on each particle. The dipole moment of a particular particle,

\begin{equation}
\textrm{\textbf{p}}_{i} = p\hat{\textrm{\textbf{p}}}_{i} = \alpha_{sp}\left(\textrm{\textbf{E}}_{0} + p\sum_{i\neq j}\boldsymbol{\Lambda_{ij}}\cdot\hat{\textrm{\textbf{p}}}_{i}\right)
\label{dipolemoment}
\end{equation} 
 responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles. For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$. We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where

\begin{equation}
\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
\label{magneticmoment}
\end{equation}
is the magnetic dipole moment. From these equations, we find that

\begin{equation}
\alpha_{M} = \frac{(kR)^{2}N}{4\varepsilon_{b}}\left(\frac{\alpha_{sp}}{1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j} }\right)
\label{alphaM}
\end{equation}

The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.

To compute the effective permittivity of the same ring of nanoparticles, the unit cell is prepared in a uniform electric field. This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$. The dipole moment on each particle is as above in Eq. \equation{dipolemoment}. Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$. This polarizability governs the total electric response of the ring to an electric field, as opposed to the polarizability of a single particle, and is given by

\begin{equation}
\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
\label{alphaE}
\end{equation}

From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$. The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative. A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.

Repeat this for more complicated unit cells! (twomer + sixmer) 
\section{Same as above, but qds}

\section{Conclusion}
It has been shown that magnetic plasmon oligomers are a highly versatile, highly tunable material. The magnetic behavior of tesselated rings of nanoparticles is dependent on size, spacing, arrangement, and environment. Equipped with an understanding of how information propagates along these materials and how to actively influence that information, we are now in a position to study large chains and arrays of magnetic plasmon oligomers. By combining these theoretical studies with existing experimental techniques, there exist ways to directly inlfuence the propagation of information in real time, leading to new applications in detection mechanisms and perhaps leading to a new kind of plamsonic ``circuit.'' What remains is to understand the dynamics of these systems from a theoretical perspective, an exercise which is left for future studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The ``Acknowledgement'' section can be given in all manuscript
%% classes.  This should be given within the ``acknowledgement''
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
CEI, NSF, DOE, Niket, some other people, probably
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

### 2017-02-13 polarizability_nonsense/diagonalize_polarize.py

@@ -16,7 +16,7 @@ ns_sec = np.loadtxt('../../unfused_twomer/NS_corners')'''
 
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 
-for r in range(1,31):
+for r in range(1,30):
 	elec = 1.60217662e-19 # regular coulombs
 	numPart = 6 #number of particles
 	a0 = r*10**-7 #sphere radius in cm
@@ -54,19 +54,20 @@ for r in range(1,31):
 	gamma = 0.05*elec/(hbar)
 	wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 	''' First make epsilon(omega)'''
-
+	km = (frequency/c)*(elec/hbar)
 	freq_eps = epsinf - ((9.1)**2)/(np.square(frequency)+(0.05j)*frequency)
 	#print freq_eps
-	freq_alpha = (a0**3 )* ll*(freq_eps - epsb)/((ll*(freq_eps + epsb)) + epsb)
-	alpha_mlwa = freq_alpha/(1-((2.0/3.0)*1j*((frequency/c)*(elec/hbar))**3)*freq_alpha - ((frequency/c * elec/hbar)**2)*freq_alpha/a0)
-	#wsp_0 = (mie_omegas[mie_index])*elec/hbar
+	freq_alpha = 4*math.pi*(a0**3 )* ll*(freq_eps - epsb)/((ll*(freq_eps + epsb)) + epsb)
+	alpha_mlwa = freq_alpha/(1-((2.0/3.0)*1j*((frequency/c)*(elec/hbar))**3)*freq_alpha )
+	alpha_rad = (freq_alpha**-1 - 1j*(1./(math.pi*6.))*km**3 - (km**2)/(4*math.pi*a0))**-1
+	wsp_0 = (mie_omegas[mie_index])*elec/hbar
 	'''initialize w_0 and eigen'''
-	#w_0 = wsp_0
+	w_0 = wsp_0
 	alphasp_stat = ((a0**3)*3)/(epsinf+2)
 	eigen = np.zeros(2*numPart)
 	count = 1
 	H = np.zeros((2*numPart,2*numPart))
-	'''while np.sqrt(np.square(w_0*hbar/elec - eigen[2*numPart-1])) > 0.00000001:
[…]

### 2017-02-15 paper/draft.tex
new paper draft. Added stuff to quantum dots calculations

@@
 \section{results and discussion}
-The first systems we examine are a magnetic dimer\cite{Cherqui2014}, a three-ring chain, and three rings arranged in a triangle.
+The first systems we examine are a magnetic two-mer\cite{Cherqui2014}, three-mer chain, and three-mer triangle.
 Because we are interested in the effects of scale, we must define a scaling parameter for the system.
-Each of our systems begins from a unit cell: six silver, spherical MNPs placed at the corners of a regular hexagon.
-To create the dimer, two unit cells are tiled so that they share an edge, and thus two particles.
+Each of our systems begins from a unit cell called the one-mer: six silver, spherical MNPs placed at the corners of a regular hexagon.
+To create the two-mer, two unit cells are tiled so that they share an edge, and thus two particles.
 In general, if any two unit cells share an edge, they also share two nanoparticles, as in the diagrams in Figure~\ref{theory_simul} Each particle has radius $a_0$ and particles are separated by lattice spacing $r=2.2\times a_0$.
@@
 \includegraphics{theory_bem_comparison_fig1.pdf}
-\caption{Pending.}
+\caption{Eigenvalues for the magnetic two-mer (A), three-mer chain (B), and three-mer triangle (C) as computed from the tight binding model (left) and compared to MNPBEM simulations (right).
+For all three geometries, the net magnetic mode is higher in energy than the net electric mode(s) at small sizes and becomes lower at a certain critical scale value.
+The tight binding model incorrectly predicts the critical scale value but otherwise is fairly quantitatively accurate.}
 \label{theory_simul}
@@
 Both theory and simulation predict that as a function of size, the energy ordering of the magnetic plasmon modes should change.
-In the dimer system, there are two magnetic modes.
+In the two-mer system, there are two magnetic modes.
 When the system is small, the lowest energy mode is the alternating north-south (NS) mode and the in-phase north-north mode is highest.
@@
 \includegraphics{twomer_dimer.pdf}
-\caption{Pending.}
+\caption{Comparison of the magnetic two-mer (A) and the nanoparticle dimer (B) eigenmodes as a function of scale.
+Significantly, the two-mer exhibits and change in the energy-ordering of its magnetic modes.
+However, the nanoparticle dimer does not ever exhibit a change in energy ordering of its eigenmodes.
+This make energy ordering a uniquely tunable property of fused-ring magnetic oligomers.}
 \label{twomer_dimer}
@@
 \includegraphics{interactions.pdf}
-\caption{Pending.}
+\caption{Plots of the interaction terms in the fully retarded electric field for (A) collinear, (B) anti-parallel, (C) anti-collinear, and (D) parallel arrangements of dipoles in a nanoparticle dimer as a function of separation distance.
+The plots show that at different length scales, different terms in the electric field contribute more to the interaction strength between the particles.
+As a result, the interactions between one pair of particles in a larger aggregate may be dominated by the interactions between another pair of particles.}
 \label{int_strength}
@@
 \includegraphics{coupling_comparison.pdf}
-\caption{Pending.}
+\caption{Comparison of coupling schemes for nearest neighbors (A), next-nearest neighbors (B), and next-next nearest neighbors (C) using the electric dipole basis (left) and the magnetic dipole basis parametrized from the electric dipole basis (right).
+It is clear to see that by parametrizing the coupling between two rings as the difference between the eigenvalues of the NN and NS modes of two rings, we recover exactly the quantitative description provided by the electric dipole basis at much lower computational cost.}
 \label{ring_spacing}
@@
 Each dipole has natural frequency $\omega_{\textrm{M}}$, which we determine using the electric tight-binding model for a single ring.
-The coupling between each magnetic dipole is pulled from the plots in figure (w/e) - depending on the spacing between the rings, the dipoles couple through nearest, next-nearest, or next-next-nearest neighbor coupling.
+The coupling between each magnetic dipole is pulled from the plots in Figure~\ref{ring_spacing} - depending on the spacing between the rings, the dipoles couple through nearest, next-nearest, or next-next-nearest neighbor coupling.
 The Hamiltonian
@@
 The benefit of this model is shown by example.
-For the oligomer dimer, there are ten MNPs, each with two electric dipoles, resulting in twenty collectivel electric modes, two of which were magnetic in character.
+For the two-mer, there are ten MNPs, each with two electric dipoles, resulting in twenty collectivel electric modes, two of which were magnetic in character.
 In the magnetic dipole basis, because there are two rings, there are only two modes - the magnetic modes.
 This simplifies the data analysis procedures greatly.
-We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in figure (whatever), the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly.
+We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in Figure~\ref{ring_spacing}, the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly.
 We find, furthermore, that truncating to nearest or next-nearest neighbors in the magnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models.
@@
 The significant challenge here is to find a colloquial, qualitative, and accurate way to describe extended systems.
-By considering the magnetic dimer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
-Here, however, the atoms are the rings of the dimer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
+By considering the magnetic two-mer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
+Here, however, the atoms are the rings of the two-mer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
 More on this model will be presented later.
@@
 Thus, magnetic plasmon oligomers will be more likely to behave quasistatically when large.
-In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic dimers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
+In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic two-mers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
 The results show that when highly screened, even large magnetic plasmon oligomers behave quasistatically.
@@
 \includegraphics{diel_magnetization.pdf}
-\caption{Pending.}
+\caption{Two measures of the impact of dielectric background on the energy ordering of magnetic modes.
+In panel A, the difference in energy between the NN and NS modes is plotted for four scale factors as a function of background dielectric constant.
+This shows that as the dielectric background becomes more opaque, the constituent particles are screened from each other and the two-mer behaves quasistatically.
+Panel B shows the net magnetization of a periodic chain of six-membered rings at multiple values of epsilon.
+This again shows that as the constituent particles are screened from each other, the collective behavior becomes more quasistatic.
+Significantly, this plot also exhibits the property of extended magnetic systems to ``turn on'' their magnetic response within certain size regimes.}
 \label{diel_eff}
@@
 \end{equation} 
- responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
-For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$.
+ responds to the incident electric field defined by $\nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
+For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$ with $\omega$ the field frequency, $N$ the number of particles in the ring, and $\mu_{0}$ the background permeability.
 We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where
@@
 \begin{equation}
-\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
+\textrm{\textbf{m}} = -\frac{i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
 \label{magneticmoment}
 \end{equation}
-is the magnetic dipole moment. From these equations, we find that
+is the magnetic dipole moment of a ring of radius $R$. From these equations, we find that
 
@@
 The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.
+Here $N_{d}$ is the number density of rings per unit volume, and $k = \frac{\omega}{c}$ is the wavenumber in the medium.
 
@@
 This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$.
-The dipole moment on each particle is as above in Eq.
-\equation{dipolemoment}.
+The dipole moment on each particle is as above in Eq.~\ref{dipolemoment}.
 Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$.
@@
 \begin{equation}
-\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
+\alpha_{E} = \frac{N\alpha_{sp}}{\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
 \label{alphaE}
@@
 From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$.
-The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
-A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.
+The index of refraction of such a material is given by $n = \sqrt{\varepsilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
 
-Repeat this for more complicated unit cells! (twomer + sixmer) 
-\section{Same as above, but qds}
+\begin{figure}
+\begin{center}
+\includegraphics{contour_n_plot.pdf}
+\caption{Contour plots of the real index of refraction of a periodic array of one-mer unit cells (A) and two-mer unit cells (B) as a function of energy and scale factor.
+The blue slices of the plots indicate the regions in which an extended material would exhibit a negative index of refraction.}
+\label{onemer_twomer_n}
+\end{center}
+\end{figure}
+
+Extending this concept to more complicated unit cells leads to similar results.
+Figure~\ref{onemer_twomer_n} shows plots of index of refraction for unit cells composed of one ring (A) and two rings (B) as a function of energy and scale factor.
+The figures show that at certain sizes materials made of periodic arrays of these unit cells will exhibit a negative index of refraction.
+This becomes more apparent when a larger unit cell is used, such as the sixmer from Cherqui's work\cite{Cherqui2014}.
+So far, the model used to determine the index of refraction does not recover the same quantitative accuract as the tight-binding model.
+However, it offers a powerful qualitative picture to show that a material composed of particles of a certain size will exhibit a negative index of refraction over a small range of colors.
+
+\section{works in progress}
+I'd like to get plots of the index of refraction as a function of a) ring spacing and b) dielectric background. I think people in the field will care about this.
+\section{To-do list}
+Quantum dots: I don't think small, low-density quantum dots have an appreciable magnetic moment, and thus won't have a negative index of refraction.
+Everything I've computed so far doesn't have a negative index.
+Let's talk about this.
+Constructing lenses, calculating transmittance/refelctance: Not sure how to do these calculations or if I should save them for future work.
+The sixmer: I'd love to talk more about my work with the sixmer. I've computed its indeces of refraction, but I'm not sure how to put all of the information together.
 
@@
 Equipped with an understanding of how information propagates along these materials and how to actively influence that information, we are now in a position to study large chains and arrays of magnetic plasmon oligomers.
-By combining these theoretical studies with existing experimental techniques, there exist ways to directly inlfuence the propagation of information in real time, leading to new applications in detection mechanisms and perhaps leading to a new kind of plamsonic ``circuit.'' What remains is to understand the dynamics of these systems from a theoretical perspective, an exercise which is left for future studies.
+By combining these theoretical studies with existing experimental techniques, there exist ways to directly inlfuence the propagation of information in real time, leading to new applications in detection mechanisms and plamsonic information propagation.
+Furthermore, we have shown that extended networks of magnetic plasmon oligomers exhibit a negative index of refraction at optical frequencies.
+Future studies will elucidate the capabilities of materials designed using the knowledge gained in this exploration.
 

### 2017-02-15 polarizability_nonsense/diagonalize_polarize.py

@@ -234,28 +234,9 @@ for r in range(1,30):
 	plt.plot(frequency,np.real(total_n))
 	plt.show()
 
-<<<<<<< HEAD
+
 	real_n.append(np.real(total_n))
 	imag_n.append(np.imag(total_n))
-=======
-	np.savetxt('real_n_onemer',np.real(total_n))
-	np.savetxt('imag_n_onemer',np.imag(total_n))
-	'''ring_loc = []
-	array_size = [10,1]
-	for y_hop in range(0,array_size[1]):
-		x_pos = y_hop*mag_x/2.
-		y_pos = y_hop*mag_y
-		for x_hop in range(0,array_size[0]):
-			x_pos = x_pos + x_hop*mag_x
-			ring_loc.append([x_pos,y_pos])
->>>>>>> af6f383c912738fc30946f22fe41147088780df4
 
-	np.savetxt('real_n',real_n)
-	np.savetxt('imag_n', imag_n)
-
-	
-
-
-
-
-
+np.savetxt('real_n_onemer',np.real(real_n))
+np.savetxt('imag_n_onemer',np.imag(real_n))

### 2017-02-15 polarizability_nonsense/sixmer_polarize.py

@@ -1,0 +1,280 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+ll = 1
+real_n = []
+imag_n = []
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+dipole = [] # doubly degenerate
+no_dipole = [] # doubly degenerate
+all_N = [] #all north
+out_N_in_S = [] # that weird "excited state"
+alt_NS = [] # maximally out of phase magnets
+center = np.zeros(7,dtype=object)
+frequency = np.linspace(1,6,1001)
+for r in range(1,30):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 24; #number of particles
+	a0 = r*10**-7; #sphere radius in cm
+	index = (r*10)
+	''' now determine geometry.'''
+	rad = 2.2*a0
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),np.array([0,-2*e1]),
+		   np.array([e2,-e1]),np.array([e2,e1]),np.array([2*e2,2*e1]),np.array([3*e2,e1]),
+		   np.array([3*e2,-e1]),np.array([2*e2,-2*e1]),np.array([2*e2,-4*e1]),np.array([e2,-5*e1]),
+		   np.array([0,-4*e1]),np.array([-e2,-5*e1]),np.array([-2*e2,-4*e1]),np.array([-2*e2,-2*e1]),
+		   np.array([-3*e2,-e1]),np.array([-3*e2,e1]),np.array([-2*e2,2*e1]),np.array([-2*e2,4*e1]),
[…]

### 2017-02-15 polarizability_nonsense/twomer_polarize.py

@@ -56,17 +56,83 @@ for r in range(1,30):
 
 	freq_eps = epsinf - ((9.1)**2)/(np.square(frequency)+(0.05j)*frequency)
 	#print freq_eps
-	freq_alpha = (a0**3 )* ll*(freq_eps - epsb)/((ll*(freq_eps + epsb)) + epsb)
-	alpha_mlwa = freq_alpha/(1-((2.0/3.0)*1j*((frequency/c)*(elec/hbar))**3)*freq_alpha - ((frequency/c * elec/hbar)**2)*freq_alpha/a0)
+	freq_alpha = 4*math.pi*(a0**3 )* ll*(freq_eps - epsb)/((ll*(freq_eps + epsb)) + epsb)
+	alpha_mlwa = freq_alpha/(1-((1.0/(6.0*math.pi))*1j*((frequency/c)*(elec/hbar))**3)*freq_alpha - ((frequency/c * elec/hbar)**2)*freq_alpha/(a0*4*math.pi))
 	wsp_0 = (mie_omegas[mie_index])*elec/hbar
 	'''initialize w_0 and eigen'''
 	w_0 = wsp_0
 	alphasp_stat = ((a0**3)*3)/(epsinf+2)
-
+	eigen = np.zeros(2*numPart)
+	count = 1
+	H = np.zeros((2*numPart,2*numPart))
+	while np.sqrt(np.square(w_0*hbar/elec - eigen[2*numPart-1])) > 0.00000001:
+		if count == 1:
+			w_0 = wsp_0
+			count = count + 1
+			wsp = wsp_0
+		else:
+			count = count + 1
+			w_0 = eigen[2*numPart-1]*elec/hbar
+			#if w_0 > wsp:
+			#	w_0 = 3.5*elec/hbar
+			msp = (ch**2)/(alphasp_mlwa*((wsp)**2)); # sp mass (grams)
+			tau = (2*ch**2)/(3*msp*c**3) # radiation damping time
+			gamma_ret = gamma+tau*(w_0**2) # I pulled this from the beats paper
+			#print gamma_ret
+			gamma_eV = gamma_ret*hbar/elec
+			wsp = math.sqrt((wsp_0)**2 - (gamma_ret/2)**2);
+		print eigen[2*numPart-1]
+		eps_sp = epsinf - ((wsp**2))/((w_0**2)-1j*w_0*gamma)
[…]

### 2017-02-15 quantum_dots/eps_plotter.py

@@ -1,7 +1,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-data = np.loadtxt('epsilon_den_0.15_rad_10.0')
+data = np.loadtxt('density_0.15/epsilon_den_0.15_rad_10.0')
 
 plt.figure()
 plt.plot(data[0],data[1],data[0],data[2])

### 2017-02-15 quantum_dots/qd_polarize.py

@@ -1,0 +1,232 @@
+import numpy as np
+import scipy
+import math
+import matplotlib.pyplot as plt
+import string
+
+# make six particles
+for den in np.linspace(0.4,0.4,1):
+	
+	frequency = np.linspace(0,2,201) # we will need this later
+	real_n = []
+	imag_n = []
+
+	''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+	for r in np.linspace(1.5,10,35):
+		dielectrics = np.loadtxt('density_' + str(den) + '/epsilon_den_' + str(den) + '_rad_' + str(r))
+		#print dielectrics[2]
+		freq_index, maximum = max(enumerate(dielectrics[2]), key=lambda item: item[1])
+		print dielectrics[0][freq_index]
+		elec = 1.60217662e-19 # regular coulombs
+		numPart = 6 #number of particles
+		a0 = r*10**-7 #sphere radius in cm
+		ll = 1
+		''' now determine geometry.'''
+		''' begin with electric dipoles on the six-member ring '''
+		# make unit vectors in centimeters.
+		e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+		mag_x = 2*e2
+		mag_y = 3*e1
+		rad = 2.2*a0
+		Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
+			   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
+		#pol_vectors = [np.array([-1/math.sqrt(3),0]),np.array([-0.5/math.sqrt(3),-math.sqrt(3)/2/math.sqrt(3)]),np.array([0.5/math.sqrt(3),-math.sqrt(3)/2/math.sqrt(3)]),
+			   		   #np.array([1/math.sqrt(3),0]),np.array([0.5/math.sqrt(3),math.sqrt(3)/2/math.sqrt(3)]),np.array([-0.5/math.sqrt(3),math.sqrt(3)/2/math.sqrt(3)])]
[…]

### 2017-05-12 may_paper/draft_2.0.tex
new paper

--- 2017-02-13 paper/draft.tex
@@
 \title[]
-    {Towards Tunable Negative-Index Metamaterials}
+    {A Simple Model for Small Collections of Magnetic Plasmonic Oligomers}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
+Metal nanoparticles (MNPs) support collective resonances of thier conductions electrons at optical frequencies.
+These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies of two or more MNPs to produce hybridized resonances of the assembly, much like the hybridization of atomic orbitals in molecules.
+When these assemblies are arranged in rings, the single LSPRs can give rise to a fictitious, oscillating current which produces an oscillating magnetic dipole inside of the ring.
+Such systems are known as magnetic plasmon oligomers.
+
+Magnetic plasmon oligomers have been of intense focus due to their potential applications in sensing, lensing, cloaking, and information processing.
+In a recent paper, Engheta \textit{et al}.
+state that magnetic systems are well-understood on the single oligomer scale and the nearly infinite scale.
+[\textbf{CITE Engheta 2017}] However, the properties of collections of few magnetic oligomers have not been fully explored.
+Much work has been done to elucidate the properties of long chains and large arrays of magnetic oligomers.
+[\textbf{lots of Halas cites, probably}] The work of Cherqui \textit{et al}.
+has shown the properties of magnetic systems comprising one, two, and six rings.
+Furthermore, the dependence of the magnetic properties of the systems on individual nanoparticle geometry, and the relative size of the constituent oligomers has also been determined.
+This formative work has explained much of the physics behind magnetic plasmons, but it has also raised an interesting problem.
+
+In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to determine the eigenmodes of the magnetic systems.
+This model maps each  considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions.
+For one-ring systems, hereafter called monomers, the lowest energy eigenmode was determined to be the magnetic mode.
+For the two-ring system, called a twomer, the lowest- and second-lowest-energy modes were determined to be an out-of-phase magnetic mode and an in-phase magnetic mode, respectively.
+However, in confiring their results with full-wave simulations, they found a discrepancy.
+While the tight-binding model accurately described the eigenmodes, it inaccurately described their energy-ordering.
+The simulations placed the in-phase magnetic mode lower in energy than the out-of-phase mode, opposite the ordering of the tight-binding model.
+An explanation was needed to determine why this result, while counterintuitive, was in fact physical.
+
+The simulations were carried out on very large magnetic oligomers: the constituent particles were hundreds of nanometers across, and the overall oligomers were therefore nearly micron sized.
+It is well known that in large nanoparticles and over large distances, the quasistatic approximation begins to fail and the intermediate- and far-fields must be considered in order to accurately describe the optical properties.
+In this paper, we show that this apparent discrepancy is not only expected, but is rectifiable through expanding the tight-binding model to include all inter-particle interactions and the fully retarded electric field.
+Furthermore, we show that for small, multi-oligomer systems, the size, spacing, and environment greatly impact the eigenspectrum and the ordering of magnetic modes, leading to a high degree of tunability.
+We show this by building into our model a means to continuously manipulate the scale, interparticle distance, and embedding dielectric constant of each magnetic system.
+Finally, we recommend ways that this tunability might be enhanced and exploited in future studies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% OLD INTRO, SAVE FOR CITES %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Bringing two or more metal nanoparticles (MNPs) together allows their individual electric plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
@@
 
-The calculations presented here are performed using an electric tight-binding model, parametrizing the magnetic couplings, and then introducing these coupling constants into a magnetic tight-binding model.
-For all following magnetic oligomers, only the two planar dipoles per particle are considered in the electric tight binding model.
-The dipoles are mapped onto a set of harmonic oscillators and are described by the following Hamiltonian:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Back to regularly scheduled programming %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The tight-binding model used in this work maps each electric dipole plasmon onto a harmonic oscillator and allows them to interact through the fully retarded dipole-dipole coupling.
+The system Hamiltonian is
 
 \begin{equation}
-H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{\textrm{full},ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
+H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
 \end{equation}
 
-where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{\textrm{full},ij}$ is the fully retarded dipole-dipole relay tensor (expanded below).
+where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below).
 To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$.
-Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{\textrm{full},ij}$, we get:
+Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:
 
@@
 It should be noted that this Hamiltonian, when diagonilzed, results in a transcendental equation.
-The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues of the eigenvectors.
+The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues are functions of themselves.
 In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues.
@@
 \section{results and discussion}
-The first systems we examine are a magnetic dimer\cite{Cherqui2014}, a three-ring chain, and three rings arranged in a triangle.
+
+We explore and manipulate three magnetic oligomer systems in this work: a twomer, a three-ring chain, and three rings arranged in a triangle.
+In each manipulation, the particles have radius $r_0$ and interparticle spacing $r_{ij}$.
+In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model.
+The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system.
+In these manipulations, the nearest neighbor distances are held at $r_{ij} = 3 \mtimes r_0$ while $r_0$ varies from 1 nm to 30 nm.
+
+In Figure~\ref{magmodes}a, the magnetic mode eigenvalues are computed for each system.
+The solid lines depict model calculations, and the dashed lines depict simulated results.
+Interestingly, the magnetic modes exhibit a dynamic energy ordering, switching order twice as a function of scale.
+It is presumable that they continue to flip at larger and larger sizes.
+This is confirmed by simulations, with the model overestimating the eigenvalues by about 0.6\% and underestimating the crossing points by under a nanometer.
+These small errors are consistent across all three systems.
+Figure~\ref{magmodes}b displays the computed interaction strength for each eigenmode produced by the tight-binding model.
+In other words, we have plotted $\sum_{i>j}\textbf{p}_{i}\cdot\textbf{E}$ where $\textbf{p}_{i}$ is an eigenvector and $\textbf{E}$ is the field produced by the other dipoles.
+
+\begin{figure}
+\centering
+\includegraphics[width=.65\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
+\caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (\
+column b) for the magnetic twomer (first row), threemer chain (second row), and threemer ring (thir\
+d row). All of the magnetic modes range from ~3.6 eV to ~3.1 eV. In each system, the magnetic modes\
+ exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on th\
+eir scale. The model consistently overestimates the eigenvalues by 0.5 eV, and consistently underes\
+timates the crossing points by less than a nanometer. The twomer has two magnetic modes, one in-pha\
+se mode (blue trace) and one out-of-phase mode (orange trace). The threemer chain has three modes, \
+an in-phase mode (blue trace), a minimally out-of-phase mode (orange trace), and a maximally out-of\
+-phase mode (green trace). The threemer ring exhibits three magnetic modes, but the out-of-phase mo\
+des (orange trace) are degenerate so only one is depicted. The other mode is a maximally in-phase m\
+ode (blue trace). To further emphasize the impact of scale, we have plotted the total interaction s\
+trength of each eigenmode, \textit{i.e.} the sum of each eigenvector's dot product with the electri\
+c field of all of the other dipoles. This calculation reaffirms the scale dependence and predicts m\
+ode crossings at the same scale as both the eigenvalue calculation and the simulations.}
+\label{fig:magmodes}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.65\paperwidth]{dielectric_study.png}
+\caption{Magnetic mode eigenvalues for twomers (first row), threemer chains (second row), and threemer rings (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a func
+tion of the dielectric constant of an embedding medium. As the dielectric constant is increased from 1 to 3, the magnetic mode splitting decreases and the overall energy decreases. At very hi
+gh dielectric values, the magnetic mode eigenvalues converge to the single particle resonance frequency. This can be explained by the increasing opacity of the medium effectively screening in
+ter-particle interactions. It is also important to note that between $\varepsilon_b = 1$ and $\varepsilon_b = 1.5$, the magnetic modes flip order. Thus, the increasing opacity of the medium e
+ffectively decreases the scale of the system.}
+\label{fig:dielectric}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.65\paperwidth]{spacing_study.png}
+\caption{Magnetic mode eigenvalues for twomers (first row), threemer chains (second row), and threemer rings (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a func
+tion of nearest neighbor particle spearation. The separation is plotted as a function of the particle size, in units of radii. It is important to note that as the separation distance increase
+s, the magnetic modes cross multiple times and their eigenvalues converge to, and oscillate about the single particle frequency. This is a result of the decreasing interaction strength. In th
+e limit of particles infinitely far away from each other, their interaction stength is zero. The oscillating nature of the eigenvalues is a result of the complex exponential dependence of the
+ fields.}
+\label{fig:spacing}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.65\paperwidth]{dimer_interaction.png}
+\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d). Plotted are 
+the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance. Interes
+tingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles. From these plots, it can be seen that the favorability 
+of a specific dipole arrangement depends on the separation between the dipoles. This can be seen in the fact that each part of the field depends differently on the separation, and each field 
+term contains an oscillating term. At short length scales, the interaction is dominated by the near-field. However, as the distance increases, the interaction is dominated by the intermediate
+-field (a and c) or the far-field (b and d).
+As a result, there are separation distances at which normally unfavorable arrangements become favorable.
+Since magnetic oligomers can be describe through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
+\label{fig:dimers}
+\end{figure}
+
+The first systems we examine are a magnetic two-mer\cite{Cherqui2014}, three-mer chain, and three-mer triangle.
 Because we are interested in the effects of scale, we must define a scaling parameter for the system.
-Each of our systems begins from a unit cell: six silver, spherical MNPs placed at the corners of a regular hexagon.
-To create the dimer, two unit cells are tiled so that they share an edge, and thus two particles.
+Each of our systems begins from a unit cell called the one-mer: six silver, spherical MNPs placed at the corners of a regular hexagon.
+To create the two-mer, two unit cells are tiled so that they share an edge, and thus two particles.
 In general, if any two unit cells share an edge, they also share two nanoparticles, as in the diagrams in Figure~\ref{theory_simul} Each particle has radius $a_0$ and particles are separated by lattice spacing $r=2.2\times a_0$.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics{theory_bem_comparison_fig1.pdf}
-\caption{Pending.}
-\label{theory_simul}
-\end{center}
-\end{figure}
-
 The results of our theoretical calculations and full-wave simulations for the aforementioned oligomers are dispayed in Figure~\ref{theory_simul}.
 Both theory and simulation predict that as a function of size, the energy ordering of the magnetic plasmon modes should change.
-In the dimer system, there are two magnetic modes.
+In the two-mer system, there are two magnetic modes.
 When the system is small, the lowest energy mode is the alternating north-south (NS) mode and the in-phase north-north mode is highest.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics{twomer_dimer.pdf}
-\caption{Pending.}
-\label{twomer_dimer}
-\end{center}
-\end{figure}
-
 This is an unexpected phenomenon.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics{interactions.pdf}
-\caption{Pending.}
-\label{int_strength}
-\end{center}
-\end{figure}
-
 To gain a more visual and intuitive sense of the length scales of each of the terms (near, intermediate, and far) in the fully retarded electric field of a dipole (found in the coupling terms of Equation~\ref{elec_hammy_2}), we calculated the relative interaction strength between pairs of dipoles (the collective modes of the sphere dimer) as a function of dipole separation distance.
@@
 Significantly, the interaction strengths display oscillatory motion, which confirms and reinforces past studies on the oscillatory nature of radiation damping.\cite{vonPlessen2007}
-
-\begin{figure}
-\begin{center}
-\includegraphics{coupling_comparison.pdf}
-\caption{Pending.}
-\label{ring_spacing}
-\end{center}
-\end{figure}
 
@@
 The significant challenge here is to find a colloquial, qualitative, and accurate way to describe extended systems.
-By considering the magnetic dimer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
-Here, however, the atoms are the rings of the dimer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
+By considering the magnetic two-mer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
+Here, however, the atoms are the rings of the two-mer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
 More on this model will be presented later.
 
-\section{Dielectric Background and a Measure of Quasistaticity}
+\section{Dielectric Background}
 
@@
 Thus, magnetic plasmon oligomers will be more likely to behave quasistatically when large.
-In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic dimers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
+In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic two-mers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
 The results show that when highly screened, even large magnetic plasmon oligomers behave quasistatically.
-
-\begin{figure}
-\begin{center}
-\includegraphics{diel_magnetization.pdf}
-\caption{Pending.}
-\label{diel_eff}
-\end{center}
-\end{figure}
 
@@
 
-\section{Periodic Arrays of Rings - Permeability, Permittivity, and Index of Refraction}
-To determine the permeability, permittivity, and index of refraction of the six-member ring that is the unit cell, we follow Alu and Engheta\cite{Alu2006}.
-Preparing the magnetic mode of the six-member ring induces a dipole moment on each particle.
-The dipole moment of a particular particle,
-
-\begin{equation}
-\textrm{\textbf{p}}_{i} = p\hat{\textrm{\textbf{p}}}_{i} = \alpha_{sp}\left(\textrm{\textbf{E}}_{0} + p\sum_{i\neq j}\boldsymbol{\Lambda_{ij}}\cdot\hat{\textrm{\textbf{p}}}_{i}\right)
-\label{dipolemoment}
-\end{equation} 
- responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
-For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$.
-We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where
-
-\begin{equation}
-\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
-\label{magneticmoment}
-\end{equation}
-is the magnetic dipole moment. From these equations, we find that
-
-\begin{equation}
-\alpha_{M} = \frac{(kR)^{2}N}{4\varepsilon_{b}}\left(\frac{\alpha_{sp}}{1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j} }\right)
-\label{alphaM}
-\end{equation}
-
-The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.
-
-To compute the effective permittivity of the same ring of nanoparticles, the unit cell is prepared in a uniform electric field.
-This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$.
-The dipole moment on each particle is as above in Eq.
-\equation{dipolemoment}.
-Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$.
-This polarizability governs the total electric response of the ring to an electric field, as opposed to the polarizability of a single particle, and is given by
-
-\begin{equation}
-\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
-\label{alphaE}
-\end{equation}
-
-From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$.
-The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
-A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.
-
-Repeat this for more complicated unit cells! (twomer + sixmer) 
-\section{Same as above, but qds}
-
 \section{Conclusion}
@@
 \begin{acknowledgement}
-CEI, NSF, DOE, Niket, some other people, probably
+CEI, NSF, DOE?, Niket, some other people, probably
 \end{acknowledgement}

### 2017-05-12 may_paper/paper.tex
new paper

--- 2017-02-13 paper/draft.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=apchd5,manuscript=article]{achemso}
+\documentclass[journal=ancac3,manuscript=article]{achemso}
 
@@
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{xcolor}
-\usepackage{wrapfig}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author{Charles Cherqui}
-\affiliation[Department of Chemistry, University of Washington]
-{Department of Chemistry, University of Washington, Seattle, WA 98195}
 \author{David J. Masiello}
-\affiliation[Department of Chemistry, University of Washington]
-{Department of Chemistry, University of Washington, Seattle, WA 98195}
-\alsoaffiliation[Department of Applied Mathematics, University of Washington]
-{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
 \email{masiello@chem.washington.edu}
+\phone{}
+\fax{}
+\affiliation[University of Washington]
+{Department of Chemistry, University of Washington, Seattle, WA}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title[]
-    {Towards Tunable Negative-Index Metamaterials}
+\title{On the Behavior of Small Collections of Magnetic Plasmonic Oligomers}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abbreviations{MNP, LSPR, EELS}
-\keywords{plasmon, hybridization, magnetic, retardation}
+\abbreviations{LSPR, MNP}
+\keywords{plasmon, magnetic plasmon}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The abstract environment will automatically gobble the contents
-%% if an abstract is not used by the target journal.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials.
-Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing.
-For these reasons, it is imperative to understand the properties of such systems on both small and large scales.
-We show through theory and simulation that the energy ordering of the magnetic resonances of small oligomers depends greatly on the size and scale of the nanoparticle assembly in ways that purely electric plasmons do not.
-Following this, we determine the effective pemeability and permittivity of periodic arrays of nanoparticles and show that in certain size regimes they exhibit a negative index of refraction at optical frequencies.
-As a final exercise, we propose a negative-index material composed of charge tunable semiconductor quantum dots to emphasize the direct control of the optical properties of 2-D magnetic materials.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Bringing two or more metal nanoparticles (MNPs) together allows their individual electric plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
-Plasmon hybridization theory is applied to aggregates of MNPs and explains their collective behavior within the quasistatic limit in which the speed of light is taken to be infinite\cite{NordHal2003,NordProdan2004,Oubre2004,Gomez2009}.
-Recently, retardation effects on plasmon hybridization have been the focus of study for large particles\cite{Abajo2008,Gu2010} as well as dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and 2-D arrays\cite{Schatz2003,Royer2005,Chumanov2010} of nanoparticles.
-Specific arrangements of nanoparticles in 2-D arrays, such as three or more nanoparticles arranged on the vertices of a regular polygon, support a collective mode in which all of the dipole plasmons are oriented head-to-tail.
-This generates a fictitious, oscillating current loop resulting in an oscillating magnetic dipole moment in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}.
-These so-called magnetic plasmons are the lowest-energy collective modes of the oligomers and couple to and enhance the magnetic field of incident light\cite{Shalaev2007,Qian2015,Nord2007}, offering a route to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.
-The rich plasmonic modes of magnetic-plasmon-supporting systems are well-described using plasmon hybridization theory, but when in the quasistatic limit, the energy-order of the modes is not.
-
-Plasmon hybridization theory treats plasmons as point dipoles centered on their associated nanoparticles that interact through dipole-dipole coupling.
-In the quasistatic limit, these dipoles couple only through time-independent, electric near-field interactions\cite{jackson_classical_1999}, but when the size of and distance between nanoparticles becomes large, this approximation breaks down and intermediate- and far-field effects must be considered, as well as time-delay effects in the near-field\cite{jackson_classical_1999}.
-The aim of this paper is to incorporate the fully retarded electric field into plasmon hybridization theory and extend studies of retardation effects to magnetic plasmon oligomers.
-Specifically, we begin by exploring oligomers comprising two and three rings of nanoparticles and compare to full-wave simulation \cite{Hohenester2012} to verify that our approach qualitatively predicts the energy-ordering of the magnetic modes.\cite{Cherqui2014,Cherqui2016}.
-Following this, we calaculate the coupling betwen individual rings in various oligomers in order to parametrize an effective magnetic-magnetic coupling between magnetic dipoles.
-Using this new basis, we describe periodic chains and arrays of oligomers.
-
-The calculations presented here are performed using an electric tight-binding model, parametrizing the magnetic couplings, and then introducing these coupling constants into a magnetic tight-binding model.
-For all following magnetic oligomers, only the two planar dipoles per particle are considered in the electric tight binding model.
-The dipoles are mapped onto a set of harmonic oscillators and are described by the following Hamiltonian:
-
-\begin{equation}
-H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{\textrm{full},ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
-\end{equation}
-
-where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{\textrm{full},ij}$ is the fully retarded dipole-dipole relay tensor (expanded below).
-To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$.
-Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{\textrm{full},ij}$, we get:
-
-\begin{equation}
-\begin{aligned}
-H = 
-\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
-+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
-- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
-\end{aligned}
-\end{equation}
-
-In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}}{r_{ij}^3}\cos\left(\frac{\omega r_{ij}}{c}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}\omega}{r_{ij}^2 c}\sin\left(\frac{\omega r_{ij}}{c}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}\omega^2}{r_{ij} c^2}\cos\left(\frac{\omega r_{ij}}{c}\right)$, respectively.
-Additionally, the polarizability $\alpha_{sp} = \frac{e^2}{m_{sp}\omega_{sp}^2}$, $r_{ij}$ is the distance between the ith and jth LSPs, and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPs.
-Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973}.
-
-It should be noted that this Hamiltonian, when diagonilzed, results in a transcendental equation.
-The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues of the eigenvectors.
-In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues.
-Using the eigenvalue associated with the mode of interest, the Hamiltonian is diagonalized to convergence.
-The process is repeated for each mode of interest.
-
-\section{results and discussion}
-The first systems we examine are a magnetic dimer\cite{Cherqui2014}, a three-ring chain, and three rings arranged in a triangle.
-Because we are interested in the effects of scale, we must define a scaling parameter for the system.
-Each of our systems begins from a unit cell: six silver, spherical MNPs placed at the corners of a regular hexagon.
-To create the dimer, two unit cells are tiled so that they share an edge, and thus two particles.
-In general, if any two unit cells share an edge, they also share two nanoparticles, as in the diagrams in Figure~\ref{theory_simul} Each particle has radius $a_0$ and particles are separated by lattice spacing $r=2.2\times a_0$.
-With the radius of the particles defining the scale of the system, there now exists a way to probe the energy ordering of the modes as a function of size.
+\begin{figure}
+\centering
+\includegraphics[width=.65\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
+\caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (column b) for the magnetic twomer (first row), threemer chain (second row), and threemer ring (third row).
+All of the magnetic modes range from ~3.6 eV to ~3.1 eV.
+In each system, the magnetic modes exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on their scale.
+The model consistently overestimates the eigenvalues by 0.5 eV, and consistently underestimates the crossing points by less than a nanometer.
+The twomer has two magnetic modes, one in-phase mode (blue trace) and one out-of-phase mode (orange trace).
+The threemer chain has three modes, an in-phase mode (blue trace), a minimally out-of-phase mode (orange trace), and a maximally out-of-phase mode (green trace).
+The threemer ring exhibits three magnetic modes, but the out-of-phase modes (orange trace) are degenerate so only one is depicted.
+The other mode is a maximally in-phase mode (blue trace).
+To further emphasize the impact of scale, we have plotted the total interaction strength of each eigenmode, \textit{i.e.} the sum of each eigenvector's dot product with the electric field of all of the other dipoles.
+This calculation reaffirms the scale dependence and predicts mode crossings at the same scale as both the eigenvalue calculation and the simulations.}
+\label{fig:magmodes}
+\end{figure}
 
 \begin{figure}
-\begin{center}
-\includegraphics{theory_bem_comparison_fig1.pdf}
-\caption{Pending.}
-\label{theory_simul}
-\end{center}
+\centering
+\includegraphics[width=.65\paperwidth]{dielectric_study.png}
+\caption{Magnetic mode eigenvalues for twomers (first row), threemer chains (second row), and threemer rings (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of the dielectric constant of an embedding medium.
+As the dielectric constant is increased from 1 to 3, the magnetic mode splitting decreases and the overall energy decreases.
+At very high dielectric values, the magnetic mode eigenvalues converge to the single particle resonance frequency.
+This can be explained by the increasing opacity of the medium effectively screening inter-particle interactions.
+It is also important to note that between $\varepsilon_b = 1$ and $\varepsilon_b = 1.5$, the magnetic modes flip order.
+Thus, the increasing opacity of the medium effectively decreases the scale of the system.}
+\label{fig:dielectric}
 \end{figure}
 
-The results of our theoretical calculations and full-wave simulations for the aforementioned oligomers are dispayed in Figure~\ref{theory_simul}.
-Both theory and simulation predict that as a function of size, the energy ordering of the magnetic plasmon modes should change.
-In the dimer system, there are two magnetic modes.
-When the system is small, the lowest energy mode is the alternating north-south (NS) mode and the in-phase north-north mode is highest.
-When we add a ring to the system, we see a trend emerge.
-The alternating (NSN) mode is lower than the N-S mode, which is in turn lower than the NNN mode.
-As a function of size, the modes change order.
-The triangle system, as a result of its threefold symmetry (as opposed to twofold for the chains) has slightly different properties.
-At small size, its lowest energy mode is a pair of degenerate NS modes, while its higher energy mode is an all-north mode.
-These again switch order as a function of size.
-In chains with more than three rings, the pattern continues - the magnetic resonances with the most nodes between rings are the lowest energy when small, but the highest when large.
+\begin{figure}
+\centering
+\includegraphics[width=.65\paperwidth]{spacing_study.png}
+\caption{Magnetic mode eigenvalues for twomers (first row), threemer chains (second row), and threemer rings (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle spearation.
+The separation is plotted as a function of the particle size, in units of radii.
+It is important to note that as the separation distance increases, the magnetic modes cross multiple times and their eigenvalues converge to, and oscillate about the single particle frequency.
+This is a result of the decreasing interaction strength.
+In the limit of particles infinitely far away from each other, their interaction stength is zero.
+The oscillating nature of the eigenvalues is a result of the complex exponential dependence of the fields.}
+\label{fig:spacing}
+\end{figure}
 
 \begin{figure}
-\begin{center}
-\includegraphics{twomer_dimer.pdf}
-\caption{Pending.}
-\label{twomer_dimer}
-\end{center}
+\centering
+\includegraphics{dimer_interaction.png}
+\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d).
+Plotted are the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance.
+Interestingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles.
+From these plots, it can be seen that the favorability of a specific dipole arrangement depends on the separation between the dipoles.
+This can be seen in the fact that each part of the field depends differently on the separation, and each field term contains an oscillating term.
+At short length scales, the interaction is dominated by the near-field.
+However, as the distance increases, the interaction is dominated by the intermediate-field (a and c) or the far-field (b and d).
+As a result, there are separation distances at which normally unfavorable arrangements become favorable.
+Since magnetic oligomers can be described through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
+\label{fig:dimers}
 \end{figure}
 
-This is an unexpected phenomenon.
-When one considers the energy-order of the four (six) hybridized modes of the nanosphere dimer, it becomes clear that they do not exhibit this effect (Figure~\ref{twomer_dimer}).
-Notably, the sphere dimer shows no crossings while the oligomer dimer does.
-The reason for this outcome is the oligomer dimer's complex structure\cite{Cherqui2016}.
-The sphere dimer has only one length scale and consitutes only one pairwise interaction.
-However, the oligomer dimer contains many pairs of nanoparticles over multiple length scales.
-As a result, different configurations of electric dipoles will be favored at different oligomer sizes, hence the flip of the magnetic modes.
+\bibliography{references}
 
-\begin{figure}
-\begin{center}
-\includegraphics{interactions.pdf}
-\caption{Pending.}
-\label{int_strength}
-\end{center}
-\end{figure}
-
-To gain a more visual and intuitive sense of the length scales of each of the terms (near, intermediate, and far) in the fully retarded electric field of a dipole (found in the coupling terms of Equation~\ref{elec_hammy_2}), we calculated the relative interaction strength between pairs of dipoles (the collective modes of the sphere dimer) as a function of dipole separation distance.
-The results of these calculations are displayed in Figure~\ref{int_strength}, showing that at different length scales, different terms in the field contribute more to the energy of the system.
-Significantly, the interaction strengths display oscillatory motion, which confirms and reinforces past studies on the oscillatory nature of radiation damping.\cite{vonPlessen2007}
-
-\begin{figure}
-\begin{center}
-\includegraphics{coupling_comparison.pdf}
-\caption{Pending.}
-\label{ring_spacing}
-\end{center}
-\end{figure}
-
-With a functional and accurate electric dipole tight binding model, we seek a way to simplify our model.
-Figure~\ref{ring_spacing} displays the eigenvalue curves for three arrangements of two-ring systems, with the rings as (A) nearest neighbors (B) next-nearest neighbors and (C) next-next-nearest neighbors.
-It is clear that again, at different length scales and relative orientations, the eigenvalue curves behave differently, having different crossing points and energy ordering.
-Using these eigenvalue curves, the electric dipole model is transformed into a magnetic dipole model.
-A magnetic dipole is placed at the center of each ring with orientation perpendicular to the plane of the ring.
-Each dipole has natural frequency $\omega_{\textrm{M}}$, which we determine using the electric tight-binding model for a single ring.
-The coupling between each magnetic dipole is pulled from the plots in figure (w/e) - depending on the spacing between the rings, the dipoles couple through nearest, next-nearest, or next-next-nearest neighbor coupling.
-The Hamiltonian
-
-\begin{equation}
-H = \frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i}^{n}[\pi_{i}^{2}+q_{i}^{2}]+\frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i\neq j}g_{ij}^{\textrm{M}}q_{i}q_{j}
-\label{mag_hammy}
-\end{equation}
-
-is used in the same way as Equation~\ref{elec_hammy_2} - diagonalizing it for a set of $n$ magnetic dipoles produces $n$ collective magnetic modes.
-The benefit of this model is shown by example.
-For the oligomer dimer, there are ten MNPs, each with two electric dipoles, resulting in twenty collectivel electric modes, two of which were magnetic in character.
-In the magnetic dipole basis, because there are two rings, there are only two modes - the magnetic modes.
-This simplifies the data analysis procedures greatly.
-We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in figure (whatever), the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly.
-We find, furthermore, that truncating to nearest or next-nearest neighbors in the magnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models.
-It is this finding that will allow us the extension of the model to larger systems considering only nearest or next-nearest neigbor coupling.
-
-The significant challenge here is to find a colloquial, qualitative, and accurate way to describe extended systems.
-By considering the magnetic dimer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
-Here, however, the atoms are the rings of the dimer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
-More on this model will be presented later.
-
-\section{Dielectric Background and a Measure of Quasistaticity}
-
-As an additional exercise, and to emphasize the tunability and versatility of magnetic plasmon oligomers, the effect of the dielectric constant of the background ($\varepsilon_{b}$) is also taken into account.
-The dielectric constant screens the electric dipoles from each other by effectively weakening their induced electric fields.
-This means that as $\varepsilon_{b}$ gets large, intermediate and far field effects will weaken in comparison to near field contributions to the electric field.
-Thus, magnetic plasmon oligomers will be more likely to behave quasistatically when large.
-In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic dimers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
-The results show that when highly screened, even large magnetic plasmon oligomers behave quasistatically.
-
-\begin{figure}
-\begin{center}
-\includegraphics{diel_magnetization.pdf}
-\caption{Pending.}
-\label{diel_eff}
-\end{center}
-\end{figure}
-
-To extend this to a potential application, we consider now a periodic chain of magnetic monomers - essentially a 1-D system - with only nearest neighbor coupling.
-When the radii of the particles in the chain are small, the lowest energy collective mode of the chain will be an all-alternating magnetic mode, and when the radii are large it will be an all in-phase magnetic mode.
-A way to quantify this is through a measure of net magnetization.
-Diagonalizing the magnetic Hamiltonian [reference the equation], summing the eigenvectors, and dividing by n (the number of rings) gives a measure of whether the system is magnetized, and this is plotted as a function of particle radius in Figure~\ref{diel_eff}B.
-More importantly, the point at which the magnetization ``switches on'' can be controlled through the dielectric background.
-This gives rise to the ability of the experimentalist to directly introduce a phase-lag in an extended chain of magnetic oligomers by embedding certain segments of the chain in different materials.
-This is not so different from certain techniques that are being studied presently in the field\cite{odom_lasing}
-
-\section{Periodic Arrays of Rings - Permeability, Permittivity, and Index of Refraction}
-To determine the permeability, permittivity, and index of refraction of the six-member ring that is the unit cell, we follow Alu and Engheta\cite{Alu2006}.
-Preparing the magnetic mode of the six-member ring induces a dipole moment on each particle.
-The dipole moment of a particular particle,
-
-\begin{equation}
-\textrm{\textbf{p}}_{i} = p\hat{\textrm{\textbf{p}}}_{i} = \alpha_{sp}\left(\textrm{\textbf{E}}_{0} + p\sum_{i\neq j}\boldsymbol{\Lambda_{ij}}\cdot\hat{\textrm{\textbf{p}}}_{i}\right)
-\label{dipolemoment}
-\end{equation} 
- responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
-For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$.
-We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where
-
-\begin{equation}
-\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
-\label{magneticmoment}
-\end{equation}
-is the magnetic dipole moment. From these equations, we find that
-
-\begin{equation}
-\alpha_{M} = \frac{(kR)^{2}N}{4\varepsilon_{b}}\left(\frac{\alpha_{sp}}{1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j} }\right)
-\label{alphaM}
-\end{equation}
-
-The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.
-
-To compute the effective permittivity of the same ring of nanoparticles, the unit cell is prepared in a uniform electric field.
-This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$.
-The dipole moment on each particle is as above in Eq.
-\equation{dipolemoment}.
-Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$.
-This polarizability governs the total electric response of the ring to an electric field, as opposed to the polarizability of a single particle, and is given by
-
-\begin{equation}
-\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
-\label{alphaE}
-\end{equation}
-
-From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$.
-The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
-A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.
-
-Repeat this for more complicated unit cells! (twomer + sixmer) 
-\section{Same as above, but qds}
-
-\section{Conclusion}
-It has been shown that magnetic plasmon oligomers are a highly versatile, highly tunable material.
-The magnetic behavior of tesselated rings of nanoparticles is dependent on size, spacing, arrangement, and environment.
-Equipped with an understanding of how information propagates along these materials and how to actively influence that information, we are now in a position to study large chains and arrays of magnetic plasmon oligomers.
-By combining these theoretical studies with existing experimental techniques, there exist ways to directly inlfuence the propagation of information in real time, leading to new applications in detection mechanisms and perhaps leading to a new kind of plamsonic ``circuit.'' What remains is to understand the dynamics of these systems from a theoretical perspective, an exercise which is left for future studies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The ``Acknowledgement'' section can be given in all manuscript
-%% classes.  This should be given within the ``acknowledgement''
-%% environment, which will make the correct section or running title.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{acknowledgement}
-CEI, NSF, DOE, Niket, some other people, probably
-\end{acknowledgement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The appropriate \bibliography command should be placed here.
-%% Notice that the class file automatically sets \bibliographystyle
-%% and also names the section correctly.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{references}
 \end{document}

### 2017-05-12 old_papers/magret_draft_7.0/draft.tex
new paper

--- 2017-02-13 paper/draft.tex
@@
 \title[]
-    {Towards Tunable Negative-Index Metamaterials}
+    {Characterization of Magnetic Plasmons in Extended Metal Nanoparticle Oligomers}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We show through theory and simulation that the energy ordering of the magnetic resonances of small oligomers depends greatly on the size and scale of the nanoparticle assembly in ways that purely electric plasmons do not.
-Following this, we determine the effective pemeability and permittivity of periodic arrays of nanoparticles and show that in certain size regimes they exhibit a negative index of refraction at optical frequencies.
-As a final exercise, we propose a negative-index material composed of charge tunable semiconductor quantum dots to emphasize the direct control of the optical properties of 2-D magnetic materials.
+We verfiy that this is the result of retardation effects, and assert that any qualitatively accurate description of magnetic plasmons must incorporate retardation effects.
+We culminate this study with a parametrization of the fully retarded, magnetic-magnetic dipole coupling between oligomers, providing a route to characterizing extended chains and arrays of magnetic plasmon oligomers.
 \end{abstract}
@@
 \includegraphics{theory_bem_comparison_fig1.pdf}
-\caption{Pending.}
 \label{theory_simul}
@@
 \includegraphics{twomer_dimer.pdf}
-\caption{Pending.}
 \label{twomer_dimer}
@@
 \includegraphics{interactions.pdf}
-\caption{Pending.}
 \label{int_strength}
@@
 \includegraphics{coupling_comparison.pdf}
-\caption{Pending.}
 \label{ring_spacing}
@@
 We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in figure (whatever), the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly.
-We find, furthermore, that truncating to nearest or next-nearest neighbors in the magnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models.
+We find, furthermore, that truncating to nearest or next-nearest neighbors in the amgnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models.
 It is this finding that will allow us the extension of the model to larger systems considering only nearest or next-nearest neigbor coupling.
@@
 \includegraphics{diel_magnetization.pdf}
-\caption{Pending.}
 \label{diel_eff}
@@
 
-\section{Periodic Arrays of Rings - Permeability, Permittivity, and Index of Refraction}
-To determine the permeability, permittivity, and index of refraction of the six-member ring that is the unit cell, we follow Alu and Engheta\cite{Alu2006}.
-Preparing the magnetic mode of the six-member ring induces a dipole moment on each particle.
-The dipole moment of a particular particle,
+\section{A Zero-Temperature Ising Model}
+\textbf{THIS IS NOT FULLY THOUGHT-OUT AND THE MATH ISN'T DONE}
+Because we seek a way to characterize periodic systems of magnetic oligomers, and because magnetic dipoles in rings are much like spins on atoms, an Ising-like model is propsoed to qualify and quantify some properties.
+With resonant frequencies of ~3.0 eV, magnetic plasmons in general hae no thermal populations, so the Ising model must have another temperature-like parameter.
+The purpose of an Ising model is to comapre two properties of a system.
+The first property is the interaction strength between spins, which is determined, in the atomistic case, entirely by their separation distance (i.e., the scale of the system).
+In the case of magnetic plasmons, the interaction strength is also determined by other material properties of the rings.
+The other property the Ising model is concerned with is stochasticity, or the random fluctuations of the system.
+The Ising model takes into account the temperature of the environment, and this provides a source of random fluctuations.
+When the energy in the interactions is greater than the ambient energy in the environment, the systme is ordered.
+When the reverse is true, the system is disordered.
 
-\begin{equation}
-\textrm{\textbf{p}}_{i} = p\hat{\textrm{\textbf{p}}}_{i} = \alpha_{sp}\left(\textrm{\textbf{E}}_{0} + p\sum_{i\neq j}\boldsymbol{\Lambda_{ij}}\cdot\hat{\textrm{\textbf{p}}}_{i}\right)
-\label{dipolemoment}
-\end{equation} 
- responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
-For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$.
-We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where
+The obstacle to the Ising model for extended oligomer systems is that the temperatures that would induce thermal populations of plasmons are experimentally unreasonable.
+A zero-temperature Ising model, however would be a perfectly reasonable description of the system, and would allow for the calculation of descriptive properties such as the net magnetization and the spin-spin coupling.
+Some analogies could be amde to the concepts of ferromagnetism and antiferromagnetism - for instance, in long chains and arrays the major modes that switch are essentially an antiferromagnetic mode and ferromagnetic mode.
+So, we'd be using a new language to discuss the coupling terms.
 
-\begin{equation}
-\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
-\label{magneticmoment}
-\end{equation}
-is the magnetic dipole moment. From these equations, we find that
-
-\begin{equation}
-\alpha_{M} = \frac{(kR)^{2}N}{4\varepsilon_{b}}\left(\frac{\alpha_{sp}}{1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j} }\right)
-\label{alphaM}
-\end{equation}
-
-The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.
-
-To compute the effective permittivity of the same ring of nanoparticles, the unit cell is prepared in a uniform electric field.
-This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$.
-The dipole moment on each particle is as above in Eq.
-\equation{dipolemoment}.
-Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$.
-This polarizability governs the total electric response of the ring to an electric field, as opposed to the polarizability of a single particle, and is given by
-
-\begin{equation}
-\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
-\label{alphaE}
-\end{equation}
-
-From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$.
-The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
-A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.
-
-Repeat this for more complicated unit cells! (twomer + sixmer) 
-\section{Same as above, but qds}
+\section{Magnetic Band Structure of Extended Arrays}
+\textbf{I'M STILL WORKING ON THE MATH/CODING}
+Using the ``two-atom'' basis for the magnetic tight binding model, we attempt to calculate the magnetic band structure of extended sheets of magnetic oligomers.
+Because of the two-atom basis, only two bands will emerge.
+One will be an out-of-phase, zero net magnetization band, and the other will be an in-phase, non-zero net magnetization band.
+As a function of size, we expect to observe that these bands change order\cite{kogan2011,novoselov2012}.
+We may also be able to parallel these to acoustic and optical phonons, if I can think of how to do that.
 

### 2017-05-12 chains/anthracene_spacing.py

@@ -4,15 +4,11 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-bem_r = [1, 5, 10, 15, 20, 25]
-bem_NN = [3.616, 3.604, 3.558, 3.482, 3.402, 3.31]
-bem_NS = [3.61, 3.6, 3.568, 3.51, 3.416, 3.288]
-
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
-interaction = [[],[]]
+crossing = []
 elec = 1.60217662e-19 # regular coulombs
-numPart = 13; #number of particles
+numPart = 14; #number of particles
 me = 9.10938291e-28; # electron mass in g
 ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
 hbar = 1.054571726e-34; # modified Planck in J*s
@@ -25,24 +21,31 @@ Eplasma = 1.46599161e-18; # J
 gamma = 0.05*elec/(hbar*16)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 for epsb in range(1,2):
-	NN = []
-	NS = []
-	for r in range (1,31):
+	NNN = []
+	NSN = []
+	N_S = []
+	interaction = [[],[],[]]
+	#NSNS = []
+	r = 15
+	for dist in np.linspace(0,10,51):
+		NNN_count = 0
+		NSN_count = 0
+		N_S_count = 0
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
-		print r
+		print dist
+		#raw_input()
 		# make unit vectors in centimeters.
-		rij = 3*a0
-		e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
-		e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
-		Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),
-			   np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
-			   np.array([-e2, -2*e1]),np.array([0, -e1]),
-			   np.array([e2, -2*e1]),np.array([2*e2, -e1]),
[…]

### 2017-05-12 chains/chains.py

@@ -180,12 +180,16 @@ for epsb in range(1,2):
 	plt.figure()
 	plt.plot(r,NNN,r,NSN,r,N_S,r,NNN_smooth,r,N_S_smooth,r,NSN_smooth,linewidth=3)
 	plt.legend(['NNN','NSN','N-S','BEM NNN','BEM N-S','BEM NSN'])
-	plt.show()
+	plt.ylabel('Energy (eV)')
+	plt.xlabel('Particle Radius r_0 (nm)')
+	plt.savefig('threemer_eigenvalues.pdf')
 
 	plt.figure()
 	plt.plot(r,interaction[0],r,interaction[1],r,interaction[2],linewidth=3)
 	plt.legend(['NNN','N-S','NSN'])
-	plt.show()
+	plt.ylabel('Energy (eV)')
+	plt.xlabel('Particle Radius r_0 (nm)')
+	plt.savefig('threemer_interactions.pdf')
 	#np.savetxt('_'.join([str(epsb),'NN.txt']),NN)
 	#np.savetxt('_'.join([str(epsb),'NS.txt']),NS)
 

### 2017-05-12 chains/dielectric_chains.py

@@ -1,0 +1,197 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 14; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+count = 1
+counter = 0
+NNN = []
+NSN = []
+N_S = []
+interaction = [[],[],[]]
+for epsb in np.linspace(1,3,21):
+	counter += 1
+	print counter
+	
+	#NSNS = []
+	r = 30
+	a0 = r*10**-7; #sphere radius in cm
+	index = r*10 - 10
+	''' now determine geometry.'''
+	print epsb
+	#raw_input()
+	# make unit vectors in centimeters.
+	rij = 3*a0
+	e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([-3*e2,2*e1]),np.array([-4*e2,e1]),np.array([-4*e2,-e1]),np.array([-3*e2,-2*e1]),
+		   np.array([0, e1]),np.array([-e2, 2*e1]),np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
[…]

### 2017-05-12 dimer/dimer.py

@@ -31,14 +31,14 @@ anticollinear = [np.array([1,0]),np.array([-1,0])]
 r = 10
 elec = 1.60217662e-19 # regular coulombs
 numPart = 2; #number of particles
-a0 = 10e-7; #sphere radius in cm
+a0 = 30e-7; #sphere radius in cm
 
 ''' now determine geometry.'''
 
 # make unit vectors in centimeters.
-for number in range(0,100):
-	dist = float(number+1)/4
-	sep = (2+dist*.25)*a0
+for number in range(0,481):
+	#dist = 
+	sep = ((number+20)*1e-7)+2*a0
 	Loc = [np.array([sep/2, 0]),np.array([-sep/2, 0])]
 
 	#Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
@@ -63,13 +63,15 @@ for number in range(0,100):
 	'''initialize w_0 and eigen'''
 	w_0 = wsp_0
 	eigen = np.ones(2*numPart)
+	wavenumber = (w_0)/(c*math.sqrt(epsb))
 	alphasp = (a0**3)*(3/(epsinf+2*epsb))
+	alpha = alphasp/(1 - 1j*(2./3.)*(wavenumber**3)*alphasp)
 	R = Loc[(1)]-Loc[(0)] #pick out the location of each dipole, comute the distance between them
 	Rmag = math.sqrt(R[0]**2+R[1]**2) #compute magnitude of distance
 	nhat = (Loc[(1)]-Loc[(0)])/float(Rmag)
-	r_cubed = alphasp/Rmag**3 #this is the 1/r^3 term (static)
-	r_squared = (w_0*alphasp)/(c*(Rmag**2)) #this is the 1/r^2 term (imaginary part)
-	r_unit = (alphasp*w_0**2)/(Rmag*(c**2))
+	r_cubed = alpha/Rmag**3 #this is the 1/r^3 term (static)
+	r_squared = (w_0*alpha)/(c*(Rmag**2)) #this is the 1/r^2 term (imaginary part)
+	r_unit = (alpha*w_0**2)/(Rmag*(c**2))
 	space_cos = np.cos(w_0*Rmag/c) #this is the real part of the e^ikr
 	space_sin = np.sin(w_0*Rmag/c)
 
@@ -93,38 +95,42 @@ for number in range(0,100):
[…]

### 2017-05-12 trimer_ring/dielectric_ring.py

@@ -1,0 +1,173 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+interaction = [[],[]]
+elec = 1.60217662e-19 # regular coulombs
+numPart = 13; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+NN = []
+NS = []
+for epsb in np.linspace(1,3,21):
+	r = 15
+	a0 = r*10**-7; #sphere radius in cm
+	index = r*10 - 10
+	''' now determine geometry.'''
+	print epsb
+	# make unit vectors in centimeters.
+	rij = 3*a0
+	e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),
+		   np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
+		   np.array([-e2, -2*e1]),np.array([0, -e1]),
+		   np.array([e2, -2*e1]),np.array([2*e2, -e1]),
+		   np.array([2*e2 , e1]),np.array([e2 , 2*e1]),
[…]

### 2017-05-12 trimer_ring/phen_spacing.py

@@ -4,10 +4,6 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-bem_r = [1, 5, 10, 15, 20, 25]
-bem_NN = [3.616, 3.604, 3.558, 3.482, 3.402, 3.31]
-bem_NS = [3.61, 3.6, 3.568, 3.51, 3.416, 3.288]
-
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 interaction = [[],[]]
@@ -27,22 +23,25 @@ wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 for epsb in range(1,2):
 	NN = []
 	NS = []
-	for r in range (1,31):
+	r = 15
+	for dist in np.linspace(0,10,51):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
-		print r
+		print dist
+		NN_count = 0
+		NS_count = 0
 		# make unit vectors in centimeters.
-		rij = 3*a0
-		e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
-		e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
+		rij = (dist+2)*a0
+		e1 = float(1)/float(2) * rij ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * rij; #long side of 30-60-90 triangle
 		Loc = [np.array([0, e1]),np.array([-e2, 2*e1]),
 			   np.array([-2*e2, e1]),np.array([-2*e2, -e1]),
 			   np.array([-e2, -2*e1]),np.array([0, -e1]),
 			   np.array([e2, -2*e1]),np.array([2*e2, -e1]),
 			   np.array([2*e2 , e1]),np.array([e2 , 2*e1]),
 			   np.array([-e2,4*e1]),np.array([0,5*e1]),np.array([e2,4*e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
-
[…]

### 2017-05-12 varying_particle_number/dielectric_background.py

@@ -4,17 +4,13 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-static_NN = []
-static_NS = []
-bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
-bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 crossing = []
 elec = 1.60217662e-19 # regular coulombs
 
 numPart = 10; #number of particles
-
+omegas = []
 me = 9.10938291e-28; # electron mass in g
 ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
 hbar = 1.054571726e-34; # modified Planck in J*s
@@ -31,12 +27,13 @@ NN = []
 NS = []
 modes = [[],[]]
 interaction = [[],[]]
-for r in np.linspace(1,30,30):
+r = 15
+for epsb in np.linspace(1,3,21):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = r
 	''' now determine geometry.'''
-	print index
+	print epsb
 	# make unit vectors in centimeters.
 	rij = 3*a0
 	part_per_ring = numPart/2 + 1
@@ -85,7 +82,8 @@ for r in np.linspace(1,30,30):
 
 	count = 1
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
-	wsp_0 = (mie_omegas[index*10 - 10])*elec/hbar
+	wsp_0 = (mie_omegas[index*10 - 10])*(math.sqrt(epsinf+2)/math.sqrt(epsinf+2*epsb))    *elec/hbar
+	omegas.append(wsp_0*hbar/elec)
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
@@ -121,16 +119,16 @@ for r in np.linspace(1,30,30):
[…]

### 2017-05-12 varying_particle_number/twomer_spacing.py

@@ -4,10 +4,6 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-static_NN = []
-static_NS = []
-bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
-bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 crossing = []
@@ -31,14 +27,16 @@ NN = []
 NS = []
 modes = [[],[]]
 interaction = [[],[]]
-for r in np.linspace(1,30,30):
+r = 15
+for dist in np.linspace(0,10,51):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = r
+	
 	''' now determine geometry.'''
-	print index
+	print dist
 	# make unit vectors in centimeters.
-	rij = 3*a0
+	rij = (dist+2)*a0
 	part_per_ring = numPart/2 + 1
 	theta = 2*math.pi/part_per_ring
 	phi = theta/2.
@@ -89,7 +87,10 @@ for r in np.linspace(1,30,30):
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
-	for mode in range(0,2):
+	mode_count = 0
+	for mode in range(0,7):
+		mag_dipole = []
+
 		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.00001:
 			if count == 1:
 				wsp = wsp_0
@@ -167,38 +168,50 @@ for r in np.linspace(1,30,30):
 				r_unit = (alpha*w_0**2)/(Rmag*(c**2))
 				exponent = np.exp(1j*w_0*Rmag/c)
 				coupling += -(hbar/elec)*wsp*(((r_unit * (unit_dyad_term - n_dyad_term) + (r_cubed - 1j*r_squared) * (3*n_dyad_term - unit_dyad_term))) * exponent)
+		for cent in range(0,2):
+				cross = []
[…]

### 2017-05-17 may_paper/draft_2.0.tex
new threemer calculations

--- 2017-02-13 paper/draft.tex
@@
 \author{Charles Cherqui}
-\affiliation[Department of Chemistry, University of Washington]
-{Department of Chemistry, University of Washington, Seattle, WA 98195}
 \author{David J. Masiello}
@@
 {Department of Chemistry, University of Washington, Seattle, WA 98195}
-\alsoaffiliation[Department of Applied Mathematics, University of Washington]
-{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
 \email{masiello@chem.washington.edu}
@@
 \begin{abstract}
-Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials.
-Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing.
-For these reasons, it is imperative to understand the properties of such systems on both small and large scales.
-We show through theory and simulation that the energy ordering of the magnetic resonances of small oligomers depends greatly on the size and scale of the nanoparticle assembly in ways that purely electric plasmons do not.
-Following this, we determine the effective pemeability and permittivity of periodic arrays of nanoparticles and show that in certain size regimes they exhibit a negative index of refraction at optical frequencies.
-As a final exercise, we propose a negative-index material composed of charge tunable semiconductor quantum dots to emphasize the direct control of the optical properties of 2-D magnetic materials.
+Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magnetic plasmon oligomers, have been of recent interest as negative-index metamaterials and light-harvesting devices.
+For these reasons, it is imperative to understand the properties of such systems on the single- to few-oligomer scale.
+We show through theory and simulation that the energy ordering of the magnetic resonances of few-oligomer systems depends on size, scale, and environment in ways that purely electric plasmons do not.
+We show that the dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation.
+We highlight the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods.
 \end{abstract}
@@
 \section{Introduction}
-Bringing two or more metal nanoparticles (MNPs) together allows their individual electric plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
-Plasmon hybridization theory is applied to aggregates of MNPs and explains their collective behavior within the quasistatic limit in which the speed of light is taken to be infinite\cite{NordHal2003,NordProdan2004,Oubre2004,Gomez2009}.
-Recently, retardation effects on plasmon hybridization have been the focus of study for large particles\cite{Abajo2008,Gu2010} as well as dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and 2-D arrays\cite{Schatz2003,Royer2005,Chumanov2010} of nanoparticles.
-Specific arrangements of nanoparticles in 2-D arrays, such as three or more nanoparticles arranged on the vertices of a regular polygon, support a collective mode in which all of the dipole plasmons are oriented head-to-tail.
-This generates a fictitious, oscillating current loop resulting in an oscillating magnetic dipole moment in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}.
-These so-called magnetic plasmons are the lowest-energy collective modes of the oligomers and couple to and enhance the magnetic field of incident light\cite{Shalaev2007,Qian2015,Nord2007}, offering a route to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.
-The rich plasmonic modes of magnetic-plasmon-supporting systems are well-described using plasmon hybridization theory, but when in the quasistatic limit, the energy-order of the modes is not.
+Metal nanoparticles (MNPs) support collective resonances of their conduction electrons at optical frequencies.
+These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies to produce hybridized resonances, much like the hybridization of atomic orbitals in molecules\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
+When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in he center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}.
+Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing, cloaking, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}.
+In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to describe the magnetic systems\cite{Cherqui2014}; we adapt this model to expand on the results of that work.
+The original model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions.
+As a result, while it accurately predicted the nature of the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation.
+An explanation was needed to determine why the tight-binding model would predict different energy-ordering than full-wave simulations.
 
-Plasmon hybridization theory treats plasmons as point dipoles centered on their associated nanoparticles that interact through dipole-dipole coupling.
-In the quasistatic limit, these dipoles couple only through time-independent, electric near-field interactions\cite{jackson_classical_1999}, but when the size of and distance between nanoparticles becomes large, this approximation breaks down and intermediate- and far-field effects must be considered, as well as time-delay effects in the near-field\cite{jackson_classical_1999}.
-The aim of this paper is to incorporate the fully retarded electric field into plasmon hybridization theory and extend studies of retardation effects to magnetic plasmon oligomers.
-Specifically, we begin by exploring oligomers comprising two and three rings of nanoparticles and compare to full-wave simulation \cite{Hohenester2012} to verify that our approach qualitatively predicts the energy-ordering of the magnetic modes.\cite{Cherqui2014,Cherqui2016}.
-Following this, we calaculate the coupling betwen individual rings in various oligomers in order to parametrize an effective magnetic-magnetic coupling between magnetic dipoles.
-Using this new basis, we describe periodic chains and arrays of oligomers.
+In a recent paper, Engheta \textit{et al}.
+state that magnetic systems are well-understood on the single oligomer scale and the nearly infinite scale\cite{Engheta2017}.
+Furthermore, the dependence of magnetic properties on individual nanoparticle geometry and the relative size of the constituent oligomers has also been determined\cite{Cherqui2016}.
+However, the properties of few-oligomer systems have not been fully explored.
+Here we show that to fully understand the properties of magnetic oligomers on the few-oligomer scale, the simple tight-binding model described above must be extended to include both the fully-retarded electric fields and all inter-particle interactions.
+We show this through three explorations of oligomer properties: system size, dielectric constant of the environment, and inter-particle spacing, and we confirm our results using full-wave simulations\cite{Hohenester2012}.
 
-The calculations presented here are performed using an electric tight-binding model, parametrizing the magnetic couplings, and then introducing these coupling constants into a magnetic tight-binding model.
-For all following magnetic oligomers, only the two planar dipoles per particle are considered in the electric tight binding model.
-The dipoles are mapped onto a set of harmonic oscillators and are described by the following Hamiltonian:
+It is well-known that as MNPs and aggregates become larger, the quasistatic approximation breaks down.
+There has been much work done to elucidate the effects of retardation on large MNPs\cite{Abajo2008,Gu2010}, dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and extended 2-D arrays of particles\cite{Schatz2003,Royer2005,Chumanov2010}.
+Magnetic oligomers composed of two or more rings of particles have the potential to be hundreds of nanometers to microns across, justifying the need to consider retardation effects in determining their optical properties.
+In order to incorporate retardation effects into quasistatic plasmon hybridization theory, we begin by mapping the dipole plasmon of each MNP onto a set of harmonic oscillators, and allow them to couple through their electric fields according to the following Hamiltonian:
 
 \begin{equation}
-H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{\textrm{full},ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
+H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}\omega_{\textrm{sp},i}^2\textbf{X}_{i}^{2} - e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
 \end{equation}
 
-where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{\textrm{full},ij}$ is the fully retarded dipole-dipole relay tensor (expanded below).
+where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}.
 To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$.
-Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{\textrm{full},ij}$, we get:
+Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:
 
@@
 H = 
-\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
 + g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
@@
 
-In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}}{r_{ij}^3}\cos\left(\frac{\omega r_{ij}}{c}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}\omega}{r_{ij}^2 c}\sin\left(\frac{\omega r_{ij}}{c}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}\omega^2}{r_{ij} c^2}\cos\left(\frac{\omega r_{ij}}{c}\right)$, respectively.
-Additionally, the polarizability $\alpha_{sp} = \frac{e^2}{m_{sp}\omega_{sp}^2}$, $r_{ij}$ is the distance between the ith and jth LSPs, and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPs.
-Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973}.
+In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$.
+Additionally, $r_{ij}$ is the distance between the ith and jth LSPRs and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPRs.
+We further incorporate retardation effects by considering the lattice dispersion in the polarizability $\alpha_{sp}' = \left(\alpha_{sp}^{-1} - i\frac{2}{3}k^3\right)^{-1}$ with $\alpha_{sp} = r_0^3\frac{3}{\varepsilon_{\infty}-2\varepsilon_b}$.
+Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973,Draine1993}.
 
-It should be noted that this Hamiltonian, when diagonilzed, results in a transcendental equation.
-The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues of the eigenvectors.
+It should be noted that this Hamiltonian, when diagonalized, results in a transcendental equation whose solutions, the eigenvalues $\omega$, are functions of themselves.
 In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues.
@@
 
-\section{results and discussion}
-The first systems we examine are a magnetic dimer\cite{Cherqui2014}, a three-ring chain, and three rings arranged in a triangle.
-Because we are interested in the effects of scale, we must define a scaling parameter for the system.
-Each of our systems begins from a unit cell: six silver, spherical MNPs placed at the corners of a regular hexagon.
-To create the dimer, two unit cells are tiled so that they share an edge, and thus two particles.
-In general, if any two unit cells share an edge, they also share two nanoparticles, as in the diagrams in Figure~\ref{theory_simul} Each particle has radius $a_0$ and particles are separated by lattice spacing $r=2.2\times a_0$.
-With the radius of the particles defining the scale of the system, there now exists a way to probe the energy ordering of the modes as a function of size.
+\section{Results and Discussion}
+
+In this work, we model silver nanoparticles using a Drude model with $\omega_p = 9.1$ eV, $\varepsilon_{\infty} = 3.77$, and $\gamma = 0.003$ eV.
+Note that we have greatly reduced the damping constant in order to better resolve the magnetic modes in the simulations.
+The oligomer unit cell is a six-member ring, with silver nanoparticles located at the vertices of a regular hexagon.
+We explore and manipulate three magnetic oligomer systems: a twomer, a linear threemer, and a triangular threemer.
+The number of rings in a magnetic system corresponds to the number of magnetic modes in the system\cite{Cherqui2014}.
+The twomer supports an in-phase mode (North-North, or NN) and an out-of-phase mode (North-South, or NS).
+The linear threemer supports an all in-phase mode (North-North-North, or NNN), a minimally out-of-phase mode (North-Zero-South, or NZS), and a maximally out-of-phase mode (North-South-North, or NSN).
+The triangular threemer supports an all in-phase mode (North-North-North, or NNN) and two degenerate out-of-phase modes (North-South, or NS).
+These modes and their relative magnetic fields are depicted in Figures~\ref{magmodes},~\ref{dielectric}, and ~\ref{spacing}.
+In each manipulation, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$.
+In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model.
+The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system.
+In these manipulations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.
 
 \begin{figure}
-\begin{center}
-\includegraphics{theory_bem_comparison_fig1.pdf}
-\caption{Pending.}
-\label{theory_simul}
-\end{center}
+\centering
+\includegraphics[width=.6\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
+\caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (column b) for the magnetic twomer (first row), linear threemer (second row), and triangular threemer (third row).
+All of the magnetic modes range from 3.6 eV to 3.1 eV.
+In each system, the magnetic modes exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on their scale.
+The model consistently overestimates the eigenvalues by 0.05 eV, and consistently underestimates the crossing points by less than a nanometer.
+To further emphasize the impact of scale, we have plotted the total interaction strength of each eigenmode, \textit{i.e.} the sum of each eigenvector's dot product with the electric field of all of the other dipoles.
+This calculation reaffirms the scale-dependence and predicts the same mode crossings as both the eigenvalue calculation and the simulations.}
+\label{magmodes}
 \end{figure}
 
-The results of our theoretical calculations and full-wave simulations for the aforementioned oligomers are dispayed in Figure~\ref{theory_simul}.
-Both theory and simulation predict that as a function of size, the energy ordering of the magnetic plasmon modes should change.
-In the dimer system, there are two magnetic modes.
-When the system is small, the lowest energy mode is the alternating north-south (NS) mode and the in-phase north-north mode is highest.
-When we add a ring to the system, we see a trend emerge.
-The alternating (NSN) mode is lower than the N-S mode, which is in turn lower than the NNN mode.
-As a function of size, the modes change order.
-The triangle system, as a result of its threefold symmetry (as opposed to twofold for the chains) has slightly different properties.
-At small size, its lowest energy mode is a pair of degenerate NS modes, while its higher energy mode is an all-north mode.
-These again switch order as a function of size.
-In chains with more than three rings, the pattern continues - the magnetic resonances with the most nodes between rings are the lowest energy when small, but the highest when large.
+In Figure~\ref{magmodes}a, the magnetic mode eigenvalues are computed for each system.
+The solid lines depict model calculations, and the dashed lines depict simulated results.
+Interestingly, the magnetic modes exhibit a dynamic energy ordering, switching order twice as a function of scale.
+It is presumable that they continue to flip at larger and larger sizes.
+This is confirmed by simulations, with the model overestimating the eigenvalues by about 0.05 eV and underestimating the crossing points by under a nanometer.
+These small errors are consistent across all three systems.
+Figure~\ref{magmodes}b displays the computed interaction strength for each eigenmode produced by the tight-binding model,
+
+\begin{equation}
+\begin{aligned}
+U_{\textrm{int}} = -$\sum_{i>j}\textbf{p}_{i}\cdot\textbf{E}$
+\label{interactionenergy}
+\end{aligned}
+\end{equation}
+
+where $\textbf{p}_{i}$ is an eigenvector and $\textbf{E}$ is the field produced by the other dipoles.
+This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.
 
 \begin{figure}
-\begin{center}
-\includegraphics{twomer_dimer.pdf}
-\caption{Pending.}
-\label{twomer_dimer}
-\end{center}
+\centering
+\includegraphics[width=0.6\paperwidth]{dimer_interaction.png}
+\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d).
+Plotted are the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance.
+Interestingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles.
+From these plots, it can be seen that the favorability of a specific dipole arrangement depends on the separation between the dipoles.
+This can be seen in the fact that each part of the field depends differently on the separation, and each field term contains an oscillating term.
+At short length scales, the interaction is dominated by the near-field.
+However, as the distance increases, the interaction is dominated by the intermediate field (a and c) or the far-field (b and d).
+As a result, there are separation distances at which normally unfavorable arrangements become favorable.
+Since magnetic oligomers can be described through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
+\label{dimers}
 \end{figure}
 
-This is an unexpected phenomenon.
-When one considers the energy-order of the four (six) hybridized modes of the nanosphere dimer, it becomes clear that they do not exhibit this effect (Figure~\ref{twomer_dimer}).
-Notably, the sphere dimer shows no crossings while the oligomer dimer does.
-The reason for this outcome is the oligomer dimer's complex structure\cite{Cherqui2016}.
-The sphere dimer has only one length scale and consitutes only one pairwise interaction.
-However, the oligomer dimer contains many pairs of nanoparticles over multiple length scales.
-As a result, different configurations of electric dipoles will be favored at different oligomer sizes, hence the flip of the magnetic modes.
+To gain an explanation for this mode-switching phenomenon, we investigate the fully retarded electric field.
+In Figure~\ref{dimers} we plot the near-, intermediate-, far-field, and total interaction strength as a function of MNP separation for the four possible arrangements of dipoles.
+There are two overall trends.
+At small distances, the overall interaction is dominated by the near-field term due to its $\frac{1}{r_{ij}^3}$ dependence.
+At larger distances, the overall interaction follows the intermediate-field (Figure~\ref{dimers}a and c) or the far-field (Figure~\ref{dimers}b and d).
+The second trend is the changing sign of the three field terms and the total interaction.
+This distance-dependent oscillatory nature determines the energy-ordering of pairs of dipoles, and thus influences the size-dependence of the eigenmode order in amgnetic oligomers.
+In fact, it has been well documented that system length-scale has an oscillatory impact on its eigenenergies\cite{vonPlessen2007,Pinchuk2016} For example, at some length scales, the dipole-dipole interactions in the North-South mode of the twomer are more favorable than those in the North-North mode, but this favorability changes as a function of system size.
+
+We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conforn to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms.
+With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties.
+In the previous section, the scale of the systems was changed.
+However, this would be impossible to manipulate in a laboratory.
+We focus on properties with experimental analogues, namely, the dielectric constant of the embedding medium and the nearest-neighbor spacing between nanoparticles.
 
 \begin{figure}
-\begin{center}
-\includegraphics{interactions.pdf}
-\caption{Pending.}
-\label{int_strength}
-\end{center}
+\centering
+\includegraphics[width=.6\paperwidth]{dielectric_study.png}
+\caption{Magnetic mode eigenvalues (column a) for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 20 nm and magnetic mode eigenvalue differences (column b) as a function of the dielectric constant of an embedding medium.
+As the dielectric constant is increased from 1 to 3, the magnetic mode splitting approaches zero and the overall energy decreases.
+At very high dielectric values, the magnetic mode eigenvalues converge to the single particle resonance frequency.
+This is the result of the dielectric constant reducing the inter-particle interactions.
+It is also important to note that between $\varepsilon_b = 1$ and $\varepsilon_b = 1.5$, the magnetic mode differences vary sharply, either becoming much more positive or much more negative.
+This is indicative of mode-switching that is difficult to see in the eigenvalue plots.
+The increasing dielectric constant has a similar effect to increasing the scale of the system, as it recovers the same energy ordering for $r_0 > 20$ nm.}
+\label{dielectric}
 \end{figure}
 
-To gain a more visual and intuitive sense of the length scales of each of the terms (near, intermediate, and far) in the fully retarded electric field of a dipole (found in the coupling terms of Equation~\ref{elec_hammy_2}), we calculated the relative interaction strength between pairs of dipoles (the collective modes of the sphere dimer) as a function of dipole separation distance.
-The results of these calculations are displayed in Figure~\ref{int_strength}, showing that at different length scales, different terms in the field contribute more to the energy of the system.
-Significantly, the interaction strengths display oscillatory motion, which confirms and reinforces past studies on the oscillatory nature of radiation damping.\cite{vonPlessen2007}
+In order to justify the next set of model calculations, we refer to research on flowing liquid crystal over MNP aggregates and, in real-time, adjusting the refractive index of the MNP environment, influencing the resonance frequencies of the system\cite{odom_lasing}.
+We apply this concept to our tight-binding model to determine if this has any implications on the properties of magnetic oligomers.
+What we find is that, as expected, increasing the real-valued dielectric constant of the background decreases the resonance frequency of the collective modes.
+Furthermore, the embedding medium influences the energy-ordering of the eigenvalues.
+Results of one of our explorations are summarized in Figure~\ref{dielectric}.
+As the dielectric constant of the medium increases, the eigenmodes collapse onto each other, and eventually converge with the single-particle frequency.
+Because the modes collapse so quickly and appear to overlap at all values of $\varepsilon_b$, Figure~\ref{dielectric}b displays the difference in energy between all of the eigenmodes of each system.
+The values of $\varepsilon_b$ where the differences cross zero signfy mode-crossing.
+From these two observations we conclude that the opacity of the embedding medium weakens the overall inter-particle interactions.
+However, this occurs differently for each of the parts of the interaction.
+All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms, but focusing on how they differ in $k$ reveals how the dielectric constant infuences the electric field.
+The near-field term contains no other $k$-dependence, and so is reduced by one factor of $\varepsilon_b$.
+The intermediate-field term is linear in $k$, so it is reduced by a factor of $\sqrt{\varepsilon_b}$.
+Lastly, the far-field term is quadratic in $k$, so all $\varepsilon_b$-dependence is removed, besides that dependence previously mentioned.
+At higher values of the dielectric constant the far-field term dominates, much like the way particles that are far apart interact primarily through their far-fields (Figure~\ref{dimers}b and d).
+In other words, embedding magnetic systems in some dielectric medium causes them to act as though they are larger, effectively increasing their scale.
+This insight provides an experimental route to directly choosing the energy-ordering of magnetic modes, but the reduced splitting between modes might make such an experiment unfeasible.
 
 \begin{figure}
-\begin{center}
-\includegraphics{coupling_comparison.pdf}
-\caption{Pending.}
-\label{ring_spacing}
-\end{center}
+\centering
+\includegraphics[width=.6\paperwidth]{spacing_study.png}
+\caption{Magnetic mode eigenvalues for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle separation in units of radii.
+As the separation distance increases, the magnetic mode eigenvalues converge to and oscillate about the single particle frequency, exhibiting mutliple crossings.
+As in Equation~\ref{elec_hammy_2}, the interaction strength decays with increasing separation and oscillates due to its dependence on trigonometric functions.}
+\label{spacing}
 \end{figure}
 
-With a functional and accurate electric dipole tight binding model, we seek a way to simplify our model.
-Figure~\ref{ring_spacing} displays the eigenvalue curves for three arrangements of two-ring systems, with the rings as (A) nearest neighbors (B) next-nearest neighbors and (C) next-next-nearest neighbors.
-It is clear that again, at different length scales and relative orientations, the eigenvalue curves behave differently, having different crossing points and energy ordering.
-Using these eigenvalue curves, the electric dipole model is transformed into a magnetic dipole model.
-A magnetic dipole is placed at the center of each ring with orientation perpendicular to the plane of the ring.
-Each dipole has natural frequency $\omega_{\textrm{M}}$, which we determine using the electric tight-binding model for a single ring.
-The coupling between each magnetic dipole is pulled from the plots in figure (w/e) - depending on the spacing between the rings, the dipoles couple through nearest, next-nearest, or next-next-nearest neighbor coupling.
-The Hamiltonian
+There is also active research on tuning the size and shape of a plasmonic aggregate using various polymers\cite{Ginger2017} or DNA\cite{DanLuo2009,NaLiu2017}.
+Here, we implement the idea of continuously distorting the nearest-neighbor spacing, from touching to tens of radii apart.
+We present data for particle radii of 15 nm and 30 nm in Figure~\ref{spacing}a and b, respectively.
+The results of these model calculations are reminiscent of the results in Figure~\ref{dimers} in that the eigenmodes oscillate about each other as the particles move farther apart.
+In addition, similarly to Figure~\ref{dielectric}, at very large distances the eigenvalues converge to the single LSPR frequency, exhibiting small amplitude oscillations.
+This is indicative of the coupling falling very near to zero.
+It is clear that this method, as opposed to the method of tuning the dielectric constant of the background, offers a much greater degree of tunability.
+Designing a system in which the inter-particle spacing could be varied in discrete steps would lead to the ability to directly choose the resonance frequency of a specific magnetic mode.
+Furthermore, being able to directly detect the frequency of the magnetic mode optically could turn such magnetic systems into thermometers, pH probes, or detectors of any environmental factor that would change the size of the embedding polymer.
 
-\begin{equation}
-H = \frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i}^{n}[\pi_{i}^{2}+q_{i}^{2}]+\frac{\hbar\omega_{\textrm{M}}}{2}\sum_{i\neq j}g_{ij}^{\textrm{M}}q_{i}q_{j}
-\label{mag_hammy}
-\end{equation}
-
-is used in the same way as Equation~\ref{elec_hammy_2} - diagonalizing it for a set of $n$ magnetic dipoles produces $n$ collective magnetic modes.
-The benefit of this model is shown by example.
-For the oligomer dimer, there are ten MNPs, each with two electric dipoles, resulting in twenty collectivel electric modes, two of which were magnetic in character.
-In the magnetic dipole basis, because there are two rings, there are only two modes - the magnetic modes.
-This simplifies the data analysis procedures greatly.
-We find that when the couplings between rings are parametrized by the differences between the eigenvalues of the dimers in figure (whatever), the magnetic dipole Hamiltonian reproduces the results of the electric dipole Hamiltonian exactly.
-We find, furthermore, that truncating to nearest or next-nearest neighbors in the magnetic dipole model does not lead to any significant loss in quantitative or qualitative agreement between the models.
-It is this finding that will allow us the extension of the model to larger systems considering only nearest or next-nearest neigbor coupling.
-
-The significant challenge here is to find a colloquial, qualitative, and accurate way to describe extended systems.
-By considering the magnetic dimer to be a unit cell of extended systems, the path to characterizing large systems is through a method similar to a two-atom basis molecular tight-binding model.
-Here, however, the atoms are the rings of the dimer, and the elements of the hopping matrix are determined by the inter-ring couplings calculated above.
-More on this model will be presented later.
-
-\section{Dielectric Background and a Measure of Quasistaticity}
-
-As an additional exercise, and to emphasize the tunability and versatility of magnetic plasmon oligomers, the effect of the dielectric constant of the background ($\varepsilon_{b}$) is also taken into account.
-The dielectric constant screens the electric dipoles from each other by effectively weakening their induced electric fields.
-This means that as $\varepsilon_{b}$ gets large, intermediate and far field effects will weaken in comparison to near field contributions to the electric field.
-Thus, magnetic plasmon oligomers will be more likely to behave quasistatically when large.
-In Figure~\ref{diel_eff}A, the difference between the NN and NS modes for magnetic dimers of four different scaling factors embedded in media with $\varepsilon_{b} = 1$ to $10$ are presented as an example of the impact of screening on the energy ordering of magnetic modes.
-The results show that when highly screened, even large magnetic plasmon oligomers behave quasistatically.
-
-\begin{figure}
-\begin{center}
-\includegraphics{diel_magnetization.pdf}
-\caption{Pending.}
-\label{diel_eff}
-\end{center}
-\end{figure}
-
-To extend this to a potential application, we consider now a periodic chain of magnetic monomers - essentially a 1-D system - with only nearest neighbor coupling.
-When the radii of the particles in the chain are small, the lowest energy collective mode of the chain will be an all-alternating magnetic mode, and when the radii are large it will be an all in-phase magnetic mode.
-A way to quantify this is through a measure of net magnetization.
-Diagonalizing the magnetic Hamiltonian [reference the equation], summing the eigenvectors, and dividing by n (the number of rings) gives a measure of whether the system is magnetized, and this is plotted as a function of particle radius in Figure~\ref{diel_eff}B.
-More importantly, the point at which the magnetization ``switches on'' can be controlled through the dielectric background.
-This gives rise to the ability of the experimentalist to directly introduce a phase-lag in an extended chain of magnetic oligomers by embedding certain segments of the chain in different materials.
-This is not so different from certain techniques that are being studied presently in the field\cite{odom_lasing}
-
-\section{Periodic Arrays of Rings - Permeability, Permittivity, and Index of Refraction}
-To determine the permeability, permittivity, and index of refraction of the six-member ring that is the unit cell, we follow Alu and Engheta\cite{Alu2006}.
-Preparing the magnetic mode of the six-member ring induces a dipole moment on each particle.
-The dipole moment of a particular particle,
-
-\begin{equation}
-\textrm{\textbf{p}}_{i} = p\hat{\textrm{\textbf{p}}}_{i} = \alpha_{sp}\left(\textrm{\textbf{E}}_{0} + p\sum_{i\neq j}\boldsymbol{\Lambda_{ij}}\cdot\hat{\textrm{\textbf{p}}}_{i}\right)
-\label{dipolemoment}
-\end{equation} 
- responds to the incident electric field defined by $\Nabla \times \textrm{\textbf{E}}_{0} = i\omega\mu_{0}\textrm{\textbf{H}}_{0}$ and the fields scattered by each of the other dipoles.
-For the magnetic mode, $\textrm{\textbf{E}}_{0} = \frac{i\omega\mu_{0}R\textrm{H}_{0}}{2}\hat{\textrm{\textbf{p}}}_{i}$.
-We are interested in finding the magnetic polarizability, $\alpha_{M}$ that satisfies $\textrm{\textbf{m}} = \alpha_{M}\textrm{\textbf{H}}_{0}$, where
-
-\begin{equation}
-\textrm{\textbf{m}} = -\frac{-i\omega NRp}{2}\hat{\textrm{\textbf{z}}}
-\label{magneticmoment}
-\end{equation}
-is the magnetic dipole moment. From these equations, we find that
-
-\begin{equation}
-\alpha_{M} = \frac{(kR)^{2}N}{4\varepsilon_{b}}\left(\frac{\alpha_{sp}}{1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j} }\right)
-\label{alphaM}
-\end{equation}
-
-The effective permeability of a material made of a periodic arrangement of this unit cell is given by $\mu_{\textrm{eff}} = 1 + N_{d}\left(\alpha_{M} - i\frac{6\pi}{k^3}\right)$.
-
-To compute the effective permittivity of the same ring of nanoparticles, the unit cell is prepared in a uniform electric field.
-This results in a net dipole moment $\textrm{\textbf{p}}_{E} = \sum_{i=1}^{N} \textrm{\textbf{p}}_{i}$.
-The dipole moment on each particle is as above in Eq.
-\equation{dipolemoment}.
-Now however, the total dipole moment satisfies $\textrm{\textbf{p}}_{E} = \alpha_{E}\textrm{\textbf{E}}_{0}$.
-This polarizability governs the total electric response of the ring to an electric field, as opposed to the polarizability of a single particle, and is given by
-
-\begin{equation}
-\alpha_{E} = \frac{\alpha_{sp}}{N\left(1 - \alpha_{sp}\sum_{i\neq j}\hat{\textrm{\textbf{p}}}_{i} \cdot \boldsymbol{\Lambda}_{ij}\cdot\hat{\textrm{\textbf{p}}}_{j}\right)}.
-\label{alphaE}
-\end{equation}
-
-From this polarizability, the effective permittivity of a periodic lattice of this unit cell is $\varepsilon-{\textrm{eff}} = 1 + N_{d}\left(\alpha_{E} - i\frac{6\pi}{k^3} \right)$.
-The index of refraction of such a material is given by $n = \sqrt{\varesilon_{\textrm{eff}}\mu_{\textrm{eff}}}$ and will take negative values in the frequency range for which both $\varepsilon_{\textrm{eff}}$ and $\mu_{\textrm{eff}}$ are negative.
-A frequency and size regime for which a six-member ring has negative index is shown in the next figure which I haven't made yet.
-
-Repeat this for more complicated unit cells! (twomer + sixmer) 
-\section{Same as above, but qds}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% CONCLUSION. I DON'T THINK ACS NANO HAS A DISTINCT CONCLUSION SECTION %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Conclusion}
-It has been shown that magnetic plasmon oligomers are a highly versatile, highly tunable material.
-The magnetic behavior of tesselated rings of nanoparticles is dependent on size, spacing, arrangement, and environment.
-Equipped with an understanding of how information propagates along these materials and how to actively influence that information, we are now in a position to study large chains and arrays of magnetic plasmon oligomers.
-By combining these theoretical studies with existing experimental techniques, there exist ways to directly inlfuence the propagation of information in real time, leading to new applications in detection mechanisms and perhaps leading to a new kind of plamsonic ``circuit.'' What remains is to understand the dynamics of these systems from a theoretical perspective, an exercise which is left for future studies.
+We have shown that magnetic systems composed on the few-oligomer scale exhibit tunable resonances with dynamic spectral ordering.
+However, we stress that the systems studied in this work were chosen due to their theoretical simplicity.
+In simulated and experimental spectroscopies, these eigenmodes would overlap and be nearly indistinguishable.
+It has been shown that oligomers whose constituents are rod-like, elongated, or generally degeneracy-breaking have sharper, more isolated magnetic resonances\cite{Cherqui2016}.
+To this end, future studies will involve these geometries to determine if they have the same eigenmode-switching properties and tunability.
+With this groundwork on the properties of small oligomers, there is now an incentive and an avenue to expanding the concepts presented here to larger aggregates, as well as a need to confirm the predictions made here with experiments.
+The ability of the researcher to decide the resonance frequency of a particular eigenmode opens the door to the ability to dynamically and actively determine system properties.
 
@@
 \begin{acknowledgement}
-CEI, NSF, DOE, Niket, some other people, probably
+CEI, NSF, DOE?, Niket, some other people, probably, HPC.
 \end{acknowledgement}

### 2017-05-17 chains/chains.py

@@ -56,8 +56,8 @@ for epsb in range(1,2):
 		#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
 		wsp_0 = (mie_omegas[index])*elec/hbar
 		'''initialize w_0 and eigen'''
-		w_0 = 0*elec/hbar
-		eigen = np.ones(2*numPart)
+		w_0 = wsp_0
+		eigen = np.zeros(2*numPart)
 		for mode in range(0,3):
 			mag_dipole = []
 			while abs(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)]) > 0.00001:
@@ -182,14 +182,15 @@ for epsb in range(1,2):
 	plt.legend(['NNN','NSN','N-S','BEM NNN','BEM N-S','BEM NSN'])
 	plt.ylabel('Energy (eV)')
 	plt.xlabel('Particle Radius r_0 (nm)')
-	plt.savefig('threemer_eigenvalues.pdf')
+	plt.show()
+	#plt.savefig('threemer_eigenvalues.pdf')
 
-	plt.figure()
+	'''plt.figure()
 	plt.plot(r,interaction[0],r,interaction[1],r,interaction[2],linewidth=3)
 	plt.legend(['NNN','N-S','NSN'])
 	plt.ylabel('Energy (eV)')
 	plt.xlabel('Particle Radius r_0 (nm)')
-	plt.savefig('threemer_interactions.pdf')
+	plt.savefig('threemer_interactions.pdf')'''
 	#np.savetxt('_'.join([str(epsb),'NN.txt']),NN)
 	#np.savetxt('_'.join([str(epsb),'NS.txt']),NS)
 

### 2017-05-17 chains/dielectric_chains.py

@@ -26,12 +26,13 @@ NNN = []
 NSN = []
 N_S = []
 interaction = [[],[],[]]
-for epsb in np.linspace(1,3,21):
+omegas=[]
+for epsb in np.linspace(1.28,1.285,21):
 	counter += 1
 	print counter
 	
 	#NSNS = []
-	r = 30
+	r = 20
 	a0 = r*10**-7; #sphere radius in cm
 	index = r*10 - 10
 	''' now determine geometry.'''
@@ -48,16 +49,17 @@ for epsb in np.linspace(1,3,21):
 	       #np.array([4*e2,e1]),np.array([3*e2,2*e1])] #location vectors for center of each sphere - they go counterclockwise, with one being the top center particle and six being the bottom center particle.
 	center = [np.array([-3*e2,0]),np.array([-e2, 0]),np.array([e2,0])]#,np.array([3*e2,0])]
 	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
-	H = np.zeros((2*numPart,2*numPart),dtype=complex) #initialize Hammy with zeros, twenty by twenty in this case.
+	H = np.zeros((2*numPart,2*numPart),dtype=float) #initialize Hammy with zeros, twenty by twenty in this case.
 
 	'''More constants'''
 
 	
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
 	wsp_0 = (mie_omegas[index])*(math.sqrt(epsinf+2)/math.sqrt(epsinf+2*epsb))*elec/hbar
+	omegas.append(wsp_0*hbar/elec)
 	'''initialize w_0 and eigen'''
-	w_0 = 0*elec/hbar
-	eigen = np.ones(2*numPart)
+	w_0 = wsp_0
+	eigen = np.zeros(2*numPart)
 	for mode in range(0,3):
 		mag_dipole = []
 		while abs(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)]) > 0.00001:
@@ -70,14 +72,14 @@ for epsb in np.linspace(1,3,21):
 				w_0 = eigen[2*numPart-(mode+1)]*elec/hbar
 			#print w_0
 			alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
-			wavenumber = (w_0)/(c*math.sqrt(epsb))
+			wavenumber = (w_0*math.sqrt(epsb))/(c)
[…]

### 2017-05-17 chains/fixed_vectors.py

@@ -1,0 +1,92 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+bem_NNN = [3.614, 3.602, 3.564, 3.494, 3.412, 3.31, 3.2]
+bem_N_S = [3.612, 3.601, 3.566, 3.498, 3.404, 3.294, 3.18]
+bem_NSN = [3.61, 3.6, 3.57, 3.512, 3.42, 3.292, 3.12]
+bem_r = [1, 5, 10, 15, 20, 25, 30]
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 14; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NNN = []
+	NSN = []
+	N_S = []
+	interaction = [[],[],[]]
+	#NSNS = []
+	for r in range (1,31):
+		a0 = r*10**-7; #sphere radius in cm
+		index = r*10 - 10
+		''' now determine geometry.'''
+		print r
+		#raw_input()
+		# make unit vectors in centimeters.
+		rij = 3*a0
+		e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
[…]

### 2017-05-17 trimer_ring/dielectric_ring.py

@@ -22,8 +22,9 @@ gamma = 0.05*elec/(hbar*16)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 NN = []
 NS = []
+omegas = []
 for epsb in np.linspace(1,3,21):
-	r = 15
+	r = 20
 	a0 = r*10**-7; #sphere radius in cm
 	index = r*10 - 10
 	''' now determine geometry.'''
@@ -47,6 +48,7 @@ for epsb in np.linspace(1,3,21):
 	count = 1
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
 	wsp_0 = (mie_omegas[index])*(math.sqrt(epsinf+2)/math.sqrt(epsinf+2*epsb))*elec/hbar
+	omegas.append(wsp_0*hbar/elec)
 	'''initialize w_0 and eigen'''
 	w_0 = 0*elec/hbar
 	eigen = np.ones(2*numPart)
@@ -61,7 +63,7 @@ for epsb in np.linspace(1,3,21):
 				count = count + 1
 				w_0 = eigen[2*numPart-(mode+1)]*elec/hbar
 			alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
-			wavenumber = (w_0)/(c*math.sqrt(epsb))
+			wavenumber = (w_0*math.sqrt(epsb))/(c)
 			alpha = alphasp/(1 - 1j*(2./3.)*(wavenumber**3)*alphasp)
 			msp = (ch**2)/(alphasp*((wsp)**2)); # sp mass (grams)
 			tau = (2*ch**2)/(3*msp*c**3) # radiation damping time
@@ -152,12 +154,22 @@ NS = np.reshape(NS,(21,3))
 #NS_int = np.reshape(interaction[1],(21,7))
 epsb = np.linspace(1,3,21)
 plt.figure()
-plt.plot(epsb,NN,epsb,NS[:,0],linewidth=3)	
-plt.legend(['NN','NS','BEM NN','BEM NS'])
+plt.plot(epsb,NN,epsb,NS[:,0],epsb,omegas,linewidth=3)	
+plt.legend(['NN','NS','LSPR'])
 plt.ylabel('Energy (eV)')
 plt.xlabel('Embedding Medium')
-plt.savefig('ring_15_dielectric.pdf')
-plt.show()
[…]

### 2017-05-17 varying_particle_number/dielectric_background.py

@@ -27,7 +27,7 @@ NN = []
 NS = []
 modes = [[],[]]
 interaction = [[],[]]
-r = 15
+r = 20
 for epsb in np.linspace(1,3,21):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
@@ -96,7 +96,7 @@ for epsb in np.linspace(1,3,21):
 			else:
 				count = count + 1
 				w_0 = eigen[2*numPart-(mode+1)]*elec/hbar
-			wavenumber = (w_0)/(c*math.sqrt(epsb))
+			wavenumber = (w_0*math.sqrt(epsb))/(c)
 			alpha = alphasp/(1 - 1j*(2./3.)*(wavenumber**3)*alphasp)
 			msp = (ch**2)/(alpha*((wsp)**2)); # sp mass (grams)
 			tau = (2*ch**2)/(3*msp*c**3) # radiation damping time
@@ -186,8 +186,15 @@ plt.ylabel('Energy (eV)')
 plt.xlabel('Embedding Medium')		
 plt.legend(['NN','NS'])
 #plt.show()
-plt.savefig('twomer_15_withwsp.pdf')
+plt.savefig('twomer_20_withwsp.pdf')
 
+
+plt.figure()
+plt.plot(epsb, np.subtract(modes[0],modes[1]),epsb,np.zeros((len(epsb),1)), linewidth=3)
+plt.xlabel('dielectric')
+plt.ylabel('Energy (eV)')
+#plt.show()
+plt.savefig('NN-NS.pdf')
 '''plt.figure()
 plt.plot(epsb,interaction[0],epsb,interaction[1],linewidth=3)	
 plt.ylabel('Energy (eV)')

### 2017-05-21 may_paper/draft_2.0.tex
edited paper, new figures, bigger twomers for funsies

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=ancac3,manuscript=article]{achemso}
+\documentclass[journal=apchd5,manuscript=article]{achemso}
 
@@
 \title[]
-    {A Simple Model for Small Collections of Magnetic Plasmonic Oligomers}
+{Tunable Spectral Ordering of Magnetic Plasmons}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{tocentry}
-
-Some journals require a graphical entry for the Table of Contents.
-This should be laid out ``print ready'' so that the sizing of the
-text is correct.
-
-Inside the \texttt{tocentry} environment, the font used is Helvetica
-8\,pt, as required by \emph{Journal of the American Chemical
-Society}.
-
-The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-permitted for  \emph{Journal of the American Chemical Society}
-graphical table of content entries. The box will not resize if the
-content is too big: instead it will overflow the edge of the box.
-
-This box and the associated title will always be printed on a
-separate page at the end of the document.
+\includegraphics{toc_graphic.pdf}
 
@@
 These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies to produce hybridized resonances, much like the hybridization of atomic orbitals in molecules\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
-When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in he center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}.
-Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing, cloaking, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}.
+When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}.
+Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing\cite{Fang2005,Valentine2008}, cloaking\cite{Shalaev2008}, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}.
 In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to describe the magnetic systems\cite{Cherqui2014}; we adapt this model to expand on the results of that work.
-The original model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions.
-As a result, while it accurately predicted the nature of the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation.
+Cherqui's model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions.
+As a result, while it accurately predicted the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation.
 An explanation was needed to determine why the tight-binding model would predict different energy-ordering than full-wave simulations.
@@
 It is well-known that as MNPs and aggregates become larger, the quasistatic approximation breaks down.
-There has been much work done to elucidate the effects of retardation on large MNPs\cite{Abajo2008,Gu2010}, dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and extended 2-D arrays of particles\cite{Schatz2003,Royer2005,Chumanov2010}.
+There has been much work done to elucidate the effects of retardation on large MNPs\cite{Abajo2008,Gu2010}, dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and extended chains and 2-D arrays of particles\cite{Schatz2003,Royer2005,Chumanov2010,Pinchuk2016}.
 Magnetic oligomers composed of two or more rings of particles have the potential to be hundreds of nanometers to microns across, justifying the need to consider retardation effects in determining their optical properties.
-In order to incorporate retardation effects into quasistatic plasmon hybridization theory, we begin by mapping the dipole plasmon of each MNP onto a set of harmonic oscillators, and allow them to couple through their electric fields according to the following Hamiltonian:
+In order to incorporate retardation effects into quasistatic plasmon hybridization theory, we begin by mapping the dipole plasmon of each MNP onto a set of harmonic oscillators, and allow them to couple through their electric fields according to the following Hamiltonian\cite{Cherqui2014}:
 
 \begin{equation}
-H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}\omega_{\textrm{sp},i}^2\textbf{X}_{i}^{2} - e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
+H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}\omega_{\textrm{sp},i}^2\textbf{X}_{i}^{2} - e^2\sum_{i>j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
 \end{equation}
@@
 H = 
-\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i>j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
 + g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
@@
 The twomer supports an in-phase mode (North-North, or NN) and an out-of-phase mode (North-South, or NS).
-The linear threemer supports an all in-phase mode (North-North-North, or NNN), a minimally out-of-phase mode (North-Zero-South, or NZS), and a maximally out-of-phase mode (North-South-North, or NSN).
-The triangular threemer supports an all in-phase mode (North-North-North, or NNN) and two degenerate out-of-phase modes (North-South, or NS).
+The linear threemer supports an all in-phase mode (All-North, or AN), a minimally out-of-phase mode (North-South, or NS), and a maximally out-of-phase mode (North-South-North, or NSN).
+The triangular threemer supports an all in-phase mode (All-North, or AN) and two degenerate out-of-phase modes (North-South, or NS).
 These modes and their relative magnetic fields are depicted in Figures~\ref{magmodes},~\ref{dielectric}, and ~\ref{spacing}.
-In each manipulation, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$.
+In each exploration, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$.
 In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model.
 The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system.
-In these manipulations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.
+In these calculations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.
 
@@
 \centering
-\includegraphics[width=.6\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
+\includegraphics{magnetic_mode_eigenvalues_and_interactions.pdf}
 \caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (column b) for the magnetic twomer (first row), linear threemer (second row), and triangular threemer (third row).
-All of the magnetic modes range from 3.6 eV to 3.1 eV.
+All of the magnetic modes range from 3.1 eV to 3.6 eV.
 In each system, the magnetic modes exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on their scale.
@@
 \begin{aligned}
-U_{\textrm{int}} = -$\sum_{i>j}\textbf{p}_{i}\cdot\textbf{E}$
+U_{\textrm{int}} = -\sum_{i>j}\textbf{p}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{p}_{j}
 \label{interactionenergy}
@@
 
-where $\textbf{p}_{i}$ is an eigenvector and $\textbf{E}$ is the field produced by the other dipoles.
+where $\textbf{p}_{i}$ is an eigenvector and $\boldsymbol{\Lambda}_{ij}$ is the dipole relay tensor connecting all of the electric dipoles.
 This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.
@@
 \centering
-\includegraphics[width=0.6\paperwidth]{dimer_interaction.png}
+\includegraphics[height=0.6\paperheight]{interaction_strength.pdf}
+\caption{Interactions strengths for the magnetic modes of the twomer (first row), linear threemer (second row), and triangular threemer (third row).
+We plot as a function of scaling the total interaction strength between the electric plasmons (solid line), the near-field and intermediate-field interaction strength summed (circles), and the far-field interaction strength (squares).
+In all three systems, the total interaction strengths are the same as those in Figure~\ref{magmodes} and so exhibit two mode crossings.
+The near- and intermediate- fields do not exhibit any crossings at all, and the interaction strengths for each mode simply diverge more and more with greater scaling.
+The far-field terms do exhibit one crossing towards the larger end of the scaling spectrum, and it is this interplay of far-field with near- and intermediate-field interactions that causes the mode-switching in these magnetic systems.}
+\label{interactions}
+\end{figure}
+
+To gain a more complete understanding of why mode-switching does occur in magnetic systems, we compute not only the total interaction strength for the electric plasmons of each magnetic mode, but we break that calculation into its near-, intermediate-, and far-field components.
+The results of this calculation are displayed in Figure~\ref{interactions}.
+This exploration shows definitively that the near- and intermediate-field terms contribute a total shift of the interaction strength, but the far-field term alone contributes to the mode switching.
+This can be seen quite clearly in the dipole relay tensors for the near- and intermediate-field,
+
+\begin{equation}
+\begin{aligned}
+\boldsymbol{\Lambda}_{ij}^{\textrm{NF,IF}} = 3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} -\textbf{1}
+\label{lambda_NFIF}
+\end{aligned}
+\end{equation}
+
+and the far-field,
+
+\begin{equation}
+\begin{aligned}
+\boldsymbol{\Lambda}_{ij}^{\textrm{FF}} = \textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}
+\label{lambda_FF}
+\end{aligned}
+\end{equation}
+
+where \textbf{1} is the unit dyad.
+Looking at Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF}, we see that the ordering of the terms is switched.
+The form of Equation~\ref{lambda_NFIF} shows that linearly oriented dipoles contribute more to the interaction energy than parallel dipoles.
+However, Equation~\ref{lambda_FF} has no contribution from pairs of linearly oriented dipoles and only has equal and opposite contributions from pairs of parallel dipoles [\textbf{should I cite the JPCC Steve wrote?
+Lots about ordering and arrangements of dipoles...}].
+Furthermore, the difference in sign on the two dyadic terms in the dipole relay tensors implies that the contributions to the interaction energy from those terms will be of opposite sign for the same pairs of dipoles.
+The distance-dependence of each field term for different pairs of dipoles is further outlined in Figure~\ref{dimers}.
+The opposition of signs, as well as the crossing in the far-field interaction term, are enough to explain the phenomenon of mode-switching in magnetic oligomers.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\paperwidth]{dimer_interaction.pdf}
 \caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d).
@@
 
-To gain an explanation for this mode-switching phenomenon, we investigate the fully retarded electric field.
-In Figure~\ref{dimers} we plot the near-, intermediate-, far-field, and total interaction strength as a function of MNP separation for the four possible arrangements of dipoles.
-There are two overall trends.
-At small distances, the overall interaction is dominated by the near-field term due to its $\frac{1}{r_{ij}^3}$ dependence.
-At larger distances, the overall interaction follows the intermediate-field (Figure~\ref{dimers}a and c) or the far-field (Figure~\ref{dimers}b and d).
-The second trend is the changing sign of the three field terms and the total interaction.
-This distance-dependent oscillatory nature determines the energy-ordering of pairs of dipoles, and thus influences the size-dependence of the eigenmode order in amgnetic oligomers.
-In fact, it has been well documented that system length-scale has an oscillatory impact on its eigenenergies\cite{vonPlessen2007,Pinchuk2016} For example, at some length scales, the dipole-dipole interactions in the North-South mode of the twomer are more favorable than those in the North-North mode, but this favorability changes as a function of system size.
-
-We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conforn to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms.
+We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conform to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms.
 With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties.
@@
 \centering
-\includegraphics[width=.6\paperwidth]{dielectric_study.png}
+\includegraphics{dielectric_study.pdf}
 \caption{Magnetic mode eigenvalues (column a) for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 20 nm and magnetic mode eigenvalue differences (column b) as a function of the dielectric constant of an embedding medium.
@@
 Because the modes collapse so quickly and appear to overlap at all values of $\varepsilon_b$, Figure~\ref{dielectric}b displays the difference in energy between all of the eigenmodes of each system.
-The values of $\varepsilon_b$ where the differences cross zero signfy mode-crossing.
-From these two observations we conclude that the opacity of the embedding medium weakens the overall inter-particle interactions.
+The values of $\varepsilon_b$ where the differences cross zero signify mode-crossing.
+From these two observations we conclude that increasing the dielectric constant of the embedding medium weakens the overall inter-particle interactions.
 However, this occurs differently for each of the parts of the interaction.
-All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms, but focusing on how they differ in $k$ reveals how the dielectric constant infuences the electric field.
+All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms, but focusing on how each term depends differently on $k$ in the numerator of the coupling constants (Equation~\ref{elec_hammy_2}) reveals how the dielectric constant influences the electric field.
 The near-field term contains no other $k$-dependence, and so is reduced by one factor of $\varepsilon_b$.
@@
 In other words, embedding magnetic systems in some dielectric medium causes them to act as though they are larger, effectively increasing their scale.
-This insight provides an experimental route to directly choosing the energy-ordering of magnetic modes, but the reduced splitting between modes might make such an experiment unfeasible.
+This insight provides an experimental route to directly choosing the energy-ordering of magnetic modes, but the reduced splitting between modes might make such an experiment infeasible.
 
@@
 \centering
-\includegraphics[width=.6\paperwidth]{spacing_study.png}
+\includegraphics[width=.6\paperwidth]{spacing_study.pdf}
 \caption{Magnetic mode eigenvalues for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle separation in units of radii.
-As the separation distance increases, the magnetic mode eigenvalues converge to and oscillate about the single particle frequency, exhibiting mutliple crossings.
+As the separation distance increases, the magnetic mode eigenvalues converge to and oscillate about the single particle frequency, exhibiting multiple crossings.
 As in Equation~\ref{elec_hammy_2}, the interaction strength decays with increasing separation and oscillates due to its dependence on trigonometric functions.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The ``Acknowledgement'' section can be given in all manuscript
-%% classes.  This should be given within the ``acknowledgement''
+%% The ``Acknowledgment'' section can be given in all manuscript
+%% classes.  This should be given within the ``acknowledgment''
 %% environment, which will make the correct section or running title.

### 2017-05-21 chains/chains.py

@@ -31,7 +31,7 @@ for epsb in range(1,2):
 	N_S = []
 	interaction = [[],[],[]]
 	#NSNS = []
-	for r in range (1,31):
+	for r in range (1,2):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
@@ -133,12 +133,13 @@ for epsb in range(1,2):
 					r_unit = (alpha*w_0**2)/(Rmag*(c**2))
 					exponent = np.exp(1j*w_0*Rmag/c)
 					coupling += -(hbar/elec)*wsp*(((r_unit * (unit_dyad_term - n_dyad_term) + (r_cubed - 1j*r_squared) * (3*n_dyad_term - unit_dyad_term))) * exponent)
-			'''x,y = zip(*Loc)
+			x,y = zip(*Loc)
 			u,v = zip(*vec)
 			plt.quiver(x,y,u,v)
 			plt.title("radius = " + str(r))
-			plt.show()'''
-			#raw_input()
+			plt.show()
+			raw_input()
+			np.savetxt('mode_vec_'+ str(mode) + '.txt',np.real(vec))
 			for cent in range(0,3):
 				cross = []
 				for part in range(0,numPart):
@@ -183,14 +184,5 @@ for epsb in range(1,2):
 	plt.ylabel('Energy (eV)')
 	plt.xlabel('Particle Radius r_0 (nm)')
 	plt.show()
-	#plt.savefig('threemer_eigenvalues.pdf')
-
-	'''plt.figure()
-	plt.plot(r,interaction[0],r,interaction[1],r,interaction[2],linewidth=3)
-	plt.legend(['NNN','N-S','NSN'])
-	plt.ylabel('Energy (eV)')
-	plt.xlabel('Particle Radius r_0 (nm)')
-	plt.savefig('threemer_interactions.pdf')'''
-	#np.savetxt('_'.join([str(epsb),'NN.txt']),NN)
-	#np.savetxt('_'.join([str(epsb),'NS.txt']),NS)
+	
 

### 2017-05-21 chains/mode_plotter.py

@@ -1,0 +1,70 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import pandas as pd
+
+bem_NNN = [3.614, 3.602, 3.564, 3.494, 3.412, 3.31, 3.2]
+bem_N_S = [3.612, 3.601, 3.566, 3.498, 3.404, 3.294, 3.18]
+bem_NSN = [3.61, 3.6, 3.57, 3.512, 3.42, 3.292, 3.12]
+bem_r = [1, 5, 10, 15, 20, 25, 30]
+
+NNN = np.loadtxt('NNN.txt')
+NSN = np.loadtxt('NSN.txt')
+N_S = np.loadtxt('N_S.txt')
+
+NNN_NSN_diff = np.subtract(NNN,NSN)
+NNN_N_S_diff = np.subtract(NNN,N_S)
+NSN_N_S_diff = np.subtract(NSN,N_S)
+
+NNN_int = np.loadtxt('NNN_coupling.txt')
+NSN_int = np.loadtxt('NSN_coupling.txt')
+N_S_int = np.loadtxt('N_S_coupling.txt')
+
+NNN_nearmid = np.loadtxt('NNN_near_mid.txt')
+NNN_far = np.loadtxt('NNN_far.txt')
+NSN_nearmid = np.loadtxt('NSN_near_mid.txt')
+NSN_far = np.loadtxt('NSN_far.txt')
+N_S_nearmid = np.loadtxt('N_S_near_mid.txt')
+N_S_far = np.loadtxt('N_S_far.txt')
+
+r = np.linspace(1,30,30)
+epsb = np.linspace(1,3,21)
+
+NNN_smooth = spline(bem_r,bem_NNN,r)
+N_S_smooth = spline(bem_r,bem_N_S,r)
+NSN_smooth = spline(bem_r,bem_NSN,r)
+print 'boop'
+'''plt.figure()
+plt.plot(r,NNN,r,NSN,r,N_S,r,NNN_smooth,r,NSN_smooth,r,N_S_smooth,linewidth=3)
+plt.legend(['NNN','NSN','N-S','BEM NNN','BEM N-S','BEM NSN'])
+plt.ylabel('Energy (eV)')
+plt.xlabel('Particle Radius r_0 (nm)')
+#plt.show()
+plt.savefig('threemer_eigenvalues_new.pdf')'''
+#
+
+plt.figure()
[…]

### 2017-05-21 dimer/dimer.py

@@ -28,17 +28,17 @@ collinear = [np.array([1,0]),np.array([1,0])]
 antiparallel = [np.array([0,1]),np.array([0,-1])]
 parallel = [np.array([0,1]),np.array([0,1])]
 anticollinear = [np.array([1,0]),np.array([-1,0])]
-r = 10
+r = 30
 elec = 1.60217662e-19 # regular coulombs
 numPart = 2; #number of particles
-a0 = 30e-7; #sphere radius in cm
+a0 = r*(1e-7); #sphere radius in cm
 
 ''' now determine geometry.'''
 
 # make unit vectors in centimeters.
-for number in range(0,481):
-	#dist = 
-	sep = ((number+20)*1e-7)+2*a0
+for number in range(0,101):
+	dist = number/10.
+	sep = dist*a0+(2*a0)
 	Loc = [np.array([sep/2, 0]),np.array([-sep/2, 0])]
 
 	#Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
@@ -95,7 +95,7 @@ for number in range(0,481):
 	anco_tot.append(anco_near[number] + anco_int[number] + anco_far[number])
 	para_tot.append(para_near[number] + para_int[number] + para_far[number])
 #print coll_tot
-sep = np.linspace(20,500,481)
+sep = np.linspace(0,10,101)
 plt.figure(1)
 plt.plot(sep,coll_near,sep,coll_int,sep,coll_far,sep,coll_tot,lw=3)
 plt.xlabel('Separation Distance (nm)')

### 2017-05-21 trimer_ring/ring_trimer.py

@@ -4,9 +4,9 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-bem_r = [1, 5, 10, 15, 20, 25]
-bem_NN = [3.616, 3.604, 3.558, 3.482, 3.402, 3.31]
-bem_NS = [3.61, 3.6, 3.568, 3.51, 3.416, 3.288]
+bem_r = [1, 5, 10, 15, 20, 25, 30]
+bem_NN = [3.616, 3.604, 3.558, 3.482, 3.402, 3.31, 3.19]
+bem_NS = [3.61, 3.6, 3.568, 3.51, 3.416, 3.288, 3.11]
 
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
@@ -27,6 +27,9 @@ wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 for epsb in range(1,2):
 	NN = []
 	NS = []
+	NF = [[],[]]
+	IF = [[],[]]
+	FF = [[],[]]
 	for r in range (1,31):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
@@ -106,6 +109,9 @@ for epsb in range(1,2):
 			vec = eigenVectors[:,(2*numPart)-(mode+1)]
 			vec = np.reshape(vec,[numPart,2])
 			coupling = 0
+			nearfield = 0
+			midfield = 0
+			farfield = 0
 			for x in range(0,numPart):
 				for y in range(x,numPart):
 					if x == y:
@@ -121,6 +127,9 @@ for epsb in range(1,2):
 					r_unit = (alpha*w_0**2)/(Rmag*(c**2))
 					exponent = np.exp(1j*w_0*Rmag/c)
 					coupling += -(hbar/elec)*wsp*(((r_unit * (unit_dyad_term - n_dyad_term) + (r_cubed - 1j*r_squared) * (3*n_dyad_term - unit_dyad_term))) * exponent)
+					nearfield += -(hbar/elec) * wsp * r_cubed*exponent*(3*n_dyad_term - unit_dyad_term)
[…]

### 2017-05-21 varying_particle_number/big_twomer.py

@@ -1,0 +1,146 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10; #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+
+for r in range(100,101):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r
+	''' now determine geometry.'''
+	print index
+	# make unit vectors in centimeters.
+	rij = 2.75*a0
+	part_per_ring = numPart/2 + 1
+	theta = 2*math.pi/part_per_ring
+	phi = theta/2.
+	#print theta
+	#print phi
+	#print np.cos(phi)
+	#print np.sin(phi)
+	cent_dist = rij/(2*np.tan(phi))
+	part_to_cent = math.sqrt((rij/2)**2 + (cent_dist)**2)
+	centers = [np.array([-cent_dist,0]),np.array([cent_dist,0])]
+	#print centers
+	places = []
+	for num in range(part_per_ring-1):
+		if part_per_ring%2 == 0:
+			#print 'hello'
+			places.append(centers[0] + np.array([(part_to_cent*np.cos(phi+theta*(num))),(part_to_cent*np.sin(phi+theta*(num)))]))
[…]

### 2017-05-21 varying_particle_number/particle_number.py

@@ -31,6 +31,10 @@ NN = []
 NS = []
 modes = [[],[]]
 interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NFIF = [[],[]]
 for r in np.linspace(1,30,30):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
@@ -152,6 +156,10 @@ for r in np.linspace(1,30,30):
 		#print vec
 		#raw_input()
 		coupling = 0
+		nearfield = 0
+		midfield = 0
+		farfield = 0
+		partial_sum = 0
 		for x in range(0,numPart):
 			for y in range(x,numPart):
 				if x == y:
@@ -167,6 +175,10 @@ for r in np.linspace(1,30,30):
 				r_unit = (alpha*w_0**2)/(Rmag*(c**2))
 				exponent = np.exp(1j*w_0*Rmag/c)
 				coupling += -(hbar/elec)*wsp*(((r_unit * (unit_dyad_term - n_dyad_term) + (r_cubed - 1j*r_squared) * (3*n_dyad_term - unit_dyad_term))) * exponent)
+				nearfield += -(hbar/elec) * wsp * r_cubed*exponent*(3*n_dyad_term - unit_dyad_term)
+				midfield += -(hbar/elec) * wsp * -1j*r_squared * (3*n_dyad_term - unit_dyad_term) * exponent
+				farfield += -(hbar/elec) * wsp * r_unit * exponent * (unit_dyad_term - n_dyad_term)
+				#partial_sum += (nearfield + midfield)/2
 
 
 
@@ -175,9 +187,17 @@ for r in np.linspace(1,30,30):
 		if np.isclose(abs(np.sum(vec)),0):
 			modes[0].append(eigen[(2*numPart)-(mode+1)])
 			interaction[0].append(coupling)
+			NF[0].append(nearfield)
+			IF[0].append(midfield)
+			FF[0].append(farfield)
+			#NFIF[0].append(partial_sum)
 		else:
 			modes[1].append(eigen[(2*numPart)-(mode+1)])
 			interaction[1].append(coupling)
+			NF[1].append(nearfield)
+			IF[1].append(midfield)
+			FF[1].append(farfield)
+			#NFIF[1].append(partial_sum)
 
 
[…]

### 2017-05-23 may_paper/draft_2.0.tex
more paper stuff

@@
 \begin{tocentry}
-\includegraphics{toc_graphic.pdf}
+\includegraphics{toc_graphic_2.pdf}
 
@@
 We show through theory and simulation that the energy ordering of the magnetic resonances of few-oligomer systems depends on size, scale, and environment in ways that purely electric plasmons do not.
-We show that the dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation.
-We highlight the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods.
+The dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation.
+This work highlights the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods.
 \end{abstract}
@@
 Cherqui's model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions.
-As a result, while it accurately predicted the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation.
-An explanation was needed to determine why the tight-binding model would predict different energy-ordering than full-wave simulations.
+As a result, while it accurately predicted the magnetic eigenmodes, it inaccurately described the energy ordering predicted by full-wave simulation.
+An explanation was needed to determine why the tight-binding model would predict different energy-ordering.
 
@@
 
-where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}.
+\noindent where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}.
 To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$.
@@
 H = 
-\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i>j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{\varepsilon_b}\sum_{i>j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
 + g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
@@
 
-In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$.
+In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$ and $\omega$ is the frequency of each collective mode.
 Additionally, $r_{ij}$ is the distance between the ith and jth LSPRs and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPRs.
@@
 The triangular threemer supports an all in-phase mode (All-North, or AN) and two degenerate out-of-phase modes (North-South, or NS).
-These modes and their relative magnetic fields are depicted in Figures~\ref{magmodes},~\ref{dielectric}, and ~\ref{spacing}.
+These modes and their relative magnetic fields are depicted as insets in Figures~\ref{magmodes},~\ref{interaction_strength},~\ref{dielectric}, and~\ref{spacing}.
 In each exploration, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$.
@@
 
-where $\textbf{p}_{i}$ is an eigenvector and $\boldsymbol{\Lambda}_{ij}$ is the dipole relay tensor connecting all of the electric dipoles.
+\noindent where $\textbf{p}_{i}$ is an eigenvector and $\boldsymbol{\Lambda}_{ij}$ is the dipole relay tensor connecting all of the electric dipoles.
 This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.
@@
 \centering
-\includegraphics[height=0.6\paperheight]{interaction_strength.pdf}
+\includegraphics{interaction_strength.pdf}
 \caption{Interactions strengths for the magnetic modes of the twomer (first row), linear threemer (second row), and triangular threemer (third row).
-We plot as a function of scaling the total interaction strength between the electric plasmons (solid line), the near-field and intermediate-field interaction strength summed (circles), and the far-field interaction strength (squares).
-In all three systems, the total interaction strengths are the same as those in Figure~\ref{magmodes} and so exhibit two mode crossings.
-The near- and intermediate- fields do not exhibit any crossings at all, and the interaction strengths for each mode simply diverge more and more with greater scaling.
-The far-field terms do exhibit one crossing towards the larger end of the scaling spectrum, and it is this interplay of far-field with near- and intermediate-field interactions that causes the mode-switching in these magnetic systems.}
+We plot the total interaction strength between the electric plasmons (solid line), the near-field and intermediate-field interaction strength summed (circles), and the far-field interaction strength (squares) as a function of scaling.
+The near- and intermediate- fields do not exhibit any crossings and diverge with greater scaling.
+The far-field terms exhibit one crossing.
+The interplay of far-field with near- and intermediate-field interactions causes mode-switching in magnetic systems.}
 \label{interactions}
@@
 
-To gain a more complete understanding of why mode-switching does occur in magnetic systems, we compute not only the total interaction strength for the electric plasmons of each magnetic mode, but we break that calculation into its near-, intermediate-, and far-field components.
-The results of this calculation are displayed in Figure~\ref{interactions}.
-This exploration shows definitively that the near- and intermediate-field terms contribute a total shift of the interaction strength, but the far-field term alone contributes to the mode switching.
-This can be seen quite clearly in the dipole relay tensors for the near- and intermediate-field,
+To gain a more complete understanding of this mode-switchings, we compute the total interaction strength for the electric plasmons of each magnetic mode and we break that calculation into its near-, intermediate-, and far-field components.
+Figure~\ref{interactions} shows that the near- and intermediate-field terms contribute a total shift of the interaction strength, the far-field term alone contributes to the mode switching.
+This can be seen in the dipole relay tensors for the near- and intermediate-field,
 
@@
 \begin{aligned}
-\boldsymbol{\Lambda}_{ij}^{\textrm{NF,IF}} = 3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} -\textbf{1}
+\boldsymbol{\Lambda}_{ij}^{\textrm{NF,IF}} \propto 3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} -\textbf{1}
 \label{lambda_NFIF}
@@
 
-and the far-field,
+\noindent and the far-field,
 
@@
 \begin{aligned}
-\boldsymbol{\Lambda}_{ij}^{\textrm{FF}} = \textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}
+\boldsymbol{\Lambda}_{ij}^{\textrm{FF}} \propto \textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}
 \label{lambda_FF}
@@
 
-where \textbf{1} is the unit dyad.
-Looking at Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF}, we see that the ordering of the terms is switched.
-The form of Equation~\ref{lambda_NFIF} shows that linearly oriented dipoles contribute more to the interaction energy than parallel dipoles.
-However, Equation~\ref{lambda_FF} has no contribution from pairs of linearly oriented dipoles and only has equal and opposite contributions from pairs of parallel dipoles [\textbf{should I cite the JPCC Steve wrote?
-Lots about ordering and arrangements of dipoles...}].
-Furthermore, the difference in sign on the two dyadic terms in the dipole relay tensors implies that the contributions to the interaction energy from those terms will be of opposite sign for the same pairs of dipoles.
-The distance-dependence of each field term for different pairs of dipoles is further outlined in Figure~\ref{dimers}.
-The opposition of signs, as well as the crossing in the far-field interaction term, are enough to explain the phenomenon of mode-switching in magnetic oligomers.
+\noindent where \textbf{1} is the unit dyad.
+Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF} differ by a factor of 3 on the unit vector term and an overall factor of -1.
+For this reason, collinear and anticollinear interact more strongly in the near- and intermediate-fields.
+However, linearly oriented dipoles do not interact through the far-field at all and only parallel and antiparallel dipoles contribute to this term.
+[\textbf{should I cite the JPCC Steve wrote?
+Lots about ordering and arrangements of dipoles...}] The factor of -1 difference between Equations~\ref{lambda_NFIF} and ~\ref{lambda_FF} further implies that parallel and anti-parallel arrangements of dipoles will contribute interaction energies of opposite sign.
+The distance-dependence of each field term for different orientations of dipoles is further outlined in Figure~\ref{dimers}.
+The opposition of signs, as well as the crossing in the far-field interaction term, explain the phenomenon of mode-switching in magnetic oligomers.
 
@@
 \centering
-\includegraphics[width=0.6\paperwidth]{dimer_interaction.pdf}
+\includegraphics{dimer_interaction.pdf}
 \caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d).
@@
 
-We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conform to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms.
+We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conform to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is due to the interplay of the three parts of the fully reatrded electric field.
+Most notably, without the inclusion of the far-field term and all inter-particle interactions, no mode-switching is observed.
 With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties.
@@
 However, this occurs differently for each of the parts of the interaction.
-All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms, but focusing on how each term depends differently on $k$ in the numerator of the coupling constants (Equation~\ref{elec_hammy_2}) reveals how the dielectric constant influences the electric field.
-The near-field term contains no other $k$-dependence, and so is reduced by one factor of $\varepsilon_b$.
-The intermediate-field term is linear in $k$, so it is reduced by a factor of $\sqrt{\varepsilon_b}$.
-Lastly, the far-field term is quadratic in $k$, so all $\varepsilon_b$-dependence is removed, besides that dependence previously mentioned.
+All of the field terms contain similar $k$-dependence through $\alpha_{\textrm{sp}}'$ and the trigonometric terms.
+Focusing on the different $k$-dependence in each of the coupling contants (~\ref{elec_hammy_2}) reveals the infuence of the dielectric constant on the electric field.
+$g_{ij}^\textrm{NF}$ contains no other $k$-dependence, so the near-field contribution is reduced by one factor of $\varepsilon_b$.
+$g_{ij}^\textrm{IF}$ is linear in $k$, so it is reduced by a factor of $\sqrt{\varepsilon_b}$.
+Lastly,  $g_{ij}^\textrm{FF}$ is quadratic in $k$, so all $\varepsilon_b$-dependence is removed, besides that dependence previously mentioned.
 At higher values of the dielectric constant the far-field term dominates, much like the way particles that are far apart interact primarily through their far-fields (Figure~\ref{dimers}b and d).
@@
 \centering
-\includegraphics[width=.6\paperwidth]{spacing_study.pdf}
+\includegraphics{spacing_study.pdf}
 \caption{Magnetic mode eigenvalues for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a function of nearest neighbor particle separation in units of radii.
@@
 
-There is also active research on tuning the size and shape of a plasmonic aggregate using various polymers\cite{Ginger2017} or DNA\cite{DanLuo2009,NaLiu2017}.
+Another topic of great interest is tuning the size and shape of a plasmonic aggregate using various polymers\cite{Ginger2017} or DNA\cite{DanLuo2009,NaLiu2017}.
 Here, we implement the idea of continuously distorting the nearest-neighbor spacing, from touching to tens of radii apart.
@@
 \section{Conclusion}
-We have shown that magnetic systems composed on the few-oligomer scale exhibit tunable resonances with dynamic spectral ordering.
+We have shown that magnetic systems on the few-oligomer scale exhibit tunable resonances with dynamic spectral ordering.
+This unique property is due to the interplay of near-, intermediate-, and far-field interactions and the variation of those interactions with size, distance, and the dielectric constant of the environment.
 However, we stress that the systems studied in this work were chosen due to their theoretical simplicity.

### 2017-05-31 chains/chains.py
some new code, some new paper stuff

@@ -115,74 +115,41 @@ for epsb in range(1,2):
 				#print eigen
 			    #w_old = w_0
 			    #w_0 = eigen[2*numPart-1]
-			vec = eigenVectors[:,(2*numPart)-(mode+1)]
-			vec = np.reshape(vec,[numPart,2])
-			coupling = 0
-			for x in range(0,numPart):
-				for y in range(x,numPart):
-					if x == y:
-						continue
-					else:
-						pass
-					Rmag = math.hypot(Loc[x][0]-Loc[y][0], Loc[x][1]-Loc[y][1])
-					unit_vector = (Loc[x] - Loc[y])/Rmag
-					unit_dyad_term = np.dot(vec[x],vec[y])
-					n_dyad_term = np.dot(vec[x],unit_vector)*np.dot(unit_vector,vec[y])
-					r_cubed = alpha/(Rmag**3) #this is the 1/r^3 term (static)
-					r_squared = (alpha*w_0)/(c*(Rmag**2)) #this is the 1/r^2 term (imaginary part)
-					r_unit = (alpha*w_0**2)/(Rmag*(c**2))
-					exponent = np.exp(1j*w_0*Rmag/c)
-					coupling += -(hbar/elec)*wsp*(((r_unit * (unit_dyad_term - n_dyad_term) + (r_cubed - 1j*r_squared) * (3*n_dyad_term - unit_dyad_term))) * exponent)
-			x,y = zip(*Loc)
+			vec = np.reshape(eigenVectors[:,2*numPart - (mode+1)],[numPart,2])
+			grid_x = 2.5*e2
+			grid_y = 2.5*e1
+			size = 251
+			Bfield_total = np.zeros((size,size),dtype=float)
+			for number in range(0,14):
+				point = Loc[number]
+				xcount = 0
+				Bfield = np.empty((size,size),dtype=float)
+				for xx in np.linspace(-grid_y,grid_y,size):
+					ycount = 0
+					for yy in np.linspace(-4.5*e2,2.5*e2,size):
+						rmag = np.sqrt((point[0]-yy)**2 + (point[1]-xx)**2)
+						nhat = -([yy,xx]-point)/rmag
+						#print rmag
+						#raw_input()
+						#vec[number][0],vec[number][1] = vec[number][1],vec[number][0]
+						if rmag < .5*a0:
+							Bfield[xcount,ycount] = 0
+						else:
[…]

### 2017-05-31 coronine_ret/fixed_vec_6mer.py

@@ -1,0 +1,137 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+dipole = [] # doubly degenerate
+no_dipole = [] # doubly degenerate
+all_N = [] #all north
+out_N_in_S = [] # that weird "excited state"
+alt_NS = [] # maximally out of phase magnets
+center = np.zeros(7,dtype=object)
+mode = []
+interaction = []
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+for r in range(1,31):
+	elec = 1.60217662e-19 # regular coulombs
+	numPart = 24; #number of particles
+	a0 = r*10**-7; #sphere radius in cm
+	index = (r - 1) * 10
+	''' now determine geometry.'''
+
+	# make unit vectors in centimeters.
+	e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
+	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),np.array([0,-2*e1]),
+		   np.array([e2,-e1]),np.array([e2,e1]),np.array([2*e2,2*e1]),np.array([3*e2,e1]),
+		   np.array([3*e2,-e1]),np.array([2*e2,-2*e1]),np.array([2*e2,-4*e1]),np.array([e2,-5*e1]),
+		   np.array([0,-4*e1]),np.array([-e2,-5*e1]),np.array([-2*e2,-4*e1]),np.array([-2*e2,-2*e1]),
+		   np.array([-3*e2,-e1]),np.array([-3*e2,e1]),np.array([-2*e2,2*e1]),np.array([-2*e2,4*e1]),
[…]

### 2017-05-31 may_figures/fields.py

@@ -1,0 +1,241 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+static_NN = []
+static_NS = []
+bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
+bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10; #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+NN = []
+NS = []
+modes = [[],[]]
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NFIF = [[],[]]
+NS_vec = np.loadtxt('mode_0_vec.txt')
+NN_vec = np.loadtxt('mode_1_vec.txt')
+for r in np.linspace(1,1,1):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r
+	''' now determine geometry.'''
+	print index
+	# make unit vectors in centimeters.
+	rij = 3*a0
+	part_per_ring = numPart/2 + 1
+	theta = 2*math.pi/part_per_ring
+	phi = theta/2.
+	#print theta
+	#print phi
+	#print np.cos(phi)
[…]

### 2017-05-31 polarizability_nonsense/diagonalize_polarize.py

@@ -17,21 +17,21 @@ ns_sec = np.loadtxt('../../unfused_twomer/NS_corners')'''
 
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 
-for r in range(1,30):
+for r in range(1,31):
 	elec = 1.60217662e-19 # regular coulombs
 	numPart = 6 #number of particles
 	a0 = r*10**-7 #sphere radius in cm
-	mie_index = (r*10)
-	index = r-1
+	mie_index = (r*10)-10
+	index = r
 	ll = 1
 	''' now determine geometry.'''
 	''' begin with electric dipoles on the six-member ring '''
 	# make unit vectors in centimeters.
-	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
-	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
 	mag_x = 2*e2
 	mag_y = 3*e1
-	rad = 2.2*a0
+	rad = 3*a0
 	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([-e2,-e1]),
 		   np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
 	#pol_vectors = [np.array([-1/math.sqrt(3),0]),np.array([-0.5/math.sqrt(3),-math.sqrt(3)/2/math.sqrt(3)]),np.array([0.5/math.sqrt(3),-math.sqrt(3)/2/math.sqrt(3)]),
@@ -68,65 +68,73 @@ for r in range(1,30):
 	eigen = np.zeros(2*numPart)
 	count = 1
 	H = np.zeros((2*numPart,2*numPart))
-	while np.sqrt(np.square(w_0*hbar/elec - eigen[2*numPart-1])) > 0.00000001:
-		if count == 1:
-			w_0 = wsp_0
-			count = count + 1
-			wsp = wsp_0
+	for mode in range(0,2):
+		while np.sqrt(np.square(w_0*hbar/elec - eigen[2*numPart-1])) > 0.00000001:
[…]

### 2017-05-31 varying_particle_number/fields.py

@@ -1,0 +1,193 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+static_NN = []
+static_NS = []
+bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
+bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10; #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+NN = []
+NS = []
+modes = [[],[]]
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NFIF = [[],[]]
+for r in np.linspace(1,1,1):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r
+	''' now determine geometry.'''
+	print index
+	# make unit vectors in centimeters.
+	rij = 3*a0
+	e1 = .5*rij
+	e2 = rij*math.sqrt(3)/2
+	part_per_ring = numPart/2 + 1
+	theta = 2*math.pi/part_per_ring
+	phi = theta/2.
+	#print theta
+	#print phi
+	#print np.cos(phi)
+	#print np.sin(phi)
+	cent_dist = rij/(2*np.tan(phi))
[…]

### 2017-05-31 varying_particle_number/particle_number.py

@@ -13,7 +13,7 @@ mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 crossing = []
 elec = 1.60217662e-19 # regular coulombs
 
-numPart = 10; #number of particles
+numPart = 10 #number of particles
 
 me = 9.10938291e-28; # electron mass in g
 ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
@@ -27,18 +27,11 @@ Eplasma = 1.46599161e-18; # J
 gamma = 0.05*elec/(hbar*16)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 epsb = 1
-NN = []
-NS = []
-modes = [[],[]]
-interaction = [[],[]]
-NF = [[],[]]
-IF = [[],[]]
-FF = [[],[]]
-NFIF = [[],[]]
-for r in np.linspace(1,30,30):
+
+for r in range(1,2):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
-	index = r
+	index = (r-1)*10
 	''' now determine geometry.'''
 	print index
 	# make unit vectors in centimeters.
@@ -89,12 +82,12 @@ for r in np.linspace(1,30,30):
 
 	count = 1
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
-	wsp_0 = (mie_omegas[index*10 - 10])*elec/hbar
+	wsp_0 = mie_omegas[index]*elec/hbar
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
-	for mode in range(0,2):
-		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.00001:
+	for mode in range(0,3):
+		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.0000001:
 			if count == 1:
 				wsp = wsp_0
 				count = count + 1
@@ -109,7 +102,7 @@ for r in np.linspace(1,30,30):
 			gamma_ret = gamma+tau*(w_0**2) # I pulled this from the beats paper
 			gamma_eV = gamma_ret*hbar/elec
 			#wsp = wsp_0
[…]

### 2018-01-16 paper_fall_2017/draft_fall_2017.tex
lots of new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}
\date{September 4, 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Tunable Spectral Ordering and Directional Radiation in Magnetic Plasmon Oligomers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{plasmon, hybridization, magnetic, retardation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Magnetic plasmon resonances, the collective response of cyclic arrangements of plasmonic nanoparticles, have been of great recent interest due to their ability to couple to both the electric and magnetic field of light. At small sizes, these metal nanoparticle aggregates, called magnetic oligomers, satisfy the quasistatic approximation and couple weakly to the magnetic field of light. At large sizes, the magnetic and electric effects interfere with one another, resulting in size- and frequency-dependent radiative properties. This allows for tunable and controllable directionality of light scattered from these systems, opening the path to applications that require direct control over the directionality of specific colors of light.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{introduction}
The collective plasmon resonances of cyclic arrangements of metal nanoparticles (MNPs), called magnetic plasmon oligomers, are known to couple to and enhance both the electric and magnetic field of light [cites]. Theoretical studies of such oligomers has often focused on either single oligomers or infinite planar arrays [cites], leaving many open questions surrunding the properties of mutli-oligomer clusters in this interemdiate size regime [cites]. In fact, there is still disagreement in the field on the energy-ordering of multiple magnetic plasmons, the effect of size on their energy ordering, and the applicability of the quasistatic approximation. While much work has been done to describe MNP dimers, chains, and arrays beyond the quasistatic limit, fully retarded models combined with full-wave simulation have not been applied to magnetic plasmon oligomers. Interestingly, because these systems store energy in their magnetic fields, it is apparent that retardation effects are in fact necessary to properly describe them.

In this work, we extend the coupled dipole approximation to include retardation effects and apply it to multi-oligomer MNP clusters to determine their magnetic normal modes and eigenenergies. In doing so, we explain a previously reported discrepancy and discover that the magnetic modes change spectral order with changing system size. Comparing these results with a quasistatic model produces an approximate limit upon the applicability of static approxiamtions. Furthermore, we show using full-wave simulations that these mode crossings are observable in angle-resolved cathodoluminescence (CL) spectroscopy, electron energy loss spectroscopy (EELS) maps, and CL maps. Finally, we show that the overlapping and interfering electric and magnetic plasmons of multi-oligomer systems produce directional radiation that would not be observable with purely electric resonances. Understanding the spectral ordering and optical properties of plasmon oligomers will aid in the construction of devices for nanoscale etching, enhancement of magnetic dipole transitions in the rare earth ions, or tunable, multi-wavelength cloaking devices.

(((due to their applicability to biological sensing and imaging, electromagnetic cloaking, and information processing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano,Zhang2006,NordHal2011,NordHal2012}. These collective magnetic responses occur when three or more metal nanoparticles are arranged on the vertices of a polygon, a structure known as a magnetic plasmon oligomer. The properties of single oligomers have been well-documented, as well as the properties of infinite metal nanoparticle arrays, but there are open questions regarding the behavior of few-oligomer systems.\cite{Dionne2011,Dionne2016,Weick2013,Engheta2017,Cherqui2014,Cherqui2016} Problems such as magnetic plasmon hybridization and electric-magnetic plasmon interference are still open and are the key to utilizing the unique optical properties of magnetic oligomers.

Aggregates of metal nanoparticles resembling conjugated hydrocarbon rings have been of particular interest due to their strong enhancement of magnetic fields [\textbf{cite this 2017 paper on metal clusters, also Engheta 2017}]. Because of their unique ability to couple efficiently to both electric and magnetic fields, they make an excellent model system with which to study the size-dependence of magnetic effects in metal nanoparticle oligomers. Specifically, using conjugated hydrocarbon-like aggregates, we show that the energy ordering of magnetic plasmons is tunable, a result not found using quasistatic models. Furthermore, the interference between magnetic and electric plasmons on one oligomer is shown to be size- and frequency-dependent.

In the single-oligomer regime, the quasistatic approximation is good and describes magnetic oligomers accurately\cite{Nord2006,Dionne2016}. While retardation effects have been considered in studies of both large MNPs and infinite MNP arrays\cite{Abajo2008,Gu2010,vonPlessen2007,Rechbacher2003,Kottman2001,Schatz2003,Royer2005,Chumanov2010,Pinchuk2016}, the breakdown of the quasistatic approximation and size-dependent tunability have not been studied in magnetic oligomers. Incorporating retardation effects into a simple model, such as the tight-binding model previously utilized\cite{Cherqui2014}, is the first step to accurately modeling magnetic plasmon-supporting aggregates. When augmented with retardation effects, this model not only explains the reason why a quasistatic model and full-wave simulations should disagree, but it shows in addition that the magnetic modes of planar, few-oligomer systems exhibit dynamic and tunable energy-ordering. As suggested by previous work, single magnetic oligomers exhibit electric-magnetic interferences.\cite{Dionne2011}  Planar, multi-oligomer systems exhibit similar properties with both size- and frequency-dependence. As a result, it is possible to use magnetic oligomers to scatter light of specific colors in different directions, suggesting increased tunability and control of light.)))

\section{Model Systems and Magnetic Plasmon Resonances}

\begin{figure}
\includegraphics[width=6.5in]{fields_new_arrows.pdf}
\caption{Magnetic field plots of the two-ring (a and b), linear three-ring (c, d, and e), and triangular three-ring (f, g, and h) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The nodeless magnetic plasmons (b, e, and h) support a net magnetic dipole moment and are excitable by the magnetic field of light. The single-node magnetic plasmons (a, c, f, and g) support net electric dipole moments. The two-node magnetic mode of the linear three-ring system is inaccessible by light.}
\label{field_plots}
\end{figure}

To begin, we investigate a model system comprising two hexagonal rings fused on a side, resulting in a ten MNP aggregate resembling the molecule naphthalene. These conjugated hydrocarbon-like systems have been of great interest recently, and this system in particular represents the simplest of such systems supporting more than one magnetic plasmon. Once this system has been investigated in full, it will be extended to a more detailed system, and finally the concepts will be applied to aggregates that have been the focus of more recent research. The aggregates presented are composed of identical silver MNPs. In order to compute their collective eigenmodes and eigenenergies, we map the individual electric dipole plasmon of each MNP onto a harmonic oscillator and couple them through dipole-dipole interactions as follows\cite{ARPC}

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{equation_of_motion}
\end{equation}

\noindent where $\omega_{\textrm{sp}}$ is the natural frequency of a single electric plasmon, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the surface plasmon effective mass defined by the polarizability $\alpha_{\textrm{sp}}$, the plasmon oscillator dipole moment $\textbf{d}_i = e\textbf{q}_i$, and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field from the $j^{\textrm{th}}$ dipole at the position of the $i^{\textrm{th}}$ dipole and is defined as

\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{k^2}{r_{ij}}\left(\textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j.
\label{electric_field_lambda}
\end{equation}

\noindent Here, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ is the wavenumber of the collective mode with frequency $\omega$, and $\varepsilon_b$ is the dielectric constant of the background medium. The fully retarded electric field contains three important terms. The term with $1/r_{ij}^3$-dependence is called the near-field, because it decays very quickly with increasing distance. In fact, this term is what remains when taking the quasistatic limit. The second term, with the $k/r_{ij}^2$-dependence, is the intermediate-field term. The third term, with $k^2/r_{ij}$-dependence, is the far-field term, called such because it dominates after the other two have decayed. All three terms are dressed by a complex exponential, which depends both on $k$ and on $r_{ij}$. This shows that at specific separation distances, the interaction energies can change sign and go from energy-lowering to energy-raising. Using just the fully retarded electric field, we have incorporated all necessary retardation effects\cite{Purcell1973}.

Solving the system of Equations~\ref{equation_of_motion} for all of the dipoles in a single aggregate yields as many hybridized modes as there are degrees of freedom, in this case, two times the number of particles. Similarly, each system supports a number of magnetic plasmons equal to the number of oligomers. The eigenvectors of these collective modes represent the dipole moments on each nanoparticle. Figure~\ref{field_plots} shows these magnetic mode eigenvectors overlayed with plots of the signed magnetic field magnitude of each normal mode. Each mode is named for its particular magnetic field distribution after the poles of a magnet (e.g. the 2-mer's North-South and North-North mode). It is important to note which magnetic modes can couple to the far-field. The top right-hand corner of each field plot in Figure~\ref{field_plots} displays whether the magnetic mode depicted exhibits a net electric dipole, a net magnetic dipole, or neither. Because it is possible to excite both a magnetic dipole moment and an electric dipole moment orthogonal to one another in these oligomers, they exhibit tunable directionality in the light that they scatter. This will be an important discussion later in this work when outlining the properties of magnetic oligomer systems. To begin, we apply the fully retarded tight-binding model to the magnetic modes of the 2mer system to determine where and why the quasistatic approximation breaks down in magnetic oligomer systems.

\section{Spectral Ordering of Magnetic Modes in the 2-mer}
To determine the breakdown of the quasistatic limit as a function of size and the impact of incorporating retardation effects, we introduce two parameters: scale and spacing. Defining a nearest-neighbor distance between individual nanoparticles $r_{\textrm{nn}} = (s + 2)r_0$ allows both scale (changing $r_0$ with fixed $s$) and spacing (changing $s$ withfixed $r_0$) to be vary independently. Figure~\ref{scaling} shows the results of varying both $r_0$ (a-d) and $s$ (e-h) in vacuum and in water ($\varepsilon_b = 1.77$). At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits easily into a wavelength of light and the near-field dominates the electric field.\cite{Cherqui2014} As the system scale increases, the magnetic modes change order. This is due to the far-field term in Equation~\ref{electric_field_lambda} becoming strong relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b. In other words, as the system gets larger, the near-field interaction becomes less important relative to other parts of the electric field. At larger sizes, the modes switch again, recovering the spectral ordering predicted in the quasistatic limit. However, this does not mean that the quasistatic approximation is suddenly accurate again for these larger systems. Rather, both eigenmode crossings are due entirely to retardation effects. The interaction energy in each magnetic mode,

\begin{equation}
U_{\textrm{int}} = -\sum_i \textbf{d}_i \cdot \sum_{j \neq i} \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}

\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes. The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode. Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in water the crossing points are shifted towards smaller scale. This is to be expected, as the wavelength of light is compressed in a medium, meaning that light sees objects as much bigger than they really are. This analysis shows that the quasistatic approximation is good for very small magnetic oligomers in vacuum, and for smaller oligomers in medium. This can also be explained through the impact of a dielectric medium on coupling strength. While a medium should contribute an overall increase to the coupling strength (which is predicted in Figure~\ref{scaling}b and f), the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008} Through comparison with simulation (dashed lines in Figure~\ref{scaling}a), it can be shown that this simple and efficient model is accurate to within 0.05 eV and accurately describes the behavior of magnetic plasmon oligomers.

\begin{figure}
\includegraphics[width=4in]{2mer_eig_combined.pdf}
\caption{Eigenvalues and interaction energies as functions of total aggregate scale and interparticle distance for the magnetic modes of the 2mer. (a) The eigenvalues of the North-South (orange) and North-North (blue) modes for $r_0 = $ 1 to 30 nm computed using the equations of motion (solid) and compared with full-wave simulations (dashed). Note the agreement to within 0.05 eV. The modes cross twice, once at around 7 nm and a second time at around 20 nm. (b) Total (solid), near- plus intermediate-field (circles), and far-field (squares) interaction energies for each mode as a function of increasing $r_0$. The splitting between the interaction energies in the far-field has the opposite sign as in the near- and intermeidate-field, resulting in the eigenmodes crossing. (c) and (d) Magnetic mode eigenvalues as a function of increasing interparticle distance, with $r_0 =$ 15 and 30 nm, respectively. With increasing spacing, the eigenvalues tend towards the noninteracting, single-particle frequency and exhibit large oscillations and splittings. (e-h) Eigenvalues and interaction energies computed in a similar fashion to (a-d), with $\varepsilon_b = 1.77$, the dielectric constant of water.}
\label{scaling}
\end{figure}

While good for theoretical studies of system properties, scale is not tunable in real time, meaning these properties can't be easily measured. Recent research has focused heavily on finding controllable and reversible ways to manipulate the aggregation scheme of a metal nanoparticle array using tools like DNA, polymers, and stretchable embedding media\cite{Yang2016,Ginger2017,NaLiu2017,DanLuo2009}. We employ this idea by fixing the particle radii and the aggregation scheme of the structure and inflating the interparticle distances. Figure~\ref{scaling}e-h shows the results of fixing $r_0$ at 15 and 30 nm and increasing $s$. Increasing the distance between particles regardless of particle size and environment weakens the coupling as the distance approaches infinity, which can be seen in Equation~\ref{electric_field_lambda}. As a result, the collective frequencies of the magnetic modes approach the single plasmon frequency. On the way, the modes oscillate about each other, exhibiting multiple crossings. The amplitude of these crossings appears to increase with increasing particle size and with increasing background dielectric constant, which can be seen in Figure~\ref{scaling}f and h. The quasistatic approximation cannot explain this phenomenon. The fully retarded electric field contains a complex exponential term that depends on interparticle separation. It is this term that dresses all of the interaction terms in the field and changes the sign of the interaction from negative to positive at certain distances. This is clear evidence that the magnetic modes of the 2-mer are tunable in real time in a laboratory with splittings as small as 0.01 eV and as large as 0.1 eV.

The concept of magnetic plasmons switching spectral order has not been discussed in the literature. This is likely because the splittings between the modes in the systems analyzed are smaller than the spectral resolution of most detection methods, including scattering experiments and STEM/EELS. Additionally, magnetic oligomers exhibit many other electrically bright modes that are close in energy and broad, which tends to wash out most spectra. In order to make magnetic oligomers useful, either the modes must be made fewer and more narrow, or techniques must be found that can identify and utilize the modes regardless of breadth. One such method is the measurement of directional or angle-resolved scattering.

\section{Angle-Resolved Cathodoluminescence Studies on the 2mer}
Electron beam spectroscopies, such as EELS and CL, conducted in a STEM are very useful for high spatial and spectral reoslution studies of nanomaterials. While EELS measures the probability that a passing electron loses energy to the material, CL measures the probability that the material's excited behavior results in photon emission. Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize a material. Using a STEM fitted with a parabolic mirror over the sample, the user can collect emitted light with angular information within $0 \leq \theta \leq \pi/2$ and $0 \leq \phi \leq \pi$. Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes and their crossing can be observed in spectra.

Some figures and discussion.

\section{Angle-Resolved Cathodolumiescence Studies on the 3mer}
As we have seen in the section I haven't finished writing, the 3mer resembling a phenalene molecule supports not only an all-North magnetic plasmon, but two degenerate, orthogonal North-South magnetic plasmons as well. This is due to its threefold symmetry axis, or in the language of group theory, its D3h point group. Again, due to their different polarizations, the all-North mode can be distinguished from the North-South modes using angle-resolved CL spectroscopy.

Some figures and discussion.

\section{Now that we're done proving it to you, here are some systems that people are making right now!}
Data from Kagan paper. Emphasize where the magnetic dipole plasmon shows up. (Not always the lowest, but never as far away as the Kagan paper predicts.)

Some figures and discussion.

\section{Directional Scattering in the 2-mer}
It has been predicted and shown experimentally that single magnetic oligomers scatter light anisotropically when both their magnetic dipole and their electric dipole are excited by light.\cite{Dionne2011,Cherqui2016} This is evident from the difference between forward and backward scattering spectra, but can also be shown by computing the differential scattering pattern,\cite{jackson_classical_1999,schwinger1998classical}

\begin{equation}
\frac{dP}{d\Omega} = \frac{c}{8\pi}\left[r^2\hat{\textbf{n}}\cdot\sum_i\textbf{E}_i \times \sum_{j}\textbf{B}_{j}^*\right]
\label{dp_field_1}
\end{equation}

\begin{figure}
\includegraphics[width=5in]{scattering_diagrams.png}
\caption{Diagrams of the incident light and orientation of the (a and b) 2mer, (c and d) linear 3mer, and (e and f) triangular 3mer systems to be referenced with Figures~\ref{yz_scattering},~\ref{xz_scattering},~\ref{l3mer_combined}, and~\ref{t3mer_forback}.}
\label{diagrams}
\end{figure}

\noindent where $\hat{\textbf{n}}$ is the unit vector pointing to the detector a distance $r >> \lambda$ away and $\textbf{E}_i$ and $\textbf{B}_j^*$ are the electric field and conjugate magnetic inductance of the interfering collective modes of the 2mer. From here, we perform full-wave simulations to compute scattering spectra and differential scattering patterns on the 2mer and 3mers.\cite{Hohenester2012} According to the diagram in Figure~\ref{diagrams}a and b, the incident light is polarized such that the magnetic field threads the rings of the 2mer, while the electric fieldpoints along its short axis. Using the far-fields scattered by these collective dipole moments, and subsittuting them into Equation~\ref{dp_field_1}, the differential scattering becomes\cite{Engheta2006}

\begin{equation}
\frac{dP}{d\Omega} = \frac{ck^4N^2}{4\pi}\left[|\textbf{d}_{e}|^2(1-(\hat{\textbf{n}}\cdot\hat{\textbf{y}})^2) + k^2R^2|\textbf{d}_{m}|^2(1-(\hat{\textbf{n}}\cdot\hat{\textbf{z}})^2) + kR(\textbf{d}_{e}\cdot\textbf{d}_{m}^* +\textbf{d}_{e}^*\cdot\textbf{d}_{m})(\hat{\textbf{n}}\cdot\hat{\textbf{x}})\right].
\label{dp_dipoles_1}
\end{equation}

\noindent Here, $N$ is the number of particles in an aggregate, $\textbf{d}_e$ is the electric dipole moment of a single particle in the collective electric mode, $\textbf{d}_m$ is the electric dipole moment of a single particle in the collective magnetic mode, and $R$ is the radius of a cluster. In the case that $d_m = 0$, the second and third terms vanish, resulting in a scattering pattern traditionally associated with a dipole oriented in the y-direction. When $d_e = 0$, the first and third terms vanish, and the same pattern is recovered but in the z-direction. Finally, when both sets of dipole moments are non-zero, the third term contributes an overall asymmetry in the x-direction, which here is the light propagation direction. This means that when the collective electric and the collective magentic mode interfere when both are excited simultaneously. We use this model to gain intuition about and explain the results of the simulated differential scattering patterns.

\begin{figure}
\includegraphics[width=5.5in]{yz_scat.pdf}
\caption{Scattering spectra and differential scattering patterns for the 2mer in vacuum and in water. (a) Scattering spectrum for the 2mer with $r_0 =$ 1 nm and $s = 1$ displaying z-directed (red) and y-directed (blue) scattering. (b) Differential scattering pattern verifying that the z-directed scattering is much larger than the y-directed scattering. (c) Scattering spectrum for the 2mer with $r_0 =$ 20 nm and $s=1$, again with z-directed (red) and y-directed (blue) light. (d) Differential scattering pattern veryifying that at the chosen frequency, the y-directed scattering is greater than the z-directed scattering. (e-h) Scattering calculations in the same fashion as (a-d), with $\varepsilon_b = 1.77$, the dielectric constant of water.}
\label{yz_scattering}
\end{figure}

Analyzing first the y- and z-oriented scattering gives a measure of the relative strength of the electric and magnetic modes. When $d_e >> d_m$ the y-directed scattering should approach zero while the z-oriented scattering will be maximized. This can be seen quite clearly in Figure~\ref{yz_scattering}a and b, where the electric dipole mode's dominance is evident through the primarily z-oriented scattering, especially at the peak frequency (dashed black line). As discussed previously, when the oligomers are small they behave quasistatically with almost no magnetic effects, so it is expected that the purely electric physics should dominate. Figure~\ref{yz_scattering}c and d shows that at larger sizes the dominance of either y- or z-directed scattering is frequency dependent, signifying that the magnetic dipole moment can dominate the scattered light at certain frequencies. The scattering pattern in (d) corresponds to the black dashed line in (c), emphasizing the frequency at which the magnetic dipole is strongest compared to the electric dipoles. This shows that magnetic oligomers scatter light of certain colors in different directions. While Equation~\ref{dp_dipoles_1} suggests through its $R$-dependence that at large sizes the magnetic dipole moment should dominate the scattering, the presence of the individual dipole moments suggests a dependence on the oscillator strength of the collective modes. At the resonant frequency of the magnetic mode, it dominates the scattering pattern, but at other frequencies the electric dipole modes dominate. This suggests that the magnetic mode is much narrower and harder to force than the electric modes. This is interesting because this implies a method of detecting the frequency at which the all-North magnetic mode significantly impacts the optical properties of a given magnetic oligomer. Further emphasizing this is the fact that increasing the spacing between the particles shifts the resonances to higher energy, so probing at the same frequency results in a different scattering pattern, as depicted in [\textbf{Figure not done yet!}]. This offers a way to controllably choose the directionality of specific colors of light by manipulating the aggregation scheme of magnetic oligomers. These results are consistent in water as well, as shown in Figure~\ref{yz_scattering}e-h.

Using the y- and z-directed scattering to understand the relative strength of the magnetic and electric dipole moments is only one side of the story. Looking instead at the x- and z-directed scattering opens up a tool to quantify the extent to which electric and magnetic plasmons interfere with one another. As suggested by the third term of Equation~\ref{dp_dipoles_1}, in the direction of propagation we should expect to see asymmetry when both the electric dipole moment and magnetic dipole moment are of appreciable magnitude. Figure~\ref{xz_scattering} shows spectra computed in the forward and backward direction for particles of $r_0 = $ 1 nm and 20 nm (a and c) as well as differential scattering patterns in the xz-plane (b and d) in vacuum, and similarly in water (e-h). The differential scattering patterns have been computed at the frequencies that maximize the forward-to-backward ratio. As suggested by the $R$-dependence and the dependence on dipole strength in Equation~\ref{dp_dipoles_1}, at small sizes the radiation is isotropic in the forward (red) and backward (blue) direction. This again makes sense, as small oligomers are dominated by electric near-field effects. However, with increasing size, the interference term in Equation~\ref{dp_dipoles_1} begins to influence the spectrum and the scattering, leading to a large amount of directional radiation. Like before, this is dependent upon not only the size of the system but upon the oscillator strength of each mode, and so probing off resonance of the magnetic mode diminshes its influence and leads to more significant backward-directed radiation. However, at all frequencies the forward scattering is larger than the backward scattering, and even upon changing the interparticle distance this remains true. This suggests that once the magnetic mode is strong and broad enough to interfere with the electric modes, the directional radiation can not be completely turned off except by moving the particles infinitely far away from each other. Furthermore, this must be a collective effect as the constituent particles here are too small to exhibit appreciable magnetic moments and radiate unidirectionally by themselves. Magnetic dipole-electric dipole scattering interference has been predicted and observed in metal-dielectric core-shell systems and single magnetic oligomer systems, and directional or angle-resolved scattering experiments are common practice on metal nanoparticle aggregates.\cite{Dionne2011,Kivshar2012,Polman2014,Smith2014,Tsutomu2017}

\begin{figure}
\includegraphics[width=5.5in]{for_back_spectra.pdf}
\caption{Forward and backward scattering spectra and differential scattering patterns for the 2mer. (a) Forward (red) and backward (blue) scattering spectra for the 2mer with $r_0 =$ 1 nm and $s=1$ nearly overlap. (b) The isotropic radiation pattern in the forward and backward direction computed using the model in Equation~\ref{dp_dipoles_1} (blue dots) and full-wave simulations (orange line). (c) Forward (red) and backward (blue) scattering spectra for the 2mer with $r_0 =$ 20 nm and $s=1$ are vastly different, showing that the forward scattering is almost always greater than the backward scattering. (d) The differential scattering pattern at the frequency marked by the dashed line in (c) shows that the scattering is nearly unidirectional both using the model (blue dots) and simulations (orange). (e-h) Scattering spectra and patterns computed in the same way as (a-d), except with $\varepsilon = 1.77$.}
\label{xz_scattering}
\end{figure}

\section{Methods}
Here we show how to derive the equations of motion, and solve an example system of two coupled oscillators. The Hamiltonian for a system of $N$ coupled oscillators

\begin{equation}
H = \sum_{i}\frac{\textbf{p}_i^2}{2m_{\textrm{sp}}}+\frac{1}{2}m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i^2 - \frac{e}{2}\sum_{j\neq i}\textbf{q}_i\cdot\textbf{E}_j(\textbf{r}_i),
\label{hammy}
\end{equation}

\noindent where $\textbf{p}_i$ are the momenta of the plasmon oscillators with coordinates $\textbf{q}_i$, $m_{\textrm{sp}}$ is the plasmon mass, $\omega_{\textrm{sp}}$ is the plasmon frequency, and $\textbf{E}_j(\textbf{r}_i)$ is defined in Equation~\ref{electric_field_lambda}. The next step is to write Hamilton's equations of motion,

\begin{equation}
\dot{\textbf{p}}_i = -\frac{\partial H}{\partial\textbf{q}_i} = -m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i + e\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{p_dot}
\end{equation}

\noindent and

\begin{equation}
\dot{\textbf{q}}_i = \frac{\partial H}{\partial\textbf{p}_i} = \frac{\textbf{p}_i}{m_{\textrm{sp}}}.
\label{q_dot}
\end{equation}

Finally, taking another time derivative of Equation~\ref{q_dot} and plugging in Equation~\ref{p_dot}, we obtain the equation of motion

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\text\
bf{r}_i)
\label{equation_of_motion_again}
\end{equation}

\noindent which is exactly Equation~\ref{equation_of_motion}. From here, introducing time-dependence as a complex exponential, rewriting the electric field in terms of the plasmon coordinate, and performing a Fourier transform results in equations of motion in the frequency domain

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)\textbf{q}_i -\frac{e^2}{m_\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}\cdot\textbf{q}_j = 0.
\label{fourier_eom}
\end{equation}

It is this system of equations for the plasmon oscillator coordinates that we solve for the normal modes. As an example, we demonstrate this calculation for two coupled oscillators displaced and oriented along the x-axis. Knowing the dipole orientation allows us to project out the vector components and reduce the coupling term to a constant, resulting in

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{1,2}q_2 = 0
\label{fourier_eom_1}
\end{equation}

and

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{1,2}q_1 = 0.
\label{fourier_eom_2}
\end{equation}

Putting these equations of motion in matrix form allows us to solve for the eigenvalues and eigenvectors as follows.

\begin{equation}
\begin{bmatrix}
(\omega_{\textrm{sp}}^2-\omega^2) & -g_{1,2}\\
-g_{1,2} & (\omega_{\textrm{sp}}^2-\omega^2)
\end{bmatrix}
\begin{bmatrix}
q_1\\
q_2
\end{bmatrix}
=
\begin{bmatrix}
0\\
0
\end{bmatrix}
\label{eom_matrix}
\end{equation}

Finding the determinant of this matrix yields the eigenvalues of the collective modes,

\begin{equation}
\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{1,2}}.
\label{eigenvalues}
\end{equation}

\noindent Of course, the coupling terms $g_{1,2}$ in fact depend on the frequency of the collective mode, which is demonstrated in Equation~\ref{electric_field_lambda}. Because of this, the eigenvalue problem must be solved iteratively until the eigenvalues converge. This example can be extended to systems of an arbitrary number of dipoles, and this exact method is used to solve for the eigenvalues of the magnetic plasmon modes.

\section{Eigenvalue Calculations on the 3mers}
\begin{figure}
\includegraphics[width=5in]{3mer_eig_combined.pdf}
\caption{Eigenvalues and interaction energies of the magnetic modes of both the linear and triangular 3mers in vacuum and water. (a) The eigenvalues computed from the model on the three modes of the linear 3mer, showing crossing points at around 7.5 nm and 21 nm and compared with simulation results (dashed lines). (b) Interaction energies computed from Equation~\ref{interactionenergy}, with the far-field (squares) being entirely responsible for the crossing points in (a) while the near- and intermediate-field terms (circles) contribute only a net shift to the total (solid) interaction. (c and d) Similar plots to (a and b) with a background of water, which moves both crossing points to smaller size. (e) Eigenvalues as a function of interparticle spacing for particles of radius 15 nm, exhibit multiple crossings and low-amplitude oscillations when compared to larger (f) particles. (g and h) Similar results to (a and b), with a background of water, causing a net shift to lower energy of all eigenvalues and larger oscillations, but no drastic qualitative change. (i-p) Display similar results to (a-h) for the triangular 3mer. The analysis is very similar, as the eigenmodes have crossing points in similar locations and the eigenvalues and interaction energies are similarly impacted by the background of water.}
\label{3mer_eig}
\end{figure}

The model presented earlier in this paper can also be applied to the 3mer systems. Looking first at Figure~\ref{field_plots}, each 3mer supports three magnetic modes, rather than two. However, the triangular 3mer's two electric dipole modes (f and g) are degenerate. This is represented in Figure~\ref{3mer_eig}, where the plots concerning the linear 3mer have 3 traces and the plots concerning the triangular 3mer have two traces. What is interesting about this analysis is that the 3mers do not differ greatly in spectral ordering from the 2mer. The eigenvalue plots and the interaction energy plots have similar qualitative features amongst all three systems. This may be evident of a kind of saturation length to individual electric plasmon interaction, predicted in previous work.\cite{Pinchuk2016} However, for the purposes of this paper, this simply shows that the model can be extended to larger systems without loss of accuracy or efficiency. More importantly, these magnetic modes can influence the directionality of scattered light, much like those of the 2mer.

\section{Scattering Results from the 3mers}
Now that we have thoroughly analyzed the properties of the 2mer, we next present results on the two 3mers mentioned previously, whose modes and aggregation schemes were displayed in Figure~\ref{field_plots}. Calculations similar to those presented in Figure~\ref{scaling} for the linear and triangular 3mers are shown in the Supporting Information. These results show no new trends, but verify that the theoretical method works for larger aggreagtes with more complicated aggregation schemes. From here, we present scattering spectra and differential scattering patterns for both 3mers.

\begin{figure}
\includegraphics[width=5.5in]{l3mer_scattering_combined.pdf}
\caption{(a-h) Scattering spectra and differential scattering patterns comapring the y- (blue) and z-directed (red) scattering of the linear 3mer. (i-p) Forward (red) and backward (blue) scattering spectra and scattering patterns for the linear 3mer. (a) The y-directed scattering is much larger than the z-directed scattering for a linear 3mer with $r_0 =$ 1 nm and $s=1$, confirmed by (b) the simulated differential scattering in that plane. For a linear 3mer with $r_0 =$ 15 nm (c), the difference between the two directions depends on frequency. At the frequency marked by the dotted line, the differential scattering pattern in (d) shows that the y-directed scattering is much higher than z-directed. (e-h) Similar computations as in (a-d), except performed with a background of water. (i) The forward and backward scattering for a linear 3mer with $r_0 = $ 1 nm and $s=1$ are nearly identical, as confirmed by (j) the isotropic scattering pattern. (k) For a 3mer of larger particles, the forward scattering is greater than the backward scattering at all computed frequencies. At the frequency marked by the dotted line, (l) the diffraction pattern shows a large degree of directionality. (m-p) Similar calculations as (i-l), computed in water. }
\label{l3mer_combined}
\end{figure}

Much like the 2mer, The directionality of scattered light is a measure of how much the magnetic dipoles of the 3mers contribute to their overall optical properties. Introducing a third ring at the end of the 2mer to produce the linear 3mer does not starkly change the optical properties, except that the dominance of the magnetic mode occurs at even smaller sizes, with $r_0=$ 15 nm, as opposed to 20 nm in the 2mer. The spectra and differential scattering patterns in Figure~\ref{l3mer_combined} share a strong resemblance to those of the 2mer, showing that at small sizes, the z-directed scattering dominates and the forward and backward scattering are isotropic. This is evidence that only a net electric diple moment is exciteable on small systems. At large size, the magnetic and electric dipole moments fight for dominance at different frequencies, but at all frequencies the forward scattering is much larger than the backward scattering.

\begin{figure}
\includegraphics[width=5.5in]{t3mer_all_scattering.pdf}
\caption{Scattering spectra and differential scattering patterns computed in the y- and z-directions (a-h) and in the forward and backward directions (i-p). (a) The z-directed scattering is far greater than the y-directed scattering for the triangular 3mer with $r_0 = 1$ nm and $s=1$, owing to the excitation of only a net electric dipole moment in this size regime. This is confirmed by (b) the differential scattering pattern. (c) When the 3mer is composed of particles with $r_0 = 20$ nm, the directionality of light is frequency-dependent. Contrary to previous results, the peaks and dips in each scattering direction are uncorrelated, which is confirmed by (d) the differential scattering pattern collected at the frequency marked by the dashed line. This shows that some other collective mode of the system is weakly interfering and radiating, disrupting the symmetry expected from linear magnetic oligomers. These results are reproduced in water in (e-h). Similarly to the 2mer and the linear 3mer, (i) the forward (red) and backward (blue) scattering at small sizes are nearly equal, which is confirmed by (j) the differential scattering pattern. At larger sizes, (k and l) the triangular 3mer scatters light nearly completely unidirectionally at the chosen frequency, evidence of almost perfect interference between the magetic and electric dipole moments in the system. The results in water are qualitatively similar (m-p), showing that these properties do not drastically change in medium.}
\label{t3mer_forback}
\end{figure}

The triangular 3mers exhibit new effects that can't be explained using either the 2mer or linear 3mer for comparison. Figure~\ref{t3mer_forback} shows that at small sizes, the triangular 3mer behaves much like the 2mer and the linear 3mer, likely because it fits entirely into a wavelength of light and is too small for magentic effects to matter. However, at large sizes, the spectra and scattering patterns of the triangular 3mer do not exhibit nicely correlated peaks and dips the way that the 2mer and linear 3mer do. This is likely because of the threefold symmetry of the triangular 3mer. Previous work has shown that systems with threefold symmetry exhibit unexpected directionality in their scattered radiation.\cite{Tsutomu2017} This is likely due to the degeneracy of the dipole moments on the this 3mer and the ability to weakly excite electric dipole moments with different orientations using only one polarization of light (imagine rotating Figure~\ref{field_plots}f about a threefold axis).

Scattering calculations on the linear 3mer show that preserving twofold symmetry, and keeping electric dipole moments with different orientations spectrally distinct, does not starkly change the optical properties of a magnetic oligomer but rather causes the magnetic effects to take over at smaller sizes. The opposite is true of the triangular 3mer, which shows that giving a magnetic oligomer system some kind of radial symmetry makes the distinction between electric dipole scattering and magnetic dipole scattering harder to determine. However, all of this points to unique and direct control over the directionality and color of scattered photons.

\section{Conclusion}
Using a simple tight-binding model, we have built in retardation effects in order to elucidate the spectral tunability of magnetic plasmon oligomers. The key to observing and using magnetic plasmons lies in the direction in which they scatter light. Planar magnetic oligomers constructed of fused rings of nanoparticles exhibit all the usual electric plasmon resonances, but also exhibit magnetic dipole moments oriented solely perpendicular to the plane of the oligomer. A properly polarized exciting field can probe simultaneously the in-plane electric plasmons and the out-of-plane magnetic plasmons. As a result, the scattering spectra and patterns will exhibit signatures of magnetic dipole dominance and magnetic-electric interference. These properties make magnetic plasmon oligomers an ideal candidate for the direction-dependent manipulation of light.

\begin{acknowledgement}
CEI for money, HPC/Hyak/Mox for computing time, Niket and Harrison for good conversations.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

%When two or more metal nanoparticles (MNPs) are brought together, their individual electric plasmons can hybridize to produce new, collective plasmon resonances\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a sizeable magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. These aggregates can couple to and enhance the magnetic field of light, leading to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.

%Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Similar to how a pair of electric plasmons can produce an electrically bright and an electrically dark mode, a pair of magnetic plasmons can produce a magnetically bright mode and a magnetically dark mode. This understanding opens up new routes to preferentially exciting magnetic and electric plasmons and distinguishing between the different plasmonic modes of a particular aggregate. Studies of the properties of magnetic plasmons have focused on plasmon propagation and hybridization, but have not sought to determine under what circumstances the magnetic plasmons of a system dominate its optical properties. Key to answering this question is the influence of retardation effects.

%This work utilizes and augments a previously published tight-binding model\cite{Cherqui2014}. The model in question maps the electric plasmon of each nanoparticle onto a harmonic oscillator and allows them to couple through quasistatic, near-field interactions using the Hamiltonian

%\begin{equation}
%\frac{H}{\hbar\omega_{\textrm{sp}}} = \frac{1}{2}\sum_{i}\left[\boldsymbol{\Pi}_{i}^2 + \textbf{Q}_{i}^{2}\right] - \frac{\alpha_{\textrm{sp}}}{2}\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}.
%\label{full_hammy}
%\end{equation}

%Here, $\omega_{\textrm{sp}}$ is the resonant frequency of the individual electric plasmons, the $\boldsymbol{\Pi}_{i}$ are the generalized momenta conjugate to the generalized coordinates $\textbf{Q}_{i}$, $\alpha_{\textrm{sp}}$ is the polarizability of each individual MNP, and $\boldsymbol{\Lambda}_{ij}$ is the near-field dipole-dipole relay tensor. In this work, retardation effects are incorporated into the dipole-dipole relay tensor through the intermediate- and far-field terms in the dipole electric field as follows:

%\begin{equation}
%\boldsymbol{\Lambda}_{ij} = \left[\left(\frac{1}{r_{ij}^3} - \frac{\textrm{i}\omega}{cr_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{\omega^2}{c^2r_{ij}}\left(\textbf{1} - \hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right]e^{\textrm{i}\omega/c r},
%\label{dipoledipole}
%\end{equation}

%where $r_{ij}$ is the distance between the $i^{\textrm{th}}$ and $j^{\textrm{th}}$ dipoles along the unit vector $\hat{\textbf{n}}_{ij}$, \textbf{1} is the unit dyad, $c$ is the speed of light, and $\omega$ is the collective frequency at which all of the dipoles oscillate. Using Equations~\ref{full_hammy} and ~\ref{dipoledipole}, Hamilton's equations of motion,

%\begin{equation}
%\ddot{\textbf{Q}}_{i} = -\textbf{Q}_{i} + \sum_{j\neq i}\boldsymbol{Lambda}_{ij}\cdot\textbf{Q}_{j}
%\label{eom}
%\end{equation}

% can be found and the system of equations can be solved for the eigenvalues and eigenvectors of the nanoparticle array. The eigenvectors are the generalized coordinates corresponding to each dipole moment in the aggregate. It is important to note that because the eigenvalues, the collective frequencies, appear in the coupling terms, this will result in a system of transcendental equations which must be solved iteratively.

%In this paper, three model systems are considered. Following previous work, the model systems are constructed from fused, six-member rings of silver nanospheres, resembling conjugated hydrocarbon rings. The aggregates considered are a two-ring system, a linear three-ring system, and a triangular three-ring system. Solving for the magnetic eigenmodes of each system results in a set of eigenvectors for each mode which correspond to electric dipole moments. Figure~\ref{field_plots} shows the oligomers, the dipole moments on each sphere, and the magnetic field distribution computed from\cite{jackson_classical_1999}

%\begin{equation}
%\textbf{B}_{\textrm{tot}}(\textbf{r},\omega) = \frac{\omega^2}{c^2}\sum_{j}(\hat{\textbf{n}}_{j}\times\textbf{p}_{j})\frac{e^{\textrm{i}\omega/c r_j}}{r_j}\left(1 - \frac{c}{\textrm{i}\omega r_{j}}\right).
%\label{magnetic_field}
%\end{equation}

### 2018-01-16 paper_fall_2017/fall_2017.tex
lots of new stuff

\documentclass[12pt, letterpaper, twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{wrapfig}
\doublespacing
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\bibliographystyle{ieeetr}
\title{Magnetic Effects in Metal Nanoparticle Arrays}
\author{Nicholas P. Montoni}
\date{\center{Wednesday, August 16, 2017\\Chemistry Building 339, 9:30 AM}}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Interest in the collective magnetic response of arrays of metal nanoparticles, called magnetic oligomers, has exploded in recent years. This is due to the possibility of applying magnetic plasmon resonances to problems such as biological sensing and imaging, electromagnetic cloaking, and information processing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano,Zhang2006,NordHal2011,NordHal2012}. Plasmonic systems exhibiting magnetic properties have been thoroughly characterized on both the single-oligomer scale and the infinite scale, but open questions remain about the properties and usefulness of magnetic oligomers in the size regime between these two limits\cite{Dionne2016,Weick2013,Engheta2017}. Emphasizing this point is a wealth of research focusing on large, multi-oligomer arrays of nanoparticles. In particular, one such work highlights the complexity of these systems and sets the stage for the tunability and usefulness of magnetic plasmon resonances.

The recent work in question focused on describing one-, two-, and six-oligomer systems using both a quasistatic tight-binding model and full-wave simulations. The quasistatic approximation assumes that an object is so small that light and information travel across it infinitely quickly, or at least faster than the lifetime of any relevant physical phenomenon, such as a plasmon resonance. This is important to note because the formulation of the model is therefore fundamentally different from the simulations; the simulations include retardation effects. So it comes as no surprise that the model and the simulations predicted different properties for the two- and six-oligomer systems. The discrepancy occurred in the spectral ordering of the closed-loop magnetic modes: the tight-binding model predicted that the nodeless magnetic mode was higher in energy while simulations predicted that it was lower in energy. This discrepancy is a clear indication that the quasistatic approximation breaks down for magnetic systems and that retardation effects are in fact necessary to proeprly describe them.

When two or more metal nanoparticles (MNPs) are allowed to interact, the collective excitations of their conduction electrons, called electric plasmons, can hybridize to produce new excitations\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Much work has been done to describe magnetic plasmons both in the single oligomer limit\cite{}, where the aggregates are well-described by the quasistatic approximation, and in the infinite limit, where extended systems are well-defined by condensed matter approaches\cite{}. In between these limits, however, there are still open questions about how to think about magnetic plasmons and what models work best\cite{}.

Work that has attempted to describe finite arrays of magnetic oligomers within the quasistatic limit has had its limitations\cite{Cherqui2014}. Making the approximation that magnetic oligomers are small compared to the speed of light results in good qualitative analysis but lacks in quantitative accuracy when compared with full-wave electrodynamics simulations. Specifically, the quasistatic model predicted the wrong spectral order of the closed loop magnetic modes of two- and six-ring oligomers. This was corrected in a coarse-grained model, but the question remains of what the quasistatic model needed to predict the correct energy-ordering. Because the simulations use the fully-retarded formulation of Maxwell's equations, this work will use retardation effects to augment the simple model used previously in order to achieve quantitative accuracy and to explain why the quasistatic approximation is not accurate for magnetic oligomers. Retardation effects have been considered in studies of both large MNPs and infinite MNP arrays\cite{Abajo2008,Gu2010,vonPlessen2007,Rechbacher2003,Kottman2001,Schatz2003,Royer2005,Chumanov2010}, but have not yet been used to describe the optical properties of magnetic oligomers.

Beyond investigating previous work, the intuition gained from the simple model will be applied to suggest and explore applications and observables of magnetic plasmon oligomers. Specifically, because these aggregates can couple to and enhance the magnetic field of light, and because of their unique radiative properties, magnetic oligomers have applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{}. This paper documents those unique properties and leverages them as a measure of the importance of retardation effects. As a final exercise, two explanations for these properties are proposed in order to gain insight and intuition into the behavior of more complicated MNP aggregates.

\section*{Methods}
In this paper, three model systems are considered. Following previous work\cite{Cherqui2014,Weick2013,Engheta2017}, the model systems are constructed from fused, six-member rings of identical silver nanospheres, resembling conjugated hydrocarbon rings. The aggregates considered are a two-ring system (twomer), a linear three-ring system (1D threemer), and a triangular three-ring system (2D threemer). The model used in this work maps the electric plasmon of each MNP onto a harmonic oscillator and allows them to couple through quasistatic, near-field interactions using the Hamiltonian\cite{Cherqui2014}

\begin{equation}
\frac{H}{\hbar\omega_{\textrm{sp}}} = \frac{1}{2}\sum_{i}\left[\boldsymbol{\Pi}_{i}^2 + \textbf{Q}_{i}^{2}\right] - \frac{\alpha_{\textrm{sp}}}{2}\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}.
\label{full_hammy}
\end{equation}

\noindent Here, $\omega_{\textrm{sp}}$ is the resonant frequency of the individual electric plasmons, the $\boldsymbol{\Pi}_{i}$ are the generalized momenta conjugate to the generalized coordinates $\textbf{Q}_{i}$, $\alpha_{\textrm{sp}} = 3r_0^3/(\varepsilon_{\infty}+2\varepsilon_b)$ is the polarizability of each MNP of radius $r_0$, and $\boldsymbol{\Lambda}_{ij}$ is the near-field dipole-dipole relay tensor. In this work, retardation effects are incorporated into the dipole-dipole relay tensor through the intermediate- and far-field terms in the dipole electric field as follows:

\begin{equation}
\boldsymbol{\Lambda}_{ij} = \left[\left(\frac{1}{r_{ij}^3} - \frac{\textrm{i}\omega}{cr_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{\omega^2}{c^2r_{ij}}\left(\textbf{1} - \hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right]e^{\textrm{i}\omega r_{ij}/c},
\label{dipoledipole}
\end{equation}

\noindent where $r_{ij}$ is the distance between the $i^{\textrm{th}}$ and $j^{\textrm{th}}$ dipoles along the unit vector $\hat{\textbf{n}}_{ij}$, \textbf{1} is the unit dyad, $c$ is the speed of light, and $\omega$ is the collective frequency at which all of the dipoles oscillate. Using Equations~\ref{full_hammy} and ~\ref{dipoledipole}, Hamilton's equations of motion,

\begin{equation}
\ddot{\textbf{Q}}_{i} = -\textbf{Q}_{i} + \alpha_{\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}
\label{eom}
\end{equation}

\noindent can be found and the system of equations can be solved for the eigenvalues and eigenvectors of the nanoparticle array. The eigenvectors are the generalized coordinates corresponding to each dipole moment in the aggregate. It is important to note that because the eigenvalues, the collective frequencies, appear in the coupling terms, this will result in a system of transcendental equations which must be solved iteratively. To do this, an initial guess ($\omega = 0$) is made, and each successive answer is plugged back into the coupling term until the eigenvalue in question converges. In this way, each eigenvalue and set of eigenvectors is obtained one at a time.

\begin{figure}
\centering
\includegraphics[width=6in]{fields_new_arrows.pdf}
\caption{Magnetic fields produced by each of the magnetic eigenmodes of the twomer (a and b), 1D threemer (c, d, and e), and 2D threemer (f, g, and h). The magnetic field distributions and orientation of electric dipoles can be used to determine whether each magnetic mode is magnetically or electrically bright or dark. Red regions are labeled ``N'' for ``North'' and ``S'' for ``South'' in reference to the north and south poles of a magnet. Interestingly, each oligomer supports exactly one magnetically bright mode (b, e, h) that will couple to the magnetic, rather than the electric, field of light. That this mode's dipole moment is out of the plane of the oligomer allows it to be excited mutually with the electric dipole modes.}
\label{field_plots}
\end{figure}

\section*{Results and Discussion}
Using Equation~\ref{eom} to build and solve a system of equations results in the eigenvalues and eigenvectors for each mode of the oligomers. Figure~\ref{field_plots} shows the oligomers, the dipole moments on each sphere, and the magnetic field distribution of each magnetic mode, computed from\cite{jackson_classical_1999}

\begin{equation}
\textbf{B}_{\textrm{tot}} = \frac{\omega^2}{c^2}\sum_{j}(\hat{\textbf{n}}_{j}\times\textbf{p}_{j})\frac{e^{\textrm{i}\omega r_j/c}}{r_j}\left(1 - \frac{c}{\textrm{i}\omega r_{j}}\right).
\label{magnetic_field}
\end{equation}

\noindent From the magnetic field distributions and the orientation of electric dipoles, some key observations can be made about the magnetic modes. Each magnetic oligomer supports exactly one magnetically bright mode and at least one electrically bright closed-loop mode. Furthermore, the magnetically bright and electrically bright modes are orthogonal to each other, implying that they can be either mutually excited or exclusively excited by the proper polarization of light. Furthermore, this implies that the magnetically bright mode will radiate a different pattern than the in-plane electric modes of the oligomers. These details will be significant in the discussion of observables and applications, as they lead to stark differences in the radaition pattern of light scattered by the oligomer.

The model can now be used to show how properties such as scale of the oligomer and separation distance between MNPs impact the eigenvalues. To do this, a nearest neighbor distance is defined as $r_{\textrm{nn}} = (s+2)r_0$ where $r_0$ is the particle radius and $s$ is the face-to-face distance in units of $r_0$. Figure~\ref{scaling}a shows the magnetic eigenmode frequencies as a function of oligomer scale. This is calculated by fixing the parameter $s=1$ and varying $r_0$ from 1 nm to 30 nm. It can be seen that the eigenmodes of each oligomer change order mutliple times as a function of size. Interestingly, when the oligomers are small they preserve the quasistatic ordering predicted by previous work\cite{Cherqui2014}. As the oligomers grow larger, the spectral ordering changes, a prediction not made by the quasistatic model. This is the result of incorporation of retardation effects, which will be made clearer in Figure~\ref{scaling}b.

\begin{figure}
\centering
\includegraphics[width=6in]{scale_eigs.png}
\caption{Theoretical and simulated magnetic mode eigenvalues (a) and total, near plus intermediate, and far interaction strengths (b) plotted as a function of $r_0$, with interparticle distances scaling up. Each row corresponds to one of the oligomer systems studied in this work as pictured on the left. In column (a), note that the eigenvalues all decrease with increasing $r_0$, but the eigenvalues cross at 5 nm and 21 nm. This is corroborated by full-wave simulation (dashed lines). Interestingly, these crossings are mirrored in (b) by the fluctuations in the far-field (squares) interaction. By themselves, the near- and intermediate-fields (circles) would never contribute any mode crossings to the total interaction (solid). Due to the opposite inflection of the far-field interaction, however, the crossings become possible.}
\label{scaling}
\end{figure}

In order to more fully explain the effects of incorporating retardation, Figure~\ref{scaling}b shows the total interaction strength, the sum of the near- and intermediate-field interaction strengths, and the far-field interaction strength for each of the closed-loop magnetic modes of the oligomers. In other words, this is the computation of $U_{\textrm{int}} = \sum_{i}\textbf{p}_i \cdot \textbf{E}_{\textrm{tot}}$ for a set of eigenvectors corresponding to each of the closed-loop magnetic modes, where $\textbf{E}_{\textrm{tot}}$ is the electric field of all of the dipoles except the $i^{\textrm{th}}$. Because there are no crossings exhibited in the near- and intermediate-field terms, and because the far-field term exhibits the opposite behavior of the other terms, it can be seen that inclusion of the far-field term results in spectral switching of the eigenmodes. This is because, as can be seen in Equation~\ref{dipoledipole}, the far-field term contributes the opposite ordering to the dyadic structure of the tensor. In other words, the far-field term is 180 degrees out of phase with the near- and intermediate-field terms, and therefore accounts for the ability of the modes to switch order.

Aggregate scale is not something that can be easily manipulated in real time in a laboratory, as it would require the refrabrication of a different aggregate for each experiment. However, recent research has focused on the ability of DNA and polymers to change shape and size in response to stimuli such as heat and pH\cite{DanLuo2009,NaLiu2017,Ginger2017,odom_lasing,Yang2016}. Specifically, these techniques have been used to continuously and reversibly tune the aggregation scheme or environment of a MNP array. Applying these concepts to small magnetic oligomers reveals a high degree of tunability in not only the eigenvalues but their ordering.

\begin{figure}
\centering
\includegraphics[width=6in]{spacing_study.png}
\caption{Magnetic mode eigenvalues as a function of increasing nearest-neighbor distance for the twomer (first row), 1D threemer (second row), and 2D threemer (third row). For all of the oligomers, the eigenvalues approach the single MNP frequency (black dashed lines) at large separation distances. When the constituent MNPs are 15 nm in radius (column a), the eigenvalues cross minimally and level off to the single MNP frequency rapidly. However, for MNPs of 30 nm in radius (column b) the eigenvalues exhibit larger splittings, more crossings, and larger amplitude oscillations as a function of increasing distance. This is evidence of the increased importance of retardation effects for larger-sized particles at larger distances from each other.}
\label{spacing}
\end{figure}

Figure~\ref{spacing} shows the eigenvalues of each closed-loop mode of the oligomesrs as a function of face-to-face distances for particles of 15 (a) and 30 (b) nm. As the space between particles increases, the magnetic modes collectively increase in energy, tending towards the single plasmon resonant frequency. This is expected, as in the limit that the particles are infinitely far apart they should not interact (see Equation~\ref{dipoledipole}). The eigenvalues appear to cross and exhibit low-amplitude oscillations for both particle sizes, but the crossings and oscillations are much more pronounced for the 30 nm particles. This is evidence of real time tunability and versatility and, more importantly, it implies an overall size dependence to the impact of retardation effects. Comparing the behavior of the smaller particles and the larger particles shows that retardation effects, as expected, play a more important role in aggregates that are both composed of larger particles and span larger distances. As a result, it can be seen that utilizing and understanding the role of retardation effects can lead to increased versatility of magnetic plasmon oligomers.

There is a drawback in this line of reasoning, however. The splitting between the magnetic modes is very small, on the order of hundredths of electron volts, tenths at the most. Due to natural broadening of the plasmonic modes with increasing particle size, it can be difficult to pick apart these modes in optical spectra. In order to fully utilize magnetic oligomers, a technique is required to unravel these overlapping modes. As previously mentioned, the all in-phase magnetic modes scatter light in different directions than the in-plane electric modes (see Figure~\ref{field_plots}). This distinctive radiation pattern can be detected\cite{Polman2014,Smith2014}, and it will be shown that it can be used as a measure of the importance of retardation effects. Furthermore, because the magnetic and electric dipole moments have orthogonal orientations, they are mutually excitable and interfere with each other to produce directional radiation\cite{Kivshar2012,Tsutomu2017}.

The following discussion stems from calculations performed using a full-wave Maxwell's equations solver\cite{Hohenester2012}. The results of those calculations are shown in Figures~\ref{polar_plots_yz} and~\ref{beaming}. As in the figures, polarizing an incident light wave such that its magnetic field threads the rings of a magnetic oligomer and its electric field is in the plane of the oligomer along its y-axis allows both the excitation of the closed-loop, in-phase magnetic mode and all of the in-plane electric modes oriented along the electric field.

\begin{figure}
\centering
\includegraphics[width=6in]{polar_plots_yz.pdf}
\caption{Differential scattering plots for the twomer (a), 1D threemer (b), and 2D threemer (c) computed in the plane along the dotted lines in each diagram (the E,B or y,z plane). In the columns marked i the differential scattering is computed at the magnetic plasmon frequency with changing scale, and in the columns marked ii the differential scattering is computed at a fixed frequency with fixed particle radius as a function of increasing spacing. The scale calculations show that at small sizes, the radiation pattern is dominated by the electric dipole, which scatters heavily in the z-direction and not at all in the y-direction. At large sizes, the magnetic dipole dominates, as the scattering pattern changes to show heavy radiation in the y-direction and very little in the z-direction. The spacing calculations show that when looking at a fixed frequency, the magnetic oligomers can be brought into and out of their magnetic dipole resonance, seen for all three systems at $r_{\textrm{nn}}=3.0\times r_0$. Interestingly the scattering patterns of the 2D threemer are biased towards the y-direction. Due to the degeneracy in its electric dipole moments, the x-directed dipoles can be weakly excited with this polarization of light and, at larger sizes, can influence the radiation pattern.}
\label{polar_plots_yz}
\end{figure}

Figure~\ref{polar_plots_yz} displays the scattered power of the oligomers in the plane containing the electric field vector and the magnetic field vector, the yz-plane. It can be seen that at small sizes (columns marked i) the electric dipole radiation dominates the differential power, but with increasing size the magnetic dipole wins. This is evidence that the magnetic dipole moments of the oligomers only impact the oligomer's optical properties when the system is too large to be described by the quasistatic limit. In other words, when retaradtion effects are important, so too are the magnetic plasmons. Furthermore, computing the differential scattering at a fixed frequency with fixed MNP radius and changing the spacing of the oligomer (columns marked ii) results in a scattering pattern that detects when the magnetic mode is in resonance. This is direct evidence of the utility of magnetic plasmon oligomers as switches because the radiation pattern can be directly tuned and detected.

\begin{figure}
\centering
\includegraphics[width=6in]{beaming.pdf}
\caption{Differential scattering plots for the twomer (a), 1D threemer (b), and 2D threemer (c) computed in the plane along the dotted lines in each diagram (the k,B or x,z plane). In the columns marked i the differential scattering is computed at the magnetic plasmon frequency with changing scale, and in the columns marked ii the differential scattering is computed at a fixed frequency with fixed particle radius as a function of increasing spacing. The scale calculations show that at small sizes, the radiation pattern is dominated by the electric dipole, which scatters nearly isotropically in the x- and z-directions. At large sizes, the magnetic dipole begins to influence the radiation pattern, evidenced by the biasing of the radiation pattern to the x-direction. This is an indication of unidirectional scattering, very likely brought about by the interference of the magnetic and electric dipoles. The spacing calculations show that once the oligomers are large enough to exhibit magnetic-electric interference, it is difficult to turn the interference off. This can be seen in the differential scattering patterns as they remain unidirectional or somewhat biased to one direction at all spacings. However, there is a spacing at which the radiation unidirectionality is optimized.}
\label{beaming}
\end{figure}

Upon switching the plane of detection in these radiation pattern calculations, another interesting property of magnetic oligomers comes to light: their ability to emit directional radiation. Figure~\ref{beaming} displays the radiation patterns collected in the plane defined by the light propagation direction and the impinging magnetic field (the xz-plane, see dotted lines). At small sizes (columns marked i) each magnetic oligomer exhibits nearly isotropic radiation due to the scattering of the electric dipole. However, as the oligomers grow, the radiation begins to bias towards the propagation direction. Interestingly, changing the spacing at constant size and frequency doesn't greatly impact the radiation patterns (columns marked ii). These pieces of information taken together point to the interference of the magnetic dipole modes and the electric dipole modes. This is predicted for metal-semiconductor core-shell nanoparticles, but not for magnetic oligomers\cite{Kivshar2012}, creating an impetus for a simple model to explain these phenomena.

These scattering properties of magnetic plasmon oligomers are interesting in that they are observable and applicable. However, what is missing is an intuitive understanding of why these systems should produce directional radiation. A few hypothetical models are proposed in the Future Work section. Barring that, this work has shown that magnetic plasmon oligomers exhibit tunable spectral ordering of their closed-loop magnetic modes. Additionally, it has been shown computationally that magnetic plasmon oligomers scatter light in different directions depending on morphological parameters. This directionality can be turned on and off both by moving the MNPs and by rotating the laser polarization, a result which implies switching and sensing applications for magnetic plasmon oligomers.

\section*{Future Work}
Presented here are two hypothetical models of the differential power of the magnetic plasmon oligomers. The first comes from computing the electric and magnetic fields scattered by each dipole in the aggregate. The second comes from approximating each ring as a unit cell with a distinct magnetic and electric dipole moment\cite{Kivshar2012}.

Computing the differential power of the full aggregate requires\cite{jackson_classical_1999}

\begin{multline}
\frac{dP}{d\Omega} = \frac{c}{8\pi}\textrm{Re}\left[r^2 \hat{\textbf{n}}\cdot \sum_i \textbf{E}_i \times \sum_j \textbf{B}_j\right]\\
= \frac{\omega^4}{8\pi c^3}\textrm{Re}\left[\hat{\textbf{n}}\cdot \left(\sum_i \left(\frac{\textbf{r}-\textbf{r}_i}{r}\times\textbf{p}_i\right)\times\frac{\textbf{r}-\textbf{r}_i}{r}\right)e^{\textrm{i}\omega|\textbf{r}-\textbf{r}_i|/c} \times \sum_j\left(\frac{\textbf{r}-\textbf{r}_j}{r}\times\textbf{p}_j\right)e^{\textrm{i}\omega|\textbf{r}-\textbf{r}_j|/c}\right]
\label{diff_power_full}
\end{multline}

\noindent where at every point $\textbf{r}$ on the flux screen the fields scattered by each dipole located at positions $\textbf{r}_i$ are added together before the cross product is taken. There are two relevant limits to take: one in which the loop of dipoles is very small compared to the distance to the detector ($|\textbf{r}-\textbf{r}_i| \approx r$) and one in which the loop is finite in size ($|\textbf{r}-\textbf{r}_i| \approx r-\hat{\textbf{n}}\cdot\textbf{r}_i$). Taking the first limit results in

\begin{equation}
\frac{dP}{d\Omega} = \frac{\omega}{2\pi c r^2}|\textbf{m}|^2\textrm{sin}^2\theta
\label{mag_dp}
\end{equation}

\noindent a term which decays to zero for a flux screen at infinity. Here, $\textbf{m} = (N\omega Rp/2c)\hat{\textbf{z}}$ with $R$ the radius of one ring of nanoarticles.\cite{Cherqui2014,jackson_classical_1999}. Allowing the loop to have finite size, however, introduces phase effects. It is these that contribute to the overall radiation of the loops of dipoles. Keeping the exponential terms and again letting the magnetic dipole terms decay to zero gives

\begin{equation}
\frac{dP}{d\Omega} = \frac{\omega^4}{8\pi c^3}\sum_{ij}\left[\textbf{p}_i\textbf{p}_j - (\textbf{p}_i\cdot\hat{\textbf{n}})(\textbf{p}_j\cdot\hat{\textbf{n}})\right]\textrm{e}^{\textrm{i}\omega\hat{\textbf{n}}\cdot(\textbf{r}_j-\textbf{r}_i)/c}.
\label{dipoles_only_dp}
\end{equation}

\noindent From this, it can be seen that the radiation pattern of a collection of dipoles, regardless of arrangement, is dependent only on the orientations and locations of the dipoles in relation to one another. This equation is not immediately intuitive, however, and does not paint a physical picture of how the magnetic modes interfere with one another.

The second approach stems from the demonstrated ability of a magnetic dipole moment and an electric dipole moment to interfere and produce directional radiation\cite{Kivshar2012}. Applying this concept to magnetic oligomers results begins with\cite{schwinger1998classical}

\begin{multline}
\frac{dP}{d\Omega} = \frac{\omega^4}{4\pi c^3}\left[\hat{\textbf{n}}\times(\textbf{p} - \hat{\textbf{n}}\times\textbf{m})\right]^2= \frac{\omega^4}{4\pi c^3}\left[(\hat{\textbf{n}}\times\textbf{p})^2 + (\hat{\textbf{n}}\times\textbf{m})^2 + 2\hat{\textbf{n}}\cdot(\textbf{p}\times\textbf{m})\right].
\label{schwing_dP_1}
\end{multline}

\noindent Using the same light polarization in Figures~\ref{polar_plots_yz} and ~\ref{beaming} generates an electric dipole in the y-direction and a magnetic dipole in the z-direction associated with each ring of nanoparticles in the oligomer. Enforcing these conditions, Equation~\ref{schwing_dP_1} becomes

\begin{equation}
\frac{dP}{d\Omega}=\frac{\omega^4}{4\pi c^3}\sum_{i}\left[p_i^2(1 - (\hat{\textbf{n}}\cdot\hat{\textbf{y}})^2) + m_i^2(1 - (\hat{\textbf{n}}\cdot\hat{\textbf{z}})^2) + 2d_im_i(\hat{\textbf{n}}\cdot\hat{\textbf{x}})\right],
\label{schwing_dP_2}
\end{equation}

\noindent showing that an asymmetric interference term arises from the cross product of the magnetic and electric dipole.Equation~\ref{schwing_dP_2} shows that if either of the dipole moments is far greater than the other, that one will dominate the scattered power, but if they are nearly commensurate in strength, the unidirectionality will be optimized. This expression intuitively and qualitatively agrees with the data presented in Figures~\ref{polar_plots_yz} and~\ref{beaming}, but whether or not this is a good approximation has not been verified.

Beyond computing radiation patterns, the model of magnetic plasmon oligomers will be useful for other future projects. Incorporating a time component and initial conditions into the model will result in the ability to prepare a magnetic or electric plasmon and study its propagation through some oligomeric aggregate. This is especially interesting in light of Figures~\ref{scaling} and ~\ref{spacing}. One question that can be asked is whether the initial frequency of a magnetic plasmon impacts its phase as it propagates through an aggregate. Another question is how the propagation times and lengths of electric and magnetic plasmons on the same oligomer compare to each other.

Another application of the model proposed in this work is investigation of arrays of semiconductor nanocrystals (SNCs). SNCs are of interest to the plasmonics community because they offer yet another knob to turn, specifically offering direct control over the electron density in the nanocrystals\cite{Gamelin2014}. SNCs have been shown to produce narrow plasmon resonances in the infrared. It has been previously proposed that magnetic plasmon oligomers composed of SNCs are the perfect medium to couple to the magnetic dipole transition in Yb,Er nanocrystals. It is thought that a metamaterial of this composition, when combined in a photovoltaic device, can be a route to surpassing the Shockley-Quiesser limit through upconversion of infrared photons into blue or violet light.

With a versatile, accurate, and fast model that contains many knobs to turn, these explorations should be both possible and fruitful. They are the next steps in turning magnetic plasmon oligomers into useful and functional nanoscale technologies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

### 2018-01-16 paper_fall_2017/general_exam/general_paper.tex
lots of new stuff

--- 2018-01-16 paper_fall_2017/fall_2017.tex
@@
 \bibliographystyle{ieeetr}
-\title{Magnetic Effects in Metal Nanoparticle Arrays}
+\title{Quantifying the Role of Magnetic Effects in Metal Nanoparticle Arrays}
 \author{Nicholas P. Montoni}
@@
 \section*{Introduction}
-Interest in the collective magnetic response of arrays of metal nanoparticles, called magnetic oligomers, has exploded in recent years.
-This is due to the possibility of applying magnetic plasmon resonances to problems such as biological sensing and imaging, electromagnetic cloaking, and information processing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano,Zhang2006,NordHal2011,NordHal2012}.
-Plasmonic systems exhibiting magnetic properties have been thoroughly characterized on both the single-oligomer scale and the infinite scale, but open questions remain about the properties and usefulness of magnetic oligomers in the size regime between these two limits\cite{Dionne2016,Weick2013,Engheta2017}.
-Emphasizing this point is a wealth of research focusing on large, multi-oligomer arrays of nanoparticles.
-In particular, one such work highlights the complexity of these systems and sets the stage for the tunability and usefulness of magnetic plasmon resonances.
-
-The recent work in question focused on describing one-, two-, and six-oligomer systems using both a quasistatic tight-binding model and full-wave simulations.
-The quasistatic approximation assumes that an object is so small that light and information travel across it infinitely quickly, or at least faster than the lifetime of any relevant physical phenomenon, such as a plasmon resonance.
-This is important to note because the formulation of the model is therefore fundamentally different from the simulations; the simulations include retardation effects.
-So it comes as no surprise that the model and the simulations predicted different properties for the two- and six-oligomer systems.
-The discrepancy occurred in the spectral ordering of the closed-loop magnetic modes: the tight-binding model predicted that the nodeless magnetic mode was higher in energy while simulations predicted that it was lower in energy.
-This discrepancy is a clear indication that the quasistatic approximation breaks down for magnetic systems and that retardation effects are in fact necessary to proeprly describe them.
-
 When two or more metal nanoparticles (MNPs) are allowed to interact, the collective excitations of their conduction electrons, called electric plasmons, can hybridize to produce new excitations\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}.
@@
 Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}.
-Much work has been done to describe magnetic plasmons both in the single oligomer limit\cite{}, where the aggregates are well-described by the quasistatic approximation, and in the infinite limit, where extended systems are well-defined by condensed matter approaches\cite{}.
-In between these limits, however, there are still open questions about how to think about magnetic plasmons and what models work best\cite{}.
+Much work has been done to describe magnetic plasmons both in the single oligomer limit\cite{Dionne2016}, where the aggregates are well-described by the quasistatic approximation, and in the infinite limit, where extended systems are well-defined by condensed matter approaches\cite{Weick2013}.
+In between these limits, however, there are still open questions about how to think about magnetic plasmons and what models work best\cite{Engheta2017}.
 
@@
 Beyond investigating previous work, the intuition gained from the simple model will be applied to suggest and explore applications and observables of magnetic plasmon oligomers.
-Specifically, because these aggregates can couple to and enhance the magnetic field of light, and because of their unique radiative properties, magnetic oligomers have applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{}.
+Specifically, because these aggregates can couple to and enhance the magnetic field of light, and because of their unique radiative properties, magnetic oligomers have applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.
 This paper documents those unique properties and leverages them as a measure of the importance of retardation effects.

### 2018-01-16 paper_fall_2017/old_draft/draft.tex
lots of new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Quantifying the Role of Retardation Effects in Magnetic Plasmon Supporting Metal Nanoparticle Arrays}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{plasmon, hybridization, magnetic, retardation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Magnetic plasmons, the collective response of cyclic arrangements of electric plasmon-supporting metal nanoparticles, have been of recent theoretical and experimental interest. As magnetic-plasmon-supporting aggregates are often large (hundreds of nanometers to microns in size), information takes time to propagate across such nanostructures. As a result, they are not well-described in the quasistatic limit with plasmon hybridization theory. In this Letter it is shown that for small magnetic oligomers the quasistatic approximation is sufficient, but, as the systems grow in size, retardation effects must be considered. The quasistatic tight-binding model can be manipulated to include retardation effects by utilizing the full electric field of a dipole. This fully retarded tight-binding model accurately predicts the energy-ordering of magnetic plasmon modes in agreement with full-wave simulations.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
When two or more metal nanoparticles (MNPs) are brought together, their individual electric plasmons can hybridize to produce new, collective plasmon resonances\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a sizeable magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. These aggregates can couple to and enhance the magnetic field of light, leading to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.

Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Similar to how a pair of electric plasmons can produce an electrically bright and an electrically dark mode, a pair of magnetic plasmons can produce a magnetically bright mode and a magnetically dark mode. This understanding opens up new routes to preferentially exciting magnetic and electric plasmons and distinguishing between the different plasmonic modes of a particular aggregate. Studies of the properties of magnetic plasmons have focused on plasmon propagation and hybridization, but have not sought to determine under what circumstances the magnetic plasmons of a system dominate its optical properties. Key to answering this question is the influence of retardation effects.

Much work has been done on magnetic plasmons in the quasistatic limit, which assumes that electromagnetic information propagates infinitely quickly. While retardation effects have been considered in studies of both large MNPs and infinite MNP arrays\cite{Abajo2008,Gu2010,vonPlessen2007,Rechbacher2003,Kottman2001,Schatz2003,Royer2005,Chumanov2010}, they have never been incorporated into models of intermediate-sized MNP arrays. Certainly, the single particle, single oligomer, and infinite system limits have been well-studied while the size regime in between is still relatively uncharted[\textbf{Kagan2017}]. This paper will show that, contrary to intuition, retardation effects play a significant role in the optical properties of magnetic-plasmon-supporting MNP aggregates int he intermediate size regime. It will be shown that by incorporating retardation effects into a simple model, the magnetic mode frequencies can be accurately predicted. Following this, it will be shown that the spectral order of the magnetic modes can be directly controlled, and that due to the specific radiative properties of each magnetic mode, it is possible to track one of the magnetic modes as a function of energy, scale, and size. Finally, the magnetic and electric plasmons on single oligomers will be shown to interfere in such a way as to produce unidirectional radiation. The tracking of the magnetic modes and their interference with the electric modes is the key to determining when retardation effects must be included to produce an accurate model.

This work utilizes and augments a previously published tight-binding model\cite{Cherqui2014}. The model in question maps the electric plasmon of each nanoparticle onto a harmonic oscillator and allows them to couple through quasistatic, near-field interactions using the Hamiltonian

\begin{equation}
\frac{H}{\hbar\omega_{\textrm{sp}}} = \frac{1}{2}\sum_{i}\left[\boldsymbol{\Pi}_{i}^2 + \textbf{Q}_{i}^{2}\right] - \frac{\alpha_{\textrm{sp}}}{2}\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}.
\label{full_hammy}
\end{equation}

Here, $\omega_{\textrm{sp}}$ is the resonant frequency of the individual electric plasmons, the $\boldsymbol{\Pi}_{i}$ are the generalized momenta conjugate to the generalized coordinates $\textbf{Q}_{i}$, $\alpha_{\textrm{sp}}$ is the polarizability of each individual MNP, and $\boldsymbol{\Lambda}_{ij}$ is the near-field dipole-dipole relay tensor. In this work, retardation effects are incorporated into the dipole-dipole relay tensor through the intermediate- and far-field terms in the dipole electric field as follows:

\begin{equation}
\boldsymbol{\Lambda}_{ij} = \left[\left(\frac{1}{r_{ij}^3} - \frac{\textrm{i}\omega}{cr_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{\omega^2}{c^2r_{ij}}\left(\textbf{1} - \hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right]e^{\textrm{i}\omega/c r},
\label{dipoledipole}
\end{equation}

where $r_{ij}$ is the distance between the $i^{\textrm{th}}$ and $j^{\textrm{th}}$ dipoles along the unit vector $\hat{\textbf{n}}_{ij}$, \textbf{1} is the unit dyad, $c$ is the speed of light, and $\omega$ is the collective frequency at which all of the dipoles oscillate. Using Equations~\ref{full_hammy} and ~\ref{dipoledipole}, Hamilton's equations of motion,

\begin{equation}
\ddot{\textbf{Q}}_{i} = -\textbf{Q}_{i} + \sum_{j\neq i}\boldsymbol{Lambda}_{ij}\cdot\textbf{Q}_{j}
\label{eom}
\end{equation}

 can be found and the system of equations can be solved for the eigenvalues and eigenvectors of the nanoparticle array. The eigenvectors are the generalized coordinates corresponding to each dipole moment in the aggregate. It is important to note that because the eigenvalues, the collective frequencies, appear in the coupling terms, this will result in a system of transcendental equations which must be solved iteratively.

In this paper, three model systems are considered. Following previous work, the model systems are constructed from fused, six-member rings of silver nanospheres, resembling conjugated hydrocarbon rings. The aggregates considered are a two-ring system, a linear three-ring system, and a triangular three-ring system. Solving for the magnetic eigenmodes of each system results in a set of eigenvectors for each mode which correspond to electric dipole moments. Figure~\ref{field_plots} shows the oligomers, the dipole moments on each sphere, and the magnetic field distribution computed from\cite{jackson_classical_1999}

\begin{equation}
\textbf{B}_{\textrm{tot}}(\textbf{r},\omega) = \frac{\omega^2}{c^2}\sum_{j}(\hat{\textbf{n}}_{j}\times\textbf{p}_{j})\frac{e^{\textrm{i}\omega/c r_j}}{r_j}\left(1 - \frac{c}{\textrm{i}\omega r_{j}}\right).
\label{magnetic_field}
\end{equation}

\begin{figure}
\includegraphics[width=7in]{fields_new_arrows.pdf}
\caption{Magnetic fields produced by each of the magnetic eigenmodes of the twomer (a and b), 1D threemer (c, d, and e), and 2D threemer (f, g, and h). The magnetic field distributions and orientation of electric dipoles can be used to determine whether each magnetic mode is magnetically or electrically bright of dark. Red regions are labeled ``N'' for ``North'' and ``S'' for ``South'' in reference to the north and south poles of a magnet. As such, the modes are referred to by their associated aggregate and acronym.}
\label{field_plots}
\end{figure}

From the magnetic field distributions and the orientation of electric dipoles, some key observations can be made about the magnetic modes. The in-phase magnetic mode of each oligomer (Figure~\ref{field_plots}b, e, and h) has a net magnetic dipole, meaning it will couple to the magnetic field of light. The out-of-phase magnetic modes in Figure~\ref{field_plots}a, d, f, and g all have net electric dipole moments, so they will interact with the electric field of light. The magnetic mode in Figure~\ref{field_plots} has no dipole moments at all, making it optically dark. The classification of electrically bright and magnetically bright will play an important role in later discussion.

With the model producing the correct eigenmodes, it can now be used to show how properties such as scale of the oligomer and separation distance between MNPs impact the eigenvalues. To do this, a nearest neighbor distance is defined as $r_{nn} = (s+2)a_0$ where $a_0$ is the particle radius and $s$ is a face-to-face distance in units of $a_0$. Figure~\ref{scaling}a shows the magnetic eigenmode frequencies as a function of oligomer scale. This is calculated by fixing the parameter $s=1$ and varying $a_0$ from 1 nm to 30 nm. It can be seen for all three oligomers that at $a0 = 5$ nm the in-phase magnetic mode becomes the lowest in energy, contrary to predictions made by models in past work. Even more interesting is that the eigenmodes change spectral order again at 25 nm. Figure~\ref{scaling}a also includes comparison to simulation, showing that the model overestimates the eigenvalues by about 0.05 eV.

\begin{figure}
\includegraphics[width=7in]{scale_eigs.pdf}
\caption{Theoretical and simulated magnetic mdoe eigenvalues (a) and total, near plus intermediate, and far interaction strengths (b) plotted as a function of system scale. Each row corresponds to one of the oligomer systems studied in this work. In column (a), note that the eigenvalues all decrease with increasing $r_0$, but the eigenvalues cross at 5 nm and 21 nm. This is corroborated by full-wave simulation (dashed lines). Interestingly, these crossings are mirrored in (b) by the fluctuations in the far-field (squares) interaction. By themselves, the near- and intermediate-fields (circles) would never contribute any mode crossings to the total interaction (solid). Due to the opposite inflection of the far-field interaction, however, the crossings become possible.}
\label{scaling}
\end{figure}

Spectral switching of eigenmodes is counterintuitive and unexplored. In order to more fully explain why this could happen, Figure~\ref{scaling}b shows the total interaction strengths between dipoles in each eigenmode. More specifically, the total strength is computed, as well as the sum of the near- and intermediate-field strengths, followed by the far-field strength separately. This breakdown shows that the eigenmode crossings are due entirely to the far-field interaction. There are no crossings exhibited in the near- and intermediate-field terms, so these contribute only to net shifting of the eigenmodes. It is the change in relative magnitude of the far-field interaction that causes the eigenmodes to change spectral order. This is the most important point to take away from these plots: the far-field term is the magnetic term, and so it alone gives a measure of the importance of magnetic effects on these systems. And from these plots, it would seem that it becomes important for particles as small as 5 nm, and for separation distances between 15 nm and 50 nm.

Aggregate scale is not something that can be easily manipulated in real time in a laboratory, as it would require the refrabrication of a different aggregate for each experiment. However, recent research has focused on the ability of DNA and polymers to change shape and size in response to stimuli such as heat and pH[\textbf{cite Odom, Ginger, Schatz}]. Specifically, these techniques have been used to continuously and reversibly tune the aggregation scheme of a MNP array. Using this concept, the following set of calculations varies the nearest neighbor spacing, $r_{nn}$ by varying $s$ from 0 to 10 and keeping $a_0$ constant at 15 and 30 nm.

\begin{figure}
\includegraphics[width=7in]{spacing_study.pdf}
\caption{}
\label{spacing}
\end{figure}

Figure~\ref{spacing}a shows the eigenvalues of each oligomer as a function of spacing for the 15 nm radius particles. As the space between particles increases, the magnetic modes collectively increase in energy, tending towards the single plasmon resonant frequency. The eigenvalues appear to cross and exhibit slight oscillatory motion. The crossings and oscillations are much more pronounced for the 30 nm particles (Figure~\ref{spacing}b). This is interesting because it shows that magnetic oligomers show a high degreee of spectral tunability. It can be seen that the energy order of the magnetic modes depends on a parameter that can be manipulated in a laboratory. This versatility could be exploited to design optical magnetic switches and detectors.

There is a drawback in this line of reasoning, however. The splitting between the magnetic modes is very small, on the order of hundredths of electron volts, tenths at the most. In order to fully utilize magnetic oligomers, a technique is required to unravel these overlapping modes. Because the magnetic modes exhibit distinct, orthogonal magnetic and electric dipole moments, they can be individually or mutually excited by incoming light. Furthermore, because the dipole moments have orthogonal orientations, they scatter light in different directions. Finally, when the modes are mutually excited, they can interfere with each other to produce unidirectional radiation[\textbf{cite Kivshar and others}]. These properties are explored both as a way to observe the magnetic modes and as a way to quantify the importance of retardation effects. Because there are techniques that can measure the angular distribution of scattered light from a nanomaterial, this is presented as a way to infer the importance of the in-phase magnetic mode[\textbf{cite two papers measuring angular scattering}].

In planar plasmonic oligomers, the magnetic and electric collective plasmons are orthogonal to each other (see Figure~\ref{field_plots}. Because of this, it is possible to probe multiple modes with a single laser polarization, specifically one in which the magnetic field of the incident light is directed through the rings of the oligomer. Because of the breadth and overlap of the magnetic modes, this will make it possible to observe both at once, but more importantly, this will make it possible to detect the point at which the magnetic plasmons dominate the spectrum.

The angular distribution of power scattered by the olgiomers from the light polarization descibed above is dependent on the size of the oligomer and the frequency at which the light is collected. Here, the angular distribution is calculated from

\begin{equation}
\frac{dP}{d\Omega} = \frac{c}{8\pi}\textrm{Re}[r^2 \hat{\textbf{n}}\cdot \sum_i \textbf{E}_i \times \sum_j \textbf{B}_j]\\
= \frac{\omega^4}{8\pi c^3}\textrm{Re}[\hat{\textbf{n}}\cdot \left(\sum_i \left(\frac{\textbf{r}-\textbf{r}_i}{r}\times\textbf{p}_i\right)\times\frac{\textbf{r}-\textbf{r}_i}{r}\right)\textrm{e}^{\textrm{i}k|\textbf{r}-\textbf{r}_i|} \times \sum_j\left(\frac{\textbf{r}-\textbf{r}_j}{r}\times\textbf{p}_j\right)\textrm{e}^{\textrm{i}k|\textbf{r}-\textbf{r}_i|}
\label{diff_power_full}
\end{equation}

where at every point $\textbf{r}$ on the flux screen the fields scattered by each dipole located at positions $\textbf{r}_i$ are added together before the cross product is taken. There are two relevant limits to take: one in which the loop of dipoles is very small ($\textbf{r}_i = \textbf{0}$) and one in which the loop is finite in size, but the detector is infinitely far away ($r = \infty$). Taking the first limit results in

\begin{equation}
\frac{dP}{d\Omega} = \frac{\omega}{8\pi c r^2}|\textbf{m}|^2
\label{mag_dp}
\end{equation}

a term which decays to zero for a flux screen at infinity. Allowing the loop to have finite size, however, introduces phase effects. It is these that contribute to the overall radiation of the loops of dipoles. Keeping the exponential terms and again letting the magnetic dipole terms decay to zero gives

\begin{equation}
\frac{dP}{d\Omega} = \frac{ck^4}{8\pi}\sum_{ij}[\textbf{p}_i\textbf{p}_j - (\textbf{p}_i\cdot\hat{\textbf{n}})(\textbf{p}_j\cdot\hat{\textbf{n}})]\textrm{e}^{\textrm{i}k\hat{\textbf{n}}\cdot(\textbf{r}_j-\textbf{r}_i)}.
\label{dipoles_only_dp}
\end{equation}

From this, it can be seen that the radiation pattern of a collection of dipoles, regardless of arrangement, is dependent only on the orientations and locations of the dipoles in relation to one another. This equation can be used to gain insight into the angular dependence of the scattered light of collections of dipoles and to exlpain the results from numerical simulations. The results of those simulations are shown and discussed below.

\begin{figure}
\includegraphics[width=5in]{polar_plots_yz.pdf}
\label{polar_plots_yz}
\end{figure}

Figure~\ref{polar_plots_yz} shows this analysis in depth. The radiation pattern collected at the in-phase magnetic plasmon frequency of the twomer system is plotted in the plane containing the electric and magnetic field as a function of both scale and spacing. At small scalings, the scattered power appears to be entirely due to the electric plasmons. As the systems get larger, the magnetic scattered radiation dominates the pattern. This can be further seen in the scaling calculations, where the radiation pattern at a specific frequency changes from electric-dominated to magnetic-dominated and back again. This is significant because it is the first step towards identifying and observing the phenomenon of magnetic mode switching. By watching a particular frequency and varying some system parameter, the radiation pattern can be shown to change. These results are even more significant because they show that even with particles as small as 10 nm in radius, retardation effects have a measureable impact on the optical properties of MNP aggregates.

\begin{figure}
\includegraphics[width=5in]{beaming.pdf}
\label{polar_plots_xz}
\end{figure}

Changing the plane in which radiation is collected from these systems reveals another interesting property of magnetic plasmon oligomers. Collecting scattered light in the plane perpendicular to the previous set of calculations gives another measure of the role of retardation effects. When the magnetic and electric plasmons are of commensurate strength, their fields interfere destructively in some regions of space and constructively in others, leading to directionality in their emitted light. This can be seen in Figure~\ref{polar_plots_xz}. As a function of scale, the radiation pattern can be seen to shift from pure electric dipole to unidirectional, and at large scalings, more magnetic in character. Similarly, as a function of spacing it can be seen that the unidirectionality dominates at certain energies and configurations. However, unlike the distinctive radiation patterns from the previous section, it would seem that once the magnetic plasmons are strong enough to interfere with the electric plasmons, the interference effects never truly go away, except in the case of particles infinitely far away from each other. According to equation [\textbf{PUT IN THAT EQUATION WHEN YOU'RE DONE AND SURE}], there is a sweet spot where the magnetic and electric plasmons can maximally interefere, and it occurs when they of nearly equal magnitude. This result is significant because it is the most convincing evidence yet that magnetic effects matter and contribute significantly to the optical properties of MNP aggregates. The point where the magnetic and electric plasmons maximally interfere is the point where magnetic, and by extension, retardation effects, matter most.

Even more interestingly, this phenomenon appears to break down with increasing length of the oligomer chain. Looking at chains of three, four, five, ten, and twenty oligomers, the beaming capabilities decrease as the chains become longer. This is further evidence of the idea the magnetic and electric dipole modes must be of commensurate strength in order to interfere and produce unidirectional radiation. Chains of magnetic oligomers behave much like particle-in-a-box states; this can be seen in the nodal structure of the twomer and linear threemer in Figure~\ref{field_plots}. As the chains become longer, the magnetic modes will exhibit increasingly dilute field density, leading to weak interferences between modes. As a result, the radiation emitted by these structures loses its directionality. This is important because it emphasizes the significance of smaller magnetic oligomers as the perfect tools to understanding magnetic plasmons and retardation effects. The lack of unidirectionality of longer chains is displayed in Figure ~\ref{bad_beaming}.

Magnetic plasmon supporting aggregates consisting of few oligomers are excellent tools for analyzing the role of retardation effects on MNP aggregates. More conclusion.

\section{Future Work}

\begin{acknowledgement}
CEI, Niket, Harrison, HPC/Hyak/Mox.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

### 2018-01-16 paper_nov_2017/achemso-demo.tex
lots of new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Andrew N. Other}
\altaffiliation{A shared footnote}
\author{Fred T. Secondauthor}
\altaffiliation{Current address: Some other place, Othert\"own,
Germany}
\author{I. Ken Groupleader}
\altaffiliation{A shared footnote}
\email{i.k.groupleader@unknown.uu}
\phone{+123 (0)123 4445556}
\fax{+123 (0)123 4445557}
\affiliation[Unknown University]
{Department of Chemistry, Unknown University, Unknown Town}
\alsoaffiliation[Second University]
{Department of Chemistry, Second University, Nearby Town}
\author{Susanne K. Laborator}
\email{s.k.laborator@bigpharma.co}
\affiliation[BigPharma]
{Lead Discovery, BigPharma, Big Town, USA}
\author{Kay T. Finally}
\affiliation[Unknown University]
{Department of Chemistry, Unknown University, Unknown Town}
\alsoaffiliation[Second University]
{Department of Chemistry, Second University, Nearby Town}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{A Comparison of Optical and Electronic Methods for the Characterization of Plasmon-Supporting Metal Nanoparticle Systems.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{IR,NMR,UV}
\keywords{American Chemical Society, \LaTeX}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.  The document should begin with an
%% abstract, if appropriate.  If one is given and should not be, the
%% contents will be gobbled.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Electron-energy loss spectroscopy (EELS) is an experimentally viable method of nanoscale imaging and probing plasmonic character of metal nanoparticle (MNP) systems. Another well-known technique, cathodoluminescence (CL), also provides information. A similar technique that provides new information, called Electron Energy Gain Spectroscopy (EEGS) is a method that has yet to be studied in full. Here, we present a comparison of the observables gleaned from EELS, CL, EEGS, and optical scattering and absorption simulations on MNP systems.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
This is a paragraph of text to fill the introduction of the
demonstration file.  The demonstration file attempts to show the
modifications of the standard \LaTeX\ macros that are implemented by
the \textsf{achemso} class.  These are mainly concerned with content,
as opposed to appearance.

\section{Results and discussion}

\subsection{Outline}

The document layout should follow the style of the journal concerned.
Where appropriate, sections and subsections should be added in the
normal way. If the class options are set correctly, warnings will be
given if these should not be present.

\subsection{References}

The class makes various changes to the way that references are
handled.  The class loads \textsf{natbib}, and also the
appropriate bibliography style.  References can be made using
the normal method; the citation should be placed before any
punctuation, as the class will move it if using a superscript
citation style
\cite{Mena2000,Abernethy2003,Friedman-Hill2003,EuropeanCommission2008}.
The use of \textsf{natbib} allows the use of the various citation
commands of that package: \citeauthor{Abernethy2003} have shown
something, in \citeyear{Cotton1999}, or as given by
Ref.~\citenum{Mena2000}.  Long lists of authors will be
automatically truncated in most article formats, but not in
supplementary information or reviews \cite{Pople2003}. If you
encounter problems with the citation macros, please check that
your copy of \textsf{natbib} is up to date. The demonstration
database file \texttt{achemso-demo.bib} shows how to complete
entries correctly. Notice that ``\latin{et al.}'' is auto-formatted
using the \texttt{\textbackslash latin} command.

Multiple citations to be combined into a list can be given as
a single citation.  This uses the \textsf{mciteplus} package
\cite{Johnson1972,*Arduengo1992,*Eisenstein2005,*Arduengo1994}.
Citations other than the first of the list should be indicated
with a star. If the \textsf{mciteplus} package is not installed,
the standard bibliography tools will still work but starred
references will be ignored. Individual references can be referred
to using \texttt{\textbackslash mciteSubRef}:
``ref.~\mciteSubRef{Eisenstein2005}''.

The class also handles notes to be added to the bibliography.  These
should be given in place in the document \bibnote{This is a note.
The text will be moved the the references section.  The title of the
section will change to ``Notes and References''.}.  As with
citations, the text should be placed before punctuation.  A note is
also generated if a citation has an optional note.  This assumes that
the whole work has already been cited: odd numbering will result if
this is not the case \cite[p.~1]{Cotton1999}.

\subsection{Floats}

New float types are automatically set up by the class file.  The
means graphics are included as follows (Scheme~\ref{sch:example}).  As
illustrated, the float is ``here'' if possible.
\begin{scheme}
  Your scheme graphic would go here: \texttt{.eps} format\\
  for \LaTeX\, or \texttt{.pdf} (or \texttt{.png}) for pdf\LaTeX\\
  \textsc{ChemDraw} files are best saved as \texttt{.eps} files:\\
  these can be scaled without loss of quality, and can be\\
  converted to \texttt{.pdf} files easily using \texttt{eps2pdf}.\\
  %\includegraphics{graphic}
  \caption{An example scheme}
  \label{sch:example}
\end{scheme}

\begin{figure}
  As well as the standard float types \texttt{table}\\
  and \texttt{figure}, the class also recognises\\
  \texttt{scheme}, \texttt{chart} and \texttt{graph}.
  \caption{An example figure}
  \label{fgr:example}
\end{figure}

Charts, figures and schemes do not necessarily have to be labelled or
captioned.  However, tables should always have a title. It is
possible to include a number and label for a graphic without any
title, using an empty argument to the \texttt{\textbackslash caption}
macro.

The use of the different floating environments is not required, but
it is intended to make document preparation easier for authors. In
general, you should place your graphics where they make logical
sense; the production process will move them if needed.

\subsection{Math(s)}

The \textsf{achemso} class does not load any particular additional
support for mathematics.  If packages such as \textsf{amsmath} are
required, they should be loaded in the preamble.  However,
the basic \LaTeX\ math(s) input should work correctly without
this.  Some inline material \( y = mx + c \) or $ 1 + 1 = 2 $
followed by some display. \[ A = \pi r^2 \]

It is possible to label equations in the usual way (Eq.~\ref{eqn:example}).
\begin{equation}
  \frac{\mathrm{d}}{\mathrm{d}x} \, r^2 = 2r \label{eqn:example}
\end{equation}
This can also be used to have equations containing graphical
content. To align the equation number with the middle of the graphic,
rather than the bottom, a minipage may be used.
\begin{equation}
  \begin{minipage}[c]{0.80\linewidth}
    \centering
    As illustrated here, the width of \\
    the minipage needs to allow some  \\
    space for the number to fit in to.
    %\includegraphics{graphic}
  \end{minipage}
  \label{eqn:graphic}
\end{equation}

\section{Experimental}

The usual experimental details should appear here.  This could
include a table, which can be referenced as Table~\ref{tbl:example}.
Notice that the caption is positioned at the top of the table.
\begin{table}
  \caption{An example table}
  \label{tbl:example}
  \begin{tabular}{ll}
    \hline
    Header one  & Header two  \\
    \hline
    Entry one   & Entry two   \\
    Entry three & Entry four  \\
    Entry five  & Entry five  \\
    Entry seven & Entry eight \\
    \hline
  \end{tabular}
\end{table}

Adding notes to tables can be complicated.  Perhaps the easiest
method is to generate these using the basic
\texttt{\textbackslash textsuperscript} and
\texttt{\textbackslash emph} macros, as illustrated (Table~\ref{tbl:notes}).
\begin{table}
  \caption{A table with notes}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \hline
    Header one                            & Header two \\
    \hline
    Entry one\textsuperscript{\emph{a}}   & Entry two  \\
    Entry three\textsuperscript{\emph{b}} & Entry four \\
    \hline
  \end{tabular}

  \textsuperscript{\emph{a}} Some text;
  \textsuperscript{\emph{b}} Some more text.
\end{table}

The example file also loads the optional \textsf{mhchem} package, so
that formulas are easy to input: \texttt{\textbackslash ce\{H2SO4\}}
gives \ce{H2SO4}.  See the use in the bibliography file (when using
titles in the references section).

The use of new commands should be limited to simple things which will
not interfere with the production process.  For example,
\texttt{\textbackslash mycommand} has been defined in this example,
to give italic, mono-spaced text: \mycommand{some text}.

\section{Extra information when writing JACS Communications}

When producing communications for \emph{J.~Am.\ Chem.\ Soc.}, the
class will automatically lay the text out in the style of the
journal. This gives a guide to the length of text that can be
accommodated in such a publication. There are some points to bear in
mind when preparing a JACS Communication in this way.  The layout
produced here is a \emph{model} for the published result, and the
outcome should be taken as a \emph{guide} to the final length. The
spacing and sizing of graphical content is an area where there is
some flexibility in the process.  You should not worry about the
space before and after graphics, which is set to give a guide to the
published size. This is very dependant on the final published layout.

You should be able to use the same source to produce a JACS
Communication and a normal article.  For example, this demonstration
file will work with both \texttt{type=article} and
\texttt{type=communication}. Sections and any abstract are
automatically ignored, although you will get warnings to this effect.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}

Please use ``The authors thank \ldots'' rather than ``The
authors would like to thank \ldots''.

The author thanks Mats Dahlgren for version one of \textsf{achemso},
and Donald Arseneau for the code taken from \textsf{cite} to move
citations after punctuation. Many users have provided feedback on the
class, which is reflected in all of the different demonstrations
shown in this document.

\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{suppinfo}

This will usually read something like: ``Experimental procedures and
characterization data for all new compounds. The class will
automatically add a sentence pointing to the information on-line:

\end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{achemso-demo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tocentry}

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

\end{tocentry}

\end{document}

### 2018-01-16 paper_nov_2017/doc/latex/achemso/achemso-demo.tex
lots of new stuff

--- 2018-01-16 paper_nov_2017/achemso-demo.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jacsat,manuscript=article]{achemso}
+\documentclass[journal=acnac3,manuscript=article]{achemso}
 
@@
 \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\usepackage[T1]{fontenc}       % Use modern font encodings
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Andrew N. Other}
-\altaffiliation{A shared footnote}
-\author{Fred T. Secondauthor}
-\altaffiliation{Current address: Some other place, Othert\"own,
-Germany}
-\author{I. Ken Groupleader}
-\altaffiliation{A shared footnote}
-\email{i.k.groupleader@unknown.uu}
-\phone{+123 (0)123 4445556}
-\fax{+123 (0)123 4445557}
-\affiliation[Unknown University]
-{Department of Chemistry, Unknown University, Unknown Town}
-\alsoaffiliation[Second University]
-{Department of Chemistry, Second University, Nearby Town}
-\author{Susanne K. Laborator}
-\email{s.k.laborator@bigpharma.co}
-\affiliation[BigPharma]
-{Lead Discovery, BigPharma, Big Town, USA}
-\author{Kay T. Finally}
-\affiliation[Unknown University]
-{Department of Chemistry, Unknown University, Unknown Town}
-\alsoaffiliation[Second University]
-{Department of Chemistry, Second University, Nearby Town}
+\author{Nicholas P. Montoni}
+\author{Steven C. Quillin}
+\author{Charles Cherqui}
+\author{David J. Masiello}
+\email{masiello@chem.washington.edu}
+\affiliation[University of Washington]
+{Department of Chemistry, University of Washington, Seattle, WA, 98195}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{A Comparison of Optical and Electronic Methods for the Characterization of Plasmon-Supporting Metal Nanoparticle Systems.}
+\title[The Effects of Retardation on the Energy Ordering and Tunability of Magnetic Plasmon Resonances]
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abbreviations{IR,NMR,UV}
-\keywords{American Chemical Society, \LaTeX}
+\abbreviations{LSPR, EELS, MNP}
+\keywords{plasmon}
 
-\begin{document}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% The manuscript does not need to include \maketitle, which is
-%% executed automatically.  The document should begin with an
-%% abstract, if appropriate.  If one is given and should not be, the
-%% contents will be gobbled.
+%% executed automatically.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The "tocentry" environment can be used to create an entry for the
+%% graphical table of contents. It is given here as some journals
+%% require that it is printed as part of the abstract page. It will
+%% be automatically moved as appropriate.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{tocentry}
+
+Some journals require a graphical entry for the Table of Contents.
+This should be laid out ``print ready'' so that the sizing of the
+text is correct.
+
+Inside the \texttt{tocentry} environment, the font used is Helvetica
+8\,pt, as required by \emph{Journal of the American Chemical
+Society}.
+
+The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
+permitted for  \emph{Journal of the American Chemical Society}
+graphical table of content entries. The box will not resize if the
+content is too big: instead it will overflow the edge of the box.
+
+This box and the associated title will always be printed on a
+separate page at the end of the document.
+
+\end{tocentry}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The abstract environment will automatically gobble the contents
+%% if an abstract is not used by the target journal.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
-  Electron-energy loss spectroscopy (EELS) is an experimentally viable method of nanoscale imaging and probing plasmonic character of metal nanoparticle (MNP) systems.
-Another well-known technique, cathodoluminescence (CL), also provides information.
-A similar technique that provides new information, called Electron Energy Gain Spectroscopy (EEGS) is a method that has yet to be studied in full.
-Here, we present a comparison of the observables gleaned from EELS, CL, EEGS, and optical scattering and absorption simulations on MNP systems.
+Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials.
+Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing.
+For these reasons, it is imperative to understand the properties of such systems on small and large scales.
+We show, through theory and simulation, that the energy ordering of the magnetic modes of these systems depends on factors such as size, spacing, and environment in ways that purely electric plasmons do not.
+We culminate this study with a parametrization of the fully retarded magnetic coupling, providing a route to characterizing extended chains and arrays of magnetic plasmon oligomers.
 \end{abstract}
@@
 \section{Introduction}
-This is a paragraph of text to fill the introduction of the
-demonstration file.  The demonstration file attempts to show the
-modifications of the standard \LaTeX\ macros that are implemented by
-the \textsf{achemso} class.  These are mainly concerned with content,
-as opposed to appearance.
+Intro: rephrase and elaborate on 2016 Nano Letters.
+Discuss plasmon hybridization theory and incorporating retardation effects.
+Discussion of issue with twomer, how we plan to solve it.
+Probably going to put the big, important equation there and discuss iterative method?
+\section{Results and discussion}
+Moving on to the results to prove that our patch-up of the Hamiltonian works well.
+Compare twomer, threemer (chain and ring), potentially fourmer to BEM simulation.
+Will need a couple of good figures, including diagrams.
+Discuss parametrization of magnetic coupling. Implement, compare full couplings to only nearest-neighbor couplings - surprise! Nearest neighbor coupling does really, really well.
+Finally, explore dielectric background (that cool plot of NN-NS)
+Now that we all agree, move on to periodic/infinite systems.
+Do pretty much the same shit as before, except now you are plotting net magnetization instead of energy eigenvalues.
+Perhaps find a way to represent spin-spin correlation.
 
-\section{Results and discussion}
-
-\subsection{Outline}
-
-The document layout should follow the style of the journal concerned.
-Where appropriate, sections and subsections should be added in the
-normal way. If the class options are set correctly, warnings will be
-given if these should not be present.
+\section{Conclusion}
+We have shown that magnetic plasmon oligomers are highly versatile and tunable.
+We have offered various routes towards using both small and extended arrays of oligomers as optical switches.
+The anti-/ferromagnetic modes of magnetic plasmon oligomers exhibit a disinct and contrary-to-intuition tendency to switch energy ordering as a function of system scale.
+Utiliziing this property, arrays of oligomers can be desined to have specific optical properties, and extended chains or arrays can be designed to switch their favored magnetic character on a location-by-location basis.
+These properties open the doors for specific nanoscale sensing and information transmission.
 
@@
 
-This will usually read something like: ``Experimental procedures and
-characterization data for all new compounds. The class will
-automatically add a sentence pointing to the information on-line:
+A listing of the contents of each file supplied as Supporting Information
+should be included. For instructions on what should be included in the
+Supporting Information as well as how to prepare this material for
+publications, refer to the journal's Instructions for Authors.
+
+The following files are available free of charge.
+\begin{itemize}
+  \item Filename: brief description
+  \item Filename: brief description
+\end{itemize}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The "tocentry" environment can be used to create an entry for the
-%% graphical table of contents.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{tocentry}
-
-Some journals require a graphical entry for the Table of Contents.
-This should be laid out ``print ready'' so that the sizing of the
-text is correct.
-
-Inside the \texttt{tocentry} environment, the font used is Helvetica
-8\,pt, as required by \emph{Journal of the American Chemical
-Society}.
-
-The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-permitted for  \emph{Journal of the American Chemical Society}
-graphical table of content entries. The box will not resize if the
-content is too big: instead it will overflow the edge of the box.
-
-This box and the associated title will always be printed on a
-separate page at the end of the document.
-
-\end{tocentry}
-
 \end{document}

### 2018-01-16 paper_winter_2017/draft_winter_2017.tex
lots of new stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%\usepackage{multline}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}
\date{September 4, 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Tunable Spectral Ordering of Magnetic Plasmon Resonances}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{magnetic plasmons, plasmon metamolecules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\begin{centering}
\includegraphics[width=7cm]{toc.png}
\end{centering}
\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored. A fully retarded coupled dipole model is employed, expanding upon past work in the field, to explore the dependence of the resonant frequencies and spectral ordering of the magnetic resonances on cluster size. It is shown that magnetic resonances change spectral order as metal nanoparticle oligomers change in size, and that these mode switches are observable in full-wave numerical electrodynamics simulations of angle-resolved cathodoluminescence spectra. Electron-beam spectroscopies are uniquely suited to observing this phenomenon, as they provide nanometer spatial and sub-eV spectral resolution and can preferentially excite one magnetic resonance over another. Furthermore, angle-resolved spectroscopies leverage the specific radiation patterns attributed to each magnetic plasmon, clearly differentiating spectral signatures of each individual magnetic plasmon resonance.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years. Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Alu2006,Alu2008,Dionne2011,Cherqui2014,Dionne2016,Cherqui2016,Engheta2017}. The magnetic properties of single oligomers, i.e. those systems composed of only one ring of MNPs, are now well understood based upon models in the quasistatic limit\cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. Conversely, the infinite-oligomer regime has also been understood within the language of tight-binding models of solid-state physics\cite{Schatz2003,Weick2013}. Recently, a disconnect between these size regimes and methods has arisen, leading to open questions in how magnetic plasmon resonances behave in few-oligomer assemblies, called the intermediate size regime\cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.

Most crucial to this disconnect is the question of when and how retardation effects matter. For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}. Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{vonPlessen2007}, and infinite chains and arrays\cite{Kottman2001,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Chumanov2010,Pinchuk2016}. However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers. Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size. This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials. [Pendry superlens, other stuff]

In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $n$-mers with scaling by including the full field within a coupled dipole approach describing their interaction. Interestingly, as a function of scaling, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}. We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2012,Coenen2011,CoPol2011,Polman2014}. The spectral ordering depends not only on aggregate scale but also upon oligomer morphology which we examine below. [Reword, superlensing and cloaking!] Tunability of the relative phase of magnetic fields in a single MNP cluster may lead to advances in detection methods\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, anti-reflective coatings\cite{Alu2006,Alu2008}, and information processing\cite{NordHal2011,NordHal2012}.

\section{Model Theory}

\begin{figure}
\includegraphics[width=6.5in]{2mer_3mer_fields.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}

Figure~\ref{field_plots} displays two model systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to naphthalene and phenalene. The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood [lots of cites]. In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic response of the oligomer are

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
\label{equation_of_motion}
\end{equation}

\noindent where $\omega_{\textrm{sp}}$ is the natural frequency of the Mie resonance, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$, with $\varepsilon_{\infty}$ and $\varepsilon_b$ the high-frequency and background dielectric functions. The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position ri [format], is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole. It is defined by

\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{k^2}{r_{ij}}\left(\textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
\label{electric_field_lambda}
\end{equation}

\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{rm}}$ dipole. The field is decomposed into three parts: [put in scaling] the near-, intermediate-, and far-field. All dipolar retardation effects are included in this field\cite{Purcell1973}. Due to the relative magnitudes of these terms and the sign of [e to the ikr] the interaction energies can change sign and go from energy-lowering to energy-raising.

As described in the methods section, there are as many normal modes of each N-mer as there are electric dipole plasmons. Of these normal modes, some are electric in character and some are magnetic in character with $n$ magnetic plasmon resonances for each $n$-mer studied here. Figure~\ref{field_plots} shows these magnetic plasmon normal modes overlaid with their associated signed magnetic field magnitude. Each mode is named for its particular magnetic field distribution after the poles of a magnet, either all-North (aN) or North-South (NS). The top right-hand corner of each panel indicates whether the  mode depicted has a net electric dipole or a net magnetic dipole moment. In planar geometries, the magnetic dipole moments are always perpendicular to the in-plane electric dipole moments. As a result, they scatter light with different directionality as will be discussed.

\section{Spectral Ordering of Magnetic Modes in Model Systems}

To determine the impact of incorporating retardation effects, it is first useful to consider the quasistatic limit. Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = rij/a$ and not upon the overall oligomer size. That is, if this ratio $s$ of inter-particle distance $r_{ij}$ to particle size $a$ remains constant, as the particles grow the collective frequencies do not change. This is evident by considering the k goes to zero limit of the electric field in Equation~\ref{electric_field_lambda},

\begin{equation}
\begin{aligned}
\frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij} &= \omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \\
&= \omega_{\textrm{sp}}^2 \left(\frac{3r_0^3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{(sr_0)^3}.
\end{aligned}
\label{quasistatic_coupling}
\end{equation}

\noindent where msp and alphasp are rewritten in terms of fundamental parameters. Retardation effects, however, remove this invariance and introduce size-dependence into both the individual plasmon natural frequency as well as into the electric field. Consequently, in the following we choose the individual MNP radius as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $n$-mers.

\begin{figure}
\includegraphics[width=4in]{2mer-3mer-eig.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}

Figure~\ref{scaling} shows the predicted eigenenergies and the simulated spectral peak positions for the magnetic modes of the 2mer and 3mer with varying $r_0$. At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits easily into a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}. In fact, a fully retarded scattering spectrum of an aggregate of this size is qualitatively identical to quasistatic simulations of the same system at all sizes. This implies that the quasistatic approximation is accurate only for magnetic oligomers spanning less than a quarter of the wavelength of light, smaller than suggested by previous work for single particles\cite{Economou1974}. As the system scale increases, the eigenenergies decrease and appear to cross at $r_0 = 7$ nm, and once more at $r_0 = 20$ nm. This is due to the far-field term in Equation~\ref{electric_field_lambda} becoming strong relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares). As the system gets larger, it takes information longer to propagate across the aggregate, meaning that retardation effects become important. The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is accurate again. Rather, both eigenmode crossings are due entirely to retardation effects. The interaction energy between all the dipoles in each magnetic mode, [reformat equation]

\begin{equation}
U_{\textrm{int}} = -\sum_i \textbf{d}_i \cdot \sum_{j \neq i} \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}

\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes. The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode. Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in water the crossing points are shifted towards smaller scale. This is to be expected, as the wavelength of light is compressed in a medium, meaning that light sees objects as much bigger than they really are. This analysis shows that the quasistatic approximation is good for very small magnetic oligomers in vacuum, and for smaller oligomers in medium. This can also be explained through the impact of a dielectric medium on coupling strength. While a medium should contribute an overall increase to the coupling strength (which is predicted in Figure~\ref{scaling}b and f), the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008} Through comparison with simulation (dashed lines in Figure~\ref{scaling}a), it can be shown that this simple and efficient model is accurate to within 0.05 eV and accurately describes the behavior of magnetic plasmon oligomers.

Previous work has explored the oscillatory nature of resonance frequency and radiation damping as a function of size in plasmonic systems\cite{vonPlessen2007}. We have shown that a fully retarded coupled dipole approach predicts magnetic plasmon resonance switching, and explains that it is due to inclusion of the far-field term in the dipole relay tensor. From here, we use simulated angle-resolved CL spectroscopy to observe this magnetic mode switching, leveraging the specific radiative properties of each magnetic plasmon and the ability of the electron beam to isolate specific plasmon modes.

\section{Radiative Properties of Magnetic Plasmon Resonances}
In order to detect the spectral switching of magnetic plasmons, we must exploit their unique radiative properties. Only those magnetic eigenmodes supporting net dipole moments should radiate to the far field. Furthermore, the aN magnetic mode dipole moment is perpendicular to the NS mode electric dipole moment(s) in both the model 2mer and 3mer, meaning that they radiate with different directional-dependence. It has been predicted and shown experimentally that single magnetic oligomers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited.\cite{Dionne2011,Cherqui2016} This is evident from the difference between forward and backward scattering spectra, but can also be shown by computing the differential scattering pattern,\cite{jackson_classical_1999,schwinger1998classical}

\begin{equation}
\frac{dP}{d\Omega} = \frac{c}{8\pi}\textrm{Re}\left[r^2\hat{\textbf{n}}\cdot\sum_i\textbf{E}_i \times \sum_{j}\textbf{B}_{j}^*\right]
\label{dp_field_1}
\end{equation}

\noindent where $\hat{\textbf{n}}$ is the unit vector pointing to the detector a distance $r >> \lambda$ away and $\textbf{E}_i$ and $\textbf{B}_j^*$ are the electric field and conjugate magnetic inductance originating from each oligomer ring. In order to predict the qualitative properties of independently and mutually exciting an orthogonal magnetic and electric plasmon, we coarse-grain our approach by assuming that each ring of the oligomer supports one collective electric and one collective magnetic dipole moment, co-located at the center of each ring. Using the far-fields scattered by such an arrangement of electric and magnetic dipoles reduces the differential scattering to\cite{Alu2006}

\begin{equation}
\frac{dP}{d\Omega} = \frac{ck_e^2k_m^2}{8\pi} \textrm{Re} \left[\hat{\textbf{n}} \cdot \sum_{i} (\hat{\textbf{n}} \times \textbf{d}_i) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_i \times \sum_{j} \hat{\textbf{n}} \times \textbf{d}_j^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_j^*) \times \hat{\textbf{n}}\right]
\label{dp_coarse_grain}
\end{equation}

Performing the vector operations in Equation~\ref{dp_coarse_grain} yields

\begin{multline}
\frac{dP}{d\Omega} = \frac{ck^4}{8\pi} \textrm{Re} [ \sum_{ij} \textbf{d}_i \cdot \textbf{d}_j^* - (\hat{\textbf{n}} \cdot \textbf{d}_i)(\hat{\textbf{n}} \cdot \textbf{d}_j^*) + \boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_i)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_j^*) \\ + \hat{\textbf{n}} \cdot (\textbf{d}_i \times \boldsymbol{\mu}_j^* + \textbf{d}_j^* \times \boldsymbol{\mu}_i) ].
\label{dp_dipoles_1}
\end{multline}

\noindent To build intuition, we demand the magnetic dipole $\boldsymbol{\mu}$ is oriented in the z-direction, and the electric dipole $\textbf{d}$ is oriented in the y-direction. The coarse-grained electric dipole and magnetic dipole can be written in terms of their constituent dipoles $\textbf{d} = \sum_n d_{e,n} \hat{\textbf{y}}$ and $\boldsymbol{\mu} = \frac{k_m}{2}\sum_n(\textbf{r}_n \times d_{m,n} \hat{\boldsymbol{\phi}}_n) = \frac{k_mNRd_m}{2}\hat{\textbf{z}}$ where the sums are taken over the $n$-th and $m$-th dipoles, respectively. Using these definitions, reducing the sum to a single oligomer for simplicity, and giving each dipole equivalent magnitude, the differential scattering becomes

\begin{equation}
\frac{dP}{d\Omega} = \frac{N^2ck_e^2k_m^2}{8\pi}\left[ d_e^2(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{y}})^2) + \frac{k_m^2R^2d_m^2}{4}(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{z}})^2) + d_ed_mk_mR(\hat{\textbf{n}} \cdot \hat{\textbf{x}})\right]
\label{dp_dipoles_2}
\end{equation}

Equation~\ref{dp_dipoles_2} shows that exciting different combinations of dipoles leads to very specific radiation patterns. Exciting only a net electric dipole moment and setting $d_m = 0$ results in a dipolar radiation pattern with a node of zero radiation along the electric dipole axis, in this case the y-axis. Similarly, setting $d_e = 0$ and exciting only a net magnetic dipole results in another dipolar radiation pattern with a node along the magnetic dipole axis, which in this case is the z-axis. Finally, exciting both an electric and a magnetic dipole results in contributions from both patterns in the y- and z-directions. However, the third term of Equation~\ref{dp_dipoles_2} contributes an asymmetry, increasing the radiation in the positive x-direction, or the forward direction in this case, while decreasing the radiation in the backwards direction. This intuitively shows that interfering othrogonal electric and magnetic plasmons radiate with low or no back scattering\cite{Dionne2011}.

\begin{figure}
\includegraphics[width=5in]{scattering_patterns.pdf}
\caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane. The magnetic dipole exhibits the expected dipolar doughnut, or two lobe, shape with a node along the z-axis. The electric dipole moment also shows the expected pattern with a node along the y-axis.}
\label{scattering}
\end{figure}

Using the scattering patterns in Figure~\ref{scattering} computed from Equation~\ref{dp_dipoles_2}, we can make predictions about how to observe each individual magnetic plasmon resonance. The aN modes support a z-oriented magnetic dipole and radiate in the xy-plane. The NS mode in the 2mer is oriented in the y-direction, and so it radiates in the xz-plane. The cyclic 3mer is more complicated. Due to its threefold symmetry, its x- and y-oriented NS modes are degenerate and linearly dependent, meaning that they can be mutually excited. When exciting the 3mer with a y-oriented electric field, it radiates strongly in the xz-plane and weakly in the yz-plane. Using an x-oriented electric field results in the opposite. When choosing field polarizations that excite both the all-North mode and the North-South mode, the systems radiate very strongly in the direction of light propagation, and exhibit very weak back scattering. Strong forward to backward scattering ratios are also predicted and demonstrated in metal-semiconductor core-shell nanoparticles, which similarly exploit the interference between an electric plasmon and a magnetic plasmon\cite{Kivshar2012}. With these radiative properties in mind, we can now observe each magnetic plasmon separately. By collecting photons in the directions that each plasmon radiates weakly, we should be able to see one more strongly than the other. To help this selectivity, we will preferentially excite each magnetic plasmon using an electron beam.

\section{Angle-Resolved Cathodoluminescence for Observing Spectral Switching}
Electron beam spectroscopies, such as EELS and CL, in a STEM are useful for high spatial and spectral resolution studies of nanomaterials\cite{Coenen2011,CoPol2011,Abajo2013,Polman2014,ARPC}. While EELS measures the probability that a passing electron loses energy to a material, CL measures the probability that an excitation in the sample decays into photon emission. Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize a material. Using a STEM fitted with a parabolic mirror over the sample, the user can collect emitted light with angular information within $0 \leq \theta \leq \pi/2$ and $0 \leq \phi \leq \pi$\cite{Coenen2011,CoPol2011,Polman2014}. Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes and their crossing can be observed in spectra. The previous section built up intuition regarding the directionality of light scattered by the magnetic modes of the 2mer and 3mer. This intuition informas the specific angles at which to collect CL spectra. Using the selection rules imposed by the electron beam and the directionality of light, it is possible to distinguish the magnetic modes and observe them switch spectral order.

\begin{figure}
\includegraphics[width=6in]{CL_2mer_3mer.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}

In Figure~\ref{CL_2mer_3mer} we show point CL spectra on the 2mer and 3mer, with the electron beam positions represented in the diagrams by a blue x and  an orange x chosen to excite the aN modes and the NS modes, respectively. However, due to the symmetry of the model systems, the blue position can weakly excite the NS mode, meaning that signatures of it will appear in both spectra. Recalling that the aN mode should radiate in the xy-plane and the North-South mode should radiate in the z-direction and either the x- or the y- direction, it is possible to distinguish the modes by collecting photons at different angular distributions. The angles chosen are reported in Figure~\ref{CL_2mer_3mer}. These spectra confirm the predictions made in Figure~\ref{scaling}, specifically that between $r_0 = 15$ nm and $r_0 = 30$ nm, the aN mode and the NS mode switch spectral order.

We have now shown that the fully retarded coupled dipole approximation can qualitatively and, to small error, quantitatively predict the eigenenergies and spectral switching of magnetic plasmons, we are prepared to explore more complicated geometries that are active areas of research. Before moving on, we must make a quick note about accuracy. Experimentally measured Drude model parameters for metals are often reported with wide uncertainty ranges, which results in the ability to arbitrarily choose Drude model parameters to best fit data\cite{Raschke2015}. We have chosen Drude model parameters for silver that accurately predict the single plasmon frequency at all the sizes we explore, specifically $\varepsilon_{\infty} = 3.77$, $\hbar\omega_p = 9.15$ eV, and $\hbar\gamma = 0.05$ eV. However, these parameters also appear in the static polarizability which dresses the coupling terms. As a result, any error introduced from the choice of Drude model would increase with increasing particle number. Though this is the case for larger and more complicated systems, we assert that the fully retarded coupled dipole method is qualitatively sound and that magnetic plasmon mode switching is a physical phenomenon.

\section{Eigenspectra and CL Spectra of Hexagonally-Packed Arrays}

In order to show that this discussion of mode-switching is experimentally relevant, we use the intuition we have built from the model systems and previous simulated CL experiments to investigate magnetic oligomer systems of recent interest. Specifically, we look at hexagonally packed clusters of 13, 19, and 31 MNPs originally designed and characterized by Greybush \textit{et al.}\cite{Engheta2017}. The arrangement of MNPs and the magnetic plasmon modes that we discuss are shown in Figure~\ref{kagan_fields}. Using the discussion of model systems above as a template, for each system we track the eigenenergies of an aN mode and a NS mode and also show that their switching can be observed in simulated angle-resolved CL measurements.

\begin{figure}
\includegraphics[width=6in]{kagan_fields.pdf}
\caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters. Similarly to the 2mer and 3mer from before, we present only those magnetic modes with either NS and electric dipole character (a, b, d, e, g, and h) or with aN and magnetic dipole character (c, f, and i).}
\label{kagan_fields}
\end{figure}

The magnetic modes of the structures shown in Figure~\ref{kagan_fields} show two kinds of magnetic character. The aN mode of each cluster consists of concentric rings of head-to-tail electric dipoles, with a z-oriented magnetic dipole. The NS modes of each cluster, which are degenerate, exhibit two equal-sized regions of out-of-phase magnetic character, as well as net electric dipoles. In fact, the NS modes of these planar arrays behave the same way as the NS modes of the 3mer in that due to the sixfold symmetry, the "x-oriented" and "y-oriented" dipoles are linearly dependent and mutually excitable by a single plane wave. However, because an electron beam excitation would break this symmetry, the two modes can be distinguished between beam positions and angular distributions of radiation.

\begin{figure}
\includegraphics[width=6in]{13_19_31_eigen.pdf}
\caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters. Unlike the previous 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes. However, for each system a crossing point does occur between $r_0 = 30$ nm and $r_0 = 40$ nm. While the modes of the 13-particle system behave as expected, the aN and NS modes of the larger clusters behave contrary to the intuition built from the earlier model systems. At larger sizes, instead of a monotonic decrease in eigenenergies, the modes exhibit an increase in energy. Looking at the interaction energies, it becomes clear that this is again due to retardation effects, as the term that contributes the most anti-bonding character to the total interaction energy is the far-field. Furthermore, the 31-particle system exhibits a second crossing, unlike the other two structures, and the increase in its eigenenergies is maximized at smaller sizes.}
\label{kagan_eigen}
\end{figure}

The magnetic mode eigenenergies shown in Figure~\ref{kagan_eigen} behave counter to the intuition we have built using the fused, empty ring systems like the 2mer and 3mer. This is because, quite simply, these clusters are constructed from a different aggregation scheme. Though the eigenmodes don't exhibit identical behavior to those shown in Figure~\ref{scaling}, the tools presented earlier are still valid for explaining why the modes cross. Most surprising is the tendency of the modes of the 19- and 31-particle systems to increase in energy at large scale values. This is contrary to the model systems and to plasmonic intuition, in which increasing size causes redshifts. However, we again show the interaction energies, and the dominance of the far-field term is solely responsible for the net positive coupling. In other words, at certain sizes and distances, these magnetic modes become anti-bonding. This is not so unexpected; separating a MNP dimer causes its resonance frequency to oscillate about a central frequency, from bonding to anti-bonding and back\cite{vonPlessen2007}. Angle-resolved CL spectra will show that this phenomenon is indeed physical.

\begin{figure}
\includegraphics[width=6in]{kagan_CL_spectra.pdf}
\caption{Simulated angle-resolved cathodoluminescence spectra of the 13-, 19-, and 31-particle systems. Blue spectra were acquired at the beam positions marked with a blue x in order to preferentially excite the aN mode. Orange spectra were collected at the points marked with an orange x in order to preferentially excite the x-polarized NS mode. Spectra for the 13-particle aggregate were computed for $r_0 = 10$ nm (a) and $r_0 = 50$ nm (b). Spectra for the 19-particle aggregate were computed for $r_0 = 10$ nm (c) and $r_0 = 40$ nm (d). Spectra for the 31-particle aggregate were computed for $r_0 = 10$ nm (e) and $r_0 = 30$ nm (f). The dashed lines in each spectrum indicate the peak location of the aN modes (blue curves) and the NS modes (orange curves). Each panel also displays the collection angles for each spectrum.}
\label{kagan_CL}
\end{figure}

Figure~\ref{kagan_CL} shows simulated CL spectra for the 13-, 19-, and 31-particle system. The selection rules and radiative properties of each mode help to deconvolute the spectra. Because the aN mode radiates strongly in the xy-plane, and weakly in the z-direction, it is the most easily detected at angles of $theta$ larger than 0 radians. The NS mode can be detected either with $theta$ very close to 0 radians, or in the y-direction for this particular beam position. The aN beam position also weakly excites the NS modes, so the spectrum at that position should exhibit a feature that corroborates the spectral location of that mode. After comparing and contrasting between multiple angular spectra,  we show only those spectra that clearly display shoulders or peaks corresponding to the NS mode or the aN mode.

This analysis is experimentally accessible and can be further supported by computing EELS or CL maps of these clusters. Using the field and dipole plots in Figure~\ref{kagan_fields}, the EELS and CL maps of the aN mode and NS mode should be distinguishable. The aN map will exhibit low probability around the central particle, where the dipole moment is smallest, while the NS mode will exhibit large probability around the central dipole where the dipole moment is largest. As a result, electron beam spectroscopies are the perfect tool to experimentally probe the spectral ordering of magnetic plasmon resonances.

\section{Methods}
Here we show how to derive the equations of motion, and solve an example system of two coupled oscillators. The Hamiltonian for a system of $N$ coupled oscillators

\begin{equation}
H = \sum_{i}\frac{\textbf{p}_i^2}{2m_{\textrm{sp}}}+\frac{1}{2}m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i^2 - \frac{e}{2}\sum_{j\neq i}\textbf{q}_i\cdot\textbf{E}_j(\textbf{r}_i),
\label{hammy}
\end{equation}

\noindent where $\textbf{p}_i$ are the momenta of the plasmon oscillators with coordinates $\textbf{q}_i$, $m_{\textrm{sp}}$ is the plasmon mass, $\omega_{\textrm{sp}}$ is the plasmon frequency, and $\textbf{E}_j(\textbf{r}_i)$ is defined in Equation~\ref{electric_field_lambda}. The next step is to write Hamilton's equations of motion,

\begin{equation}
\dot{\textbf{p}}_i = -\frac{\partial H}{\partial\textbf{q}_i} = -m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i + e\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{p_dot}
\end{equation}

\noindent and

\begin{equation}
\dot{\textbf{q}}_i = \frac{\partial H}{\partial\textbf{p}_i} = \frac{\textbf{p}_i}{m_{\textrm{sp}}}.
\label{q_dot}
\end{equation}

Finally, taking another time derivative of Equation~\ref{q_dot} and plugging in Equation~\ref{p_dot}, we obtain the equation of motion

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{equation_of_motion_again}
\end{equation}

\noindent which is exactly Equation~\ref{equation_of_motion}. From here, introducing time-dependence as a complex exponential, rewriting the electric field in terms of the plasmon coordinate, and performing a Fourier transform results in equations of motion in the frequency domain

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)\textbf{q}_i -\frac{e^2}{m_\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}\cdot\textbf{q}_j = 0.
\label{fourier_eom}
\end{equation}

It is this system of equations for the plasmon oscillator coordinates that we solve for the normal modes. As an example, we demonstrate this calculation for two coupled oscillators displaced and oriented along the x-axis. Knowing the dipole orientation allows us to project out the vector components and reduce the coupling term to a constant, resulting in

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{1,2}q_2 = 0
\label{fourier_eom_1}
\end{equation}

and

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{1,2}q_1 = 0.
\label{fourier_eom_2}
\end{equation}

Putting these equations of motion in matrix form allows us to solve for the eigenvalues and eigenvectors as follows.

\begin{equation}
\begin{bmatrix}
(\omega_{\textrm{sp}}^2-\omega^2) & -g_{1,2}\\
-g_{1,2} & (\omega_{\textrm{sp}}^2-\omega^2)
\end{bmatrix}
\begin{bmatrix}
q_1\\
q_2
\end{bmatrix}
=
\begin{bmatrix}
0\\
0
\end{bmatrix}
\label{eom_matrix}
\end{equation}

Finding the determinant of this matrix yields the eigenvalues of the collective modes,

\begin{equation}
\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{1,2}}.
\label{eigenvalues}
\end{equation}

\noindent Of course, the coupling terms $g_{1,2}$ in fact depend on the frequency of the collective mode, which is demonstrated in Equation~\ref{electric_field_lambda}. Because of this, the eigenvalue problem must be solved iteratively until the eigenvalues converge. This example can be extended to systems of an arbitrary number of dipoles, and this exact method is used to solve for the eigenvalues of the magnetic plasmon modes.

\section{Conclusion}
Magnetic plasmon oligomers of experimentally relevant size cannot be properly modeled using the quasistatic approximation. We have shown that a fully retarded coupled dipole method accurately predicts the energetics and ordering of magnetic plasmon resonances. Angle resolved cathodoluminescence spectroscopy confirms the predictions of the model, both on fused-ring oligomers and hexagonally-packed clusters of MNPs. This suggests yet another knob to turn in the field of plasmonics: the spectral ordering of resonances. The tunability of the relative phase of magnetic fields will allow advances in information processing, biological detection, and nanoscale etching.

\begin{acknowledgement}
This material is based in part upon work supported by the State of Washington through the University of Washington Clean Energy Institute and via funding from the Washington Research Foundation. This work was facilitated though the use of advanced computational, storage, and networking infrastructure provided by the Hyak supercomputer system and funded by the STF at the University of Washington. N.P.M. would like to thank Dr. Niket Thakkar and Harrison Goldwyn for helpful discussions and advice.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

%While good for theoretical studies of system properties, scale is not tunable in real time, meaning these properties can't be easily measured. Recent research has focused heavily on finding controllable and reversible ways to manipulate the aggregation scheme of a metal nanoparticle array using tools like DNA, polymers, and stretchable embedding media\cite{Yang2016,Ginger2017,NaLiu2017,DanLuo2009}. We employ this idea by fixing the particle radii and the aggregation scheme of the structure and inflating the interparticle distances. Figure~\ref{scaling}e-h shows the results of fixing $r_0$ at 15 and 30 nm and increasing $s$. Increasing the distance between particles regardless of particle size and environment weakens the coupling as the distance approaches infinity, which can be seen in Equation~\ref{electric_field_lambda}. As a result, the collective frequencies of the magnetic modes approach the single plasmon frequency. On the way, the modes oscillate about each other, exhibiting multiple crossings. The amplitude of these crossings appears to increase with increasing particle size and with increasing background dielectric constant, which can be seen in Figure~\ref{scaling}f and h. The quasistatic approximation cannot explain this phenomenon. The fully retarded electric field contains a complex exponential term that depends on interparticle separation. It is this term that dresses all of the interaction terms in the field and changes the sign of the interaction from negative to positive at certain distances. This is clear evidence that the magnetic modes of the 2-mer are tunable in real time in a laboratory with splittings as small as 0.01 eV and as large as 0.1 eV.

%When two or more metal nanoparticles (MNPs) are brought together, their individual electric plasmons can hybridize to produce new, collective plasmon resonances\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a sizeable magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. These aggregates can couple to and enhance the magnetic field of light, leading to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.

%Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Similar to how a pair of electric plasmons can produce an electrically bright and an electrically dark mode, a pair of magnetic plasmons can produce a magnetically bright mode and a magnetically dark mode. This understanding opens up new routes to preferentially exciting magnetic and electric plasmons and distinguishing between the different plasmonic modes of a particular aggregate. Studies of the properties of magnetic plasmons have focused on plasmon propagation and hybridization, but have not sought to determine under what circumstances the magnetic plasmons of a system dominate its optical properties. Key to answering this question is the influence of retardation effects.

%This work utilizes and augments a previously published tight-binding model\cite{Cherqui2014}. The model in question maps the electric plasmon of each nanoparticle onto a harmonic oscillator and allows them to couple through quasistatic, near-field interactions using the Hamiltonian

%\begin{equation}
%\frac{H}{\hbar\omega_{\textrm{sp}}} = \frac{1}{2}\sum_{i}\left[\boldsymbol{\Pi}_{i}^2 + \textbf{Q}_{i}^{2}\right] - \frac{\alpha_{\textrm{sp}}}{2}\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}.
%\label{full_hammy}
%\end{equation}

%Here, $\omega_{\textrm{sp}}$ is the resonant frequency of the individual electric plasmons, the $\boldsymbol{\Pi}_{i}$ are the generalized momenta conjugate to the generalized coordinates $\textbf{Q}_{i}$, $\alpha_{\textrm{sp}}$ is the polarizability of each individual MNP, and $\boldsymbol{\Lambda}_{ij}$ is the near-field dipole-dipole relay tensor. In this work, retardation effects are incorporated into the dipole-dipole relay tensor through the intermediate- and far-field terms in the dipole electric field as follows:

%\begin{equation}
%\boldsymbol{\Lambda}_{ij} = \left[\left(\frac{1}{r_{ij}^3} - \frac{\textrm{i}\omega}{cr_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{\omega^2}{c^2r_{ij}}\left(\textbf{1} - \hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right]e^{\textrm{i}\omega/c r},
%\label{dipoledipole}
%\end{equation}

%where $r_{ij}$ is the distance between the $i^{\textrm{th}}$ and $j^{\textrm{th}}$ dipoles along the unit vector $\hat{\textbf{n}}_{ij}$, \textbf{1} is the unit dyad, $c$ is the speed of light, and $\omega$ is the collective frequency at which all of the dipoles oscillate. Using Equations~\ref{full_hammy} and ~\ref{dipoledipole}, Hamilton's equations of motion,

%\begin{equation}
%\ddot{\textbf{Q}}_{i} = -\textbf{Q}_{i} + \sum_{j\neq i}\boldsymbol{Lambda}_{ij}\cdot\textbf{Q}_{j}
%\label{eom}
%\end{equation}

% can be found and the system of equations can be solved for the eigenvalues and eigenvectors of the nanoparticle array. The eigenvectors are the generalized coordinates corresponding to each dipole moment in the aggregate. It is important to note that because the eigenvalues, the collective frequencies, appear in the coupling terms, this will result in a system of transcendental equations which must be solved iteratively.

%In this paper, three model systems are considered. Following previous work, the model systems are constructed from fused, six-member rings of silver nanospheres, resembling conjugated hydrocarbon rings. The aggregates considered are a two-ring system, a linear three-ring system, and a triangular three-ring system. Solving for the magnetic eigenmodes of each system results in a set of eigenvectors for each mode which correspond to electric dipole moments. Figure~\ref{field_plots} shows the oligomers, the dipole moments on each sphere, and the magnetic field distribution computed from\cite{jackson_classical_1999}

%\begin{equation}
%\textbf{B}_{\textrm{tot}}(\textbf{r},\omega) = \frac{\omega^2}{c^2}\sum_{j}(\hat{\textbf{n}}_{j}\times\textbf{p}_{j})\frac{e^{\textrm{i}\omega/c r_j}}{r_j}\left(1 - \frac{c}{\textrm{i}\omega r_{j}}\right).
%\label{magnetic_field}
%\end{equation}

### 2018-01-16 CL_points/anth_CL_points.m

@@ -1,0 +1,177 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+clear all
+close all
+clc
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('silver_normal.dat')};
+for num = [1,5,10,15,20,25,30];
+sep = [2.5];
+radius2 = num;
+r = sep*radius2;
+diameter2 = 2*radius2;
+
+ps = trisphere(256,diameter2);
+
+ex = sqrt(3)/2 * r;
+ey = (1/2) * r;
+
+p1 = shift(ps,[-2*ex,2*ey,0]);
+p2 = shift(ps,[-3*ex,ey,0]);
+p3 = shift(ps,[-3*ex,-ey,0]);
+p4 = shift(ps,[-2*ex,-2*ey,0]);
+p5 = shift(ps,[-ex,-ey,0]);
+p6 = shift(ps,[0,-2*ey,0]);
+p7 = shift(ps,[ex,-ey,0]);
+p8 = shift(ps,[2*ex,-2*ey,0]);
+p9 = shift(ps,[3*ex,-ey,0]);
+p10 = shift(ps,[3*ex,ey,0]);
+p11 = shift(ps,[2*ex,2*ey,0]);
+p12 = shift(ps,[ex,ey,0]);
+p13 = shift(ps,[0,2*ey,0]);
+p14 = shift(ps,[-ex,ey,0]);
+
+Ptot= {p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11,p12,p13,p14};
+
+pret=comparticle(epstab,Ptot,[2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1],1,2,3,4,5,6,7,8,9,10,11,12,13,14,op2);
+
+units;
+
+[ width, vel ] = deal( 0.01, eelsbase.ene2vel( 200e3 ) );
+
+imp = [-ex, ey+1.1*radius2; -ex-1.1*radius2, ey; -3*ex-1.1*radius2, 0; 0, 2*ey+1.1*radius2];
+
+dir1 = [sin(pi/4)*cos(0), sin(pi/4)*sin(0), cos(pi/4)];
+dir2 = [sin(pi/4)*cos(pi/2), sin(pi/4)*sin(pi/2), cos(pi/4)];
[…]

### 2018-01-16 bem_plot.py

@@ -1,9 +1,131 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-for num in [10]:
-	A = np.loadtxt('new_spacing_bem_data/nm' + str(num) + '_twomer')
+'''80:-1'''
+'''0:101'''
+'''eV = np.linspace(3.3,3.6,31)'''
+
+A = np.loadtxt('../eegs_seels/eegs_rod_3.3')
+AA = np.loadtxt('../eegs_seels/eels_rod_3.3')
+AAA = np.loadtxt('../eegs_seels/seels_rod_3.3')
+
+eV = np.linspace(1,4,151)
+
+plt.figure()
+plt.plot(eV,AA,eV,AAA)
+plt.legend(['EELS','SEELS'])
+plt.xlabel('Energy (eV)')
+plt.ylabel('Probability')
+plt.savefig('../eegs_seels/eels_seels_rod_3.3.pdf')
+plt.show()
+
+'''n = 1
+eV = 1.6
+levels = np.linspace(0,1,21)
+A = np.loadtxt('../eegs_seels/n='+str(n)+'/rod_EEGS_map_'+str(eV))
+B = np.loadtxt('../eegs_seels/n='+str(n)+'/rod_EELS_map_'+str(eV))
+C = np.loadtxt('../eegs_seels/n='+str(n)+'/rod_SEELS_map_'+str(eV))
+plt.figure()
+plt.contourf(A,levels=np.linspace(A.min(),A.max(),21))
+plt.colorbar()
+plt.savefig('../eegs_seels/rod_eegs_n='+str(n)+'_'+str(eV)+'.pdf')
+plt.show()
+EELS = np.concatenate([B[0:len(B)/2-1],B[len(B)/2+1:-1]],axis=1)
+SEELS = np.concatenate([C[0:len(C)/2-1],C[len(C)/2+1:-1]],axis=1)
+diff = SEELS-EELS
+normdiff = diff/diff.max()
+plt.figure()
+plt.contourf(EELS,levels=np.linspace(EELS.min(),EELS.max(),21))
+plt.colorbar()
+plt.savefig('../eegs_seels/rod_eels_n='+str(n)+'_'+str(eV)+'.pdf')
+plt.show()
+
+plt.figure()
+plt.contourf(SEELS,levels=np.linspace(SEELS.min(),SEELS.max(),21))
[…]

### 2018-01-16 chains/chain_poynting.py

@@ -1,0 +1,160 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+
+bem_NNN = [3.614, 3.602, 3.564, 3.494, 3.412, 3.31, 3.2]
+bem_N_S = [3.612, 3.601, 3.566, 3.498, 3.404, 3.294, 3.18]
+bem_NSN = [3.61, 3.6, 3.57, 3.512, 3.42, 3.292, 3.12]
+bem_r = [1, 5, 10, 15, 20, 25, 30]
+poynting_points = 16
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 14; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NNN = []
+	NSN = []
+	N_S = []
+	interaction = [[],[],[]]
+	#NSNS = []
+	for r in range (20,21):
+		a0 = r*10**-7; #sphere radius in cm
+		index = r*10 - 10
+		''' now determine geometry.'''
+		print r
+		#raw_input()
+		# make unit vectors in centimeters.
+		rij = 3*a0
+		e1 = float(1)/float(2) * (rij) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (rij); #long side of 30-60-90 triangle
[…]

### 2018-01-16 chains/fixed_vectors.py

@@ -3,6 +3,8 @@ import math
 import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
 
 bem_NNN = [3.614, 3.602, 3.564, 3.494, 3.412, 3.31, 3.2]
 bem_N_S = [3.612, 3.601, 3.566, 3.498, 3.404, 3.294, 3.18]
@@ -23,103 +25,130 @@ Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd i
 epsinf = 3.77; # does this have units?
 '''Properties for silver.'''
 Eplasma = 1.46599161e-18; # J
-gamma = 0.05*elec/(hbar*16)
-mode = []
-interaction = []
-NF = [[],[]]
-IF = [[],[]]
-FF = [[],[]]
+gamma = 0.05*elec/(hbar)
+NNN = []
+NSN = []
+N_S = []
+interaction = [[],[],[]]
+NF = [[],[],[]]
+IF = [[],[],[]]
+FF = [[],[],[]]
+epsb = 1.77
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
-for epsb in np.linspace(0.1,5,50):
-	for r in range (15,16):
+vec_1 = np.loadtxt('mode_vec_0.txt')
+vec_2 = np.loadtxt('mode_vec_1.txt')
+vec_3 = np.loadtxt('mode_vec_2.txt')
+vectors = [[vec_1],[vec_2],[vec_3]]
+for sep in np.linspace(1,1,1):
+	for r in range (1,31):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
 		print r
 		#raw_input()
 		# make unit vectors in centimeters.
-		rij = 3*a0
-		e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
-		e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
+		rij = (2+sep)*a0
+		e1 = float(1)/float(2) * (rij) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (rij); #long side of 30-60-90 triangle
[…]

### 2018-01-16 chains/long_chain.py

@@ -1,0 +1,173 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+
+#bem_NNN = [3.614, 3.602, 3.564, 3.494, 3.412, 3.31, 3.2]
+#bem_N_S = [3.612, 3.601, 3.566, 3.498, 3.404, 3.294, 3.18]
+#bem_NSN = [3.61, 3.6, 3.57, 3.512, 3.42, 3.292, 3.12]
+#bem_r = [1, 5, 10, 15, 20, 25, 30]
+poynting_points = 100
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+numPart = 22; #number of particles
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; # does this have units?
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+for epsb in range(1,2):
+	NNN = []
+	NSN = []
+	N_S = []
+	interaction = [[],[],[]]
+	#NSNS = []
+	for r in range (20,21):
+		a0 = r*10**-7; #sphere radius in cm
+		index = r*10 - 10
+		''' now determine geometry.'''
+		print r
+		#raw_input()
+		# make unit vectors in centimeters.
+		rij = 3*a0
+		e1 = float(1)/float(2) * (rij) ; #short side of 30-60-90 triangle
+		e2 = float(math.sqrt(3))/float(2) * (rij); #long side of 30-60-90 triangle
[…]

### 2018-01-16 chains/poynting.py

@@ -1,0 +1,42 @@
+p_dot_e = 0
+for x in range(0,numPart):
+    electric = np.multiply([0,1],np.exp(1j*wavenumber*np.sqrt(Loc[x][0]**2 + Loc[x][1]**2)))
+p_dot_E += np.dot(vec[x],electric)
+screen_dist = 1000000000000*a0
+vec = vec*p_dot_E
+for number in range(0,numPart):
+    location = list(Loc[number])
+location.append(0)
+
+Bfield = np.empty((poynting_points,poynting_points,3),dtype=complex)
+Efield = np.empty((poynting_points,poynting_points,3),dtype=complex)
+phi_count = 0
+
+for phi in np.linspace(0,2*math.pi,poynting_points):
+    theta_count = 0
+    for theta in np.linspace(0,math.pi,poynting_points):
+        nhat = [np.cos(phi)*np.sin(theta), np.sin(phi)*np.sin(theta), np.cos(theta)]
+    point = np.multiply(screen_dist,nhat)
+rmag = np.sqrt((point[0]-location[0])**2 + (point[1]-location[1])**2 + point[2]**2)
+nhat_dip = (location-point)/rmag
+Bfield[theta_count,phi_count] = (wavenumber**2)*np.cross(nhat_dip,vec[number])*np.exp(1j*wavenumber*rmag)/rmag #
+Efield[theta_count,phi_count] = np.cross(Bfield[theta_count,phi_count],nhat_dip)/(epsb)
+theta_count += 1
+phi_count += 1
+Bfield_total = Bfield_total + Bfield
+Efield_total = Efield_total + Efield
+poynting = np.empty((poynting_points,poynting_points),dtype=float)
+for idx1 in range(poynting_points):
+    for idx2 in range(poynting_points):
+        poynting[idx1,idx2] = (screen_dist**2)*np.linalg.norm(np.real(np.cross(Efield_total[idx1,idx2],np.conj(Bfield_total[idx1,idx2]))))
+theta = np.linspace(0,math.pi,poynting_points)
+phi = np.linspace(0,2*math.pi,poynting_points)
+PHI,THETA = np.meshgrid(phi,theta)
+X = poynting * np.cos(PHI)*np.sin(THETA)
+Y = poynting * np.sin(PHI)*np.sin(THETA)
+Z = poynting * np.cos(THETA)
+norm = poynting/poynting.max()
+fig = plt.figure()
[…]

### 2018-01-16 chains/three/three_plotter.py

@@ -1,62 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import scipy.interpolate as scint
-
-'''A = np.loadtxt('nm1_three_chain')
-B = np.loadtxt('nm4_chain_three')
-C = np.loadtxt('nm8_chain_three')
-D = np.loadtxt('nm10_chain_three')'''
-
-A = np.loadtxt('three_chain_eigen',skiprows=1)
-NNN = np.loadtxt('../NNN.txt')
-N_S = np.loadtxt('../N_S.txt')
-NSN = np.loadtxt('../NSN.txt')
-
-rad = A[:,0]
-NSN_BEM = A[:,1]
-N_S_BEM = A[:,2]
-NNN_BEM = A[:,3]
-radnew = np.linspace(1,10,291)
-
-NNN_smooth = scint.interp1d(rad,NNN_BEM,'quadratic')
-N_S_smooth = scint.interp1d(rad,N_S_BEM,'quadratic')
-NSN_smooth = scint.interp1d(rad,NSN_BEM,'quadratic')
-
-r = np.linspace(1,30,291)
-plt.figure(1)
-plt.plot(r,NNN,lw=3,label='NNN theory')
-plt.plot(r,N_S,lw=3,label='N_S theory')
-plt.plot(r,NSN,lw=3,label='NSN theory')
-plt.xlim(1,30)
-plt.xlabel('Radius (nm)')
-plt.ylabel('Energy (eV)')
-plt.legend()
-plt.savefig('three_chain_theory.pdf')
-plt.figure(2)
-plt.plot(radnew,NNN_smooth(radnew),lw=3,label='NNN bem')
-plt.plot(radnew,N_S_smooth(radnew),lw=3,label='N_S bem')
-plt.plot(radnew,NSN_smooth(radnew),lw=3,label='NSN bem')
-plt.ylim([3.02,3.10])
-plt.xlabel('Radius (nm)')
-plt.ylabel('Energy (eV)')
-plt.legend()
-plt.savefig('three_chain_mnpbem.pdf')
-plt.show()
-
-'''plt.figure(1)
-plt.plot(A[:,0],A[:,1],label = 'left')
-plt.plot(A[:,0],A[:,2],label = 'top')
-plt.legend()
-plt.figure(2)
-plt.plot(B[:,0],B[:,1],label = 'left')
-plt.plot(B[:,0],B[:,2],label = 'top')
[…]

### 2018-01-16 dumb_geometry_test.py

@@ -1,0 +1,27 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+r_i = [[0,1,0],[-1,0,0],[0,-1,0],[1,0,0]]
+p_i = [[-1,0,0],[0,-1,0],[1,0,0],[0,1,0]]
+
+thing = np.zeros((181,1))
+
+for num in range(0,4):
+	theta_count = 0
+	for theta in np.linspace(0,math.pi,181):
+		phi_count = 0
+		for phi in np.linspace(math.pi,math.pi,1):
+			nhat = [np.cos(phi)*np.sin(theta),np.sin(phi)*np.sin(theta),np.cos(theta)]
+			thing[theta_count,phi_count] += np.linalg.norm(np.cross(np.cross(nhat,p_i[num]),nhat)*np.dot(nhat,r_i[num]))
+			phi_count += 1
+		theta_count += 1
+
+theta = np.linspace(0,math.pi,181)
+plt.figure()
+plt.polar(theta,np.sin(theta))
+plt.polar(theta,thing[:,0],marker='o')
+plt.legend(['sin(theta)','sine and cosine term in e-field'])
+#plt.savefig('sine_comparison.pdf')
+plt.show()
+

### 2018-01-16 greybush_2017/CL_13.m

@@ -1,0 +1,150 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+clear all
+close all
+clc
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('silver_normal.dat')};
+for num = [10,20,30,40,50];
+
+numPart = 6;
+theta = linspace(0,2*pi,numPart+1);
+phi = 2*pi/(numPart*2);
+diam = 2*num;
+%diam=5;
+separation = 1.5*diam;
+RAD = separation/(2*sin(phi));
+second_layer = sqrt(3)*separation;
+third_layer = 2*separation;
+fourth_layer = sqrt(7)*separation;
+sphere = trisphere(144,diam);
+
+p0 = sphere;
+p1 = shift(sphere, [RAD*cos(theta(1)), RAD*sin(theta(1)), 0]);
+p2 = shift(sphere, [RAD*cos(theta(2)), RAD*sin(theta(2)), 0]);
+p3 = shift(sphere, [RAD*cos(theta(3)), RAD*sin(theta(3)), 0]);
+p4 = shift(sphere, [RAD*cos(theta(4)), RAD*sin(theta(4)), 0]);
+p5 = shift(sphere, [RAD*cos(theta(5)), RAD*sin(theta(5)), 0]);
+p6 = shift(sphere, [RAD*cos(theta(6)), RAD*sin(theta(6)), 0]);
+p7 = shift(sphere, [second_layer*cos(theta(1)+phi), second_layer*sin(theta(1)+phi), 0]);
+p8 = shift(sphere, [second_layer*cos(theta(2)+phi), second_layer*sin(theta(2)+phi), 0]);
+p9 = shift(sphere, [second_layer*cos(theta(3)+phi), second_layer*sin(theta(3)+phi), 0]);
+p10 = shift(sphere, [second_layer*cos(theta(4)+phi), second_layer*sin(theta(4)+phi), 0]);
+p11 = shift(sphere, [second_layer*cos(theta(5)+phi), second_layer*sin(theta(5)+phi), 0]);
+p12 = shift(sphere, [second_layer*cos(theta(6)+phi), second_layer*sin(theta(6)+phi), 0]);
+
+p = comparticle( epstab, { p0, p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12 },  ...
[…]

### 2018-01-16 greybush_2017/CL_19.m

@@ -1,0 +1,156 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+clear all
+close all
+clc
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('silver_normal.dat')};
+for num = [10,20,30,40,50];
+
+numPart = 6;
+theta = linspace(0,2*pi,numPart+1);
+phi = 2*pi/(numPart*2);
+diam = 2*num;
+%diam=5;
+separation = 1.5*diam;
+RAD = separation/(2*sin(phi));
+second_layer = sqrt(3)*separation;
+third_layer = 2*separation;
+fourth_layer = sqrt(7)*separation;
+sphere = trisphere(144,diam);
+
+p0 = sphere;
+p1 = shift(sphere, [RAD*cos(theta(1)), RAD*sin(theta(1)), 0]);
+p2 = shift(sphere, [RAD*cos(theta(2)), RAD*sin(theta(2)), 0]);
+p3 = shift(sphere, [RAD*cos(theta(3)), RAD*sin(theta(3)), 0]);
+p4 = shift(sphere, [RAD*cos(theta(4)), RAD*sin(theta(4)), 0]);
+p5 = shift(sphere, [RAD*cos(theta(5)), RAD*sin(theta(5)), 0]);
+p6 = shift(sphere, [RAD*cos(theta(6)), RAD*sin(theta(6)), 0]);
+p7 = shift(sphere, [second_layer*cos(theta(1)+phi), second_layer*sin(theta(1)+phi), 0]);
+p8 = shift(sphere, [second_layer*cos(theta(2)+phi), second_layer*sin(theta(2)+phi), 0]);
+p9 = shift(sphere, [second_layer*cos(theta(3)+phi), second_layer*sin(theta(3)+phi), 0]);
+p10 = shift(sphere, [second_layer*cos(theta(4)+phi), second_layer*sin(theta(4)+phi), 0]);
+p11 = shift(sphere, [second_layer*cos(theta(5)+phi), second_layer*sin(theta(5)+phi), 0]);
+p12 = shift(sphere, [second_layer*cos(theta(6)+phi), second_layer*sin(theta(6)+phi), 0]);
+p13 = shift(sphere, [third_layer*cos(theta(1)), third_layer*sin(theta(1)), 0]);
[…]

### 2018-01-16 greybush_2017/CL_31.m

@@ -1,0 +1,168 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+clear all
+close all
+clc
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('silver_normal.dat')};
+for num = [10,20,30,40,50];
+
+numPart = 6;
+theta = linspace(0,2*pi,numPart+1);
+phi = 2*pi/(numPart*2);
+diam = 2*num;
+%diam=5;
+separation = 1.5*diam;
+RAD = separation/(2*sin(phi));
+second_layer = sqrt(3)*separation;
+third_layer = 2*separation;
+fourth_layer = sqrt(7)*separation;
+sphere = trisphere(144,diam);
+
+p0 = sphere;
+p1 = shift(sphere, [RAD*cos(theta(1)), RAD*sin(theta(1)), 0]);
+p2 = shift(sphere, [RAD*cos(theta(2)), RAD*sin(theta(2)), 0]);
+p3 = shift(sphere, [RAD*cos(theta(3)), RAD*sin(theta(3)), 0]);
+p4 = shift(sphere, [RAD*cos(theta(4)), RAD*sin(theta(4)), 0]);
+p5 = shift(sphere, [RAD*cos(theta(5)), RAD*sin(theta(5)), 0]);
+p6 = shift(sphere, [RAD*cos(theta(6)), RAD*sin(theta(6)), 0]);
+p7 = shift(sphere, [second_layer*cos(theta(1)+phi), second_layer*sin(theta(1)+phi), 0]);
+p8 = shift(sphere, [second_layer*cos(theta(2)+phi), second_layer*sin(theta(2)+phi), 0]);
+p9 = shift(sphere, [second_layer*cos(theta(3)+phi), second_layer*sin(theta(3)+phi), 0]);
+p10 = shift(sphere, [second_layer*cos(theta(4)+phi), second_layer*sin(theta(4)+phi), 0]);
+p11 = shift(sphere, [second_layer*cos(theta(5)+phi), second_layer*sin(theta(5)+phi), 0]);
+p12 = shift(sphere, [second_layer*cos(theta(6)+phi), second_layer*sin(theta(6)+phi), 0]);
+p13 = shift(sphere, [third_layer*cos(theta(1)), third_layer*sin(theta(1)), 0]);
[…]

### 2018-01-16 greybush_2017/fixed_vec_greybush.py

@@ -1,0 +1,189 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+static_NN = []
+static_NS = []
+bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
+bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
+mie_omegas = np.loadtxt('../mie_omegas_vacuum.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 13 #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 9.15*elec/hbar; # J
+gamma = 0.05*elec/(hbar)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+NN = []
+NS = []
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NN_vec = np.loadtxt('13_0_vec.txt')
+NS_vec = np.loadtxt('13_4_vec.txt')
+vectors = [NN_vec,NS_vec]
+for r in range(1,51):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r-1
+	''' now determine geometry.'''
+	print index
+	# make unit vectors in centimeters.
+	rij = 3*a0#2*a0+(2.5*10**-7)
+	part_per_ring = numPart
+	theta = 2*math.pi/(6)
+	phi = theta/2.
+	#print theta
+	#print phi
+	#print np.cos(phi)
[…]

### 2018-01-16 greybush_2017/greybush.py

@@ -8,12 +8,12 @@ static_NN = []
 static_NS = []
 bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
 bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
-mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+mie_omegas = np.loadtxt('../mie_omegas_vacuum.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 crossing = []
 elec = 1.60217662e-19 # regular coulombs
 
-numPart = 13 #number of particles
+numPart = 31 #number of particles
 
 me = 9.10938291e-28; # electron mass in g
 ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
@@ -21,21 +21,22 @@ hbar = 1.054571726e-34; # modified Planck in J*s
 c = 2.99e10; # speed of light in cm/s
 eps0 = 8.85418782e-12; # permittivity of free space
 Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
-epsinf = 9.84; 
+epsinf = 3.77; 
 '''Properties for silver.'''
 Eplasma = 9.0*elec/hbar; # J
 gamma = 0.069*elec/(hbar)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
-epsb = 2.1
+epsb = 1
 
-for r in range(1,2):
-	a0 = 27.5*r*10**-7; #sphere radius in cm
+
+for r in range(10,11):
+	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
-	index = (r-1)*10
+	index = r-1
 	''' now determine geometry.'''
 	print index
 	# make unit vectors in centimeters.
-	rij = 2*a0
+	rij = 3*a0
 	part_per_ring = numPart
 	theta = 2*math.pi/(6)
 	phi = theta/2.
@@ -61,24 +62,27 @@ for r in range(1,2):
 			elif 6 <= num < 12:
[…]

### 2018-01-16 greybush_2017/greybush_CL_points_au.m

@@ -1,0 +1,168 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+clear all
+close all
+clc
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('gold.dat')};
+for num = [10,20,30,40,50];
+
+numPart = 6;
+theta = linspace(0,2*pi,numPart+1);
+phi = 2*pi/(numPart*2);
+diam = 2*num;
+%diam=5;
+separation = 1.5*diam;
+RAD = separation/(2*sin(phi));
+second_layer = sqrt(3)*separation;
+third_layer = 2*separation;
+fourth_layer = sqrt(7)*separation;
+sphere = trisphere(144,diam);
+
+p0 = sphere;
+p1 = shift(sphere, [RAD*cos(theta(1)), RAD*sin(theta(1)), 0]);
+p2 = shift(sphere, [RAD*cos(theta(2)), RAD*sin(theta(2)), 0]);
+p3 = shift(sphere, [RAD*cos(theta(3)), RAD*sin(theta(3)), 0]);
+p4 = shift(sphere, [RAD*cos(theta(4)), RAD*sin(theta(4)), 0]);
+p5 = shift(sphere, [RAD*cos(theta(5)), RAD*sin(theta(5)), 0]);
+p6 = shift(sphere, [RAD*cos(theta(6)), RAD*sin(theta(6)), 0]);
+p7 = shift(sphere, [second_layer*cos(theta(1)+phi), second_layer*sin(theta(1)+phi), 0]);
+p8 = shift(sphere, [second_layer*cos(theta(2)+phi), second_layer*sin(theta(2)+phi), 0]);
+p9 = shift(sphere, [second_layer*cos(theta(3)+phi), second_layer*sin(theta(3)+phi), 0]);
+p10 = shift(sphere, [second_layer*cos(theta(4)+phi), second_layer*sin(theta(4)+phi), 0]);
+p11 = shift(sphere, [second_layer*cos(theta(5)+phi), second_layer*sin(theta(5)+phi), 0]);
+p12 = shift(sphere, [second_layer*cos(theta(6)+phi), second_layer*sin(theta(6)+phi), 0]);
+p13 = shift(sphere, [third_layer*cos(theta(1)), third_layer*sin(theta(1)), 0]);
[…]

### 2018-01-16 poynting_test/magnetic_dipole.py

@@ -1,0 +1,85 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+
+a0 = 10e-8
+numPart = 4
+poynting_points = 32
+pynts = poynting_points
+mu = [0,0,1]
+vec = [np.array([0,1,0])]#,np.array([1,0,0])]#,np.array([0,-1,0]),np.array([1,0,0])]
+loc = [np.array([a0,0,0])]#,np.array([a0,0,0])]#,np.array([-a0,0,0]),np.array([0,-a0,0])]
+screen_dist = 1000
+poynting_mu = np.zeros((pynts,pynts))
+'''Magnetic Dipole First'''
+theta_count = 0
+for theta in np.linspace(0,math.pi,pynts):
+	phi_count = 0
+	for phi in np.linspace(0,2*math.pi,pynts):
+		nhat = [np.cos(phi)*np.sin(theta), np.sin(phi)*np.sin(theta), np.cos(theta)]
+		point = np.multiply(screen_dist,nhat)
+		rmag = np.sqrt((point[0])**2 + (point[1])**2 + point[2]**2)
+		poynting_mu[theta_count,phi_count] = (np.dot(mu,mu) - (np.dot(mu,nhat))**2)
+		phi_count += 1
+	theta_count += 1
+wavenumber = 1e5
+Bfield_total = np.zeros((poynting_points,poynting_points,3),dtype=complex)
+Efield_total = np.zeros((poynting_points,poynting_points,3),dtype=complex)
+for number in range(0,1):
+	location = list(loc[number])
+	#location.append(0)
+	
+	Bfield = np.empty((poynting_points,poynting_points,3),dtype=complex)
+	Efield = np.empty((poynting_points,poynting_points,3),dtype=complex)
+	phi_count = 0
+	
+	for phi in np.linspace(0,2*math.pi,poynting_points):
+		theta_count = 0
+		for theta in np.linspace(0,math.pi,poynting_points):
+			nhat = [np.cos(phi)*np.sin(theta), np.sin(phi)*np.sin(theta), np.cos(theta)]
+			point = np.multiply(screen_dist,nhat)
[…]

### 2018-01-16 reverse_bowtie/fixed_vec_bow.py

@@ -1,0 +1,135 @@
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+
+omegas = np.loadtxt('../mie_omegas_vacuum.txt')
+
+NN = []
+NS = []
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+'''Begin by choosing a number of particles and a number of rings, defining constants and material properties'''
+numPart = 6
+numRings = 2
+Q = [[1,0],[0,1]]
+#mie_omegas = np.loadtxt('mie_omegas_eV.txt')
+# [.5,-math.sqrt(3)/2],[.5,math.sqrt(3)/2],[1,0],[-.5,-math.sqrt(3)/2],[-.5,math.sqrt(3)/2],[-1,0]
+light = 3.0e8 # speed of light in m/s
+hbar = 1.054e-34 # hbar in J*s
+nm = 1e-9 # how many nanometers are in a meter?
+vacuum_perm = 8.854e-12 # Farads/meter (ugh)
+
+elec = 1.602e-19 # electric charge (coulombs)
+
+# properties for : silver
+plasma_frequency = 9.15 # eV
+gamma = 0.05 # eV, reduced by a factor of 16
+epsinf = 3.77
+
+epsb = 1
+
+NN_vec = np.loadtxt('vectors_mode_1')
+NS_vec = np.loadtxt('vectors_mode_2')
+vector = [NN_vec,NS_vec]
+# create a loop over length scales, defined by particle radius
+radius = np.linspace(1,30,30)
+for rad in radius:
+	rad = int(rad)
+	a0 = rad * nm
+	rij = 3*a0
+	minor = a0
+	major = 8 * a0
+	inter_particle_dist = 3 * a0
+	theta = np.linspace(0,2*math.pi,numPart+1) # angles for placing particles around a circle
+	phi = math.pi/numPart # angle for determining distance from center of circle
+	dist_to_center = inter_particle_dist/(2*math.sin(phi)) # compute distance to center of ring
+	ey = (major)/4
+	ex = math.sqrt(3)/3 * major + rij/2
+	Loc = [np.array([-ex,ey]),np.array([-ex,-ey]),np.array([-rij/2,0]),
+		   np.array([rij/2,0]),np.array([ex,-ey]),np.array([ex,ey])]
[…]

### 2018-01-16 reverse_bowtie/fixed_vec_hex.py

@@ -1,0 +1,140 @@
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+
+
+omegas = [2.76,2.755,2.745,2.74,2.735,2.73,2.715,2.71,2.7,2.685,2.67,2.655,2.64,2.625,2.595,
+		  2.58,2.55,2.52,2.505,2.475,2.46,2.43,2.4,2.385,2.355,2.34,2.31,2.28,2.265,2.235]
+rad = np.linspace(1,30,30)
+radrad = np.linspace(1,30,291) #300 represents number of points to make between T.min and T.max
+
+omegas_smooth = spline(rad,omegas,radrad)
+NN = []
+NS = []
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+'''Begin by choosing a number of particles and a number of rings, defining constants and material properties'''
+numPart = 12
+numRings = 2
+Q = [[1,0],[0,1]]
+#mie_omegas = np.loadtxt('mie_omegas_eV.txt')
+# [.5,-math.sqrt(3)/2],[.5,math.sqrt(3)/2],[1,0],[-.5,-math.sqrt(3)/2],[-.5,math.sqrt(3)/2],[-1,0]
+light = 3.0e8 # speed of light in m/s
+hbar = 1.054e-34 # hbar in J*s
+nm = 1e-9 # how many nanometers are in a meter?
+vacuum_perm = 8.854e-12 # Farads/meter (ugh)
+
+elec = 1.602e-19 # electric charge (coulombs)
+
+# properties for : silver
+plasma_frequency = 9.15 # eV
+gamma = 0.05 # eV, reduced by a factor of 16
+epsinf = 3.77
+
+epsb = 1
+
+NN_vec = np.loadtxt('hex_vec_mode_0')
+NS_vec = np.loadtxt('hex_vec_mode_1')
+vector = [NN_vec,NS_vec]
+# create a loop over length scales, defined by particle radius
+radius = np.linspace(1,30,30)
+for rad in radius:
+	
+	a0 = rad * nm
+	minor = a0
+	major = 2.5*a0
+	rij = 3*a0
+	inter_particle_dist = 3 * a0
+	theta = np.linspace(0,2*math.pi,numPart+1) # angles for placing particles around a circle
[…]

### 2018-01-16 reverse_bowtie/hexagons.py

@@ -1,0 +1,75 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+masses = np.loadtxt('prolate_2.5_to_1_masses.txt')
+alphas = np.loadtxt('prolate_2.5_to_1_alphas.txt')
+omegas = np.loadtxt('prolate_2.5_to_1_omegas.txt')
+sigmas = np.loadtxt('prolate_2.5_to_1_sigmas.txt')
+gammas = np.loadtxt('prolate_2.5_to_1_gammas.txt')
+numPart = 12
+c = 3e10
+stat = 4.80326e-10
+elec = 1.602e-19
+hbar = 1.054e-34
+epsb = 1
+for r in range(1,31):
+	minor = r*1e-7
+	major = 2.5*r*1e-7
+	mass = masses[r-1] #kg
+	alpha = alphas[r-1] #m^3
+	omega = omegas[r-1] #eV
+	gamma = gammas[r-1] #eV
+	ex = major/2
+	ey = major*math.sqrt(3)/2
+	Loc = [[-5*ex,0],[-4*ex,ey],[-4*ex,-ey],[-2*ex,ey],[-2*ex,-ey],[-ex,0],[ex,0],[2*ex,-ey],[2*ex,ey],[4*ex,-ey],[4*ex,ey],[5*ex,0]]
+	#Loc = [[-2*major,major],[-3*major,0],[-2*major,-major],[-1*major,0],[1*major,0],[2*major,-major],[3*major,0],[2*major,major]]
+	Q = [[1,0],[0,1]]
+	H = (np.zeros((2*numPart,2*numPart),dtype=float))
+	eigen = np.zeros(2*numPart)
+	w_mode = omega
+	for mode in [0,1]:
+		while abs(w_mode - eigen[2*numPart-(mode+1)]) > 0.001:
+			w_mode = eigen[2*numPart-(mode+1)]
+			wavenumber = np.sqrt(epsb)*w_mode*elec/(c*hbar)
+			for n in range(0,2*numPart):
+				for m in range(0,2*numPart):
+					if m == n: #if m and n are the same, the hammy gets the plasmon energy
+						H[n,m] = (omega*elec/hbar)**2#(hbar*wsp/elec)
+						#print H[n,m]
+					elif m == n+1 and n%2 == 0: #if m and n are on the same particle, they don't couple
+						H[n,m] = 0
[…]

### 2018-01-16 reverse_bowtie/old_bowtie.py

@@ -1,0 +1,84 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+masses = np.loadtxt('prolate_2.5_to_1_masses.txt')
+alphas = np.loadtxt('prolate_2.5_to_1_alphas.txt')
+omegas = np.loadtxt('prolate_2.5_to_1_omegas.txt')
+sigmas = np.loadtxt('prolate_2.5_to_1_sigmas.txt')
+gammas = np.loadtxt('prolate_2.5_to_1_gammas.txt')
+numPart = 6
+c = 3e10
+stat = 4.80326e-10
+elec = 1.602e-19
+hbar = 1.054e-34
+epsb = 1
+NN = []
+NS = []
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NN_vec = np.loadtxt('vectors_mode_1')
+NS_vec = np.loadtxt('vectors_mode_2')
+vector = [NN_vec,NS_vec]
+for r in range(1,31):
+	minor = r*1e-7
+	major = 2.5*r*1e-7
+	mass = masses[r-1] #kg
+	alpha = alphas[r-1] #m^3
+	omega = omegas[r-1] #eV
+	wsp = omega*elec/hbar
+	gamma = gammas[r-1] #eV
+	ex = (math.sqrt(3) + 2)*major
+	ey = major
+	Loc = [[-ex,ey],[-ex,-ey],[-2*major,0],[2*major,0],[ex,-ey],[ex,ey]]
+	#Loc = [[-2*major,major],[-3*major,0],[-2*major,-major],[-1*major,0],[1*major,0],[2*major,-major],[3*major,0],[2*major,major]]
+	Q = [[1,0],[0,1]]
+	w_mode = 0
+	coupling = 0
+	for mode in [1,2]:
+		vec = vector[mode-1]
+		w_mode = 0
+		coupling = 0
+		while abs(w_mode - (omega + np.real(coupling))) > 0.001:
+			w_mode = omega + np.real(coupling)
+			wavenumber = np.sqrt(epsb)*w_mode*elec/(c*hbar)
+			coupling = 0
+			nearfield = 0
+			midfield = 0
+			farfield = 0
+			for x in range(0,numPart):
+				for y in range(x,numPart):
+					if x == y:
+						continue
+					else:
+						pass
[…]

### 2018-01-16 reverse_bowtie/prolate_params.py

@@ -1,0 +1,23 @@
+import math
+import numpy as np
+
+omega_sp = [2.85,2.84,2.84,2.83,2.83,2.82,2.81,2.8,2.78,2.77,2.75,2.74,2.72,2.7,2.68,2.66,2.64,2.61,2.59,2.56,2.54,2.51,2.48,2.46,2.43,2.40,2.37,2.34,2.32,2.29]
+sigma_abs = [44.76,352.2,1202,2670,5051,8126,11610,15080,18340,21350,23220,24540,25250,25280,24830,24050,23030,22080,21000,19910,18880,17910,16960,16150,15380,14680,14040,13460,12960,12500]
+gamma_sp = [0.05,0.05,0.05,0.05,0.05,0.05,0.06,0.06,0.06,0.07,0.08,0.09,0.1,0.11,0.12,0.13,0.14,0.16,0.18,0.19,0.2,0.22,0.24,0.26,0.27,0.3,0.33,0.34,0.37,0.4]
+msp = []
+alpha_sp = []
+stat = 4.80326e-10
+coul = 1.602e-19
+hbar = 1.054e-34
+c = 3e10
+for r in range(1,31):
+	mass = (2*math.pi*stat**2)/(3*c*sigma_abs[r-1]*(1e-14)*gamma_sp[r-1]*coul/hbar)
+	alpha = (stat**2)/(mass*(omega_sp[r-1]**2)*(coul/hbar)**2)
+	msp.append(mass)
+	alpha_sp.append(alpha)
+
+np.savetxt('prolate_2.5_to_1_masses.txt',msp)
+np.savetxt('prolate_2.5_to_1_alphas.txt',alpha_sp)
+np.savetxt('prolate_2.5_to_1_omegas.txt',omega_sp)
+np.savetxt('prolate_2.5_to_1_sigmas.txt',sigma_abs)
+np.savetxt('prolate_2.5_to_1_gammas.txt',gamma_sp)

### 2018-01-16 reverse_bowtie/reverse_bowtie.py

@@ -1,0 +1,75 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+masses = np.loadtxt('prolate_2.5_to_1_masses.txt')
+alphas = np.loadtxt('prolate_2.5_to_1_alphas.txt')
+omegas = np.loadtxt('prolate_2.5_to_1_omegas.txt')
+sigmas = np.loadtxt('prolate_2.5_to_1_sigmas.txt')
+gammas = np.loadtxt('prolate_2.5_to_1_gammas.txt')
+numPart = 6
+c = 3e10
+stat = 4.80326e-10
+elec = 1.602e-19
+hbar = 1.054e-34
+epsb = 1
+for r in range(1,2):
+	minor = r*1e-7
+	major = 2.5*r*1e-7
+	mass = masses[r-1] #kg
+	alpha = alphas[r-1] #m^3
+	omega = omegas[r-1] #eV
+	gamma = gammas[r-1] #eV
+	ex = (math.sqrt(3) + 1)*major
+	ey = major
+	Loc = [[-ex,ey],[-ex,-ey],[-major,0],[major,0],[ex,-ey],[ex,ey]]
+	#Loc = [[-2*major,major],[-3*major,0],[-2*major,-major],[-1*major,0],[1*major,0],[2*major,-major],[3*major,0],[2*major,major]]
+	Q = [[1,0],[0,1]]
+	H = (np.zeros((2*numPart,2*numPart),dtype=float))
+	eigen = np.zeros(2*numPart)
+	w_mode = omega
+	for mode in [1,2]:
+		while abs(w_mode - eigen[2*numPart-(mode+1)]) > 0.001:
+			w_mode = eigen[2*numPart-(mode+1)]
+			wavenumber = np.sqrt(epsb)*w_mode*elec/(c*hbar)
+			for n in range(0,2*numPart):
+				for m in range(0,2*numPart):
+					if m == n: #if m and n are the same, the hammy gets the plasmon energy
+						H[n,m] = (omega*elec/hbar)**2#(hbar*wsp/elec)
+						#print H[n,m]
+					elif m == n+1 and n%2 == 0: #if m and n are on the same particle, they don't couple
+						H[n,m] = 0
+					elif n == m+1 and m%2 == 0: #if m and n are on the same particle, they don't couple
+						H[n,m] = 0
+					else: # all other dipoles are fair game
+						R = np.subtract(Loc[(n/2)],Loc[(m/2)]) #pick out the location of each dipole, comute the distance between them
[…]

### 2018-01-16 schwinger_dP_test/indi_dipoles_t3mer.py

@@ -1,0 +1,218 @@
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+# these are unit vectors in each direction
+zhat = [0,0,1]
+yhat = [0,1,0]
+xhat = [1,0,0]
+
+p = 1
+# flux screen distance
+screen = 100000
+energies = np.array([3.61,3.6,3.56,3.52,3.42,3.3,3.17])
+#energies = np.array([3.25,1,1,1,2.8,1,1])
+# some pre-defined stuff for loading data
+r_and_eV = [['1',3.61],['5',3.6],['10',3.56],['15',3.52],['20',3.42],['25',3.3],['30',3.17]]
+#r_and_eV = [['1',3.25],[],[],[],['20',2.8]]
+
+numPart = 13
+
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+#frequency = np.linspace(2,4,201) # we will need this later
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10 #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1.
+frequency = np.linspace(2,4,201)
+km = (frequency*elec/hbar)/c
+NS_vec = np.loadtxt('../trimer_ring/vec_mode_0')
+dip_vec = np.loadtxt('../trimer_ring/vec_mode_1')
+NN_vec = np.loadtxt('../trimer_ring/vec_mode_2')
[…]

### 2018-01-16 sphere_trimer/trimer_ret.py

@@ -2,27 +2,29 @@ import numpy as np
 import math
 import scipy.linalg
 import matplotlib.pyplot as plt
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
 
-
+vec =[[],[],[]]
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 #north_north = np.loadtxt('../dielectric_study/NN_right.txt')
 #north_south = np.loadtxt('../dielectric_study/NS_right.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 mag = []
-for r in range(10,301):
+for r in np.linspace(10,10,1):
 	elec = 1.60217662e-19 # regular coulombs
 	numPart = 3 #number of particles
-	a0 = .1*r*10**-7 #sphere radius in cm
-	mie_index = r-10
-	index = r-10
+	a0 = r*10**-7 #sphere radius in cm
+	mie_index = (r-1)*10
+	index = r
 
 	''' now determine geometry.'''
 	''' begin with electric dipole on the six-member ring '''
 	# make unit vectors in centimeters.
-	e1 = float(1)/float(2) * (2.2*a0) ; #short side of 30-60-90 triangle
-	e2 = float(math.sqrt(3))/float(2) * (2.2*a0); #long side of 30-60-90 triangle
+	e1 = float(1)/float(2) * (3*a0) ; #short side of 30-60-90 triangle
+	e2 = float(math.sqrt(3))/float(2) * (3*a0); #long side of 30-60-90 triangle
 	m_sep = 2*e2
-	Loc = [np.array([0,2*e1]),np.array([-e2,e1]),np.array([0,0])]
+	Loc = [np.array([0,e2]),np.array([-e1,0]),np.array([e1,0])]
 		   #np.array([0,-2*e1]),np.array([e2,-e1]),np.array([e2,e1])]
 
 	Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
@@ -45,86 +47,118 @@ for r in range(10,301):
 	Eplasma = 1.46599161e-18; # J
 	gamma = 0.05*elec/(hbar*16)
 	wplasma = Eplasma/hbar; # plasma frequency (rad/s)
[…]

### 2018-01-16 trimer_ring/phen_spacing.py

@@ -3,7 +3,9 @@ import math
 import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
-
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+poynting_points = 46
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 interaction = [[],[]]
@@ -23,8 +25,8 @@ wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 for epsb in range(1,2):
 	NN = []
 	NS = []
-	r = 15
-	for dist in np.linspace(0,10,51):
+	r = 20
+	for dist in np.linspace(0,4,9):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
@@ -44,138 +46,94 @@ for epsb in range(1,2):
 		center = [np.array([-e2, 0]),np.array([e2,0]),np.array([0, 3*e1])]
 		'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
 		H = np.zeros((2*numPart,2*numPart),dtype=complex) #initialize Hammy with zeros, twenty by twenty in this case.
-
+		alphasp = a0**3 * (3/(epsinf+2))
 		'''More constants'''
 
 		count = 1
 		#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
 		wsp_0 = (mie_omegas[index])*elec/hbar
 		'''initialize w_0 and eigen'''
-		w_0 = 3*elec/hbar
-		eigen = np.ones(2*numPart)
-		for mode in range(0,10):
-			mag_dipole = []
-			print NN_count + NS_count
-			if NS_count + NN_count == 2:
-				continue
-			while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.00000001:
-				if count == 1:
-					wsp = wsp_0
-					count = count + 1
-					w_0 = 0
+		w_mode = 0
+		
+		vec_NS_y = np.loadtxt('vec_mode_0')
[…]

### 2018-01-16 trimer_ring/ring_trimer.py

@@ -30,7 +30,7 @@ for epsb in range(1,2):
 	NF = [[],[]]
 	IF = [[],[]]
 	FF = [[],[]]
-	for r in range (1,31):
+	for r in range (1,2):
 		a0 = r*10**-7; #sphere radius in cm
 		index = r*10 - 10
 		''' now determine geometry.'''
@@ -57,7 +57,7 @@ for epsb in range(1,2):
 		'''initialize w_0 and eigen'''
 		w_0 = 3*elec/hbar
 		eigen = np.ones(2*numPart)
-		for mode in range(0,3):
+		for mode in range(2,3):
 			while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.00000001:
 				if count == 1:
 					wsp = wsp_0
@@ -107,17 +107,19 @@ for epsb in range(1,2):
 			    #w_old = w_0
 			    #w_0 = eigen[2*numPart-1]
 			vec = np.reshape(eigenVectors[:,2*numPart - (mode+1)],[numPart,2])
+			#np.savetxt('vec_mode_'+str(mode),np.real(vec))
+			#continue
 			grid_x = 2.5*e2
 			grid_y = 2.5*e1
-			size = 251
+			size = 101
 			Bfield_total = np.zeros((size,size),dtype=float)
 			for number in range(0,13):
 				point = Loc[number]
 				xcount = 0
 				Bfield = np.empty((size,size),dtype=float)
-				for xx in np.linspace(-2.5*e1,5.5*e1,size):
+				for xx in np.linspace(-3*e1,6*e1,size):
 					ycount = 0
-					for yy in np.linspace(-2.5*e2,2.5*e2,size):
+					for yy in np.linspace(-3*e2,3*e2,size):
 						rmag = np.sqrt((point[0]-yy)**2 + (point[1]-xx)**2)
 						nhat = -([yy,xx]-point)/rmag
 						#print rmag
@@ -131,16 +133,16 @@ for epsb in range(1,2):
 					xcount += 1
 				Bfield_total = Bfield_total + Bfield
 			# ,levels=np.linspace(np.amin(Bfield_total),np.amax(Bfield_total),30)
-			xx = np.linspace(-2.5*e2,2.5*e2,size)
-			yy = np.linspace(-2.5*e1,5.5*e1,size)
+			xx = np.linspace(-3*e2,3*e2,size)
[…]

### 2018-01-16 varying_particle_number/2D_poynting.py

@@ -1,0 +1,187 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+
+
+static_NN = []
+static_NS = []
+bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
+bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10; #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 5
+NN = []
+NS = []
+modes = [[],[]]
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NFIF = [[],[]]
+for r in np.linspace(15,15,1):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r
+	''' now determine geometry.'''
+	print index
+	# make unit vectors in centimeters.
+	rij = 3*a0
+	e1 = .5*rij
+	e2 = rij*math.sqrt(3)/2
+	part_per_ring = numPart/2 + 1
+	theta = 2*math.pi/part_per_ring
+	phi = theta/2.
+	#print theta
+	#print phi
+	#print np.cos(phi)
+	#print np.sin(phi)
[…]

### 2018-01-16 varying_particle_number/2mer_contour_plotter.py

@@ -1,0 +1,29 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+NN_vac = np.loadtxt('NN_contour_vacuum.txt')
+NS_vac = np.loadtxt('NS_contour_vacuum.txt')
+NN_wat = np.loadtxt('NN_contour_water.txt')
+NS_wat = np.loadtxt('NS_contour_water.txt')
+
+vacuum = NN_vac - NS_vac
+water = NN_wat - NS_wat
+vaclev = np.linspace(-vacuum.max(),vacuum.max(),11) 
+watlev = np.linspace(-water.max(),water.max(),11) 
+plt.figure()
+plt.contourf(vacuum,levels=vaclev,cmap='bwr')
+plt.colorbar()
+plt.title('vacuum 2mer')
+plt.xlabel('separation')
+plt.ylabel('scaling')
+plt.savefig('vacuum_2mer_contour.pdf')
+plt.show()
+
+plt.figure()
+plt.contourf(water,levels=watlev,cmap='bwr')
+plt.colorbar()
+plt.title('water 2mer')
+plt.xlabel('separation')
+plt.ylabel('scaling')
+plt.savefig('water_2mer_contour.pdf')
+plt.show()

### 2018-01-16 varying_particle_number/big_twomer.py

@@ -4,7 +4,8 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-
+NN = []
+NS = []
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 
 elec = 1.60217662e-19 # regular coulombs
@@ -23,15 +24,16 @@ Eplasma = 1.46599161e-18; # J
 gamma = 0.05*elec/(hbar*16)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 epsb = 1
-
-for r in range(100,101):
+wsp_0 = np.multiply([3.49, 3.31, 3.07, 2.75, 2.41, 2.11, 1.88, 1.7],elec/hbar)
+rcount = 0
+for r in [30,40,50,60,70,80,90,100]:
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = r
 	''' now determine geometry.'''
 	print index
 	# make unit vectors in centimeters.
-	rij = 2.75*a0
+	rij = 3*a0
 	part_per_ring = numPart/2 + 1
 	theta = 2*math.pi/part_per_ring
 	phi = theta/2.
@@ -76,16 +78,17 @@ for r in range(100,101):
 
 	'''More constants'''
 
-	count = 1
+	
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
-	wsp_0 = (1.8)*elec/hbar
+	
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
 	for mode in range(0,2):
+		count = 0
 		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.0000001:
-			if count == 1:
-				wsp = wsp_0
+			if count == 0:
+				wsp = wsp_0[rcount]
 				count = count + 1
 				w_0 = 0
 			else:
@@ -98,7 +101,7 @@ for r in range(100,101):
 			gamma_ret = gamma+tau*(w_0**2) # I pulled this from the beats paper
 			gamma_eV = gamma_ret*hbar/elec
[…]

### 2018-01-16 varying_particle_number/fields.py

@@ -35,7 +35,7 @@ NF = [[],[]]
 IF = [[],[]]
 FF = [[],[]]
 NFIF = [[],[]]
-for r in np.linspace(1,1,1):
+for r in range(20,21):
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = r
@@ -94,7 +94,12 @@ for r in np.linspace(1,1,1):
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
+	grid_x = 3*e2
+	grid_y = 3*e1
+	size = 101
+	
 	for mode in range(0,2):
+		Bfield_total = np.zeros((size,size),dtype=complex)
 		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.00001:
 			if count == 1:
 				wsp = wsp_0
@@ -153,18 +158,17 @@ for r in np.linspace(1,1,1):
 			eigenVectors = v[:,idx] # sorting
 
 			eigen=((hbar/elec)*wsp)*(np.sqrt(eigenValues))# the eigenvalues have units of energy^2, so we take the square root
-		vec = np.reshape(eigenVectors[:,2*numPart - (mode+1)],[numPart,2])
-		grid_x = 2.5*e2
-		grid_y = 2.5*e1
-		size = 251
-		Bfield_total = np.zeros((size,size),dtype=float)
+		vec = (mode+1)*np.reshape(eigenVectors[:,2*numPart - (mode+1)],[numPart,2])
+		
+		
 		for number in range(0,10):
 			point = Loc[number]
 			xcount = 0
-			Bfield = np.empty((size,size),dtype=float)
+			Bfield = np.empty((size,size),dtype=complex)
 			for xx in np.linspace(-grid_y,grid_y,size):
 				ycount = 0
 				for yy in np.linspace(-grid_x,grid_x,size):
+
 					rmag = np.sqrt((point[0]-yy)**2 + (point[1]-xx)**2)
 					nhat = -([yy,xx]-point)/rmag
 					#print rmag
@@ -173,7 +177,7 @@ for r in np.linspace(1,1,1):
 					if rmag < .5*a0:
 						Bfield[xcount,ycount] = 0
 					else:
[…]

### 2018-01-16 varying_particle_number/particle_number.py

@@ -4,8 +4,9 @@ import scipy.linalg
 import matplotlib.pyplot as plt
 from scipy.interpolate import spline
 
-static_NN = []
-static_NS = []
+NN = []
+NS = []
+max_length = []
 bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
 bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
 mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
@@ -28,7 +29,8 @@ gamma = 0.05*elec/(hbar*16)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 epsb = 1
 
-for r in range(1,2):
+for r in range(1,31):
+	numPart = 10
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = (r-1)*10
@@ -65,8 +67,9 @@ for r in range(1,2):
 			pass
 		else:
 			Loc[count] = x'''
-
-
+	numPart = 12
+	places.append(centers[0])
+	places.append(centers[1])
 	#Loc = np.unique(Loc)
 	#print places
 	Loc = places
@@ -79,14 +82,14 @@ for r in range(1,2):
 	H = (np.zeros((2*numPart,2*numPart),dtype=float))#initialize Hammy with zeros, twenty by twenty in this case.
 
 	'''More constants'''
-
+	distances = []
 	count = 1
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
-	wsp_0 = mie_omegas[index]*elec/hbar
+	wsp_0 = (mie_omegas[index]*elec/hbar)*math.sqrt(epsinf+2)/math.sqrt(epsinf+2*epsb)
 	'''initialize w_0 and eigen'''
 	w_0 = 0
 	eigen = np.ones(2*numPart)
-	for mode in range(0,3):
+	for mode in range(2):
 		while np.sqrt(np.square(w_0*hbar/elec - eigen[(2*numPart)-(mode+1)])) > 0.0000001:
 			if count == 1:
 				wsp = wsp_0
@@ -95,14 +98,14 @@ for r in range(1,2):
 			else:
 				count = count + 1
[…]

### 2018-01-16 varying_particle_number/poynting.py

@@ -1,0 +1,245 @@
+import numpy as np
+import math
+import scipy.linalg
+import matplotlib.pyplot as plt
+from scipy.interpolate import spline
+import mpl_toolkits.mplot3d.axes3d as axes3d
+from matplotlib import cm
+
+poynting_points = 91
+static_NN = []
+static_NS = []
+bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
+bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
+mie_omegas = np.loadtxt('../mie_omegas_eV.txt')
+''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
+crossing = []
+elec = 1.60217662e-19 # regular coulombs
+
+numPart = 10; #number of particles
+
+me = 9.10938291e-28; # electron mass in g
+ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
+hbar = 1.054571726e-34; # modified Planck in J*s
+c = 2.99e10; # speed of light in cm/s
+eps0 = 8.85418782e-12; # permittivity of free space
+Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
+epsinf = 3.77; 
+'''Properties for silver.'''
+Eplasma = 1.46599161e-18; # J
+gamma = 0.05*elec/(hbar*16)
+wplasma = Eplasma/hbar; # plasma frequency (rad/s)
+epsb = 1
+NN = []
+NS = []
+modes = [[],[]]
+interaction = [[],[]]
+NF = [[],[]]
+IF = [[],[]]
+FF = [[],[]]
+NFIF = [[],[]]
+r = 20
+for dist in np.linspace(1,1,1):
+	a0 = r*10**-7; #sphere radius in cm
+	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
+	index = r
+	''' now determine geometry.'''
+	
+	# make unit vectors in centimeters.
+	rij = (2+dist)*a0
+	# print 2+dist
+	e1 = .5*rij
+	e2 = rij*math.sqrt(3)/2
+	part_per_ring = numPart/2 + 1
+	theta = 2*math.pi/part_per_ring
+	phi = theta/2.
+	#print theta
[…]

### 2018-03-07 paper_winter_2017/draft_winter_2017.tex
new figures, updated draft

@@
 \email{masiello@chem.washington.edu}
-\date{September 4, 2017}
+\date{February 12, 2017}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{centering}
-\includegraphics[width=7cm]{toc.png}
+\includegraphics[height=3.5cm]{toc.png}
 \end{centering}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored.
+Abstract.
+%Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored.
 A fully retarded coupled dipole model is employed, expanding upon past work in the field, to explore the dependence of the resonant frequencies and spectral ordering of the magnetic resonances on cluster size.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years.
-Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Alu2006,Alu2008,Dionne2011,Cherqui2014,Dionne2016,Cherqui2016,Engheta2017}.
+Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years\cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016}.
+Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
 The magnetic properties of single oligomers, i.e.
@@
 For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}.
-Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{vonPlessen2007}, and infinite chains and arrays\cite{Kottman2001,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Chumanov2010,Pinchuk2016}.
+Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}.
 However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers.
@@
 This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials.
-[Pendry superlens, other stuff]
 
-In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $n$-mers with scaling by including the full field within a coupled dipole approach describing their interaction.
-Interestingly, as a function of scaling, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}.
-We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2012,Coenen2011,CoPol2011,Polman2014}.
-The spectral ordering depends not only on aggregate scale but also upon oligomer morphology which we examine below.
-[Reword, superlensing and cloaking!] Tunability of the relative phase of magnetic fields in a single MNP cluster may lead to advances in detection methods\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, anti-reflective coatings\cite{Alu2006,Alu2008}, and information processing\cite{NordHal2011,NordHal2012}.
+In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $N$-mers with size by including the full field within a coupled dipole approach describing their interaction.
+Interestingly, as a function of size, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}.
+We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}.
+The spectral ordering depends not only on aggregate size but also upon oligomer morphology which we examine below.
+The ability to choose the resonance frequency of specific magnetic plasmon resonances will lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications stem directly from tunable negative-index metamaterials\cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.
 
@@
 \begin{figure}
-\includegraphics[width=6.5in]{2mer_3mer_fields.pdf}
+\includegraphics{2mer_3mer_fields.pdf}
 \caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers.
@@
 Figure~\ref{field_plots} displays two model systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to naphthalene and phenalene.
-The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood [lots of cites].
+The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood\cite{ARPC}.
 In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic response of the oligomer are
@@
 \begin{equation}
-\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
+\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{i,j\neq i}\textbf{E}_j(\textbf{r}_i),
 \label{equation_of_motion}
@@
 \noindent where $\omega_{\textrm{sp}}$ is the natural frequency of the Mie resonance, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$, with $\varepsilon_{\infty}$ and $\varepsilon_b$ the high-frequency and background dielectric functions.
-The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position ri [format], is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole.
-It is defined by
+The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole.
+The electric field is defined by
 
@@
 \textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
-= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{k^2}{r_{ij}}\left(\textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
+= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
 \label{electric_field_lambda}
@@
 
-\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{rm}}$ dipole.
-The field is decomposed into three parts: [put in scaling] the near-, intermediate-, and far-field.
+\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{th}}$ dipole.
+Interestingly, the far-field term carries the opposite sign of the near-field term.
+The field is decomposed into three parts: the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$).
 All dipolar retardation effects are included in this field\cite{Purcell1973}.
-Due to the relative magnitudes of these terms and the sign of [e to the ikr] the interaction energies can change sign and go from energy-lowering to energy-raising.
+Due to the relative magnitudes of these terms and the sign of $e^{\textrm{i}kr_{ij}}$ the interaction energies can change sign and go from energy-lowering to energy-raising.
 
 As described in the methods section, there are as many normal modes of each N-mer as there are electric dipole plasmons.
-Of these normal modes, some are electric in character and some are magnetic in character with $n$ magnetic plasmon resonances for each $n$-mer studied here.
+Of these normal modes, some are electric in character and some are magnetic in character with $N$ magnetic plasmon resonances for each $N$-mer studied here.
 Figure~\ref{field_plots} shows these magnetic plasmon normal modes overlaid with their associated signed magnetic field magnitude.
@@
 To determine the impact of incorporating retardation effects, it is first useful to consider the quasistatic limit.
-Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = rij/a$ and not upon the overall oligomer size.
+Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = r_{ij}/a$ and not upon the overall oligomer size.
 That is, if this ratio $s$ of inter-particle distance $r_{ij}$ to particle size $a$ remains constant, as the particles grow the collective frequencies do not change.
@@
 \begin{aligned}
-\frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij} &= \omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \\
-&= \omega_{\textrm{sp}}^2 \left(\frac{3r_0^3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{(sr_0)^3}.
+\lim_{k \to 0}\textbf{E}_j(\textbf{r}_i) &= \frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij}\\ 
+&= \frac{\omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}^2}{\varepsilon_b}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \cdot \textbf{d}_j \\
+&= \frac{\omega_{\textrm{sp}}^2}{\varepsilon_b} \left(\frac{3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{s^3} \cdot \textbf{d}_j
 \end{aligned}
@@
 
-\noindent where msp and alphasp are rewritten in terms of fundamental parameters.
+\noindent where $m_{\textrm{sp}}$ and $\alpha_{\textrm{sp}}$ are rewritten in terms of fundamental parameters for silver: $\varepsilon_{\infty} = 3.77$, $\hbar\gamma = 0.05$ eV, and $\hbar\omega_{p} = 9.1$ eV.
 Retardation effects, however, remove this invariance and introduce size-dependence into both the individual plasmon natural frequency as well as into the electric field.
-Consequently, in the following we choose the individual MNP radius as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $n$-mers.
+Consequently, in the following we choose the individual MNP radius $a$ as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $N$-mers.
 
 \begin{figure}
-\includegraphics[width=4in]{2mer-3mer-eig.pdf}
+\includegraphics{2mer-3mer-eig.pdf}
 \caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer.
@@
 
-Figure~\ref{scaling} shows the predicted eigenenergies and the simulated spectral peak positions for the magnetic modes of the 2mer and 3mer with varying $r_0$.
-At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits easily into a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}.
-In fact, a fully retarded scattering spectrum of an aggregate of this size is qualitatively identical to quasistatic simulations of the same system at all sizes.
-This implies that the quasistatic approximation is accurate only for magnetic oligomers spanning less than a quarter of the wavelength of light, smaller than suggested by previous work for single particles\cite{Economou1974}.
-As the system scale increases, the eigenenergies decrease and appear to cross at $r_0 = 7$ nm, and once more at $r_0 = 20$ nm.
-This is due to the far-field term in Equation~\ref{electric_field_lambda} becoming strong relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares).
-As the system gets larger, it takes information longer to propagate across the aggregate, meaning that retardation effects become important.
+Figure~\ref{scaling} shows the predicted resonance energies from both the model and full-wave optical simulations of the 2-mer and 3-mer with increasing $a$.\cite{Hohenester2012} At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits within a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}.
+As the system size increases, the resonance energies decrease and to cross at $a = 7$ nm, and once more at $a = 20$ nm.
+This is due to the far-field contribution in Equation~\ref{electric_field_lambda} becoming large relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares).
 The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is accurate again.
@@
 \begin{equation}
-U_{\textrm{int}} = -\sum_i \textbf{d}_i \cdot \sum_{j \neq i} \textbf{E}_j(\textbf{r}_i),
+U_{\textrm{int}} = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
 \label{interactionenergy}
@@
 Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field.
-Perhaps more interestingly, in water the crossing points are shifted towards smaller scale.
-This is to be expected, as the wavelength of light is compressed in a medium, meaning that light sees objects as much bigger than they really are.
-This analysis shows that the quasistatic approximation is good for very small magnetic oligomers in vacuum, and for smaller oligomers in medium.
+Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction.
 This can also be explained through the impact of a dielectric medium on coupling strength.
-While a medium should contribute an overall increase to the coupling strength (which is predicted in Figure~\ref{scaling}b and f), the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008} Through comparison with simulation (dashed lines in Figure~\ref{scaling}a), it can be shown that this simple and efficient model is accurate to within 0.05 eV and accurately describes the behavior of magnetic plasmon oligomers.
+While a medium should contribute an overall increase to the coupling strength, the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008}
 
-Previous work has explored the oscillatory nature of resonance frequency and radiation damping as a function of size in plasmonic systems\cite{vonPlessen2007}.
-We have shown that a fully retarded coupled dipole approach predicts magnetic plasmon resonance switching, and explains that it is due to inclusion of the far-field term in the dipole relay tensor.
-From here, we use simulated angle-resolved CL spectroscopy to observe this magnetic mode switching, leveraging the specific radiative properties of each magnetic plasmon and the ability of the electron beam to isolate specific plasmon modes.
+Previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonance frequencies and radiation damping as a function of separation in noble metal dimers\cite{vonPlessen2007}.
+Analogously, our work shows that magnetic plasmon resonance energies also oscillate with interparticle separation and can be understood via analysis of the contributions to the dipole-dipole interaction.
 
 \section{Radiative Properties of Magnetic Plasmon Resonances}
-In order to detect the spectral switching of magnetic plasmons, we must exploit their unique radiative properties.
-Only those magnetic eigenmodes supporting net dipole moments should radiate to the far field.
-Furthermore, the aN magnetic mode dipole moment is perpendicular to the NS mode electric dipole moment(s) in both the model 2mer and 3mer, meaning that they radiate with different directional-dependence.
-It has been predicted and shown experimentally that single magnetic oligomers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited.\cite{Dionne2011,Cherqui2016} This is evident from the difference between forward and backward scattering spectra, but can also be shown by computing the differential scattering pattern,\cite{jackson_classical_1999,schwinger1998classical}
+Only those magnetic resonances supporting net electric or magnetic dipole moments will radiate to the far field.
+The magnetic dipole moment of the aN magnetic mode is perpendicular to the electric dipole moment(s) of the NS mode in both the model 2-mer and 3-mer.
+This means that these modes radiate with different directionality.
+It has been predicted and shown experimentally that 1-mers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited,\cite{Dionne2011,Cherqui2016} as is evident in differential scattering spectra and profiles.
+Both observations stem from the differential power,\cite{jackson_classical_1999,schwinger1998classical}
 
@@
 
-\noindent where $\hat{\textbf{n}}$ is the unit vector pointing to the detector a distance $r >> \lambda$ away and $\textbf{E}_i$ and $\textbf{B}_j^*$ are the electric field and conjugate magnetic inductance originating from each oligomer ring.
-In order to predict the qualitative properties of independently and mutually exciting an orthogonal magnetic and electric plasmon, we coarse-grain our approach by assuming that each ring of the oligomer supports one collective electric and one collective magnetic dipole moment, co-located at the center of each ring.
-Using the far-fields scattered by such an arrangement of electric and magnetic dipoles reduces the differential scattering to\cite{Alu2006}
+\noindent $\textbf{E}_i$ and $\textbf{B}_i$ are produced from the sum of effective electric ($\textbf{d}_i$) and magnetic ($\boldsymbol{\mu}_i$) dipole moments of each ring of the $N$-mer, assumed to be co-located at the center of the $i$-th ring and oscilalting in time as $e^{-\textrm{i}\omega t}$.
+In this approxiamtion, the differential power becomes\cite{Alu2006}
 
 \begin{equation}
-\frac{dP}{d\Omega} = \frac{ck_e^2k_m^2}{8\pi} \textrm{Re} \left[\hat{\textbf{n}} \cdot \sum_{i} (\hat{\textbf{n}} \times \textbf{d}_i) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_i \times \sum_{j} \hat{\textbf{n}} \times \textbf{d}_j^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_j^*) \times \hat{\textbf{n}}\right]
-\label{dp_coarse_grain}
+\begin{aligned}
+\frac{dP}{d\Omega} &= \frac{ck^4}{8\pi} \textrm{Re} \left\{\hat{\textbf{n}} \cdot \left[\left(\sum_{i} (\hat{\textbf{n}} \times \textbf{d}_i) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_i\right) \times \left(\sum_{j} \hat{\textbf{n}} \times \textbf{d}_j^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_j^*) \times \hat{\textbf{n}}\right)\right]\right\}\\
+&= \frac{ck^4}{8\pi} \textrm{Re} \Bigg[ \sum_{ij} \textbf{d}_i \cdot \textbf{d}_j^* - (\hat{\textbf{n}} \cdot \textbf{d}_i)(\hat{\textbf{n}} \cdot \textbf{d}_j^*) + \boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_i)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_j^*) \\ &+ \hat{\textbf{n}} \cdot (\textbf{d}_i \times \boldsymbol{\mu}_j^* + \textbf{d}_j^* \times \boldsymbol{\mu}_i) \Bigg].
+\label{dp_dipoles_1}
+\end{aligned}
 \end{equation}
 
-Performing the vector operations in Equation~\ref{dp_coarse_grain} yields
-
-\begin{multline}
-\frac{dP}{d\Omega} = \frac{ck^4}{8\pi} \textrm{Re} [ \sum_{ij} \textbf{d}_i \cdot \textbf{d}_j^* - (\hat{\textbf{n}} \cdot \textbf{d}_i)(\hat{\textbf{n}} \cdot \textbf{d}_j^*) + \boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_i)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_j^*) \\ + \hat{\textbf{n}} \cdot (\textbf{d}_i \times \boldsymbol{\mu}_j^* + \textbf{d}_j^* \times \boldsymbol{\mu}_i) ].
-\label{dp_dipoles_1}
-\end{multline}
-
-\noindent To build intuition, we demand the magnetic dipole $\boldsymbol{\mu}$ is oriented in the z-direction, and the electric dipole $\textbf{d}$ is oriented in the y-direction.
-The coarse-grained electric dipole and magnetic dipole can be written in terms of their constituent dipoles $\textbf{d} = \sum_n d_{e,n} \hat{\textbf{y}}$ and $\boldsymbol{\mu} = \frac{k_m}{2}\sum_n(\textbf{r}_n \times d_{m,n} \hat{\boldsymbol{\phi}}_n) = \frac{k_mNRd_m}{2}\hat{\textbf{z}}$ where the sums are taken over the $n$-th and $m$-th dipoles, respectively.
-Using these definitions, reducing the sum to a single oligomer for simplicity, and giving each dipole equivalent magnitude, the differential scattering becomes
-
-\begin{equation}
-\frac{dP}{d\Omega} = \frac{N^2ck_e^2k_m^2}{8\pi}\left[ d_e^2(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{y}})^2) + \frac{k_m^2R^2d_m^2}{4}(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{z}})^2) + d_ed_mk_mR(\hat{\textbf{n}} \cdot \hat{\textbf{x}})\right]
-\label{dp_dipoles_2}
-\end{equation}
-
-Equation~\ref{dp_dipoles_2} shows that exciting different combinations of dipoles leads to very specific radiation patterns.
-Exciting only a net electric dipole moment and setting $d_m = 0$ results in a dipolar radiation pattern with a node of zero radiation along the electric dipole axis, in this case the y-axis.
-Similarly, setting $d_e = 0$ and exciting only a net magnetic dipole results in another dipolar radiation pattern with a node along the magnetic dipole axis, which in this case is the z-axis.
-Finally, exciting both an electric and a magnetic dipole results in contributions from both patterns in the y- and z-directions.
-However, the third term of Equation~\ref{dp_dipoles_2} contributes an asymmetry, increasing the radiation in the positive x-direction, or the forward direction in this case, while decreasing the radiation in the backwards direction.
-This intuitively shows that interfering othrogonal electric and magnetic plasmons radiate with low or no back scattering\cite{Dionne2011}.
+\noindent Notice that the first two terms are due to electric and magnetic dipole radiation, while the third term is due to their interference.
+To build intuition, we demand the magnetic dipole $\boldsymbol{\mu}$ is oriented in the z-direction, and the electric dipole $\textbf{d}$ is oriented in the y-direction.
+The coarse-grained electric dipole and magnetic dipole can be written in terms of their constituent dipoles $\textbf{d} = \sum_n d_{e,n} \hat{\textbf{y}}$ and $\boldsymbol{\mu} = \frac{k}{2}\sum_n(\textbf{r}_n \times d_{m,n} \hat{\boldsymbol{\phi}}_n) = \frac{kNRd_m}{2}\hat{\textbf{z}}$ where the sums are taken over the $n$-th and $m$-th dipoles, respectively.
 
 \begin{figure}
-\includegraphics[width=5in]{scattering_patterns.pdf}
+\includegraphics{differential_power_diagrams.pdf}
 \caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane.
@@
 
-Using the scattering patterns in Figure~\ref{scattering} computed from Equation~\ref{dp_dipoles_2}, we can make predictions about how to observe each individual magnetic plasmon resonance.
-The aN modes support a z-oriented magnetic dipole and radiate in the xy-plane.
-The NS mode in the 2mer is oriented in the y-direction, and so it radiates in the xz-plane.
-The cyclic 3mer is more complicated.
-Due to its threefold symmetry, its x- and y-oriented NS modes are degenerate and linearly dependent, meaning that they can be mutually excited.
-When exciting the 3mer with a y-oriented electric field, it radiates strongly in the xz-plane and weakly in the yz-plane.
-Using an x-oriented electric field results in the opposite.
-When choosing field polarizations that excite both the all-North mode and the North-South mode, the systems radiate very strongly in the direction of light propagation, and exhibit very weak back scattering.
-Strong forward to backward scattering ratios are also predicted and demonstrated in metal-semiconductor core-shell nanoparticles, which similarly exploit the interference between an electric plasmon and a magnetic plasmon\cite{Kivshar2012}.
-With these radiative properties in mind, we can now observe each magnetic plasmon separately.
-By collecting photons in the directions that each plasmon radiates weakly, we should be able to see one more strongly than the other.
-To help this selectivity, we will preferentially excite each magnetic plasmon using an electron beam.
+Figure~\ref{scattering} displays the differential power profiles associated with the aN and NS magnetic plasmon resonances, as well as the interference pattern, of any $N$-mer.
+Since the aN mode has only a z-oriented magnetic dipole, its radiation pattern is orthogonally oriented with respect to that of the y-directed electric dipole of the NS mode.
+Thus, examination of the directionality of radiation allows one to determine the net electric or magnetic dipole character.
+Strong forward/backward scattering asymmetries are also predicted and demonstrated in metal-semiconductor core-shell nanoparticle assemblies, which similarly exploit the interference between electric and magnetic plasmons\cite{Kivshar2012}.
 
 \section{Angle-Resolved Cathodoluminescence for Observing Spectral Switching}
-Electron beam spectroscopies, such as EELS and CL, in a STEM are useful for high spatial and spectral resolution studies of nanomaterials\cite{Coenen2011,CoPol2011,Abajo2013,Polman2014,ARPC}.
-While EELS measures the probability that a passing electron loses energy to a material, CL measures the probability that an excitation in the sample decays into photon emission.
-Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize a material.
-Using a STEM fitted with a parabolic mirror over the sample, the user can collect emitted light with angular information within $0 \leq \theta \leq \pi/2$ and $0 \leq \phi \leq \pi$\cite{Coenen2011,CoPol2011,Polman2014}.
-Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes and their crossing can be observed in spectra.
-The previous section built up intuition regarding the directionality of light scattered by the magnetic modes of the 2mer and 3mer.
-This intuition informas the specific angles at which to collect CL spectra.
-Using the selection rules imposed by the electron beam and the directionality of light, it is possible to distinguish the magnetic modes and observe them switch spectral order.
+Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize plasmon resonances in noble metal nanoparticles\cite{Coenen2011,CoPol2011,Abajo2013,Polman2014,ARPC}.
+Using an electron microscope fitted with a parabolic mirror, emitted CL radiation can be collected across a large portion of the backward scattering hemisphere\cite{Coenen2011,CoPol2011,Polman2014}.
+Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes of the $N$-mers and their crossings can be observed in angle-resolved CL spectra.
+The previous section built up intuition regarding the directionality of light scattered by the magnetic modes of the 2-mer and 3-mer.
+This intuition informs the particular angles at which to collect CL spectra associated with each magnetic mode.
+More specifically, based upon the selection rules imposed by the electron beam and the directionality of CL radiation, it is possible to distinguish the magnetic modes and their spectral ordering as a function of size.
 
 \begin{figure}
-\includegraphics[width=6in]{CL_2mer_3mer.pdf}
+\includegraphics{CL_incomplete.pdf}
 \caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d).
@@
 
-In Figure~\ref{CL_2mer_3mer} we show point CL spectra on the 2mer and 3mer, with the electron beam positions represented in the diagrams by a blue x and  an orange x chosen to excite the aN modes and the NS modes, respectively.
-However, due to the symmetry of the model systems, the blue position can weakly excite the NS mode, meaning that signatures of it will appear in both spectra.
-Recalling that the aN mode should radiate in the xy-plane and the North-South mode should radiate in the z-direction and either the x- or the y- direction, it is possible to distinguish the modes by collecting photons at different angular distributions.
-The angles chosen are reported in Figure~\ref{CL_2mer_3mer}.
-These spectra confirm the predictions made in Figure~\ref{scaling}, specifically that between $r_0 = 15$ nm and $r_0 = 30$ nm, the aN mode and the NS mode switch spectral order.
+In Figure~\ref{CL_2mer_3mer} we show simulated point angle-resolved CL spectra of the 2-mer and 3-mer, with the electron beam position chosen so as to excite the aN (blue) and NS (orange) modes.
+Note however, due to the symmetry of the oligomers, the blue electron beam position excites not only the aN mode, but also weakly the NS mode.
+Since the radiation profile of the aN mode is orthogonal to that of the NS mode, it is possible to distinguish them by analyzing the angular distribution of emitted CL radiation.
+The ARCL spectra at two such angles are reported in Figure~\ref{CL_2mer_3mer}.
+These simulated spectra confirm the predictions of our model shown in Figure~\ref{scaling}; specifically, between $a = 15 - 30$ nm, the aN and NS modes switch spectral order.
 
-We have now shown that the fully retarded coupled dipole approximation can qualitatively and, to small error, quantitatively predict the eigenenergies and spectral switching of magnetic plasmons, we are prepared to explore more complicated geometries that are active areas of research.
-Before moving on, we must make a quick note about accuracy.
-Experimentally measured Drude model parameters for metals are often reported with wide uncertainty ranges, which results in the ability to arbitrarily choose Drude model parameters to best fit data\cite{Raschke2015}.
-We have chosen Drude model parameters for silver that accurately predict the single plasmon frequency at all the sizes we explore, specifically $\varepsilon_{\infty} = 3.77$, $\hbar\omega_p = 9.15$ eV, and $\hbar\gamma = 0.05$ eV.
-However, these parameters also appear in the static polarizability which dresses the coupling terms.
-As a result, any error introduced from the choice of Drude model would increase with increasing particle number.
-Though this is the case for larger and more complicated systems, we assert that the fully retarded coupled dipole method is qualitatively sound and that magnetic plasmon mode switching is a physical phenomenon.
+\section{Magnetic Plasmon Resonance Frequencies and CL Spectra of Hexagonally-Packed Nanoclusters}
 
-\section{Eigenspectra and CL Spectra of Hexagonally-Packed Arrays}
-
-In order to show that this discussion of mode-switching is experimentally relevant, we use the intuition we have built from the model systems and previous simulated CL experiments to investigate magnetic oligomer systems of recent interest.
-Specifically, we look at hexagonally packed clusters of 13, 19, and 31 MNPs originally designed and characterized by Greybush \textit{et al.}\cite{Engheta2017}.
-The arrangement of MNPs and the magnetic plasmon modes that we discuss are shown in Figure~\ref{kagan_fields}.
-Using the discussion of model systems above as a template, for each system we track the eigenenergies of an aN mode and a NS mode and also show that their switching can be observed in simulated angle-resolved CL measurements.
+Ref.
+\cite{Engheta2017} synthesizes and optically characterizes hexagonally-packed nanoclusters composed of noble metal nanoparticles in the intermediate size regime, between few particle oligomers and infinite arrays.
+Here, we apply our analytical modeling and numerical simulation to investigate the behavior of the magnetic plasmon resonances as a function of size, with an eye toward engineering magnetic resonances at particular resonance energies.
+Such tunability may be important in the design of future negative index materials with spectral tunability.
+Specifically, we consider hexagonally packed clusters composed of 13, 19, and 31 MNPs displayed in Figure~\ref{kagan_fields} as well as the insets of Figure~\ref{kagan_eigen}.
 
 \begin{figure}
-\includegraphics[width=6in]{kagan_fields.pdf}
+\includegraphics{kagan_fields.pdf}
 \caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters.
@@
 
-The magnetic modes of the structures shown in Figure~\ref{kagan_fields} show two kinds of magnetic character.
-The aN mode of each cluster consists of concentric rings of head-to-tail electric dipoles, with a z-oriented magnetic dipole.
-The NS modes of each cluster, which are degenerate, exhibit two equal-sized regions of out-of-phase magnetic character, as well as net electric dipoles.
-In fact, the NS modes of these planar arrays behave the same way as the NS modes of the 3mer in that due to the sixfold symmetry, the "x-oriented" and "y-oriented" dipoles are linearly dependent and mutually excitable by a single plane wave.
-However, because an electron beam excitation would break this symmetry, the two modes can be distinguished between beam positions and angular distributions of radiation.
+Figure~\ref{kagan_fields} displays the signed magnetic field magnitude of two magnetic plasmon resonances of the 13-, 19-, and 31-particle hexagonally packed nanoclusters.
+The NS mode of each nanocluster is doubly degenerate as would be true of any structure with sixfold symmetry.
+In analogy to the previous oligomers, these magnetic modes are chosen because they are spectrally isolated from the other magnetic modes and because their radiation patterns are spatially orthogonal.
+The arrows denote the electric dipole moments on individual nanoparticles within the magnetic normal mode and the color denotes the strength of the magnetic field.
+The net electric or magnetic dipole character of each magnetic resonance is denoted in the upper right hand corner of each panel.
+
+Figure~\ref{kagan_eigen} displays the evolution of the aN and NS magnetic resonances with size, $a$.
+In contrast to the oligomers described previously, here the behavior of the nanocluster resonances with size is different due to the hexagonal packing as opposed to the open-ring structure of the oligomers.
+Nevertheless, the analytic model described previously is capable of predicting the magnetic spectrum.
+Most surprising is the behavior of the magnetic resonances of the 19- and 31-particle nanoclusters to oscillate with size as opposed to monotonically decrease in energy.
+Panels b, d, and f of Figure~\ref{kagan_eigen} display the relative strength of the near, intermediate, and far-field contributions to the electric dipole-electric dipole interaction energy and show that this oscillatory behavior is due specifically to retardation effects.
+This is contrary to intuition where increasing size causes monotonic redshifting.
+However this oscillatory behavior is not so unexpected; separating a MNP dimer causes its hybridized electric plasmon resonance frequencies to oscillate from bonding to anti-bonding and back\cite{vonPlessen2007}.
+In these nanoclusters, ARCL and patterns spectra provide a means to demonstrate this oscillation.
 
 \begin{figure}
-\includegraphics[width=6in]{13_19_31_eigen.pdf}
+\includegraphics{13_19_31_eigen.pdf}
 \caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters.
@@
 
-The magnetic mode eigenenergies shown in Figure~\ref{kagan_eigen} behave counter to the intuition we have built using the fused, empty ring systems like the 2mer and 3mer.
-This is because, quite simply, these clusters are constructed from a different aggregation scheme.
-Though the eigenmodes don't exhibit identical behavior to those shown in Figure~\ref{scaling}, the tools presented earlier are still valid for explaining why the modes cross.
-Most surprising is the tendency of the modes of the 19- and 31-particle systems to increase in energy at large scale values.
-This is contrary to the model systems and to plasmonic intuition, in which increasing size causes redshifts.
-However, we again show the interaction energies, and the dominance of the far-field term is solely responsible for the net positive coupling.
-In other words, at certain sizes and distances, these magnetic modes become anti-bonding.
-This is not so unexpected; separating a MNP dimer causes its resonance frequency to oscillate about a central frequency, from bonding to anti-bonding and back\cite{vonPlessen2007}.
-Angle-resolved CL spectra will show that this phenomenon is indeed physical.
-
 \begin{figure}
-\includegraphics[width=6in]{kagan_CL_spectra.pdf}
+\includegraphics{kagan_CL_spectra.pdf}
 \caption{Simulated angle-resolved cathodoluminescence spectra of the 13-, 19-, and 31-particle systems.
@@
 
-Figure~\ref{kagan_CL} shows simulated CL spectra for the 13-, 19-, and 31-particle system.
-The selection rules and radiative properties of each mode help to deconvolute the spectra.
-Because the aN mode radiates strongly in the xy-plane, and weakly in the z-direction, it is the most easily detected at angles of $theta$ larger than 0 radians.
-The NS mode can be detected either with $theta$ very close to 0 radians, or in the y-direction for this particular beam position.
-The aN beam position also weakly excites the NS modes, so the spectrum at that position should exhibit a feature that corroborates the spectral location of that mode.
-After comparing and contrasting between multiple angular spectra,  we show only those spectra that clearly display shoulders or peaks corresponding to the NS mode or the aN mode.
+Figure~\ref{kagan_CL} shows simulated ARCL spectra for the 13-, 19-, and 31-particle systems acquired at the two indicated beam positions and collection angles.
+Inspection of the EELS maps of the NS and aN magnetic resonances in rows b and d of Figure~\ref{kagan_fields} indicates the optimal electron beam positions, that is, those positions with highest EEL probability, at which to excite each magnetic mode.
+As described previously, it is the electron beam selection rules and radiative profile of each mode help to identify the two magnetic resonances of interest.
+Because the aN mode radiates strongly in the xy-plane, and weakly in the z-direction, it is most easily detected at angles of $0 < \theta < \pi/2$.
+The NS mode is detected either for angles very close to the backward scattering direction ($\theta \approx 0$), or parallel to the impact plane (here, the y-direction for this particular beam position).
+The aN beam position also weakly excites the degenerate NS modes, meaning the corresponding CL spectrum will provide a secondary signature of the spectral location of that mode.
 
-This analysis is experimentally accessible and can be further supported by computing EELS or CL maps of these clusters.
-Using the field and dipole plots in Figure~\ref{kagan_fields}, the EELS and CL maps of the aN mode and NS mode should be distinguishable.
-The aN map will exhibit low probability around the central particle, where the dipole moment is smallest, while the NS mode will exhibit large probability around the central dipole where the dipole moment is largest.
-As a result, electron beam spectroscopies are the perfect tool to experimentally probe the spectral ordering of magnetic plasmon resonances.
+\section{Conclusion}
+This paper is concluded.
 
 \section{Methods}
-Here we show how to derive the equations of motion, and solve an example system of two coupled oscillators. The Hamiltonian for a system of $N$ coupled oscillators
+Here we show how to derive the equations of motion describing magnetic plasmon resonances in nanoparticle clusters.
+References 10 and 43 describe how to map the solutions of Maxwell's Equations for electric plasmon resonances onto mechanical oscillators with effective masses.
+The resulting Hamiltonian for a system of $N$ frictionless coupled oscillators is
 
 \begin{equation}
-H = \sum_{i}\frac{\textbf{p}_i^2}{2m_{\textrm{sp}}}+\frac{1}{2}m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i^2 - \frac{e}{2}\sum_{j\neq i}\textbf{q}_i\cdot\textbf{E}_j(\textbf{r}_i),
+H = \sum_{i}\frac{\textbf{p}_i^2}{2m_{\textrm{sp}}}+\frac{1}{2}m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i^2 - \frac{e}{2}\sum_{ij,i\neq j}\textbf{q}_i\cdot\textbf{E}_j(\textbf{r}_i),
 \label{hammy}
@@
 
-\noindent where $\textbf{p}_i$ are the momenta of the plasmon oscillators with coordinates $\textbf{q}_i$, $m_{\textrm{sp}}$ is the plasmon mass, $\omega_{\textrm{sp}}$ is the plasmon frequency, and $\textbf{E}_j(\textbf{r}_i)$ is defined in Equation~\ref{electric_field_lambda}.
-The next step is to write Hamilton's equations of motion,
+\noindent where qi and $\textbf{p}_i$ are the coordinate and momentum of each plasmon oscillator located at $r_i$ with effective mass $m_{\textrm{sp}}$ and resonance frequency $\omega_{\textrm{sp}}$, defined previosuly; $\textbf{E}_j(\textbf{r}_i)$ is the full electric dipole field presented in Equation~\ref{electric_field_lambda}.
+The resulting equations of motion are,
 
 \begin{equation}
-\dot{\textbf{p}}_i = -\frac{\partial H}{\partial\textbf{q}_i} = -m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i + e\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
-\label{p_dot}
-\end{equation}
-
-\noindent and
-
-\begin{equation}
-\dot{\textbf{q}}_i = \frac{\partial H}{\partial\textbf{p}_i} = \frac{\textbf{p}_i}{m_{\textrm{sp}}}.
-\label{q_dot}
-\end{equation}
-
-Finally, taking another time derivative of Equation~\ref{q_dot} and plugging in Equation~\ref{p_dot}, we obtain the equation of motion
-
-\begin{equation}
-\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
+\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i,\omega)
 \label{equation_of_motion_again}
@@
 \begin{equation}
-(\omega_{\textrm{sp}}^2-\omega^2)\textbf{q}_i -\frac{e^2}{m_\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}\cdot\textbf{q}_j = 0.
+(\omega_{\textrm{sp}}^2-\omega^2)\textbf{q}_i -\frac{e^2}{m_\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}(\omega)\cdot\textbf{q}_j = 0.
 \label{fourier_eom}
@@
 It is this system of equations for the plasmon oscillator coordinates that we solve for the normal modes.
-As an example, we demonstrate this calculation for two coupled oscillators displaced and oriented along the x-axis.
-Knowing the dipole orientation allows us to project out the vector components and reduce the coupling term to a constant, resulting in
+Considering two identical, coupled, collinear oscillators as an example with dipole-dipole coupling strength $g_{12} = $ Equation 13 becomes
 
 \begin{equation}
-(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{1,2}q_2 = 0
+(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{12}(\omega)q_2 = 0
 \label{fourier_eom_1}
@@
 \begin{equation}
-(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{1,2}q_1 = 0.
+(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{12}(\omega)q_1 = 0,
 \label{fourier_eom_2}
@@
 
-Putting these equations of motion in matrix form allows us to solve for the eigenvalues and eigenvectors as follows.
+or equivalently
 
@@
 \begin{bmatrix}
-(\omega_{\textrm{sp}}^2-\omega^2) & -g_{1,2}\\
--g_{1,2} & (\omega_{\textrm{sp}}^2-\omega^2)
+(\omega_{\textrm{sp}}^2-\omega^2) & -g_{12}(\omega)\\
+-g_{12}(\omega) & (\omega_{\textrm{sp}}^2-\omega^2)
 \end{bmatrix}
@@
 
+Solution of this system produces the hybridized resonance frequencies and normal modes.
 Finding the determinant of this matrix yields the eigenvalues of the collective modes,
@@
 \begin{equation}
-\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{1,2}}.
+\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{12}(\omega)},
 \label{eigenvalues}
@@
 
-\noindent Of course, the coupling terms $g_{1,2}$ in fact depend on the frequency of the collective mode, which is demonstrated in Equation~\ref{electric_field_lambda}.
-Because of this, the eigenvalue problem must be solved iteratively until the eigenvalues converge.
-This example can be extended to systems of an arbitrary number of dipoles, and this exact method is used to solve for the eigenvalues of the magnetic plasmon modes.
+\noindent with corresponding normal mode coordinates
 
-\section{Conclusion}
-Magnetic plasmon oligomers of experimentally relevant size cannot be properly modeled using the quasistatic approximation.
-We have shown that a fully retarded coupled dipole method accurately predicts the energetics and ordering of magnetic plasmon resonances.
-Angle resolved cathodoluminescence spectroscopy confirms the predictions of the model, both on fused-ring oligomers and hexagonally-packed clusters of MNPs.
-This suggests yet another knob to turn in the field of plasmonics: the spectral ordering of resonances.
-The tunability of the relative phase of magnetic fields will allow advances in information processing, biological detection, and nanoscale etching.
+\begin{equation}
+q_{\pm} = \frac{1}{\sqrt{2}}\left(q_1 \pm q_2\right)
+\label{eigenvectors}
+\end{equation}
+
+\noindent Note that the coupling term $g_{12}(\omega)$ is frequency dependent, meaning the eigenvalue problem must be solved iteratively until convergence.
+The magnetic plasmon resonances and normal modes described herein are obtained as a straightforward extension of this example.
 

### 2018-03-07 fields/twomer_NN.m

@@ -1,0 +1,84 @@
+addpath(genpath('/usr/lusers/montoni/MNPBEM14'));
+op2 = bemoptions( 'sim', 'ret', 'interp', 'curv' );
+
+epstab = {epsconst( 1 ),epstable('silver_022717.dat')};
+
+for radius2 = [1,5,10,15,20,25,30];
+
+val = 5;
+
+r = 3*radius2;
+diameter2 = 2*radius2;
+
+ps = trisphere(144,diameter2);
+
+ex = sqrt(3)/2 * r;
+ey = (1/2) * r;
+
+p5 = shift(ps,[-2*ex,-ey,0]);
+p6 = shift(ps,[-ex,-2*ey,0]);
+p7 = shift(ps,[0,-ey,0]);
+p8 = shift(ps,[ex,-2*ey,0]);
+p9 = shift(ps,[2*ex,-ey,0]);
+p10 = shift(ps,[2*ex,ey,0]);
+p11 = shift(ps,[ex,2*ey,0]);
+p12 = shift(ps,[0,ey,0]);
+p13 = shift(ps,[-ex,2*ey,0]);
+p14 = shift(ps,[-2*ex,ey,0]);
+
+Ptot= {p5,p6,p7,p8,p9,p10,p11,p12,p13,p14};
+
+p=comparticle(epstab,Ptot,[2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1;2,1],1,2,3,4,5,6,7,8,9,10,op2);
+
+units;
+
+exc = planewave( [ 0, 1, 0], [ 1, 0, 0], op2 );
+%  light wavelength in vacuum
+eV = linspace(3.0,3.8,41);
+enei = eV2nm./linspace( 3.0,3.8,41);
+ene = transpose(eV2nm./enei);
+
+%  allocate scattering and extinction cross sections
+sca = zeros( length( enei ), 2 );
+ext = zeros( length( enei ), 2 );
+
+
+bem = bemsolver( p, op2 );
+
+% Next Green Functions are calculated.  
+Size=75; %number of total points
+SizeX=14*radius2; %total dimension, going negative to positve
+  SizeY=11*radius2; 
+
+%  points where electric fields are computed
+[ x, y ] = meshgrid( (SizeX-1)/2 * linspace( - 1, 1, Size ),(SizeY-1)/2 * linspace( - 1, 1, Size ) ); z = 0 * x; %At this line I multiplied each component by 0 to get the field at 0.
+
[…]

### 2018-03-07 greybush_2017/fixed_vec_greybush.py

@@ -8,12 +8,12 @@ static_NN = []
 static_NS = []
 bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
 bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
-mie_omegas = np.loadtxt('../mie_omegas_vacuum.txt')
+mie_omegas = np.loadtxt('../mie/mie_omegas_vacuum.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 crossing = []
 elec = 1.60217662e-19 # regular coulombs
 
-numPart = 13 #number of particles
+numPart = 31 #number of particles
 
 me = 9.10938291e-28; # electron mass in g
 ch = 4.80326e-10; # electron charge in g^1/2 cm^3/2 s^-1
@@ -33,8 +33,8 @@ interaction = [[],[]]
 NF = [[],[]]
 IF = [[],[]]
 FF = [[],[]]
-NN_vec = np.loadtxt('13_0_vec.txt')
-NS_vec = np.loadtxt('13_4_vec.txt')
+NN_vec = np.loadtxt('31_0_vec.txt')
+NS_vec = np.loadtxt('31_1_vec.txt')
 vectors = [NN_vec,NS_vec]
 for r in range(1,51):
 	a0 = r*10**-7; #sphere radius in cm
@@ -95,7 +95,7 @@ for r in range(1,51):
 
 	count = 1
 	#wsp_0 = math.sqrt((wplasma/math.sqrt(epsinf+2*epsb))**2 - (gamma/2)**2);
-	wsp_0 = mie_omegas[index]*elec/hbar
+	wsp_0 = mie_omegas[index]*elec/hbar + (gamma/2)*1j
 	#print mie_omegas[index]
 	#raw_input()
 	'''initialize w_0 and eigen'''
@@ -114,16 +114,17 @@ for r in range(1,51):
 		coupling = 0
 		w_mode = 0
 		count = 0
-		while abs(np.real(w_mode*hbar/elec) - np.real((1 + coupling)*wsp_0*hbar/elec)) > 0.000001:
+		while abs((w_mode*hbar/elec) - ((1 + coupling)*wsp_0*hbar/elec)) > 0.0001:
+			#print abs((w_mode*hbar/elec) - ((1 + coupling)*wsp_0*hbar/elec))
[…]

### 2018-03-07 greybush_2017/greybush.py

@@ -8,7 +8,7 @@ static_NN = []
 static_NS = []
 bem_NN = [3.614, 3.603, 3.562, 3.5, 3.405, 3.295, 3.17]
 bem_NS = [3.61, 3.6, 3.569, 3.509, 3.413, 3.276, 3.112]
-mie_omegas = np.loadtxt('../mie_omegas_vacuum.txt')
+mie_omegas = np.loadtxt('../mie/mie_omegas_vacuum.txt')
 ''' So all the units are cgs, but the hamiltonian gets loaded up with energies in eVs, so the first constant below is the charge of an electron in coulombs and the rest of the units are cgs. Every constant should be labeled.'''
 crossing = []
 elec = 1.60217662e-19 # regular coulombs
@@ -23,13 +23,13 @@ eps0 = 8.85418782e-12; # permittivity of free space
 Q = [np.array([1,0]),np.array([0,1])] #dipole moments: 1st in x-direction, 2nd in y-direction
 epsinf = 3.77; 
 '''Properties for silver.'''
-Eplasma = 9.0*elec/hbar; # J
-gamma = 0.069*elec/(hbar)
+Eplasma = 9.15*elec/hbar; # J
+gamma = 0.05*elec/(hbar)
 wplasma = Eplasma/hbar; # plasma frequency (rad/s)
 epsb = 1
 
 
-for r in range(10,11):
+for r in [30]:
 	a0 = r*10**-7; #sphere radius in cm
 	alphasp = (a0**3)*(3/(epsinf+2*epsb)); # polarizability (cm^3)
 	index = r-1
@@ -80,25 +80,25 @@ for r in range(10,11):
 	#print places
 	Loc = places
 	xloc, yloc = zip(*Loc)
-	plt.scatter(xloc,yloc)
+	#plt.scatter(xloc,yloc)
 	#raw_input()
-	plt.show()
+	#plt.show()
 	#raw_input()
 	'''This part builds the Hamiltonian. We start by initializing and choosing an initial omega value.'''
-	H = (np.zeros((2*numPart,2*numPart),dtype=float))#initialize Hammy with zeros, twenty by twenty in this case.
+	H = (np.zeros((2*numPart,2*numPart),dtype=complex))#initialize Hammy with zeros, twenty by twenty in this case.
 
 	'''More constants'''
 
 	count = 1
[…]

### 2018-04-05 paper_fall_2017/draft_winter_2017.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage[T1]{fontenc}       % Use modern font encodings
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{wrapfig}
%\usepackage{multline}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}
\date{September 4, 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Tunable Spectral Ordering and Directional Radiation in Magnetic Plasmon Oligomers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{plasmon, hybridization, magnetic, retardation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\begin{centering}
\includegraphics[width=7cm]{toc.png}
\end{centering}
\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored. A fully retarded coupled dipole model is employed, expanding upon past work in the field, to explore the dependence of the resonant frequencies and spectral ordering of the magnetic resonances on cluster size. It is shown that magnetic resonances change spectral order as metal nanoparticle oligomers change in size, and that these mode switches are observable in full-wave numerical electrodynamics simulations of angle-resolved cathodoluminescence spectra. Electron-beam spectroscopies are uniquely suited to observing this phenomenon, as they provide nanometer spatial and sub-eV spectral resolution and can preferentially excite one magnetic resonance over another. Furthermore, angle-resolved spectroscopies leverage the specific radiation patterns attributed to each magnetic plasmon, clearly differentiating spectral signatures of each individual magnetic plasmon resonance.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{introduction}
Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years. These effects, called magnetic plasmon resonances, have been shown to couple to and enhance the magnetic field of light, exhibit a negative index of refraction at certain frequencies, act anti-reflectively, and even hybridize analogously to electric plasmon resonances\cite{Alu2006,Alu2008,Dionne2011,Cherqui2014,Dionne2016,Cherqui2016,Engheta2017}. Much of this work has focused on the single-oligomer regime, studying systems composed of only one ring of nanoparticles using simple models in the quasistatic limit\cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. Other approaches have involved studying the infinte-oligomer regime, in which the language of solid-state or condensed matter physics is more appropriate\cite{Schatz2003,Weick2013}. Recently, a disconnect between these size regimes and methods has arisen, leading to open questions in how magnetic plasmon resonances behave in the few-oligomer regime; that is, in the intermediate size regime\cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.

Most crucial to this concept is the question of when and how retardation effects matter when decribing magnetic plasmon resonances using analytical models. Previous work shows that for a cluster of only two oligomers, the quasistatic approximation breaks down when compared with full-wave simulations in that it predicts a different energy-ordering of magnetic plasmons than in simulated electron energy-loss spectroscopy (EELS) and cathodoluminescence (CL) experiments\cite{Cherqui2014}. Retardation effects have been incorporated into models of single MNPs, dimers, infinite chains, and infinite arrays\cite{Kottman2001,Rechbacher2003,Schatz2003,Royer2005,vonPlessen2007,Abajo2008,Chumanov2010,Gu2010,Pinchuk2016}. However, few studies have shown whether retardation effects are needed to accurately predict the behavior of magnetic plasmon resonances specifically. We aim to show that the incorporation of retardation effects actually corrects the aformentioned discrepancy between models of magnetic plasmon resonances and simulated experiments.

Because retardation effects depend on size and we are interested in the intermediate size regime, we will analyze the energetics of magnetic plasmon resonances as a function of cluster size. At small sizes, magnetic oligomers behave quasistatically; a fully retarded coupled-dipole model and a quasistatic coupled-dipole model make similar predictions, and both models agree with static simulations. However, with increasing size, magnetic oligomers deviate from quasistatic behavior and we predict never-before-reported eigenmode switching of the magnetic plasmon resonances. This is not a theoretical artifact and we demonstrate that, due to magnetic plasmon resonances' distinct radiative properties, this mode switching can be observed in angle-resolved CL spectra using full-wave simulations\cite{Hohenester2012}. Indeed, directional radiation has been previously detected using this technique\cite{Coenen2011,CoPol2011,Polman2014}. The spectral order of the magnetic plasmon resonances depends on aggregate size and mophology, meaning that it is tunable. Tunability of the relative phase of magnetic fields in a single MNP cluster may lead to advances in detection methods, anti-reflective coatings, and information processing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano,Zhang2006,NordHal2011,NordHal2012}.

\section{Model Systems and Magnetic Plasmon Resonances}

\begin{figure}
\includegraphics[width=6.5in]{2mer_3mer_fields.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}

To begin, we investigate two model systems comprising 10 and 13 silver nanospheres and resembling naphthalene and phenalene, respectively. Diagrams of these systems, from here on called the 2mer and the 3mer, are shown in Figure~\ref{field_plots}. We are interested in the collective eigenmodes of these systems that produce large magentic fields inside the rings and the eigenenergies associated with those modes. Previous work has also attempted to predict the eigenenergies of magnetic oligomer systems, and found that quasistatic predictions of the eigenspectrum, using a coupled dipole method, did not align with simulated EELS of the same oligomers.\cite{Cherqui2014} We modify the previous approach, mapping the individual electric dipole plasmon of each MNP onto a harmonic oscillator and allowing them to couple through retarded dipole-dipole interactions as follows\cite{ARPC}

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i).
\label{equation_of_motion}
\end{equation}

\noindent Here $\omega_{\textrm{sp}}$ is the natural frequency of a single electric plasmon, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the surface plasmon effective mass defined by the polarizability $\alpha_{\textrm{sp}}$, the plasmon oscillator dipole moment $\textbf{d}_i = e\textbf{q}_i$, and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field from the $j^{\textrm{th}}$ dipole at the position of the $i^{\textrm{th}}$ dipole and is defined as

\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{k^2}{r_{ij}}\left(\textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j.
\label{electric_field_lambda}
\end{equation}

\noindent Here, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ is the wavenumber of the collective mode with frequency $\omega$, and $\varepsilon_b$ is the dielectric constant of the background medium. The fully retarded electric field contains three important terms. The term with $1/r_{ij}^3$-dependence is called the near-field, because it decays very quickly with increasing distance. In fact, this term is what remains when taking the quasistatic limit. The second term, with the $k/r_{ij}^2$-dependence, is the intermediate-field term. The third term, with $k^2/r_{ij}$-dependence, is the far-field term, called such because it dominates after the other two have decayed. All three terms are dressed by a complex exponential, which depends both on $k$ and on $r_{ij}$. This shows that at specific separation distances, the interaction energies can change sign and go from energy-lowering to energy-raising. Using just the fully retarded electric field, we have incorporated all necessary retardation effects\cite{Purcell1973}. The full dipole electric field is all that is needed to obtain qualitatively and quantitatively consistent predictions of the behavior of magnetic plasmons. While previous approaches have relied on coarse-graining to build explicit magnetic dipoles into the equations of motion, we show that no such averaging procedure is necessary as the fully retarded electric field contains all of the magnetic information.

Solving the system of Equations~\ref{equation_of_motion} for all of the dipoles in a single aggregate yields as many hybridized modes as there are degrees of freedom, in this case, two times the number of particles. Similarly, each system supports a number of magnetic plasmons equal to the number of oligomers. The eigenvectors of these collective modes represent the dipole moments on each nanoparticle. Figure~\ref{field_plots} shows these magnetic mode eigenvectors overlayed with plots of the signed magnetic field magnitude of each normal mode. Each mode is named for its particular magnetic field distribution after the poles of a magnet, either all-North (aN) or North-South (NS). These magnetic modes have been chosen because each of them can be excited by light and can radiate to the far-field. The top right-hand corner of each field plot in Figure~\ref{field_plots} displays whether the magnetic mode depicted exhibits a net electric dipole or a net magnetic dipole. In planar geometries, the magnetic dipole moments are always perpendicular to the in-plane electric dipole moments. As a result, they scatter light with different directionality. This property will be exploited in angle-resolved spectra to aN magnetic modes from NS magnetic modes.

\section{Spectral Ordering of Magnetic Modes in Model Systems}

To determine the impact of incorporating retardation effects, it is first useful to look at the quasistatic model. Careful observation will show that in the quasistatic limit individual particle frequencies are not dependent on particle size, and the coupling strength is scale-invariant. If the ratio of interparticle distance $r_{ij}$ to particle size $r_0$ remains constant, as the particles grow the collective frequencies should not change. We can see this by rewriting the quasistatic coupling term

\begin{align}
\frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij} &= \frac{e^2}{m_{\textrm{sp}}}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \\
&= \omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \\
&= \omega_{\textrm{sp}}^2 \left(\frac{3r_0^3}{\varepsilon_{\infty}+2}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{(sr_0)^3} \\
&= \omega_{\textrm{sp}}^2 \left(\frac{3}{\varepsilon_{\infty}+2}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{s^3}.
\label{quasistatic_coupling}
\end{align}

\noindent However, revisiting Equation~\ref{electric_field_lambda} shows that incorporation of retardation effects removes the scale invariance of the coupling by allowing the single plasmon frequency to vary with size and by introducing more size-dependent terms into the coupling (the intermediate- and far-fields). In light of this observation, we choose the scale of the MNP clusters, or the size as a function of an individual MNP radius, as the variable to investigate retardation effects and spectral switching in magnetic plasmon resonances. In all of the explorations, both on the model systems and in future sections, the scale of the system is defined by a nearest-neighbor distance $r_{\textrm{nn}} = 3r_0$, chosen so that each nearest-neighbor pair has a face-to-face separation distance of $r_0$.

\begin{figure}
\includegraphics[width=4in]{2mer-3mer-eig.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}

Figure~\ref{scaling} shows the predicted eigenenergies and the simulated spectral peak positions for the magnetic modes of the 2mer and 3mer with varying $r_0$. At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits easily into a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}. In fact, a fully retarded scattering spectrum of an aggregate of this size is qualitatively identical to quasistatic simulations of the same system at all sizes. This implies that the quasistatic approximation is accurate only for magnetic oligomers spanning less than a quarter of the wavelength of light, smaller than suggested by previous work for single particles [\textbf{I can't find the review paper where they report the $\lambda/2$ number.}]. As the system scale increases, the eigenenergies decrease and appear to cross at $r_0 = 7$ nm, and once more at $r_0 = 20$ nm. This is due to the far-field term in Equation~\ref{electric_field_lambda} becoming strong relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares). As the system gets larger, it takes information longer to propagate across the aggregate, meaning that retaradtion effects become important. The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneaous conclusion that the quasistatic approximation is accurate again. Rather, both eigenmode crossings are due entirely to retardation effects. The interaction energy between all the dipoles in each magnetic mode,

\begin{equation}
U_{\textrm{int}} = -\sum_i \textbf{d}_i \cdot \sum_{j \neq i} \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}

\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes. The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode. Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in water the crossing points are shifted towards smaller scale. This is to be expected, as the wavelength of light is compressed in a medium, meaning that light sees objects as much bigger than they really are. This analysis shows that the quasistatic approximation is good for very small magnetic oligomers in vacuum, and for smaller oligomers in medium. This can also be explained through the impact of a dielectric medium on coupling strength. While a medium should contribute an overall increase to the coupling strength (which is predicted in Figure~\ref{scaling}b and f), the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008} Through comparison with simulation (dashed lines in Figure~\ref{scaling}a), it can be shown that this simple and efficient model is accurate to within 0.05 eV and accurately describes the behavior of magnetic plasmon oligomers.

Previous work has explored the oscillatory nature of resonance frequency and radiation damping as a function of size in plasmonic systems\cite{vonPlessen2007}. We have shown that a fully retarded coupled dipole approach predicts magnetic plasmon resonance switching, and explains that it is due to inclusion of the far-field term in the dipole relay tensor. From here, we use simulated angle-resolved CL spectroscopy to observe this magnetic mode switching, leveraging the specific radiative properties of each magnetic plasmon and the ability of the electron beam to isolate specific plasmon modes.

\section{Radiative Properties of Magnetic Plasmon Resonances}
In order to detect the spectral switching of magnetic plasmons, we must exploit their unique radiative properties. Only those magnetic eigenmodes supporting net dipole moments should radiate to the far field. Furthermore, the aN magnetic mode dipole moment is perpendicular to the NS mode electric dipole moment(s) in both the model 2mer and 3mer, meaning that they radiate with different directional-dependence. It has been predicted and shown experimentally that single magnetic oligomers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited.\cite{Dionne2011,Cherqui2016} This is evident from the difference between forward and backward scattering spectra, but can also be shown by computing the differential scattering pattern,\cite{jackson_classical_1999,schwinger1998classical}

\begin{equation}
\frac{dP}{d\Omega} = \frac{c}{8\pi}\textrm{Re}\left[r^2\hat{\textbf{n}}\cdot\sum_i\textbf{E}_i \times \sum_{j}\textbf{B}_{j}^*\right]
\label{dp_field_1}
\end{equation}

\noindent where $\hat{\textbf{n}}$ is the unit vector pointing to the detector a distance $r >> \lambda$ away and $\textbf{E}_i$ and $\textbf{B}_j^*$ are the electric field and conjugate magnetic inductance originating from each oligomer ring. In order to predict the qualitative properties of independently and mutually exciting an orthogonal magnetic and electric plasmon, we coarse-grain our approach by assuming that each ring of the oligomer supports one collective electric and one collective magnetic dipole moment, co-located at the center of each ring. Using the far-fields scattered by such an arrangement of electric and magnetic dipoles reduces the differential scattering to\cite{Engheta2006}

\begin{equation}
\frac{dP}{d\Omega} = \frac{ck_e^2k_m^2}{8\pi} \textrm{Re} \left[\hat{\textbf{n}} \cdot \sum_{i} (\hat{\textbf{n}} \times \textbf{d}_i) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_i \times \sum_{j} \hat{\textbf{n}} \times \textbf{d}_j^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_j^*) \times \hat{\textbf{n}}\right]
\label{dp_coarse_grain}
\end{equation}

Performing the vector operations in Equation~\ref{dp_coarse_grain} yields

\begin{multline}
\frac{dP}{d\Omega} = \frac{ck^4}{8\pi} \textrm{Re} [ \sum_{ij} \textbf{d}_i \cdot \textbf{d}_j^* - (\hat{\textbf{n}} \cdot \textbf{d}_i)(\hat{\textbf{n}} \cdot \textbf{d}_j^*) + \boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_i)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_j^*) \\ + \hat{\textbf{n}} \cdot (\textbf{d}_i \times \boldsymbol{\mu}_j^* + \textbf{d}_j^* \times \boldsymbol{\mu}_i) ].
\label{dp_dipoles_1}
\end{multline}

\noindent To build intuition, we demand the magnetic dipole $\boldsymbol{\mu}$ is oriented in the z-direction, and the electric dipole $\textbf{d}$ is oriented in the y-direction. The coarse-grained electric dipole and magnetic dipole can be written in terms of their constituent dipoles $\textbf{d} = \sum_n d_{e,n} \hat{\textbf{y}}$ and $\boldsymbol{\mu} = \frac{k_m}{2}\sum_n(\textbf{r}_n \times d_{m,n} \hat{\boldsymbol{\phi}}_n) = \frac{k_mNRd_m}{2}\hat{\textbf{z}}$ where the sums are taken over the $n$-th and $m$-th dipoles, respectively. Using these definitions, reducing the sum to a single oligomer for simplicity, and giving each dipole equivalent magnitude, the differential scattering becomes

\begin{equation}
\frac{dP}{d\Omega} = \frac{N^2ck_e^2k_m^2}{8\pi}\left[ d_e^2(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{y}})^2) + \frac{k_m^2R^2d_m^2}{4}(1 - (\hat{\textbf{n}} \cdot \hat{\textbf{z}})^2) + d_ed_mk_mR(\hat{\textbf{n}} \cdot \hat{\textbf{x}})\right]
\label{dp_dipoles_2}
\end{equation}

Equation~\ref{dp_dipoles_2} shows that exciting different combinations of dipoles leads to very specific radiation patterns. Exciting only a net electric dipole moment and setting $d_m = 0$ results in a dipolar radiation pattern with a node of zero radiation along the electric dipole axi, in this case the y-axis. Similarly, setting $d_e = 0$ and exciting only a net magnetic dipole results in another dipolar radiation pattern with a node along the magnetic dipole axis, which in this case is the z-axis. Finally, exciting both an electric and a magnetic dipole results in contributions from both patterns in the y- and z-directions. However, the third term of Equation~\ref{dp_dipoles_2} contributes an asymmetry, increasing the radiation in the positive x-direction, or the forward direction in this case, while decreasing the radiation in the backwards direction. This intuitively shows that interfering othrogonal electric and magnetic plasmons radiate with low or no back scattering\cite{Dionne2011}.

\begin{figure}
\includegraphics[width=5in]{scattering_patterns.pdf}
\caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane. The magnetic dipole exhibits the expected dipolar doughnut, or two lobe, shape with a node along the z-axis. The electric dipole moment also shows the expected pattern with a node along the y-axis.}
\label{scattering}
\end{figure}

Using the scattering patterns in Figure~\ref{scattering} computed from Equation~\ref{dp_dipoles_2}, we can make predictions about how to observe each individual magnetic plasmon resonance. The aN modes support a z-oriented magnetic dipole and radiate in the xy-plane. The NS mode in the 2mer is oriented in the y-direction, and so it radaites in the xz-plane. The cyclic 3mer is more complicated. Due to its threefold symmetry, its x- and y-oriented NS modes are degenerate and linearly dependent, meaning that they can be mutually excited. When exciting the 3mer with a y-oriented electric field, it radiates strongly in the xz-plane and weakly in the yz-plane. Using an x-oriented electric field results in the opposite. When choosing field polarizations that excite both the all-North mode and the North-South mode, the systems radiate very strongly in the direction of light propagation, and exhibit very weak back scattering. Strong forward to backward scattering ratios are also predicted and demonstrated in metal-semiconductor core-shell nanoparticles, which similarly exploit the interference between an electric plasmon and a magnetic plasmon\cite{Kivshar2012}. With these radiative properties in mind, we can now observe each magnetic plasmon separately. By collecting photons in the directions that each plasmon radiates weakly, we should be able to see one more strongly than the other. To help this selectivity, we will preferentially excite each magnetic plasmon using an electron beam.

\section{Angle-Resolved Cathodoluminescence for Observing Spectral Switching}
Electron beam spectroscopies, such as EELS and CL, in a STEM are useful for high spatial and spectral resolution studies of nanomaterials\cite{Coenen2011,CoPol2011,Abajo2013,Polman2014,ARPC}. While EELS measures the probability that a passing electron loses energy to a material, CL measures the probability that an excitation in the sample decays into photon emission. Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize a material. Using a STEM fitted with a parabolic mirror over the sample, the user can collect emitted light with angular information within $0 \leq \theta \leq \pi/2$ and $0 \leq \phi \leq \pi$\cite{Coenen2011,CoPol2011,Polman2014}. Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes and their crossing can be observed in spectra. The previous section built up intuition regarding the directionality of light scattered by the magnetic modes of the 2mer and 3mer. This intuition informas the specific angles at which to collect CL spectra. Using the selection rules imposed by the electron beam and the directionality of light, it is possible to distinguish the magnetic modes and observe them switch spectral order.

\begin{figure}
\includegraphics[width=6in]{CL_2mer_3mer.pdf}
\caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d). By choosing the beam positions marked on the diagrams and choosing different angles at which to measure the light emitted, the magnetic modes of each oligomer can be disentangled. The colored "x's" correspond to colored traces. The blue traces show a collection angle of $\phi = 3\pi/2$ and the orange traces are for $\phi = \pi$, while both have $\theta = \pi/4$. Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted. WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
\label{CL_2mer_3mer}
\end{figure}

In Figure~\ref{CL_2mer_3mer} we show point CL spectra on the 2mer and 3mer, with the electron beam positions represented in the diagrams by a blue x and  an orange x chosen to excite the aN modes and the NS modes, respectively. However, due to the symmetry of the model systems, the blue position can weakly excite the NS mode, meaning that signatures of it will appear in both spectra. Recalling that the aN mode should radiate in the xy-plane and the North-South mode should radiate in the z-direction and either the x- or the y- direction, it is possible to distinguish the modes by collecting photons at different angular distributions. The angles chosen are reported in Figure~\ref{CL_2mer_3mer}. These spectra confirm the predictions made in Figure~\ref{scaling}, specifically that between $r_0 = 15$ nm and $r_0 = 30$ nm, the aN mode and the NS mode switch spectral order.

We have now shown that the fully retarded coupled dipole approximation can qualitatively and, to small error, quantitatively predict the eigenenergies and spectral switching of magnetic plasmons, we are prepared to explore more complicated geometries that are active areas of research. Before moving on, we must make a quick note about accuracy. We have chosen Drude model parameters for silver that accurately predict the single plasmon frequency at all the sizes we explore, specifically $\varepsilon_{\infty} = 3.77$, $\hbar\omega_p = 9.15$ eV, and $\hbar\gamma = 0.05$ eV. However, these parameters also appear in the static polarizability which dresses the coupling terms. As a result, any error introduced from the choice of Drude model would increase with increasing particle number. Though this is the case for larger and more complicated systems, we assert that the fully retarded coupled dipole method is qualitatively sound and that magnetic plasmon mode switching is a physical phenomenon.

\section{Eigenspectra and CL Spectra of Hexagonally-Packed Arrays}

In order to show that this discussion of mode-switching is experimentally relevant, we use the intuition we have built from the model systems and previous simulated CL experiments to investigate magnetic oligomer systems of recent interest. Specifically, we look at hexagonally packed clusters of 13, 19, and 31 MNPs originally designed and characterized by Greybush \textit{et al}\cite{Engheta2017}. The arrangement of MNPs and the magnetic plasmon modes that we discuss are shown in Figure~\ref{kagan_fields}. Using the discussion of model systems above as a template, for each system we track the eigenenergies of an aN mode and a NS mode and also show that their switching can be observed in simulated angle-resolved CL measurements.

\begin{figure}
\includegraphics[width=6in]{kagan_fields.pdf}
\caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters. Similarly to the 2mer and 3mer from before, we present only those magnetic modes with either NS and electric dipole character (a, b, d, e, g, and h) or with aN and magnetic dipole character (c, f, and i).}
\label{kagan_fields}
\end{figure}

The magnetic modes of the structures shown in Figure~\ref{kagan_fields} show two kinds of magnetic character. The aN mode of each cluster consists of concentric rings of head-to-tail electric dipoles, with a z-oriented magnetic dipole. The NS modes of each cluster, which are degenerate, exhibit two equal-sized regions of out-of-phase magnetic character, as well as net electric dipoles. In fact, the NS modes of these planar arrays behave the same way as the NS modes of the 3mer in that due to the sixfold symmetry, the "x-oriented" and "y-oriented" dipoles are linearly dependent and mutually excitable by a single plane wave. However, because an electron beam excitation would break this symmetry, the two modes can be distinguished between beam positions and angular distributions of radiation.

\begin{figure}
\includegraphics[width=6in]{13_19_31_eigen.pdf}
\caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters. Unlike the previous 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes. However, for each system a crossing point does occur between $r_0 = 30$ nm and $r_0 = 40$ nm. While the modes of the 13-particle system behave as expected, the aN and NS modes of the larger clusters behave contrary to the intuition built from the earlier model systems. At larger sizes, instead of a monotonic decrease in eigenenergies, the modes exhibit an increase in energy. Looking at the interaction energies, it becomes clear that this is again due to retardation effects, as the term that contributes the most anti-bonding character to the total interaction energy is the far-field. Furthemore, the 31-particle system exhibits a second crossing, unlike the other two structures, and the increase in its eigenenergies is maximized at smaller sizes.}
\label{kagan_eigen}
\end{figure}

The magnetic mode eigenenergies shown in Figure~\ref{kagan_eigen} behave counter to the intuition we have built using the fused, empty ring systems like the 2mer and 3mer. This is because, quite simply, these clusters are constructed from a different aggregation scheme. Though the eigenmodes don't exhibit identical behavior to those shown in Figure~\ref{scaling}, the tools presented earlier are still valid for explaining why the modes cross. Most surprising is the tendency of the modes of the 19- and 31-particle systems to increase in energy at large scale values. This is contrary to the model systems and to plasmonic intuition, in which increasing size causes redshifts. However, we again show the interaction energies, and the dominance of the far-field term is solely responsible for the net positive coupling. In other words, at certain sizes and distances, these magnetic modes become antibonding. This is not so unexpected; separating a MNP dimer causes its resonance frequency to oscillate about a central frequency, from bonding to antibonding and back\cite{vonPlessen2007}. Angle-resolved CL spectra will show that this phenomenon is indeed physical.

\begin{figure}
\includegraphics[width=6in]{kagan_CL_spectra.pdf}
\caption{Simulated angle-resolved cathodoluminescence spectra of the 13-, 19-, and 31-particle systems. Blue spectra were acquired at the beam positions marked with a blue x in order to preferentially excite the aN mode. Orange spectra were collected at the points marked with an orange x in order to preferentially excite the x-polarized NS mode. Spectra for the 13-particle aggregate were computed for $r_0 = 10$ nm (a) and $r_0 = 50$ nm (b). Spectra for the 19-particle aggregate were computed for $r_0 = 10$ nm (c) and $r_0 = 40$ nm (d). Spectra for the 31-particle aggregate were computed for $r_0 = 10$ nm (e) and $r_0 = 30$ nm (f). The dashed lines in each spectrum indicate the peak location of the aN modes (blue curves) and the NS modes (orange curves). Each panel also displays the collection angles for each spectrum.}
\label{kagan_CL}
\end{figure}

Figure~\ref{kagan_CL} shows simulated CL spectra for the 13-, 19-, and 31-particle system. The selection rules and radiative properties of each mode help to deconvolute the spectra. Because the aN mode radiates strongly in the xy-plane, and weakly in the z-direction, it is the most easily detected at angles of $theta$ larger than 0 radians. The NS mode can be detected either with $theta$ very close to 0 radians, or in the y-direction for this particular beam position. The aN beam position also weakly excites the NS modes, so the spectrum at that position should exhibit a feature that corroborates the spectral location of that mode. After comparing and contrasting between multiple angular spectra,  we show only those spectra that clearly display shoulders or peaks corresponding to the NS mode or the aN mode.

This analysis is experimentally accessible and can be further supported by computing EELS or CL maps of these clusters. Using the field and dipole plots in Figure~\ref{kagan_fields}, the EELS and CL maps of the aN mode and NS mode should be distinguishable. The aN map will exhibit low probability around the central particle, where the dipole moment is smallest, while the NS mode will exhibit large probability around the central dipole where the dipole moment is largest. As a result, electron beam spectroscopies are the perfect tool to experimentally probe the spectral ordering of magnetic plasmon resonances.

\section{Methods}
Here we show how to derive the equations of motion, and solve an example system of two coupled oscillators. The Hamiltonian for a system of $N$ coupled oscillators

\begin{equation}
H = \sum_{i}\frac{\textbf{p}_i^2}{2m_{\textrm{sp}}}+\frac{1}{2}m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i^2 - \frac{e}{2}\sum_{j\neq i}\textbf{q}_i\cdot\textbf{E}_j(\textbf{r}_i),
\label{hammy}
\end{equation}

\noindent where $\textbf{p}_i$ are the momenta of the plasmon oscillators with coordinates $\textbf{q}_i$, $m_{\textrm{sp}}$ is the plasmon mass, $\omega_{\textrm{sp}}$ is the plasmon frequency, and $\textbf{E}_j(\textbf{r}_i)$ is defined in Equation~\ref{electric_field_lambda}. The next step is to write Hamilton's equations of motion,

\begin{equation}
\dot{\textbf{p}}_i = -\frac{\partial H}{\partial\textbf{q}_i} = -m_{\textrm{sp}}\omega_{\textrm{sp}}^2\textbf{q}_i + e\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{p_dot}
\end{equation}

\noindent and

\begin{equation}
\dot{\textbf{q}}_i = \frac{\partial H}{\partial\textbf{p}_i} = \frac{\textbf{p}_i}{m_{\textrm{sp}}}.
\label{q_dot}
\end{equation}

Finally, taking another time derivative of Equation~\ref{q_dot} and plugging in Equation~\ref{p_dot}, we obtain the equation of motion

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i)
\label{equation_of_motion_again}
\end{equation}

\noindent which is exactly Equation~\ref{equation_of_motion}. From here, introducing time-dependence as a complex exponential, rewriting the electric field in terms of the plasmon coordinate, and performing a Fourier transform results in equations of motion in the frequency domain

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)\textbf{q}_i -\frac{e^2}{m_\textrm{sp}}\sum_{j\neq i}\boldsymbol{\Lambda}_{ij}\cdot\textbf{q}_j = 0.
\label{fourier_eom}
\end{equation}

It is this system of equations for the plasmon oscillator coordinates that we solve for the normal modes. As an example, we demonstrate this calculation for two coupled oscillators displaced and oriented along the x-axis. Knowing the dipole orientation allows us to project out the vector components and reduce the coupling term to a constant, resulting in

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{1,2}q_2 = 0
\label{fourier_eom_1}
\end{equation}

and

\begin{equation}
(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{1,2}q_1 = 0.
\label{fourier_eom_2}
\end{equation}

Putting these equations of motion in matrix form allows us to solve for the eigenvalues and eigenvectors as follows.

\begin{equation}
\begin{bmatrix}
(\omega_{\textrm{sp}}^2-\omega^2) & -g_{1,2}\\
-g_{1,2} & (\omega_{\textrm{sp}}^2-\omega^2)
\end{bmatrix}
\begin{bmatrix}
q_1\\
q_2
\end{bmatrix}
=
\begin{bmatrix}
0\\
0
\end{bmatrix}
\label{eom_matrix}
\end{equation}

Finding the determinant of this matrix yields the eigenvalues of the collective modes,

\begin{equation}
\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{1,2}}.
\label{eigenvalues}
\end{equation}

\noindent Of course, the coupling terms $g_{1,2}$ in fact depend on the frequency of the collective mode, which is demonstrated in Equation~\ref{electric_field_lambda}. Because of this, the eigenvalue problem must be solved iteratively until the eigenvalues converge. This example can be extended to systems of an arbitrary number of dipoles, and this exact method is used to solve for the eigenvalues of the magnetic plasmon modes.

\section{Conclusion}
Magnetic plasmon oligomers of experimentally relevant size cannot be properly modeled using the quasistatic approximation. We have shown that a fully retarded coupled dipole method accurately predicts the energetics and ordering of magnetic plasmon resonances. Angle resolved cathodoluminescence spectroscopy confirms the predictions of the model, both on fused-ring oligomers and hexagonally-packed clusters of MNPs. This suggests yet another knob to turn in the field of plasmonics: the spectral ordering of resonances. The tunability of the relative phase of magnetic fields will allow advances in information processing, biological detection, and nanoscale etching.

\begin{acknowledgement}
CEI for money, HPC/Hyak/Mox for computing time, Niket and Harrison for good conversations.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}
\end{document}

%While good for theoretical studies of system properties, scale is not tunable in real time, meaning these properties can't be easily measured. Recent research has focused heavily on finding controllable and reversible ways to manipulate the aggregation scheme of a metal nanoparticle array using tools like DNA, polymers, and stretchable embedding media\cite{Yang2016,Ginger2017,NaLiu2017,DanLuo2009}. We employ this idea by fixing the particle radii and the aggregation scheme of the structure and inflating the interparticle distances. Figure~\ref{scaling}e-h shows the results of fixing $r_0$ at 15 and 30 nm and increasing $s$. Increasing the distance between particles regardless of particle size and environment weakens the coupling as the distance approaches infinity, which can be seen in Equation~\ref{electric_field_lambda}. As a result, the collective frequencies of the magnetic modes approach the single plasmon frequency. On the way, the modes oscillate about each other, exhibiting multiple crossings. The amplitude of these crossings appears to increase with increasing particle size and with increasing background dielectric constant, which can be seen in Figure~\ref{scaling}f and h. The quasistatic approximation cannot explain this phenomenon. The fully retarded electric field contains a complex exponential term that depends on interparticle separation. It is this term that dresses all of the interaction terms in the field and changes the sign of the interaction from negative to positive at certain distances. This is clear evidence that the magnetic modes of the 2-mer are tunable in real time in a laboratory with splittings as small as 0.01 eV and as large as 0.1 eV.

%When two or more metal nanoparticles (MNPs) are brought together, their individual electric plasmons can hybridize to produce new, collective plasmon resonances\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Arranging three or more MNPs on the vertices of a polygon generates a collective mode that resembles a fictitious current loop and produces a sizeable magetic moment in the center of the polygon\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014}. These aggregates can couple to and enhance the magnetic field of light, leading to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}.

%Of recent interest has been the ability of magnetic plasmons, much like electric plasmons, to hybridize\cite{Cherqui2016}. Similar to how a pair of electric plasmons can produce an electrically bright and an electrically dark mode, a pair of magnetic plasmons can produce a magnetically bright mode and a magnetically dark mode. This understanding opens up new routes to preferentially exciting magnetic and electric plasmons and distinguishing between the different plasmonic modes of a particular aggregate. Studies of the properties of magnetic plasmons have focused on plasmon propagation and hybridization, but have not sought to determine under what circumstances the magnetic plasmons of a system dominate its optical properties. Key to answering this question is the influence of retardation effects.

%This work utilizes and augments a previously published tight-binding model\cite{Cherqui2014}. The model in question maps the electric plasmon of each nanoparticle onto a harmonic oscillator and allows them to couple through quasistatic, near-field interactions using the Hamiltonian

%\begin{equation}
%\frac{H}{\hbar\omega_{\textrm{sp}}} = \frac{1}{2}\sum_{i}\left[\boldsymbol{\Pi}_{i}^2 + \textbf{Q}_{i}^{2}\right] - \frac{\alpha_{\textrm{sp}}}{2}\sum_{i\neq j}\textbf{Q}_{i}\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{Q}_{j}.
%\label{full_hammy}
%\end{equation}

%Here, $\omega_{\textrm{sp}}$ is the resonant frequency of the individual electric plasmons, the $\boldsymbol{\Pi}_{i}$ are the generalized momenta conjugate to the generalized coordinates $\textbf{Q}_{i}$, $\alpha_{\textrm{sp}}$ is the polarizability of each individual MNP, and $\boldsymbol{\Lambda}_{ij}$ is the near-field dipole-dipole relay tensor. In this work, retardation effects are incorporated into the dipole-dipole relay tensor through the intermediate- and far-field terms in the dipole electric field as follows:

%\begin{equation}
%\boldsymbol{\Lambda}_{ij} = \left[\left(\frac{1}{r_{ij}^3} - \frac{\textrm{i}\omega}{cr_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{\omega^2}{c^2r_{ij}}\left(\textbf{1} - \hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right]e^{\textrm{i}\omega/c r},
%\label{dipoledipole}
%\end{equation}

%where $r_{ij}$ is the distance between the $i^{\textrm{th}}$ and $j^{\textrm{th}}$ dipoles along the unit vector $\hat{\textbf{n}}_{ij}$, \textbf{1} is the unit dyad, $c$ is the speed of light, and $\omega$ is the collective frequency at which all of the dipoles oscillate. Using Equations~\ref{full_hammy} and ~\ref{dipoledipole}, Hamilton's equations of motion,

%\begin{equation}
%\ddot{\textbf{Q}}_{i} = -\textbf{Q}_{i} + \sum_{j\neq i}\boldsymbol{Lambda}_{ij}\cdot\textbf{Q}_{j}
%\label{eom}
%\end{equation}

% can be found and the system of equations can be solved for the eigenvalues and eigenvectors of the nanoparticle array. The eigenvectors are the generalized coordinates corresponding to each dipole moment in the aggregate. It is important to note that because the eigenvalues, the collective frequencies, appear in the coupling terms, this will result in a system of transcendental equations which must be solved iteratively.

%In this paper, three model systems are considered. Following previous work, the model systems are constructed from fused, six-member rings of silver nanospheres, resembling conjugated hydrocarbon rings. The aggregates considered are a two-ring system, a linear three-ring system, and a triangular three-ring system. Solving for the magnetic eigenmodes of each system results in a set of eigenvectors for each mode which correspond to electric dipole moments. Figure~\ref{field_plots} shows the oligomers, the dipole moments on each sphere, and the magnetic field distribution computed from\cite{jackson_classical_1999}

%\begin{equation}
%\textbf{B}_{\textrm{tot}}(\textbf{r},\omega) = \frac{\omega^2}{c^2}\sum_{j}(\hat{\textbf{n}}_{j}\times\textbf{p}_{j})\frac{e^{\textrm{i}\omega/c r_j}}{r_j}\left(1 - \frac{c}{\textrm{i}\omega r_{j}}\right).
%\label{magnetic_field}
%\end{equation}

### 2018-04-05 paper_winter_2017/draft_winter_2017.tex

@@
 Most crucial to this disconnect is the question of when and how retardation effects matter.
-For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}.
-Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}.
+For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014} Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}.
 However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers.
@@
 Simulating these CL experiments with $r_0 = 15$ nm shows the aN modes lower in energy than the NS modes, as predicted.
-WIth $r_0 = 30$ nm, the modes switch, again as predicted.}
+With $r_0 = 30$ nm, the modes switch, again as predicted.}
 \label{CL_2mer_3mer}

### 2018-04-05 paper_winter_2017/paper.tex
updated

--- 2018-03-07 paper_winter_2017/draft_winter_2017.tex
@@
 \documentclass[journal=apchd5,manuscript=article]{achemso}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{xcolor}
-\usepackage{wrapfig}
+\usepackage{amsmath,amssymb}
+%\usepackage{xcolor}
+%\usepackage{wrapfig}
 %\usepackage{multline}
@@
 \email{masiello@chem.washington.edu}
-\date{February 12, 2017}
+%\date{February 12, 2017}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\abbreviations{MNP, LSPR, EELS}
-\keywords{magnetic plasmons, plasmon metamolecules}
+%\abbreviations{MNP, LSPR, EELS}
+\keywords{magnetic plasmons, plasmon metamolecules, plasmon oligomers}
 
@@
 %% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years\cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016}.
-Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Plasmon oligomers, or plasmon metamolecules, are clusters of noble metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields even though their individual nanoparticle building blocks do not.
+Since their discovery in 2004, such magnetic plasmon resonances have impacted a variety of applied and fundamental research from negative index metamaterials to quantum tunneling and Fano interferences \cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016} [CITE US, NORDLANDER, SHALAEV].
+Magnetic plasmons have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances \cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
 The magnetic properties of single oligomers, i.e.
-those systems composed of only one ring of MNPs, are now well understood based upon models in the quasistatic limit\cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}.
-Conversely, the infinite-oligomer regime has also been understood within the language of tight-binding models of solid-state physics\cite{Schatz2003,Weick2013}.
-Recently, a disconnect between these size regimes and methods has arisen, leading to open questions in how magnetic plasmon resonances behave in few-oligomer assemblies, called the intermediate size regime\cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
+those clusters composed of only one ring of MNPs, are now well understood based upon quasistatic models \cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}.
+So too are extendend two-dimensional networks of oligomers using quasistatic tight-binding models \cite{Schatz2003,Weick2013}.
+However, recently, a disconnect between these extremes and methods has been highlighted, revealing a lack of understanding of how oligomer assemblies behave in the so-called intermediate size regime \cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
 
 Most crucial to this disconnect is the question of when and how retardation effects matter.
-For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}.
-Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}.
-However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers.
-Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size.
-This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials.
+For example, in the case of the two oligomer cluster the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the two magnetic plasmon resonances \cite{Cherqui2014}.
+Retardation effects have been incorporated into models of single MNPs \cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays \cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}.
+However, with the exception of numerical studies, no analytical models to date include retardation effects in the description of magnetic plasmon resonances.
+It is the purpose of this paper to show that the incorporation of retardation effects corrects the aforementioned disagreement between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum by changing the oligomer's size.
+The latter observation is important because it enables manipulation of the system's effective permittivity and permeability, thereby facilitating the design of future tunable optical metamaterials.
 
-In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $N$-mers with size by including the full field within a coupled dipole approach describing their interaction.
-Interestingly, as a function of size, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}.
-We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}.
-The spectral ordering depends not only on aggregate size but also upon oligomer morphology which we examine below.
-The ability to choose the resonance frequency of specific magnetic plasmon resonances will lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications stem directly from tunable negative-index metamaterials\cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.
+In the following, we build a simple analytically-solvable model to demonstrate the size-dependent evolution of the magnetic plasmons in intermediate-size $N$-mers by including the effects of retardation in the mutual interaction of their underlying electric dipole plasmon resonances.
+Interestingly, as a function of size, the magnetic plasmons switch their ordering in analogy to the way that electric plasmons in hybridized nanoparticles switch order \cite{vonPlessen2007}.
+We further analyze the distinct radiative properties of these magnetic plasmons by computing the angle-resolved cathodoluminescence (CL) spectrum \cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}.
+Building from the intuition gained, we finally analyze the size-dependent evolution of the intermediate-size plasmonic nanoclusters measured in Ref.
+\cite{Engheta2017}.
+We find that the spectral ordering depends not only on aggregate size but also upon morphology, offering the ability to tune the magnetic plasmon spectrum.
+Such understanding may someday lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications benefit directly from the tunability of system's electric and magnetic response \cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.
 
 \section{Model Theory}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{field_plots} displays two model systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to naphthalene and phenalene.
-The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood\cite{ARPC}.
-In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic response of the oligomer are
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Fig.
+\ref{field_plots} displays two model oligomer systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to the molecules naphthalene and phenalene.
+Mapping the electric plasmons of each nanoparticle onto harmonic oscillators is now well-understood \cite{ARPC} [CITE US], and forms the basis for modeling the collective magnetic plasmon responses.
+In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic behavior of the oligomer are
 \begin{equation}
-\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{i,j\neq i}\textbf{E}_j(\textbf{r}_i),
+\ddot{\textbf{q}}_i +\omega_{\textrm{sp}}^2\textbf{q}_i = \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
 \label{equation_of_motion}
 \end{equation}
-
-\noindent where $\omega_{\textrm{sp}}$ is the natural frequency of the Mie resonance, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$, with $\varepsilon_{\infty}$ and $\varepsilon_b$ the high-frequency and background dielectric functions.
-The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole.
+where $\omega_{\textrm{sp}}=\sqrt{\omega_{p}^2/(\varepsilon_\infty+2\varepsilon_b)-(\gamma/2)^2}$ is the complex Mie resonance frequency and $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$.
+Here, $\omega_p$ is the metal's bulk plasma frequency, $\varepsilon_{\infty}$ and $\varepsilon_b$ are the high-frequency and background dielectric functions, and $\gamma$ is well approximated by the Drude electron-ion scattering rate for the nanoparticle sizes under consideration.
+While the Drude frictional force is not explicitly included in the equations of motion, Drude friction does modify the frequency of the Mie resonance.
+The dipole moment $\textbf{d}_i = e\textbf{q}_i$ of each plasmon oscillator is restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j$th dipole evaluated at the position of the $i$th dipole.
 The electric field is defined by
-
 \begin{equation}
 \textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
-= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
+= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{ikr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
 \label{electric_field_lambda}
 \end{equation}
+where $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}=|{\bf r}_i-{\bf r}_j|$ and $k=\sqrt{\varepsilon_b}\omega/c.$ The field is decomposed into three parts---the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$)---which together include all dipolar retardation effects \cite{Purcell1973}.
+Interestingly, the latter term carries the opposite sign of the former two.
+As will be shown in the following, it is because of both the relative magnitude and sign of these terms as well as the oscillatory behavior of $e^{ikr_{ij}}$ that the interactions can change character and switch from energy-lowering to energy-raising.
 
-\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{th}}$ dipole.
-Interestingly, the far-field term carries the opposite sign of the near-field term.
-The field is decomposed into three parts: the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$).
-All dipolar retardation effects are included in this field\cite{Purcell1973}.
-Due to the relative magnitudes of these terms and the sign of $e^{\textrm{i}kr_{ij}}$ the interaction energies can change sign and go from energy-lowering to energy-raising.
-
-As described in the methods section, there are as many normal modes of each N-mer as there are electric dipole plasmons.
-Of these normal modes, some are electric in character and some are magnetic in character with $N$ magnetic plasmon resonances for each $N$-mer studied here.
-Figure~\ref{field_plots} shows these magnetic plasmon normal modes overlaid with their associated signed magnetic field magnitude.
+As described in the Methods Section, there are as many hybridized modes of each $N$-mer as there are electric dipole plasmons.
+Of these hybrid modes, some are electric and some are magnetic in character, with $N$ magnetic plasmon resonances for each $N$-mer studied here.
+Fig.
+\ref{field_plots} shows the magnetic plasmon modes of the 2-mer and 3-mer overlaid with their associated signed magnetic field magnitude.
 Each mode is named for its particular magnetic field distribution after the poles of a magnet, either all-North (aN) or North-South (NS).
-The top right-hand corner of each panel indicates whether the  mode depicted has a net electric dipole or a net magnetic dipole moment.
+The top right-hand corner of each panel indicates the net electric or magnetic dipole moment magnitude.
+The black arrows denote the electric dipole plasmons on each MNP within each magnetic mode, while the magenta arrow indicates the mode's net electric dipole moment.
 In planar geometries, the magnetic dipole moments are always perpendicular to the in-plane electric dipole moments.
@@
 
-\section{Spectral Ordering of Magnetic Modes in Model Systems}
-
+\section{Spectral Ordering of Magnetic Modes in Intermediate-Size $N$-mers}
 To determine the impact of incorporating retardation effects, it is first useful to consider the quasistatic limit.
-Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = r_{ij}/a$ and not upon the overall oligomer size.
-That is, if this ratio $s$ of inter-particle distance $r_{ij}$ to particle size $a$ remains constant, as the particles grow the collective frequencies do not change.
-This is evident by considering the k goes to zero limit of the electric field in Equation~\ref{electric_field_lambda},
-
+Here individual nanoparticle plasmon resonance frequencies ($\omega_{sp}$) are size independent and the coupling strength depends only upon the scale $s_{ij} = r_{ij}/a$ and not upon the overall oligomer size.
+That is, if this ratio $s_{ij}$ of interparticle distance $r_{ij}$ to nanoparticle radius $a$ remains constant, the collective resonance frequencies do not change as the nanoparticles grow.
+This is evident by considering the $ka\ll 1$ limit of the right-hand side of Eq.
+(\ref{equation_of_motion}) [CHECK UNITS],
 \begin{equation}
 \begin{aligned}
-\lim_{k \to 0}\textbf{E}_j(\textbf{r}_i) &= \frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij}\\ 
-&= \frac{\omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}^2}{\varepsilon_b}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \cdot \textbf{d}_j \\
-&= \frac{\omega_{\textrm{sp}}^2}{\varepsilon_b} \left(\frac{3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{s^3} \cdot \textbf{d}_j
+\lim_{ka \to 0}\frac{e}{m_{\textrm{sp}}}\textbf{E}_j(\textbf{r}_i) &= \frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij}\cdot{\bf q}_j\\ 
+&= \frac{\omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}^2}{\varepsilon_b}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \cdot \textbf{q}_j \\
+&= \frac{\omega_{\textrm{sp}}^2}{\varepsilon_b} \left(\frac{3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{s_{ij}^3} \cdot \textbf{q}_j.
 \end{aligned}
@@
 \end{equation}
+Retardation effects, however, remove this invariance and introduce radius-dependence into both the Mie frequency and the electric field.
+Consequently, in the following, we choose the individual MNP radius $a$ as the independent variable, fixing the nearest neighbor distance at 3$a$ to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $N$-mers.
 
-\noindent where $m_{\textrm{sp}}$ and $\alpha_{\textrm{sp}}$ are rewritten in terms of fundamental parameters for silver: $\varepsilon_{\infty} = 3.77$, $\hbar\gamma = 0.05$ eV, and $\hbar\omega_{p} = 9.1$ eV.
-Retardation effects, however, remove this invariance and introduce size-dependence into both the individual plasmon natural frequency as well as into the electric field.
-Consequently, in the following we choose the individual MNP radius $a$ as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $N$-mers.
+%where $m_{\textrm{sp}}$ and $\alpha_{\textrm{sp}}$ are rewritten in terms of fundamental parameters for silver, i.e., $\varepsilon_{\infty} = 3.77$, $\hbar\gamma = 0.05$ eV, and $\hbar\omega_{p} = 9.1$ eV.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{scaling} shows the predicted resonance energies from both the model and full-wave optical simulations of the 2-mer and 3-mer with increasing $a$.\cite{Hohenester2012} At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits within a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}.
-As the system size increases, the resonance energies decrease and to cross at $a = 7$ nm, and once more at $a = 20$ nm.
-This is due to the far-field contribution in Equation~\ref{electric_field_lambda} becoming large relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares).
-The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is accurate again.
-Rather, both eigenmode crossings are due entirely to retardation effects.
-The interaction energy between all the dipoles in each magnetic mode, [reformat equation]
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Fig.
+\ref{scaling} shows the predicted magnetic plasmon resonance energies from both Eq.
+(\ref{equation_of_motion}) and full-wave numerical electrodynamics simulation of the 2-mer and 3-mer with increasing $a$ \cite{Hohenester2012}.
+At small $a$, the magnetic modes preserve the quasistatic ordering predicted in previous work \cite{Cherqui2014}, which is to be expected when the oligomer system fits within an optical wavelength and the near-field dominates the electric field.
+As the system size increases, the resonance energies decrease and cross at $a \approx 7$ nm, and once more at $a \approx 20$ nm.
+The second crossing recovers the same spectral ordering as at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is correct again.
+Rather, both crossings are due entirely to retardation effects as can be seen from the total interaction energy
 \begin{equation}
-U_{\textrm{int}} = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
+U = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
 \label{interactionenergy}
 \end{equation}
+between each pair of electric dipole plasmons within each magnetic plasmon mode.
+It is the inclusion of the far-field that causes the mode switching, as it carries the opposite sign of the near- and intermediate-field terms.
+Fig.
+\ref{scaling} shows the competition between these field components as well as their relative contributions to the total interaction energy.
+Inspection of Fig.
+\ref{scaling}c reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field.
+Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction.
+This can be explained through the impact of dielectric medium upon the interaction energy $U,$ which increases with increasing $\varepsilon_b$ due mostly to the far-field term's dependence upon $k^2$ \cite{Elsayed2008}.
+While previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonances and radiation damping as a function of separation in noble metal dimers \cite{vonPlessen2007}, our work shows that magnetic plasmon resonances also oscillate with interparticle separation and can be understood by analysis of the different contributions to the dipole-dipole interaction.
 
-\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes.
-The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms.
-These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode.
-Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field.
-Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction.
-This can also be explained through the impact of a dielectric medium on coupling strength.
-While a medium should contribute an overall increase to the coupling strength, the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008}
-
-Previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonance frequencies and radiation damping as a function of separation in noble metal dimers\cite{vonPlessen2007}.
-Analogously, our work shows that magnetic plasmon resonance energies also oscillate with interparticle separation and can be understood via analysis of the contributions to the dipole-dipole interaction.
-
-\section{Radiative Properties of Magnetic Plasmon Resonances}
-Only those magnetic resonances supporting net electric or magnetic dipole moments will radiate to the far field.
-The magnetic dipole moment of the aN magnetic mode is perpendicular to the electric dipole moment(s) of the NS mode in both the model 2-mer and 3-mer.
+\section{Radiative Properties of Intermediate-Size $N$-mers}
+Only those magnetic resonances that have net electric or magnetic dipole moments will couple strongly to the radiation field.
+The magnetic dipole moment of the aN magnetic mode is perpendicular to the electric dipole moment(s) of the NS mode in both the 2-mer and 3-mer.
 This means that these modes radiate with different directionality.
-It has been predicted and shown experimentally that 1-mers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited,\cite{Dionne2011,Cherqui2016} as is evident in differential scattering spectra and profiles.
-Both observations stem from the differential power,\cite{jackson_classical_1999,schwinger1998classical}
-
+It has been predicted and shown experimentally that 1-mers scatter light anisotropically when both their magnetic and electric dipole moments are mutually excited, \cite{Dionne2011,Cherqui2016} as is evident in differential scattering spectra and radiation profiles.
+Both observations stem from the time-averaged differential power, \cite{jackson_classical_1999,schwinger1998classical}
 \begin{equation}
-\frac{dP}{d\Omega} = \frac{c}{8\pi}\textrm{Re}\left[r^2\hat{\textbf{n}}\cdot\sum_i\textbf{E}_i \times \sum_{j}\textbf{B}_{j}^*\right]
+\frac{dP({\bf x})}{d\Omega} = \frac{c}{8\pi}\textrm{Re}\left[r^2\hat{\textbf{n}}\cdot\sum_I\textbf{E}_I({\bf x}) \times \sum_{J}\textbf{B}_{J}^*({\bf x})\right]
 \label{dp_field_1}
 \end{equation}
+observed at the point ${\bf x}=r\hat{\bf n},$ where $I,J$ label the 1-mer unit cells within each $N$-mer.
+$\textbf{E}_I$ and $\textbf{B}_I$ are produced from the sum of effective electric ($\textbf{d}_I$) and magnetic ($\boldsymbol{\mu}_I$) dipole moments, assumed to be co-located at the center of the $I$th ring and oscillating in time as $e^{-i\omega t}$.
+In this approximation, the differential power becomes \cite{Alu2006}
+\begin{equation}
+\begin{split}
+\frac{dP({\bf x})}{d\Omega} &= \frac{ck^4}{8\pi} \textrm{Re} \left\{\hat{\textbf{n}} \cdot \left[\left(\sum_{i} (\hat{\textbf{n}} \times \textbf{d}_I) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_I\right) \times \left(\sum_{j} \hat{\textbf{n}} \times \textbf{d}_J^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_J^*) \times \hat{\textbf{n}}\right)\right]\right\}\\
+&= \frac{ck^4}{8\pi} \textrm{Re} \Bigg[ \sum_{ij} \textbf{d}_I \cdot \textbf{d}_J^* - (\hat{\textbf{n}} \cdot \textbf{d}_I)(\hat{\textbf{n}} \cdot \textbf{d}_J^*) + \boldsymbol{\mu}_I \cdot \boldsymbol{\mu}_J^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_I)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_J^*) \\
+&\hspace{2cm}+ \hat{\textbf{n}} \cdot (\textbf{d}_I \times \boldsymbol{\mu}_J^* + \textbf{d}_J^* \times \boldsymbol{\mu}_I) \Bigg].
+\label{dp_dipoles_1}
+\end{split}
+\end{equation}
+Notice that the first two terms are due to the radiation produced by electric and magnetic dipoles, while the third term is due to their interference.
+To build intuition, we define the magnetic dipole moment $\boldsymbol{\mu}$ to point in the $z$-direction and the electric dipole $\textbf{d}$ to point in the $y$-direction for all $I,J.$ The effective electric and magnetic dipoles can be written in terms of their constituent dipoles as $\textbf{d}_I = \sum_i d_{I,i} \hat{\textbf{y}}$ and $\boldsymbol{\mu}_I = ({k}/{2})\sum_i\textbf{r}_i \times d_{I,i} \hat{\boldsymbol{\phi}}_i = ({knRd_{I,i}}/{2})\hat{\textbf{z}}$, where $R$ is the radius of the 1-mer ring consisting of $n$ nanoparticles, and $d_{I,i}$ is the electric dipole moment of the $i$th nanoparticle within the $I$th unit cell.
+For each $I$, all $d_{I,i}$ are equal.
 
-\noindent $\textbf{E}_i$ and $\textbf{B}_i$ are produced from the sum of effective electric ($\textbf{d}_i$) and magnetic ($\boldsymbol{\mu}_i$) dipole moments of each ring of the $N$-mer, assumed to be co-located at the center of the $i$-th ring and oscilalting in time as $e^{-\textrm{i}\omega t}$.
-In this approxiamtion, the differential power becomes\cite{Alu2006}
-
-\begin{equation}
-\begin{aligned}
-\frac{dP}{d\Omega} &= \frac{ck^4}{8\pi} \textrm{Re} \left\{\hat{\textbf{n}} \cdot \left[\left(\sum_{i} (\hat{\textbf{n}} \times \textbf{d}_i) \times \hat{\textbf{n}} - \hat{\textbf{n}} \times \boldsymbol{\mu}_i\right) \times \left(\sum_{j} \hat{\textbf{n}} \times \textbf{d}_j^* + (\hat{\textbf{n}} \times \boldsymbol{\mu}_j^*) \times \hat{\textbf{n}}\right)\right]\right\}\\
-&= \frac{ck^4}{8\pi} \textrm{Re} \Bigg[ \sum_{ij} \textbf{d}_i \cdot \textbf{d}_j^* - (\hat{\textbf{n}} \cdot \textbf{d}_i)(\hat{\textbf{n}} \cdot \textbf{d}_j^*) + \boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j^* - (\hat{\textbf{n}} \cdot \boldsymbol{\mu}_i)(\hat{\textbf{n}} \cdot \boldsymbol{\mu}_j^*) \\ &+ \hat{\textbf{n}} \cdot (\textbf{d}_i \times \boldsymbol{\mu}_j^* + \textbf{d}_j^* \times \boldsymbol{\mu}_i) \Bigg].
-\label{dp_dipoles_1}
-\end{aligned}
-\end{equation}
-
-\noindent Notice that the first two terms are due to electric and magnetic dipole radiation, while the third term is due to their interference.
-To build intuition, we demand the magnetic dipole $\boldsymbol{\mu}$ is oriented in the z-direction, and the electric dipole $\textbf{d}$ is oriented in the y-direction.
-The coarse-grained electric dipole and magnetic dipole can be written in terms of their constituent dipoles $\textbf{d} = \sum_n d_{e,n} \hat{\textbf{y}}$ and $\boldsymbol{\mu} = \frac{k}{2}\sum_n(\textbf{r}_n \times d_{m,n} \hat{\boldsymbol{\phi}}_n) = \frac{kNRd_m}{2}\hat{\textbf{z}}$ where the sums are taken over the $n$-th and $m$-th dipoles, respectively.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Fig.
+\ref{scattering} displays the differential scattering power profiles associated with the aN (a) and NS (b) magnetic plasmon resonances as well as their interference (c) for any $N$-mer with electric and magnetic dipoles oriented as descibed above.
+Since the aN mode has only a $z$-oriented magnetic dipole, its radiation pattern is orthogonal to that of the $y$-directed electric dipole of the NS mode.
+This means that asymmetry in the radiation pattern is due to the excitation of both modes.
+Thus, examination of the radiation directionality allows one to determine the net electric or magnetic dipole character.
+Such forward/backward scattering asymmetries have been predicted and demonstrated in metal-semiconductor core-shell nanoparticle assemblies, that similarly exploit the interference between electric and magnetic plasmons to direct light \cite{Kivshar2012}.
 
-Figure~\ref{scattering} displays the differential power profiles associated with the aN and NS magnetic plasmon resonances, as well as the interference pattern, of any $N$-mer.
-Since the aN mode has only a z-oriented magnetic dipole, its radiation pattern is orthogonally oriented with respect to that of the y-directed electric dipole of the NS mode.
-Thus, examination of the directionality of radiation allows one to determine the net electric or magnetic dipole character.
-Strong forward/backward scattering asymmetries are also predicted and demonstrated in metal-semiconductor core-shell nanoparticle assemblies, which similarly exploit the interference between electric and magnetic plasmons\cite{Kivshar2012}.
+Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize plasmon resonances in noble metal nanoparticles\cite{Coenen2011,CoPol2011,Polman2014}.
+Using an electron microscope fitted with a parabolic mirror, emitted CL radiation can be collected across a large portion of the backward scattering hemisphere\cite{Coenen2011,CoPol2011,Polman2014}.
+Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of light emission, the size-dependent spectral order of the $N$-mers' magnetic plasmon modes can be observed in angle-resolved CL spectra.
 
-\section{Angle-Resolved Cathodoluminescence for Observing Spectral Switching}
-Recent studies have demonstrated the utility of angle-resolved CL spectroscopy to characterize plasmon resonances in noble metal nanoparticles\cite{Coenen2011,CoPol2011,Abajo2013,Polman2014,ARPC}.
-Using an electron microscope fitted with a parabolic mirror, emitted CL radiation can be collected across a large portion of the backward scattering hemisphere\cite{Coenen2011,CoPol2011,Polman2014}.
-Here we show that with the selection rules imposed by the location of the electron beam and the specific directionality of the emission from each magnetic mode, the magnetic modes of the $N$-mers and their crossings can be observed in angle-resolved CL spectra.
-The previous section built up intuition regarding the directionality of light scattered by the magnetic modes of the 2-mer and 3-mer.
-This intuition informs the particular angles at which to collect CL spectra associated with each magnetic mode.
-More specifically, based upon the selection rules imposed by the electron beam and the directionality of CL radiation, it is possible to distinguish the magnetic modes and their spectral ordering as a function of size.
+%More specifically, based upon the selection rules imposed by the electron beam and the directionality of CL radiation, it is possible to distinguish the magnetic modes and their spectral ordering as a function of size.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-
-In Figure~\ref{CL_2mer_3mer} we show simulated point angle-resolved CL spectra of the 2-mer and 3-mer, with the electron beam position chosen so as to excite the aN (blue) and NS (orange) modes.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The previous section built up intuition on the directionality of light scattered by the magnetic modes of the 2-mer and 3-mer.
+This intuition informs the particular angles at which to collect CL spectra.
+Fig.
+\ref{CL_2mer_3mer} shows simulated point angle-resolved CL spectra of the 2-mer and 3-mer, with the electron beam position chosen so as to excite the aN (blue) and NS (orange) modes.
 Note however, due to the symmetry of the oligomers, the blue electron beam position excites not only the aN mode, but also weakly the NS mode.
 Since the radiation profile of the aN mode is orthogonal to that of the NS mode, it is possible to distinguish them by analyzing the angular distribution of emitted CL radiation.
-The ARCL spectra at two such angles are reported in Figure~\ref{CL_2mer_3mer}.
-These simulated spectra confirm the predictions of our model shown in Figure~\ref{scaling}; specifically, between $a = 15 - 30$ nm, the aN and NS modes switch spectral order.
+The angle-resolved CL spectra at two such angles are reported in Fig.
+\ref{CL_2mer_3mer}.
+These simulated spectra confirm the predictions of the model displayed in Fig.
+\ref{scaling}; specifically, between $a = 15 - 30$ nm, the aN and NS modes switch spectral order.
+The simulation also shows mode switching at $a\approx7$ nm, however, the splitting energies are too small to be experimentally detectable with conventional CL.
+Nevertheless, experimental confirmation of the secondary mode splitting is possible, and would verify both our analytical and numerical predictions.
 
-\section{Magnetic Plasmon Resonance Frequencies and CL Spectra of Hexagonally-Packed Nanoclusters}
+\section{Magnetic Plasmon Resonances in Hexagonally-Packed Nanoclusters}
+Ref.
+\cite{Engheta2017} synthesizes and optically characterizes hexagonally-packed nanoclusters composed of noble metal nanoparticles in the intermediate size regime, between few particle nanoclusters and infinite arrays.
+Here, we apply our analytical modeling and numerical simulation to investigate the behavior of the magnetic plasmon resonances in these systems as a function of size, with an eye toward engineering magnetic resonances at particular resonance energies.
+Such tunability may be important in the design of future negative index materials with spectral tunability.
+Specifically, we consider hexagonally packed clusters composed of 13, 19, and 31 MNPs displayed in Fig.
+\ref{kagan_fields} as well as the insets of Fig.
+\ref{kagan_eigen}.
 
-Ref.
-\cite{Engheta2017} synthesizes and optically characterizes hexagonally-packed nanoclusters composed of noble metal nanoparticles in the intermediate size regime, between few particle oligomers and infinite arrays.
-Here, we apply our analytical modeling and numerical simulation to investigate the behavior of the magnetic plasmon resonances as a function of size, with an eye toward engineering magnetic resonances at particular resonance energies.
-Such tunability may be important in the design of future negative index materials with spectral tunability.
-Specifically, we consider hexagonally packed clusters composed of 13, 19, and 31 MNPs displayed in Figure~\ref{kagan_fields} as well as the insets of Figure~\ref{kagan_eigen}.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Fig.
+\ref{kagan_fields} displays the signed magnetic field magnitude of the aN (panel a) and NS (panel c) magnetic plasmon resonances of the 13-, 19-, and 31-particle nanoclusters.
+The black arrows denote the electric dipole moments of the individual MNPs within each magnetic plasmon mode, the magenta arrows denote the net electric dipole moment of the nanocluster, and the background color denotes the strength of the associated magnetic field.
+The net electric or magnetic dipole magnitude is denoted below each panel.
+Panels b and d display the energy-filtered electron energy-loss (EEL) profiles of these modes.
+It is important to note that each aN mode is weakly excitable from the middle MNP (as indicated by the low EEL probability surrounding it), while the NS mode is strongly excitable from the same location (as indicated by the high EEL probability surrounding it).
+In all cases, the NS mode is doubly degenerate as would be true of any structure with sixfold symmetry.
+In analogy to the oligomers, these magnetic modes are chosen because they are the simplest (i.e., lowest order) and their radiation patterns are spatially orthogonal.
 
-Figure~\ref{kagan_fields} displays the signed magnetic field magnitude of two magnetic plasmon resonances of the 13-, 19-, and 31-particle hexagonally packed nanoclusters.
-The NS mode of each nanocluster is doubly degenerate as would be true of any structure with sixfold symmetry.
-In analogy to the previous oligomers, these magnetic modes are chosen because they are spectrally isolated from the other magnetic modes and because their radiation patterns are spatially orthogonal.
-The arrows denote the electric dipole moments on individual nanoparticles within the magnetic normal mode and the color denotes the strength of the magnetic field.
-The net electric or magnetic dipole character of each magnetic resonance is denoted in the upper right hand corner of each panel.
-
-Figure~\ref{kagan_eigen} displays the evolution of the aN and NS magnetic resonances with size, $a$.
-In contrast to the oligomers described previously, here the behavior of the nanocluster resonances with size is different due to the hexagonal packing as opposed to the open-ring structure of the oligomers.
-Nevertheless, the analytic model described previously is capable of predicting the magnetic spectrum.
-Most surprising is the behavior of the magnetic resonances of the 19- and 31-particle nanoclusters to oscillate with size as opposed to monotonically decrease in energy.
-Panels b, d, and f of Figure~\ref{kagan_eigen} display the relative strength of the near, intermediate, and far-field contributions to the electric dipole-electric dipole interaction energy and show that this oscillatory behavior is due specifically to retardation effects.
-This is contrary to intuition where increasing size causes monotonic redshifting.
-However this oscillatory behavior is not so unexpected; separating a MNP dimer causes its hybridized electric plasmon resonance frequencies to oscillate from bonding to anti-bonding and back\cite{vonPlessen2007}.
-In these nanoclusters, ARCL and patterns spectra provide a means to demonstrate this oscillation.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters.
-Unlike the previous 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes.
+Unlike the 2mer and 3mer, at very small values of $r_0$, the aN modes are lower in energy than the NS modes.
 However, for each system a crossing point does occur between $r_0 = 30$ nm and $r_0 = 40$ nm.
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Fig.
+\ref{kagan_eigen} displays the evolution of the aN and NS magnetic resonances with size $a$ as dictated by the model.
+Here the size-dependent behavior of the nanocluster resonances is different due to the hexagonal packing as opposed to the open-ring structure of the $N$-mer.
+Nevertheless, the analytic model is capable of predicting the magnetic spectrum.
+Most surprising is the oscillatory behavior of the nanoclusters' magnetic resonances with size as opposed to the expected monotonic redshifting of those of the $N$-mer (see Fig.
+\ref{scaling}).
+Panels b and c display the total interaction energy $U$, and its near-, intermediate-, and far-field contributions, showing that this oscillatory behavior is due to retardation effects through the $e^{ikr_{ij}}$ factor in Eq.
+(\ref{electric_field_lambda}).
 
+%This is contrary to intuition where increasing size causes monotonic redshifting.
+However this oscillatory behavior is not so unexpected; separating a MNP dimer causes its hybridized electric plasmon resonance frequencies to oscillate from bonding to anti-bonding and back\cite{vonPlessen2007}.
+In these nanoclusters, ARCL and patterns spectra provide a means to demonstrate this oscillation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{kagan_CL} shows simulated ARCL spectra for the 13-, 19-, and 31-particle systems acquired at the two indicated beam positions and collection angles.
-Inspection of the EELS maps of the NS and aN magnetic resonances in rows b and d of Figure~\ref{kagan_fields} indicates the optimal electron beam positions, that is, those positions with highest EEL probability, at which to excite each magnetic mode.
-As described previously, it is the electron beam selection rules and radiative profile of each mode help to identify the two magnetic resonances of interest.
-Because the aN mode radiates strongly in the xy-plane, and weakly in the z-direction, it is most easily detected at angles of $0 < \theta < \pi/2$.
-The NS mode is detected either for angles very close to the backward scattering direction ($\theta \approx 0$), or parallel to the impact plane (here, the y-direction for this particular beam position).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure~\ref{kagan_CL} shows simulated angle-resolved CL spectra for the 13-, 19-, and 31-particle nanoclusters acquired at the two indicated beam positions and collection angles.
+Inspection of the EEL maps of the NS and aN magnetic resonances in panels b and d of Fig.
+\ref{kagan_fields} indicates the optimal electron beam positions to excite each magnetic plamson mode, i.e., those positions with highest EEL probability.
+In particular, the NS mode (Fig.
+\ref{kagan_fields}c) is most easily excited near the central MNP, while the aN mode (Fig.
+\ref{kagan_fields}a) is more easily excited from the outer MNPs surrounding the central MNP.
+In addition, the radiative profile of each mode helps to identify the two magnetic resonances of interest.
+Because the aN mode radiates strongly in the $xy$-plane, and weakly in the $z$-direction, it is most easily detected at angles between $0 < \theta < \pi/2$.
+Alternatively, the NS mode is detected either for angles very close to the backward scattering direction ($\theta \approx 0$), or parallel to the impact plane (here, the $y$-direction for this particular beam position).
 The aN beam position also weakly excites the degenerate NS modes, meaning the corresponding CL spectrum will provide a secondary signature of the spectral location of that mode.
+This fact is evident in multiple simulated CL spectra displayed in Figs.
+\ref{CL_2mer_3mer} and \ref{kagan_CL}.
 
@@
 \section{Methods}
-Here we show how to derive the equations of motion describing magnetic plasmon resonances in nanoparticle clusters.
-References 10 and 43 describe how to map the solutions of Maxwell's Equations for electric plasmon resonances onto mechanical oscillators with effective masses.
+Here we show the equations of motion describing magnetic plasmon resonances in nanoparticle clusters.
+Refs.
+\cite{Cherqui2014} and \cite{ARPC} describe how to map the solutions of Maxwell's Equations for electric plasmon resonances onto mechanical oscillators with effective masses.
 The resulting Hamiltonian for a system of $N$ frictionless coupled oscillators is
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent where qi and $\textbf{p}_i$ are the coordinate and momentum of each plasmon oscillator located at $r_i$ with effective mass $m_{\textrm{sp}}$ and resonance frequency $\omega_{\textrm{sp}}$, defined previosuly; $\textbf{E}_j(\textbf{r}_i)$ is the full electric dipole field presented in Equation~\ref{electric_field_lambda}.
+where ${\bf q}_i$ and $\textbf{p}_i$ are the coordinate and momentum of the $i$th plasmon oscillator located at ${\bf r}_i$ with effective mass $m_{\textrm{sp}}$ and resonance frequency $\omega_{\textrm{sp}}$, defined previosuly.
+$\textbf{E}_j(\textbf{r}_i)$ is the full electric dipole field presented in Eq.
+\ref{electric_field_lambda}.
 The resulting equations of motion are,
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent which is exactly Equation~\ref{equation_of_motion}.
-From here, introducing time-dependence as a complex exponential, rewriting the electric field in terms of the plasmon coordinate, and performing a Fourier transform results in equations of motion in the frequency domain
-
+which is Eq. \ref{equation_of_motion}. Assuming sinusoidal oscillation in time and rewriting the electric field in terms of the plasmon coordinate results in the equations of motion
 \begin{equation}
@@
 \end{equation}
-
-It is this system of equations for the plasmon oscillator coordinates that we solve for the normal modes.
-Considering two identical, coupled, collinear oscillators as an example with dipole-dipole coupling strength $g_{12} = $ Equation 13 becomes
-
+It is this system of equations for the plasmon oscillator coordinates that we solve to determine the magnetic plasmon resonances.
+Considering two identical, coupled, collinear oscillators as an example, Eq.
+\ref{fourier_eom} becomes
 \begin{equation}
-(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{12}(\omega)q_2 = 0
-\label{fourier_eom_1}
+\begin{split}
+(\omega_{\textrm{sp}}^2-\omega^2)q_1 -g_{12}(\omega)q_2 &= 0\\
+(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{12}(\omega)q_1 &= 0,
+\label{fourier_eom_12}
+\end{split}
 \end{equation}
-
-and
-
-\begin{equation}
-(\omega_{\textrm{sp}}^2-\omega^2)q_2 -g_{12}(\omega)q_1 = 0,
-\label{fourier_eom_2}
-\end{equation}
-
-or equivalently
-
+or, equivalently,
 \begin{equation}
 \begin{bmatrix}
-(\omega_{\textrm{sp}}^2-\omega^2) & -g_{12}(\omega)\\
--g_{12}(\omega) & (\omega_{\textrm{sp}}^2-\omega^2)
+\omega_{\textrm{sp}}^2-\omega^2 & -g_{12}(\omega)\\
+-g_{12}(\omega) & \omega_{\textrm{sp}}^2-\omega^2
 \end{bmatrix}
@@
 0
-\end{bmatrix}
+\end{bmatrix}.
 \label{eom_matrix}
 \end{equation}
-
-Solution of this system produces the hybridized resonance frequencies and normal modes.
-Finding the determinant of this matrix yields the eigenvalues of the collective modes,
-
+where $g_{12}=[HEY NICK!!!].$ Solution of this system produces the hybridized plasmon resonance frequencies and modes of the dimer. Specifically, they are
 \begin{equation}
-\omega_{\pm} = \sqrt{\omega_{sp}^2 \pm g_{12}(\omega)},
+\omega_{\pm} = \sqrt{\omega_{\textrm{sp}}^2 \pm g_{12}(\omega)}
 \label{eigenvalues}
 \end{equation}
-
-\noindent with corresponding normal mode coordinates
-
+and
 \begin{equation}
-q_{\pm} = \frac{1}{\sqrt{2}}\left(q_1 \pm q_2\right)
+q_{\pm} = \frac{1}{\sqrt{2}}\left(q_1 \pm q_2\right).
 \label{eigenvectors}
 \end{equation}
-
-\noindent Note that the coupling term $g_{12}(\omega)$ is frequency dependent, meaning the eigenvalue problem must be solved iteratively until convergence.
-The magnetic plasmon resonances and normal modes described herein are obtained as a straightforward extension of this example.
+Note that the coupling term $g_{12}(\omega)$ is frequency dependent, meaning that the eigenvalue problem must be solved iteratively until convergence.
+The magnetic plasmon resonances described herein are obtained as a straightforward extension of this dimer example.
 
 \begin{acknowledgement}
-This material is based in part upon work supported by the State of Washington through the University of Washington Clean Energy Institute and via funding from the Washington Research Foundation.
-This work was facilitated though the use of advanced computational, storage, and networking infrastructure provided by the Hyak supercomputer system and funded by the STF at the University of Washington.
+
+This work was supported by the U.S.
+Department of Energy Basic Energy Sciences under award number DE-SC0018040 (D.J.M.) and by the State of Washington through the University of Washington Clean Energy Institute and via funding from the Washington Research Foundation (N.P.M.).
+This work was facilitated through the use of advanced computational, storage, and networking infrastructure provided by the Hyak supercomputer system and funded by the STF at the University of Washington.
 N.P.M.

### 2018-04-05 paper_winter_2017/paper.tex
updated figures, added citations, formatted coupling

@@
 Plasmon oligomers, or plasmon metamolecules, are clusters of noble metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields even though their individual nanoparticle building blocks do not.
-Since their discovery in 2004, such magnetic plasmon resonances have impacted a variety of applied and fundamental research from negative index metamaterials to quantum tunneling and Fano interferences \cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016} [CITE US, NORDLANDER, SHALAEV].
+Since their discovery in 2004, such magnetic plasmon resonances have impacted a variety of applied and fundamental research from negative index metamaterials to quantum tunneling and Fano interferences \cite{Prodan2003,Shalaev2004,Alu2006,Alu2008,Liu2011,Dionne2011,Cherqui2014,Qian2015,Dionne2016,Cherqui2016}.
 Magnetic plasmons have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances \cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
@@
 So too are extendend two-dimensional networks of oligomers using quasistatic tight-binding models \cite{Schatz2003,Weick2013}.
-However, recently, a disconnect between these extremes and methods has been highlighted, revealing a lack of understanding of how oligomer assemblies behave in the so-called intermediate size regime \cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.
+However, recently, a disconnect between these extremes and methods has been highlighted, revealing a lack of understanding of how oligomer assemblies behave in the so-called intermediate size regime \cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017,Fakhraai2018,Scherer2018}.
 
@@
 We find that the spectral ordering depends not only on aggregate size but also upon morphology, offering the ability to tune the magnetic plasmon spectrum.
-Such understanding may someday lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications benefit directly from the tunability of system's electric and magnetic response \cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.
+Such understanding may someday lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications benefit directly from the tunability of system's electric and magnetic response \cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09,Tian2018}.
 
@@
 \begin{figure}
-\includegraphics{2mer_3mer_fields.pdf}
+\includegraphics{fig1.pdf}
 \caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers.
@@
 \ref{field_plots} displays two model oligomer systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to the molecules naphthalene and phenalene.
-Mapping the electric plasmons of each nanoparticle onto harmonic oscillators is now well-understood \cite{ARPC} [CITE US], and forms the basis for modeling the collective magnetic plasmon responses.
+Mapping the electric plasmons of each nanoparticle onto harmonic oscillators is now well-understood \cite{Cherqui2014,ARPC}, and forms the basis for modeling the collective magnetic plasmon responses.
 In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic behavior of the oligomer are
@@
 \begin{figure}
-\includegraphics{2mer-3mer-eig.pdf}
+\includegraphics{fig2.pdf}
 \caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer.
@@
 \begin{figure}
-\includegraphics{differential_power_diagrams.pdf}
+\includegraphics{fig3.pdf}
 \caption{Magnetic field distributions of a magnetic dipole mode (a) and an electric dipole mode (c) in the xy-plane with corresponding radiation patterns (b and d) in the yz-plane.
@@
 \begin{figure}
-\includegraphics{CL_incomplete.pdf}
+\includegraphics{fig4.pdf}
 \caption{Angle-resolved cathodoluminescence spectra of the 2mer (a and b) and 3mer (c and d).
@@
 \begin{figure}
-\includegraphics{kagan_fields.pdf}
+\includegraphics{fig5.pdf}
 \caption{Signed magnetic field magnitudes of the modes of the 13-particle (a, b, and c), 19-particle (d, e, and f), and 31-particle (g, h, and i) clusters.
@@
 \begin{figure}
-\includegraphics{13_19_31_eigen.pdf}
+\includegraphics{fig6.pdf}
 \caption{Eigenenergies and interaction energies for the magnetic modes of the 13- (a and b), 19- (c and d), and 31-particle (e and f) clusters.
@@
 \begin{figure}
-\includegraphics{kagan_CL_spectra.pdf}
+\includegraphics{fig7.pdf}
 \caption{Simulated angle-resolved cathodoluminescence spectra of the 13-, 19-, and 31-particle systems.
@@
 It is this system of equations for the plasmon oscillator coordinates that we solve to determine the magnetic plasmon resonances.
-Considering two identical, coupled, collinear oscillators as an example, Eq.
+Considering two identical, coupled, collinear oscillators as an example and projecting out the directional-dependence, Eq.
 \ref{fourier_eom} becomes
@@
 \end{equation}
-where $g_{12}=[HEY NICK!!!].$ Solution of this system produces the hybridized plasmon resonance frequencies and modes of the dimer. Specifically, they are
+where $g_{12}=-e^2/m_{\textrm{sp}}(2r_{12}^{-3} - 2ikr_{12}^{-2}).$ Solution of this system produces the hybridized plasmon resonance frequencies and modes of the dimer. Specifically, they are
 \begin{equation}
